### 2020-01-13 paper.tex
Copying previous files to new project

\documentclass[a4paper]{article}
\input{header.tex}
\title{Conditions for $d$-local-connectedness of boundaries of hyperbolic groups}
\author{Benjamin Barrett}

\begin{document}
\maketitle

\section{The Rips complex and the Gromov boundary}\label{sec:approximating}

Let $G$ be a hyperbolic group and let $S$ be a symmetric generating set for $G$.
Let $\delta \geq 0$ be such that the Cayley graph of $G$ with respect to $S$ is 
$\delta$-hyperbolic. Let $\dist(\cdot, \cdot)$ be the natural metric on the
Cayley graph.

Fix an ordering on $S$. Let $S^\star$ be the free monoid on 
$S$; order $S^\star$ by the lex-least ordering: this ordering is defined by 
requiring that shorter words precede longer and that words of equal length are 
ordered lexicographically. Let $D = 10^6\delta + 10^6$.

\begin{definition}
  We denote by $K(G)$ the \emph{Rips complex} of $G$; this is the simplicial
  complex with vertex set $G$ such that a finite set of elements of $G$ spans a
  simplex if and only if that set has diameter at most $D$ with respect to the
  word metric $d$.
\end{definition}

We will sometimes want to refer to distances between points in $K(G)$. The
precise means by which we extend the metric on $G$ to $K(G)$ will not matter
very much, so we make the following simple definition.

\begin{definition}
  For $x$ and $y$ in $K(G)$, choose vertices $x^\star$ and $y^\star$ of the
  minimal simplices containing $x$ and $y$ respectively. Then define
  $\newdist(x,y) = \dist(x^\star, y^\star)$.
\end{definition}

\begin{remark}\label{rem:dist_vs_newdist}
  The extended metric $\newdist$ is not a metric, but this will not cause a
  problem.

  Notice that $\newdist$ agrees with $\dist$ on $G$, and for any $x$ and $y$ in
  $K$, if $x^\star$ and $y^\star$ are \emph{any} vertices of simplices
  containing $x$ and $y$ respectively, then
  \begin{align*}
    \abs{\newdist(x,y) - \dist(x^\star, y^\star)} \leq 2D
  \end{align*}
\end{remark}

We denote by $\gromov{{-}}{{-}}{{-}}$ the Gromov product on $G \union
\boundary G$. Using $\newdist$ we extend the Gromov product to $K$:

\begin{definition}
  Given points $x$, $y$ and $z$ in $K$, define the \emph{Gromov product
  $\gromov{x}{y}{z}$ of $x$, $y$ and $z$} as follows.
  \begin{align*}
    \gromov{x}{y}{z} = \frac{1}{2}\left(\newdist(x,y) + \newdist(x,z) -
          \newdist(y,z)\right)
  \end{align*}
\end{definition}

We now equip $K$ with a topology as follows.

\begin{definition}
  We define a topology on $K \union \boundary G$ by describing a neighbourhood
  basis of each point.
  \begin{enumerate}
    \item For $x \in K$, the neighbourhoods of $x$ are the neighbourhoods of
      $x$ in $K$, treating $K$ with the usual topology of a simplicial complex.
    \item For $\xi \in \boundary G$, the set
      \begin{align*}
        \set{x \in K \union \boundary G \suchthat \gromov{e}{x}{\xi} \geq N}_{N\in\naturals}
      \end{align*}
      is a fundamental system of neighbourhoods for the point $x$.
  \end{enumerate}
\end{definition}

\subsection{An inverse system of complexes}

We now define a sequence of subcomplexes in $K(G)$. We will use the topology of
these complexes to approximate the topology of $\boundary G$.

\begin{definition}
  For $n \in \naturals$ let $S_n$ be the sphere in $G$ of radius $n$, i.e.\ the 
  set $\set{g \in G \suchthat \dist(e, g) = n}$ of elements of $G$ whose 
  distance from the identity element is $n$.

  Let $K_n$ be the full subcomplex of the Rips complex $K(G)$ with vertex set
  $S_n$.
\end{definition}

\begin{definition}
  For $n \geq m$ define a map $p^n_m \from S_n \to S_m$ as follows.
  Given an element $g$ of $S_n$ let $w_g \in S^\star$ be the lex-least 
  representative of $g$; note that this word necessarily has length $n$.
  Then define $p^n_m(g)$ to be the element of $G$ given by truncating $w_g$ to a 
  word of length $m$.
\end{definition}

\begin{lemma}\label{lem:psimplicial}
  For $n - m > D + \delta$, the map $p^n_m$ defines a simplicial map from
  $K_n \to K_m$.
\end{lemma}

\begin{proof}
  Let $\set{g_1, \dotsc, g_k}$ span a simplex in $K_n$.
  Then for $g_i$ and $g_j$ in $\set{g_1, \dotsc, g_k}$, $\dist([g_i, g_j], 
  p^n_m(g_i)) \geq n - m - D > \delta$, so $\dist(p^n_m(g_i), [e, g_j]) \leq 
  \delta$.  But $p^n_m(g_j) \in [e, g_j]$ and $\dist(e, p^n_m(g_i)) = 
  \dist(e, p^n_m(g_j))$ so $\dist(p^n_m(g_i), p^n_m(g_j)) \leq 2\delta 
  \leq D$. It follows that the diameter of $\set{p^n_m(g_1), \dotsc, 
  p^n_m(g_k)}$ is at most $D$ and therefore the set spans a simplex in $K_m$.
\end{proof}

Note that $p^m_l \composed p^n_m = p^n_l$ whenever these maps are defined, and 
therefore $(\set{K_n}_n, \{p^n_m\}_{n - m > D + \delta})$ is an inverse system 
of simplicial complexes.

\subsection{Projecting from $\boundary G$}

In order to define projections from $\boundary G$ into our system $(K_n)$, we
first describe a closely related system of simplicial complexes.

\begin{definition}
  For $x \in S_n$ let $U_n(x)$ be the set of limit points in $\boundary G$ of 
  geodesic rays $\gamma$ with $\gamma(0) = e$ and $\dist(\gamma(n), x) \leq 
  2\delta+1$.

  By~\cite{bridsonhaefliger99} $U_n(x)$ is a fundamental system of 
  neighbourhoods in $\boundary G$ of the set of limit points in $\boundary G$ of 
  geodesic rays $\gamma$ with $\gamma(0) = e$ and $\gamma(n) = x$, and therefore 
  $U_n(x)$ contains an open set $V_n(x) \subset \boundary G$ containing this 
  set. Then $\set{V_n(x)}_{x \in S_n}$ is an open cover of $\boundary G$.

  Let $L_n$ be the nerve of this cover, so $\Vertices(L_n)$ is naturally 
  identified with a subset of $S_n$.
\end{definition}

\begin{lemma}\label{lem:L_Ksimplicial}
  The inclusion $\Skel_0 L_n \into \Skel_0 K_n^D$ is a simplicial map.
\end{lemma}

\begin{proof}
  Let $g_1, \dotsc, g_k \subset \Vertices(L_n)$ span a simplex in $L_n$, so 
  there exists a point $\xi \in \bigintersection_{i=1}^k V_n(g_i)$.  Let
  $\gamma_1, \dotsc, \gamma_n$ be geodesic rays with $\gamma_i(0) = e$,
  $\gamma_i(\infty) = \xi$ and $\dist(\gamma_i(n), g_i) \leq 2\delta+1$.
  Then $\Diam\set{\gamma_i(n) \suchthat i=1, \dotsc, n} \leq 2\delta$, and it
  follows that
  \begin{align*}
    \Diam\{g_1, \dotsc, g_k\} \leq 6\delta+ 2 \leq D.\qedhere
  \end{align*}
\end{proof}

For each $n$, fix a partition of unity subordinate to the open covering 
\begin{align*}
  \set{V_n(x) \suchthat x \in S_n}
\end{align*} 
of $\boundary G$. This is equivalent to a continuous map $\pi_n \from \boundary
G \to L_n$. Let $p^\infty_n\from\boundary G\to K_n$ be the composition of
$\pi_n$ with the simplicial map $L_n \to K_n$ given by
\cref{lem:L_Ksimplicial}.

\begin{lemma}\label{lem:close_projections}
  Let $\xi \in \boundary G$. Then $\newdist(p^\infty_n(\xi),
  p^\infty_{n+1}(\xi)) \leq 6\delta+3 + 2D$.
\end{lemma}

\begin{proof}
  Choose vertices $x_1$ and $x_2$ respectively to be vertices of minimal
  simplices of $K_n$ and $K_{n+1}$ containing $p^\infty_n(\xi)$ and
  $p^\infty_{n+1}(\xi)$. Then for $i$ equal to $1$ or $2$ there is a geodesic
  ray $\gamma_i$ with $\gamma_i(0) = e$, $\gamma_i(\infty) = \xi$, and so that
  $\dist(\gamma_1(n), x_1) \leq 2\delta+1$ and $\dist(\gamma_2(n+1),
  x_2) \leq 2\delta+1$.

  Then let $y_1 = \gamma_1(n)$ and $y_2 = \gamma_2(n+1)$. We have
  $\dist(y_1, \gamma_2) \leq 2\delta$, so by the triangle inequality
  $\dist(y_1, y_2) \leq 4\delta +1$. It follows that $\dist(x_1, x_2)
  \leq 6\delta+3$, and so the claimed inequality holds by
  \cref{rem:dist_vs_newdist}.
\end{proof}

\begin{lemma}\label{lem:boundary_gromov_product}
  Let $\alpha_1$ and $\alpha_2$ be geodesic rays with $\alpha_1(0) =
  \alpha_2(0) = e$. Then for any $m_1$ and $m_2$,
  \begin{align*}
    \gromov{e}{\alpha_1(m_1)}{\alpha_2(m_2)} \geq 
        \min\{m_1 - 3\delta, m_2 - 3\delta, \gromov{e}{\alpha_1(\infty)}{\alpha_2(\infty)} - 6\delta\}
  \end{align*}
\end{lemma}

\begin{proof}
  By~\cite{bridsonhaefliger99},
  \begin{align*}
    \gromov{e}{\alpha_1(\infty)}{\alpha_2(\infty)} \leq \liminf_{n_1, n_2}
        \gromov{e}{\alpha_1(n_1)}{\alpha_2(n_2)} + 2\delta.
  \end{align*}
  Let $n_1 \geq m_1$ and $n_2 \geq m_2$.

  Let $p_1$ be a point on $[\alpha_1(n_1), \alpha_2(n_2)] \union \alpha_2$
  within a distance $\delta$ of $\alpha_1(m_1)$.  If $p_1$ is on $\alpha_2$
  then
  \begin{align*}
    \dist(\alpha_1(m_1), \alpha_2(m_2)) 
      & \leq \delta + \dist(p_1, \alpha_2(m_2)) \\
      & \leq 2\delta + \abs{m_1 - m_2}
  \end{align*}
  It follows that
  \begin{align*}
    \gromov{e}{\alpha_1(m_1)}{\alpha_2(m_2)} 
      &\geq \frac{1}{2}(m_1 + m_2 - 2\delta - \abs{m_1 - m_2})\\
      &\geq \min\{m_1, m_2\} - \delta
  \end{align*} 
  and the result follows. Otherwise $p_1$ is on $[\alpha_1(n_1),
  \alpha_2(n_2)]$. Similarly either the claimed result holds, or there is a
  point $p_2$ on $[\alpha_1(n_1), \alpha_2(n_2)]$ within a
  distance $\delta$ of $\alpha_1(m_2)$.

  If $p_1$ lies between $\alpha_2(n_2)$ and $p_1$ on $[\alpha_1(n_1),
  \alpha_2(n_2)]$ then, by considering the triangle with vertices $p_2$,
  $\alpha_2(m_2)$ and $\alpha_2(n_2)$, we see that $\dist(p_1, \alpha_2) \leq
  2\delta$. Therefore $\dist(\alpha_1(m_1), \alpha_2) \leq 3\delta$, and so
  \begin{align*}
    \gromov{e}{\alpha_1(m_1)}{\alpha_2(m_2)} \geq \min\{m_1, m_2\} - 3\delta
  \end{align*}
  and the result follows.

  Otherwise,
  \begin{align*}
    \dist(\alpha_1(n_1), \alpha_2(n_2)) = \dist(\alpha_1(n_1), p_1) +
        \dist(p_1, p_2) + \dist(p_2, \alpha_2(n_2)).
  \end{align*}
  Therefore,
  \begin{align*}
    \mathrlap{\gromov{e}{\alpha_1(n_1)}{\alpha_n(n_2)} - \gromov{e}{\alpha_1(m_1)}{\alpha_2(m_2)}}
    \quad\quad\phantom{{}={}}&\\
           &\mathllap{{}={}}\left(\dist(\alpha_1(m_1), \alpha_1(n_1)) - \dist(\alpha_1(m_1), p_1)\right) \\
           &+ \left(\dist(\alpha_1(m_1), \alpha_2(m_2)) - \dist(p_1, p_2)\right) \\
           &+ \left(\dist(\alpha_2(m_2), \alpha_2(n_2)) - \dist(p_2, \alpha_2(m_2))\right) \\
           &\mathllap{{}\leq{}} \delta+2\delta+\delta=4\delta 
  \end{align*}
  It follows that
  \begin{align*}
    \gromov{e}{\alpha_1(\infty)}{\alpha_2(\infty)} \leq \gromov{e}{\alpha_1(m_1)}{\alpha_2(m_2)} + 6\delta,
  \end{align*}
  which completes the proof.
\end{proof}

\begin{lemma}\label{lem:projectstoasimplex}
  Let $U$ be a subset of $\boundary G$ with diameter $\rho_0$ with respect to
  the visual metric. Let $n \leq \log_a(k_1/\rho_0)$. Then $p^\infty_n(U)$ is
  contained in a single simplex of $K_n$
\end{lemma}

\begin{proof} 
  Let $\xi_1$ and $\xi_2$ be points in $U$, so $\rho(\xi_1, \xi_2)
  \leq \rho_0$.  For $i$ equal to $1$ or $2$ let $x_i$ be a vertex of the
  minimal simplex of $K_n$ containing $p^\infty_n(\xi_i)$. Let $\alpha_i$ be a
  geodesic ray with $\alpha(0) = e$, $\alpha_i(\infty) = \xi_i$ and
  $\dist(\alpha_i(n), x_i) \leq 2\delta+1$.

  By definition of the visual metric, $\gromov{e}{\xi_1}{\xi_2} \geq
  \log_a(k_1/\rho_0)$. Therefore, by \cref{lem:boundary_gromov_product},
  \begin{align*}
    \gromov{e}{\alpha_1(n)}{\alpha_2(n)} \geq \min\{n - 3\delta, \log_a(k_1/\rho_0) - 6\delta\}.
  \end{align*}
  In particular,
  \begin{align*}
    \dist(\alpha_1(n), \alpha_2(n)) \leq \max\{6\delta, 12\delta - 2(\log(k_1/\rho_0) - n)\}
  \end{align*}
  and the result follows.
\end{proof}

\begin{lemma}
  For $\xi \in \boundary G$ and $n - m \geq D + \delta$ the points $p^n_m
  \composed p^\infty_n (\xi)$ and $p^\infty_m(\xi)$ lie in a common simplex of
  $K_n^D$.
\end{lemma}

\begin{proof}
  By definition, $p^\infty_m(\xi)$ is contained in the simplex spanned by the set
  $\set{g \in S_m \suchthat \xi \in V_m(g)}$ and $p^n_m\composed p^\infty_n(\xi)$ is
  contained in the simplex spanned by $\{p^n_m(g) \suchthat g \in S_n \text{
  and } \xi \in V_n(g)\}$.  We show that the union
  \begin{align*}
    \set{g \in S_m \suchthat \xi \in V_m(g)} \union \{p^n_m(g) \suchthat g \in S_n \text{ and } \xi \in V_n(g)\}
  \end{align*}
  of these sets spans a simplex in $K_n$; this simplex then contains
  $p^\infty_m(\xi)$ and $p^n_m\composed p^\infty_n(\xi)$.  It is sufficient to
  prove that if $\xi \in V_m(g_1) \intersection V_n(g_2)$ for $g_1 \in S_m$ and
  $g_2 \in S_n$ then $\dist(g_1, p^n_m(g_2)) \leq D$.

  For $i = 1$ or $2$ let $\gamma_i$ be a geodesic ray with $\gamma_i(0) = e$ and
  $\gamma_i(\infty) = \xi$ such that $\dist(g_1, \gamma_1(m)) \leq 2\delta
  + 1$ and $\dist(g_2, \gamma_2(n)) \leq 2\delta+1$.  As in
  \cref{lem:psimplicial}, $\dist(p^n_m(g_2), \gamma_2(m)) \leq
  2\delta$, since $n-m \geq 3\delta+1$.  Then $\dist(p^n_m(g_2), g_1) \leq
  2\delta + 2\delta + 2\delta+1 \leq D$.
\end{proof}

\section{Connectivity and double dagger conditions}\label{sec:connectivity}

\subsection{Connectivity conditions}

Recall the following standard definitions of topological connectedness 
properties.

\begin{definition}
  The space $M$ is \emph{$d$-locally-connected} (abbreviated $\LC{d}$) if for any 
  point $p \in M$ and any neighbourhood $U$ of $p$, $U$ contains a 
  subneighbourhood $V$ of $p$ such that any continuous map $S^i \to V$ for $i 
  \leq d$ is homotopic in $U$ to a constant map.

  A topological space $M$ is \emph{$d$-connected} (abbreviated $\C{d}$) if 
  any continuous map $S^i \to M$ for $i \leq d$ is homotopic to a constant map.
\end{definition}

We also define a quantitative version of the condition $\LC{d}$.

\begin{definition}
  A metric space $M$ is \emph{linearly-$d$-locally-connected} (abbreviated 
  $\lLC{d}$) if there exists constants $\lambda$ and $r_0$ such that for any 
  point $p \in M$ and any number $r \in (0,r_0)$, any continuous map $S^i \to 
  \Ball_p(r)$ for $i \leq d$ is homotopic in $\Ball_p(\lambda r)$ to a constant 
  map.
\end{definition}

\subsection{Combinatorial conditions}

In \cref{sec:criterion,sec:dd,sec:assembling} we relate local connectivity
properties, applied to the boundary of a hyperbolic group, to certain
combinatorial properties of spheres in the Rips complex of the group. We now
define these conditions. Let $G$ be a hyperbolic group and let $K_n$ be the
simplicial complex defined in \cref{sec:approximating}.

\begin{definition}
  Let $J$ be a simplicial complex. Let $\gamma \from J \to \boundary G$ be 
  continuous and let $f\from J \to K_n$ be affine. We call the triple $(J, 
  \gamma, f)_n$ a \emph{factored triple} or a \emph{factoring of $f$} if $f$ is 
  affine homotopic to $p^\infty_n\composed\gamma$. In this case we say that $f$ 
  \emph{admits a factoring}.
\end{definition}

\begin{definition}
  Let $d\geq -1$. We say that $X$ satisfies $\dd{d}$ if, for any $k$, there
  exist $n_0$ and $k'$ with the following property. Let $n\geq n_0$ and let
  $(\sd^k\boundary\Delta^{d+1}, \gamma, f)_n$ be a factored triple. If $d = 0$
  then further assume that the diameter of the image of $f$ is at most $k$.
  Then $f$ admits an affine extension to $\sd^{k'}\Delta^{d+1}$.
\end{definition}

We also introduce the following a priori stronger condition.

\begin{definition}
  Let $d\geq -1$. We say that $X$ satisfies $\Sd{d}$ if, for any $k$, there
  exist $n_0$ and $k'$ with the following property. Let $n\geq n_0$ and let
  $(\sd^k\boundary\Delta^{d+1}, \gamma, f)_n$ be a factored triple. If $d = 0$
  then further assume that the diameter of the image of $f$ is at most $k$.
  Then $\gamma$ admits a continuous extension $\gamma'$ to $\Delta^{d+1}$ and
  $f$ admits an affine extension $f'$ to $\sd^{k'}\Delta^{d+1}$ such that
  $(\sd^{k'}\Delta^{d+1}, \gamma', f')$ is a factored triple.
\end{definition}

\begin{remark}
  The base cases $\dd{-1}$ and $\Sd{-1}$ are each equivalent to the statement
  that $G$ is infinite.
\end{remark}

\begin{remark}
  The condition $\dd{0}$ is related to the double dagger condition of 
  Bestvina and Mess~\cite{bestvinamess91}. This is the reason for the choice 
  of notation.
\end{remark}

\subsection{Extending maps between simplicial complexes}

The conditions $\dd{-1}$ and $\Sd{-1}$ allow us to extend certain maps from
subcomplexes of simplicial complexes into $K_n$ in a controlled way. We now
prove a lemma to this effect.

\begin{lemma}\label{lem:extendingaffinemaps1}
  Suppose that $G$ satisfies $\Sd{d}$. Let $k \geq 0$. Then there exist numbers
  $k'$ and $n_0$ with the following property. Let $n \geq n_0$, let $J$ be a
  simplicial complex, let $J'$ be a subcomplex of $J$ containing all vertices
  of $J$ and all simplices of $J$ with dimension greater than $d+1$ and let $f$
  be a map $J' \to K_n$ satisfying the following conditions.
  \begin{enumerate}
    \item The map $f$ admits a factoring.
    \item The map $f$ is affine on the subdivision $\sd^k J'$.
    \item For any vertices $x$ and $y$ of $J'$ that are adjacent in $J$,
      $\dist(f(x), f(y)) \leq k$.
  \end{enumerate}
  Then $f$ admits an extension to $J$ that is affine on the subdivision
  $\sd^{k'} J$ and that admits a factoring.
\end{lemma}

\begin{proof}
  We prove the statement by induction on the maximal dimension of a simplex of
  $J$ that is not contained in $J'$. Let this dimension be $d'$, so $1 \leq d'
  \leq d+1$.

  By the inductive hypothesis there exist $k'$ and $n_0$ such that if $n \geq
  n_0$ and $f\from J' \to K_n$ is a map satisfying the conditions of the lemma
  then $f$ admits an extension $f'$ to $J' \union \Skel^{d'-1} J$ such that $f'$
  admits a factoring and is affine on the subdivision $\sd^{k'} (J' \union
  \Skel^{d'-1} J)$.

  The condition $\Sd{d}$ tells us that there exists $n_0' \geq n_0$ and $k''$
  such that for all $n \geq n_0'$ and any affine map $g \from
  \sd^{k'}\boundary\Delta^{d'}\to K_n$ that admits a factoring, $g$ admits an
  affine extension to $\sd^{k''}\Delta^{d+1}$ that extends the factoring.
  For each $d$-simplex $\sigma$ of $J$ not contained in $J'$, apply this fact
  to the map $f'\restricted{\boundary\sigma}$ to extend $f'$ to a map $f''\from
  J\to K_n$ that admits a factoring and is affine on $\sd^{k''} J$.
\end{proof}

If we weaken the conclusion of \cref{lem:extendingaffinemaps1} by no
longer insisting that the extension admit a factoring, then we can weaken the
assumptions to obtain the following proposition.

\begin{proposition}\label{prop:extendingaffinemaps2}
  Suppose that $G$ satisfies $\Sd{d-1}$ and $\dd{d}$. Let $k \geq 0$. Then
  there exist numbers $k'$ and $n_0$ with the following property. Let $n \geq
  n_0$, let $J$ be a simplicial complex, let $J'$ be a subcomplex of $J$
  containing all vertices of $J$ and all simplices of $J$ with dimension
  greater than $d+1$ and let $f$ be a map $J' \to K_n$ satisfying the following
  conditions.
  \begin{enumerate}
    \item The map $f$ admits a factoring.
    \item The map $f$ is affine on the subdivision $\sd^k J'$.
    \item For any vertices $x$ and $y$ of $J'$ that are adjacent in $J$,
      $\dist(f(x), f(y)) \leq k$.
  \end{enumerate}
  Then $f$ admits an extension to $J$ that is affine on the subdivision
  $\sd^{k'} J$. Furthermore $f\restricted{J' \union \Skel{d} J}$ admits a
  factoring.
\end{proposition}

\begin{proof}
  Apply \cref{lem:extendingaffinemaps1} until the final inductive step, which
  can be proved exactly analogously to the proof of the inductive step in
  \cref{lem:extendingaffinemaps1}.
\end{proof}

\section{A criterion for $d$-local-connectedness}\label{sec:criterion}

The goal in this section is to prove the following theorem.

\begin{restatable}{theorem}{ddagimpliesLCd}
  \label{thm:ddagimpliesLCd}
  Suppose that $G$ satisfies the conditions $\Sd{d-1}$ and $\dd{d}$. Then 
  $\boundary G$ is $\lLC{d}$.
\end{restatable}

\subsection{Constructing maps to $\boundary G$}

We will make frequent use of the following lemma, adapted 
from~\cite{bestvinamess91}

\begin{lemma}\cite{bestvinamess91}\label{lem:near_geod_rays}
  Let $G$ be infinite. For any $x \in X$ there exists a geodesic ray $\alpha$ 
  with $\alpha(0) = e$ and $\dist(x,\alpha) \leq 2\delta$.

  Furthermore, $\dist(x, \alpha(\dist(e,x))) \leq 4\delta$.
\end{lemma}

\begin{proof}
  For the first claim, see~\cite{bestvinamess91}. For the second, let $p$ be a 
  point on $\alpha$ such that $\dist(x, p) \leq 2\delta$. Then the triangle 
  inequality shows that $\abs{\dist(e,p), \dist(e,x)} \leq 2\delta$, and 
  so $\dist(p, \alpha(\dist(e,x))) \leq 2\delta$. Then the result 
  follows from another application of the triangle inequality.
\end{proof}

We begin the proof of \cref{thm:ddagimpliesLCd} by proving the following 
proposition.

\begin{proposition}\label{prop:ddag_implies_i}
  Let $d \geq -1$. Suppose that $G$ satisfies the conditions $\Sd{d-1}$ and
  $\dd{d}$. Then there are constants $n_0$, $k$ and $\epsilon$ such that for
  each $n\geq n_0$ there is map $i^n_{n+1}\from\Skel_{d+1} K_n \to \Skel_{d+1}
  K_{n+1}$ such that the following conditions hold.
  \begin{enumerate}
    \item For any $x \in \Vertices(K_n)$, $\dist(x, i_{n+1}^n(x)) \leq
      \epsilon$.
    \item The map $i^n_{n+1}$ is affine on the subdivision $\sd^k\Skel_{d+1}
      K_n$ of $\Skel_{d+1}K_n$.
    \item The map $i^n_{n+1}\restricted{\Skel_d K_n}$ admits a factoring.
  \end{enumerate}
\end{proposition}

\begin{proof}
  The condition $\dd{-1}$ implies the infinitude of $G$, so
  \cref{lem:near_geod_rays} is applicable. For $x \in \Vertices{K_n}$ choose an
  infinite geodesic ray $\alpha_x$ such that $\alpha(0) = 1$ and
  $\dist(\alpha(n), x) \leq 4\delta$. Define $i^n_{n+1}(x) =
  \alpha_x(n+1)$. Then $i^n_{n+1}$ satisfies the first requirement with
  $\epsilon = 4\delta+2$ and satisfies the second requirement automatically.

  Furthermore, $\alpha_x(\infty) \in V_{n+1}(\alpha_x(n+1))$, so 
  $p^\infty_{n+1}(\alpha_x(\infty))$ lies in a simplex of $K_{n+1}$ that also 
  contains $\alpha_x(n+1)$.  Therefore the map $i^n_{n+1}$ and a simplicial 
  approximation to the map $x \mapsto \alpha_x(\infty) \mapsto p^\infty_{n+1} 
  (\alpha_x(\infty))$ are related by an affine homotopy, so $i^n_{n+1}$ admits a 
  factoring.

  Now apply \cref{prop:extendingaffinemaps2} to extend $i^n_{n+1}$ from
  $\Vertices(K_n)$ to $\Skel_{d+1} K_n$ to obtain a map with the required
  properties.
\end{proof}

Throughout the remainder of this section we assume that $G$ satisfies $\dd{d-1}$ 
and $\Sd{d}$. Let $n_0$, $k$ and $\epsilon$ be the constants given in 
\cref{prop:ddag_implies_i}, and for $n\geq n_0$ let $i^n_{n+1} 
\from \sd^k\Skel_{d+1} K_n \to \Skel_{d+1} K_{n+1}$ be the affine map given by 
that proposition.  For $n \geq m \geq n_0$ let $i^m_n$ be the composition 
$i^{n-1}_n \composed \dotsb \composed i^m_{m+1} \from \Skel_{d+1} K_m \to 
\Skel_{d+1} K_n$.  This map is affine on a degree $k^{n-m}$ subdivision of 
$\Skel_{d+1} K_m$.

In what follows we require the following useful lemma.

\begin{lemma}\label{lem:useful}
  Let $(x_n)$ be a sequence of points in $G$ with $\dist(x_{n+1}, e) = 
  \dist(x_n, e) + 1$ and $\dist(x_{n+1}, x_n)$ bounded. Then,
  \begin{align*}
    \gromov{e}{x_m}{x_n} \geq \dist(e,x_m) - C
  \end{align*}
  for some constant $C$ depending only on $\delta$ and the bound on 
  $\dist(x_{n+1}, x_n)$.
\end{lemma}

\begin{proof}
  We estimate the Gromov product using the visual metric $\vdistance$ on 
  $\boundary G$; then the claimed inequality follows from the triangle 
  inequality.

  Let $i_n = \dist(x_n, e)$, so $i_n = i_0 + n$, and let 
  $\dist(x_{n+1},x_n)$ be bounded by $C_0$. By 
  \cref{lem:near_geod_rays} there exists a sequence $(\alpha_n)$ of 
  geodesic rays with $\dist(\alpha_n(i_n), x_n) \leq 4\delta$. Then 
  $\dist(\alpha_n(i_n), \alpha_{n+1}(i_{n+1})) \leq C_0 + 8\delta$. Then 
  $\gromov{e}{\alpha_n(\infty)}{ \alpha_{n+1}(\infty)} \geq i_n - (C_0 + 
  8\delta)/2$.

  By the triangle inequality it follows that for $n\geq m$ we have the following 
  inequality.
  \begin{align*}
    \vdistance(\alpha_n(\infty), \alpha_m(\infty)) \leq C_1 a^{-i_m}
  \end{align*}
  for some constants $C_1$ depending only on $\delta$ and $C_0$. Then, by
  definition of the visual metric, there exists a constant $C_2$ such that
  \begin{align*}
    \gromov{e}{\alpha_n(\infty)}{\alpha_m(\infty)} \geq i_m - C_2.
  \end{align*}

  Now, by \cref{lem:boundary_gromov_product} there exists a constant $C_3$ such
  that
  \begin{align*}
    \gromov{e}{\alpha_n(i_n)}{\alpha_m(i_m)} \geq i_m - C_3,\qedhere
  \end{align*}
  as required.
\end{proof}

\begin{lemma}\label{lem:linearproduct}
  There is a constant $C$ such that if $x \in \Skel_{d+1} K_m$ then
  \begin{align*}
    \gromov{e}{i^m_n(x)}{x} \geq m - C
  \end{align*}
  for all $n\geq m\geq n_0$.
\end{lemma}

\begin{proof}
  For $n \geq m$, let $y_n$ be a vertex of the minimal simplex of $K_n$
  containing $i^m_n(x)$. Then, for each $n \geq m$, we have $\dist(e, y_{n+1})
  = \dist(e, y_n)$.

  We now bound the distance $\dist(y_n, y_{n+1}$. To start with, $\dist(y_n,
  i^n_{n+1} y_n) \leq \epsilon$. Let $R$ be such that any two vertices in the
  1-skeleton of $\sd^k \Delta^{d+1}$ are joined by a path traversing at most
  $R$ edges. Let $\sigma$ be the minimal simplex of $K_n$ containing
  $i^m_n(x)$. Then $y_n$ is a vertex of $\sigma$ and $y_{n+1}$ is a vertex of
  the image of $\sigma$ under $i^n_{n+1}$, so $\dist(i^n_{n+1} y_n, y_{n+1})
  \leq RD$.  Putting this together,
  \begin{align*}
      \dist(y_n, y_{n+1}) \leq \epsilon + RD
  \end{align*}

  It follows from \cref{lem:useful} that there exists a constant $C$ depending
  only on $\delta$, $\epsilon$ and $k$ such that $\gromov{e}{y_n}{y_m} \geq m -
  C$.

  Finally, by applying the inequality in \cref{rem:dist_vs_newdist}, we deduce
  that
  \begin{align*}
      \gromov{e}{i^m_n(x)}{x} \geq m - C - 3D.\qedhere
  \end{align*}
\end{proof}

\begin{corollary}
  For $m \geq n_0$ and $x \in \Skel_{d+1} K_m$, the sequence
  $(i^m_n(x))_{n\geq m}$ converges to a point in $\boundary G$, which we shall
  denote $i^m_\infty(x)$.
\end{corollary}

\begin{proof}
  For $n_1$ and $n_2$ at least $m$, \cref{lem:linearproduct} implies that
  $\gromov{e}{i^m_{n_1}(x)}{i^m_{n_2}(x)} \geq \min\{n_1,n_2\} - C$, which
  tends to infinity as $n_1$ and $n_2$ tend to infinity.
\end{proof}

\begin{lemma}\label{lem:simplexproduct}
  There is a constant $C$ such that if $m \geq n_0$ and $x$ and $y$ are in a
  common simplex of $\Skel_{d+1} K_m$ then
  \begin{align*}
    \gromov{e}{i^m_n(x)}{i^m_n(y)} \geq m - C
  \end{align*}
  for all $n\geq m$.
\end{lemma}

\begin{proof}
  The inequality of \cref{lem:linearproduct} is satisfied for each of $x$ 
  and $y$. By~\cite{bridsonhaefliger99} there exist $\delta'$ depending only on 
  $\delta$ such that
  \begin{align*}
    \gromov{e}{i^m_n(x)}{i^m_n(y)} &\geq \min\{\gromov{e}{i^m_n(x)}{x}, 
    \gromov{e}{x}{y}, \gromov{e}{y}{i^m_n(y)}\} - 2\delta'\\
    &\geq \min\{m - C, m - R/2, m - C\} - 2\delta' \\
    &\geq m - C'
  \end{align*}
  for some constant $C'$.
\end{proof}

The following corollary immediately follows from \cref{lem:simplexproduct}.

\begin{corollary}\label{cor:visualdiameter}
  There is a constant $C$ such that for any $m\geq n_0$ and any simplex
  $\sigma$ of $\Skel_{d+1} K_m$, the diameter of $i^m_{\infty}(\sigma)$ with
  respect to the visual metric $\vdistance$ is bounded above by $Ca^{-m}$,
  where $a$ is the visual parameter.
\end{corollary}

\begin{proposition}\label{prop:continuouslimit}
  The map $i^m_\infty\from \Skel_{d+1} K_m \to \boundary G$ is continuous.
\end{proposition}

\begin{proof}
  Fix $x \in \Skel_{d+1} K_m$. Let $k$ be the constant given in the definition 
  of the map $i$. For $n\geq 0$ let $U_n$ be the star in $\beta^{nk} 
  \Skel_{d+1}K_m$ of the minimal simplex of $\beta^{nk}\Skel_{d+1}K_m$ 
  containing $x$. Then $U_n$ is a neighbourhood of $x$ for each $n$.

  For each $n$, the restriction of $i^m_{m+n}$ to a simplex in 
  $\beta^{nk}\Skel_{d+1}K_m$ is affine, and therefore has image contained in a 
  simplex of $\Skel_{d+1} K_{m+n}$. The point $x$ is contained in every simplex 
  of $U_n$, so for any $y \in U_n$ the points $i^m_{m+n}(x)$ and $i^m_{m+n}(y)$ 
  are contained in a common simplex of $\Skel_{d+1}K_m$. Therefore, by 
  \cref{cor:visualdiameter}, there is a constant $C$ such that 
  $\vdistance(i^m_\infty(x), i^m_\infty(y)) \leq Ca^{-(m+n)}$ for every $y \in 
  U_n$.
\end{proof}

\begin{remark}
  In fact, if $K_m$ is endowed with a metric in which each simplex is 
  isometrically identified with the standard simplex of the same dimension then 
  the map $i^m_\infty$ can be shown to be H\"{o}lder continuous with exponent 
  only depending on $\delta$ and the constants in the definition of the map $i$. 
  We do not require this strengthening of \cref{prop:continuouslimit} 
  here.
\end{remark}

Finally, we use the maps $i^n_\infty$ to construct homotopies between certain
special maps to $\boundary G$.

\begin{proposition}\label{prop:basic_homotopies}
  Let $C$ be a constant. Then there exists a number $m_0$ and a function $\mu
  \from \posreals\to\posreals$ such that $\mu(\eta)\to0$ as $\eta\to0$ with the following
  property. Let $n \geq m_0$ and let $f_0$ and $f_1$ be any maps from
  $\boundary\Delta^{d+1}$ to $K_n$ satisfying the following conditions:
  \begin{enumerate}
    \item the maps $f_0$ and $f_1$ are affine on some subdivision of
      $\boundary\Delta^{d+1}$;
    \item for any $x \in \boundary\Delta^{d+1}$, the distance 
      $\newdist(f_0(x), f_1(x))$ is at most $C$;
    \item each of $f_0$ and $f_1$ admits a factoring.
  \end{enumerate}
  Then there is a homotopy $h$ from $i^n_\infty\composed f_0$ to
  $i^n_\infty\composed f_1$ satisfying a uniform continuity condition: for any
  $x \in \boundary\Delta^{d+1}$ and any $s$ and $t$ in $[0,1]$,
  \begin{align*}
    \rho(h(x,s), h(x,t)) \leq \mu(\abs{s-t})a^{-n}.
  \end{align*}
\end{proposition}

\begin{proof}
  To start with, apply \cref{prop:extendingaffinemaps2} with $k = C + D$ to
  obtain constants $k'$ and $m_0\geq n_0$ such that the conclusion of the
  proposition holds.

  Let $n \geq m_0$.  Let $J$ be a subdivision of $\boundary\Delta^{d+1}$ such
  that $f_0$ and $f_1$ are both affine on $J$. Then the map 
  \begin{align*}
    f_0 \disjointunion f_1 \from J \times \{0\} \disjointunion J \times \{1\}
          \to K_n,
  \end{align*}
  defined on a subset of the product simplicial complex $J \times [0,1]$,
  satisfies the conditions of \cref{prop:extendingaffinemaps2}, and so admits
  an affine extension $F \from \sd^{k'} (J \times [0,1]) \to K_n$. Let $h =
  i^n_\infty \composed F$, so $h$ is a homotopy from $i^n_\infty\composed f_0$
  to $i^n_\infty\composed f_1$ and it remains to prove the uniform continuity
  assertion.

  Let $\eta_0$ be such that for $\eta$ at most $\eta_0$, 
  for any $x \in \Delta^d$, for any $s$ and $t$ in $[0,1]$ with
  $\abs{s-t} \leq \eta$, the segment $\{x\} \times [s,t]$ is contained in a
  union of at most two $(d+1)$-simplices of $\sd^{k'}(\Delta^d \times [0,1])$.
  We first define the modulus of continuity $\mu(\eta)$ for $\eta > \eta_0$.

  Let $M$ be the number of $(d+1)$-simplices in $\sd^{k'}(\Delta^d \times
  [0,1])$.  \Cref{cor:visualdiameter} gives a constant $C_0$ such that any
  $(d+1)$-simplex of $K_n$ is mapped to a subset of $\boundary G$ of diameter
  at most $C_0 a^{-n}$, and so we can take $\mu(\eta) = C_0M$ for $\eta >
  \eta_0$.

  Now, for $\eta \leq \eta_0$, there exists a maximal number $\kappa(\eta) \geq
  0$ such that for any $x \in \Delta^d$ and any $s$ and $t$ in $[0,1]$ with
  $\abs{s-t} \leq \eta$, the segment $\{x\} \times [s,t]$ is contained in a
  union of at most two $(d+1)$-simplices of
  $\sd^{\kappa(\eta)}\sd^{k'}(\Delta^d\times[0,1])$. Note that $\kappa(\eta)
  \to \infty$ as $\eta \to 0$. Now, if $N\in\naturals$ then a $(d+1)$-simplex of
  $\sd^{k^N}K_n$ is mapped by $i^n_{n+N}$ into a $(d+1)$-simplex of $K_{n+N}$,
  which is mapped by $i^{n+N}_\infty$ to a set of diameter at most
  $C_0a^{-n+N}$. Therefore, if $N$ is such that $\kappa(\eta) \geq k^N$ then
  for $x \in \boundary\Delta^{d+1}$ and $\abs{s-t} < \eta$, $\rho(h(x,s),
  h(x,t)) \leq 2C_0a^{-n-N}$. It follows that we may take $\mu(\eta)$ as follows:
  \begin{align*}
    \mu(\eta) = 2C_0 a^{-\floor*{\frac{\log\kappa(\eta)}{\log k}}}.\qedhere
  \end{align*}
\end{proof}

\subsection{Proving \Cref{thm:ddagimpliesLCd}}

We now use the maps $(i^n_{n+1})$ to prove \cref{thm:ddagimpliesLCd}. We begin
with two lemmas.

\begin{lemma}\label{lem:convergestoidentity}
  There is a constant $C$ such that the distance from $(i^m_\infty \composed 
  p^\infty_m)$ to the identity map $\boundary G\to\boundary G$ is at most 
  $Ca^{-m}$ for each $m$, where $a$ is the visual parameter.
\end{lemma}

\begin{proof}
  Let $\xi \in \boundary G$. By \cref{lem:linearproduct} there is a 
  constant $C$ such that 
  \begin{align*}
    \gromov{e}{i^m_n\composed p^\infty_m(\xi)}{p^\infty_m(\xi)} \geq m - C
  \end{align*} 
  for each $n\geq m\geq n_0$.

  Let $\alpha$ be a geodesic ray with $\alpha(0) = e$ and $\alpha(\infty) = 
  \xi$. Then $\alpha(m)$ is a vertex of a simplex in $\Skel_{d+1}K_m$ containing 
  $p^\infty_m(\xi)$, and $\gromov{e}{\alpha(m)}{\alpha(n)} = m$ for $n\geq m$.
  It follows that there is a constant $\delta'$ depending only on $\delta$ such 
  that
  \begin{align*}
    \mathrlap{\gromov{e}{\alpha(n)}{i^m_n\composed p^\infty_m(\xi)}}\quad\quad &\\
          & \geq \min\{\gromov{e}{\alpha(n)}{\alpha(m)}, 
            \gromov{e}{\alpha(m)}{p^\infty_m(\xi)}, 
            \gromov{e}{p^\infty_m(\xi)}{i^m_n\composed p^\infty_m(\xi)}\} 
            - 2\delta' \\
          &\geq \min\{m - C, m - R/2, m\} - 2\delta' \\
          &\geq m - C'
  \end{align*}
  for some constant $C'$.

  Therefore $\gromov{e}{\xi}{i^m_\infty\composed p^\infty_m(\xi)} \geq m - C'$, 
  from which the claim follows.
\end{proof}

\begin{lemma}\label{lem:name_this}
  There is a number $C$ such that, for any $\xi \in \boundary G$ and any $n
  \geq 0$ and any vertices $x_1$ and $x_2$ of the minimal simplices containing
  $i^n_{n+1}\composed p^\infty_n(\xi)$ and $p^\infty_{n+1}(\xi)$ respectively,
  \begin{align*}
    \dist(x_1, x_2) \leq C.
  \end{align*}
\end{lemma}

\begin{proof}
  By \cref{lem:close_projections} the distances $\newdist(p^\infty_n(\xi),
  p^\infty_{n+1}(\xi))$ are bounded by $6\delta + 3 + 2D$. Let $y$ be a vertex
  of a simplex containing $p^\infty_n(\xi)$; then $\newdist(y, p^\infty_n(\xi))$
  is bounded by $D$.

  Furthermore, $\dist(y, i^n_{n+1}(y))$ is uniformly bounded by the constant
  $\epsilon$ from \cref{prop:ddag_implies_i}, and $\newdist(i^n_{n+1}(y),
  i^n_{n+1}\composed p^\infty_n (\xi))$ is bounded by the product of $D$ and
  the constant $k$ appearing in \cref{prop:ddag_implies_i}. By putting all this
  together we obtain a bound $C$ on $\newdist(i^n_{n+1}\composed
  p^\infty_n(\xi), p^\infty_{n+1}(\xi))$, and then $\dist(x_1, x_2) \leq C +
  2D$.
\end{proof}

\begin{proposition}\label{prop:uniform_homotopies}
  There exists a number $m_0$ and a function $\nu\from\posreals\to\posreals$ such
  that $\nu(\eta)\to0$ as $\eta\to0$ with the following property. Let
  $\gamma\from\boundary\Delta^{d+1}\to\boundary G$ be a continuous map. Let $n
  \geq m_0$ and let $f$ be an affine approximation to
  $p^\infty_n\composed\gamma$. Then there is a homotopy $h$ from $\gamma$ to
  $i^n_\infty\composed f$ such that for any $x \in \boundary\Delta^{d+1}$ and
  any $s$ and $t$ in $[0,1]$,
  \begin{align*}
    \rho(h(x,s), h(x,t)) \leq \nu(\abs{s-t}) a^{-n}.
  \end{align*}
\end{proposition}

\begin{proof}
  Let $C$ be as in \cref{lem:name_this} and apply \cref{prop:basic_homotopies}
  to obtain a number $m_0\geq n_0$ and a function $\mu$.

  Let $\gamma\from\boundary\Delta^{d+1}\to\boundary G$, $n\geq m_0$ and
  $f\from\boundary\Delta^{d+1}\to K_n$ be as in the proposition. Let $f_0 = f$,
  and for $m > 0$ let $f_m\from\boundary\Delta^{d+1}\to K_{n+m}$ be a
  simplicial approximation to $p^\infty_{n+m}\composed\gamma$. For $m \geq 0$
  let $\gamma_m = i^{m+n}_\infty\composed f_m$. For each $m\geq 0$ the
  following observations are immediate:
  \begin{enumerate}
    \item the map $f_m$ admits a factoring;
    \item the image of $f_m$ is contained in the $d$-skeleton of $K_{n+m}$, and
      so $i^{n+m}_{n+m+1}\composed f_m$ admits a factoring;
    \item by \cref{lem:name_this} we have $\newdist(i^{n+m}_{n+m+1}\composed
      f_m(x), f_{m+1}(x)) \leq C$ for all $x \in \boundary\Delta^{d+1}$.
  \end{enumerate}
  Therefore, for each $m$, \cref{prop:basic_homotopies} gives a homotopy $h_m$
  from $i^{n+m+1}_\infty\composed f_{m+1}$ to $i^{n+m}_\infty \composed f_m$
  satisfying a uniform continuity condition. Define an infinite concatenation
  of these homotopies:
  \begin{align*}
    h(x,t) = 
    \begin{cases}
      \gamma(x) & \text{if } t = 0\\
      h_n\left(x,2^{m+1}\left(t-\frac{1}{2^{m+1}}\right)\right) 
              & \text{if $t \in \left[\frac{1}{2^{m+1}}, \frac{1}{2^m}\right]$
                    , $m\geq 0$}.
    \end{cases}
  \end{align*}
  This function is clearly continuous except possibly on
  $\boundary\Delta^{d+1}\times\{0\}$. We aim to show it is also continuous
  there, but first we define the function $\nu$.

  Let $m \in \naturals$. We aim to bound the distance $\rho(h(x,s), h(x,t))$
  for $\abs{s,t} \leq 2^{-m}$ independently of $n$ and the particular path
  $\gamma$. We first treat the case when one of $s$ and $t$ is $0$, then we
  deal with the case when $s$ and $t$ are small, and finally we treat the case
  when $s$ and $t$ are large. (Our ``small'' and ``large'' regions intersect,
  to guarantee that this covers all possibilities.)

  To begin, we bound the distance $\rho(h(x,0), h(x,t))$
  where $x \in \boundary \Delta^{d+1}$ and $t < 2^{-m}$. Let $C'$ be the
  constant appearing in \cref{lem:convergestoidentity}. Then 
  \begin{align*}
    \rho(h(x,0), h(x,2^{-m})) \leq C'a^{-m-n}.
  \end{align*}
  Furthermore, for any $m' \in \naturals$ and any $t \in [2^{-m'-1}, 2^{-m'}]$,
  \begin{align*}
    \rho(h(x,t), h(x,2^{-m'})) \leq \mu(1)a^{-m'-n}.
  \end{align*}
  It follows that for $t \leq 2^{-m}$,
  \begin{align*}
    \rho(h(x,0), h(x,t)) \leq a^{-n}\left(C'a^{-m} + \sum_{m' \geq m}
          \mu(1)a^{-m'}\right).
  \end{align*}

  Similarly, we treat the ``small'' case. Here $s$ and $t$ are \emph{small} if
  they are at most $2^{-m/2}$. If $s$ and $t$ are both at most this large
  then
  \begin{align*}
    \rho(h(x,s), h(x,t)) \leq a^{-n} \sum_{m' \geq \floor{m/2}} \mu(1) a^{-m'}
  \end{align*}

  Finally, if $s$ and $t$ are such that $\abs{s-t} \leq 2^{-m}$ but at least
  one of $s$ and $t$ is greater than $2^{-m/2}$ then both $s$ and $t$ are at
  least $2^{-m/2}$. This is the ``large'' case. It follows that 
  \begin{align*}
    \rho(h(x,s), h(x,t)) &\leq a^{-n} \mu(\abs{s-t} 2^{m/2 + 1}) \\
                         &\leq a^{-n} \mu(2^{1-m/2})
  \end{align*}

  Therefore for $\eta \in (2^{-m-1}, 2^{-m}]$ we define
  \begin{align*}
    \nu(\eta)  = \max\left\{
      C'a^{-m} + \sum_{m' \geq m} \mu(1)a^{-m'},
      \sum_{m' \geq \floor{m/2}} \mu(1) a^{-m'},
      \mu(2^{1-m/2})
    \right\},
  \end{align*}
  and we see that $\nu(\eta) \to 0$ as $\eta \to 0$, and also that
  \begin{align*}
    \rho(h(x,s), h(x,t)) \leq \nu(\abs{s-t})
  \end{align*}
  for any $x \in \boundary\Delta^{d+1}$ and $s$ and $t$ in $[0,1]$.

  It remains to show that $h$ is continuous at $(x,0)$ for each $x$ in
  $\boundary\Delta^{d+1}$. Let $\epsilon > 0$ and take a neighbourhood $U$ of
  $x$ in $\boundary\Delta^{d+1}$ such that $\rho(\gamma(x), \gamma(y)) \leq
  \epsilon/2$ for $y$ in $U$. Let $\eta > 0$ be so that $\nu(\eta) <
  \epsilon/2$. Then for any $(y, t) \in U \times [0, \eta]$, $\rho(h(x,0),
  h(y,t)) < \epsilon$.
\end{proof}

\Cref{thm:ddagimpliesLCd} follows as a corollary of this proposition.

\ddagimpliesLCd*

\begin{proof}
  To begin, let $\nu$ and $m_0 \geq n_0$ be as in
  \cref{prop:uniform_homotopies}. Let $r_0 =
  k_1a^{-m_0}$, so that, by \cref{lem:projectstoasimplex},
  $p^\infty_{m_0}\composed\gamma$ has image contained in the star of a single
  vertex of $K_{m_0}$ for any map $\gamma\from\boundary\Delta^{d+1}\to\boundary
  G$ with $\Diam\image(\gamma)\leq r_0$.

  Let $\gamma\from\boundary\Delta^{d+1}\to\boundary G$ be such a map. Let 
  \begin{align*}
    m = \floor{\log_a(k_1/\Diam\image\gamma)} \geq m_0,
  \end{align*}
  so that by \cref{lem:projectstoasimplex} $p^\infty_{m}\composed\gamma$ has
  image contained in a single vertex of $K_m$. Then a constant map
  $\boundary\Delta^{d+1} \to K_m$ is a simplicial approximation to
  $p^\infty_m\composed\gamma$; applying \cref{prop:uniform_homotopies} to
  this map immediately gives a homotopy $h$ from $\gamma$ to the constant map.

  Furthermore,
  \begin{align*}
    \Diam\image h &\leq \Diam\image\gamma + \sup_{x \in\boundary\Delta^{d+1}, s,t \in [0,1]} \rho(h(x,s), h(x,t)) \\
                  &\leq \Diam\image\gamma + a^{-m} \nu(1) \\
                  &\leq (1 + a\nu(1)/k_1) \Diam\image\gamma \qedhere
  \end{align*}
\end{proof}

\section{Criteria for $\dd{d}$ and $\Sd{d}$}\label{sec:dd}

In this section we establish sufficient conditions for $\dd{d}$ and $\Sd{d}$ to 
hold.

\subsection{A criterion for $\dd{d}$}

This section is devoted to the proof of the following theorem.

\begin{theorem}\label{thm:nocutpointimpliesdagger}
  Suppose that $\boundary G - \set\xi$ is $\C{d}$ for any $\xi \in \boundary G$. 
  Then $G$ satisfies $\dd{d+1}$.
\end{theorem}

\begin{proof}

Suppose that the conclusion of \cref{thm:nocutpointimpliesdagger} 
does not hold. Then there exists a number $k$, a sequence of affine maps 
$f_i\from\sd^k\boundary\Delta^{d+1}\to K_{n_i}$ and a sequence of continuous 
maps $\gamma_i\from\boundary\Delta^{d+1}\to\boundary G$ satisfying the following 
conditions.
\begin{enumerate}
  \item For each $i$, $(\sd^k\boundary\Delta^{d+1}, f_i, \gamma_i)_{n_i}$ is a 
    factored triple.
  \item There is no affine extension of $f_i$ to $\sd^i\Delta^{d+1}$.
  \item The sequence $n_i$ tends to infinity as $i$ tends to infinity.
\end{enumerate}

By passing to a subsequence, we may assume that the sequence $(f_i)$ has the 
following properties, where we denote by $J$ the simplicial complex 
$\sd^k\boundary\Delta^{d+1}$.
\begin{enumerate}
  \item There exist group elements $g_i$ such that $g_i(f_i(v)) = g_j(f_j(v))$ 
    for all $i$ and $j$ and for all $v \in \Vertices(J)$.
  \item Large neighbourhoods of translates by $g_i$ of the images of the vertex 
    set of $J$ under $f_i$ are identical: we have the following equality for all 
    $i$ and $j$:
    \begin{align*}
      g_i\left(N_{\min\set{i,j}}\left(f_i(\Vertices(J))\right) \intersection 
      S_{n_i}\right) = g_j\left(N_{\min\set{i,j}}\left(f_j(\Vertices(J))\right) 
      \intersection S_{n_j}\right).
    \end{align*}
  \item The restrictions of the pullbacks $g_i^\star\dist$ and 
    $g_j^\star\dist$ of the distance function to the vertex set of this 
    simplicial complex agree.
  \item The sequence $g_i = g_i\cdot 1$ of vertices of $K$ converges to a point 
    $\xi\in\boundary G$ as $i\to\infty$.
\end{enumerate}

\begin{definition}
  Let $H_i$ be the full subcomplex of $K_{n_i}$ with vertex set
  \begin{align*}
    g_i\left(N_i\left(f_i(\Vertices (J))\right)\intersection S_{n_i}\right).
  \end{align*}
  Note that $H_i$ contains $H_j$ for $i \geq j$. It will be convenient to pass 
  to a further subsequence such that for each $i$ the complex $H_{i+1}$ contains 
  all vertices of $g_i(S_{n_i})$ adjacent to $H_i$. Let $H$ be the direct
  limit of the complexes $H_i$.  We view $H$ as a horosphere, the topology of
  which approximates that of $\boundary G - \set\xi$.
  \cref{lem:geodesicsmeethorosphere}--\ref{lem:propermaps} below justify 
  this point of view.

  All of the maps $g_i \composed f_i \from J \to H$ are equal; call this map
  $f$. 
\end{definition}

\begin{lemma}\label{lem:geodesicsmeethorosphere}
  Every bi-infinite geodesic with $\xi$ in its limit set meets $H$.
\end{lemma}

\begin{proof}
  Let $\alpha$ be a bi-infinite geodesic with $\xi$ as a limit pint. Pick a
  point $w \in f(\Vertices(J))$ and let the distance $\dist(w,\alpha)$ be
  realised by a point $x \in \alpha$.

  The points $g_i$ converge to $\xi$ as $i\to\infty$, so the distances
  $\dist(x, [\xi, g_i])$ tend to infinity as $i$ tends to infinity. The
  triangle with vertices $x$, $\xi$ and $g_i$ is $\delta$-slim, so for each $i$
  there exists a point $y_i$ on $[x, g_i]$ with $\dist(y_i, \alpha) \leq
  \delta$ and $y_i\to\xi$ as $i\to\infty$.  For each $i$ let $z_i$ be a point
  on $\alpha$ with $\dist(y_i, z_i) \delta$.

  Since $\dist(g_i, x) = n_i$ for $i$ sufficiently large and $\dist(x,y_i) \to
  \infty$ as $i\to\infty$, we have the following limit.
  \begin{align*}\label{eqn:zi_closer_to_gi_than_x}
    \dist(g_i,z_i) - n_i &\leq \dist(g_i,y_i) + \delta - n_i \text{ for $i$
                                        sufficiently large} \\
                         &= - \dist(x,y_i) + \delta \\
                         &\to -\infty\text{ as $i \to \infty$} \tag{$\star$}
  \end{align*}
  Therefore, for $i$ sufficiently large, there exists a point $p_i$ on $\alpha$
  such that $z_i$ lies between $\xi$ and $p_i$ on $\alpha$ and so that
  $\dist(g_i,p_i)=n_i$. We now show that $\dist(p_i, x)$ is uniformly bounded.

  The limit~\eqref{eqn:zi_closer_to_gi_than_x}, taken together with the fact
  that $\dist(g_i, x) = \dist(g_i, p_i) = n_i$, shows that the distances
  $\dist([z_i, g_i], x)$ and $\dist([z_i, g_i], p_i)$ tend to infinity as
  $i\to\infty$.  We now divide into cases according to which of $x$ and $p_i$
  is closer to $z_i$.
  \begin{enumerate}
    \item If $x$ is between $z_i$ and $p_i$ on $\alpha$ then by considering a
      geodesic triangle with vertices $g_i$, $z_i$ and $p_i$ we see that for
      $i$ sufficiently large, $x$ is within a distance $\delta$ of a point
      $q_i$ on the geodesic from $g_i$ to $p_i$.  Therefore,
      \begin{align*}
        \dist(g_i,x)&\leq \dist(g_i,q_i)+\delta\\
                        &\leq \dist(g_i,p_i)-\dist(p_i,q_i)+\delta\\
                        &\leq \dist(g_i,p_i)-\dist(x,p_i)+2\delta.
      \end{align*}
      It follows that $\dist(x,p_i) \leq \dist(g_i,p_i)-\dist(g_i,x)+2\delta
      = 2\delta$.
    \item If $p_i$ is between $z_i$ and $x$ on $\alpha$ then by an identical 
      argument with the r\^oles of $x$ and $p_i$ reversed we can similarly 
      deduce that 
      \begin{align*}
        \dist(x,p_i)\leq\dist(g_i,x) - \dist(g_i,p_i) + 2\delta =2\delta.
      \end{align*}
  \end{enumerate}

  Either way, $\dist(w, p_i) \leq \dist(x,w) + 2\delta$. In summary, we have
  shown that for $i$ sufficiently large there is a point $p_i\in\alpha$ with
  $\dist(g_i,p_i)=n_i$ and $\dist(p_i,f(\Vertices J))$ bounded by $\dist(x,w) +
  2\delta$. Then $p_i \in H_i$ whenever $i$ is at least $\dist(x,w) + 2\delta$.
\end{proof}

\begin{lemma}\label{lem:boundedintersection}
  Let $C$ be a compact subset of $\boundary G - \set\xi$. Then the set of points 
  of intersection between $H$ and bi-infinite geodesics with one end point equal 
  to $\xi$ and the other in $C$ is bounded.
\end{lemma}

\begin{proof}
  Let $\alpha$ be any bi-infinite geodesic with $\alpha(-\infty)=\xi$ and 
  $\alpha(\infty)\in C$. Let $x \in \alpha \intersection H$. Since $C$ is
  compact, there exists a point $v \in \alpha$, between $\xi$ and $x$ on
  $\alpha$, such for that any bi-infinite geodesic $\beta$ with
  $\beta(-\infty)$ in $C$ and $\beta(\infty) = \alpha(\infty)$, $\beta$ does
  not meet the $100\delta$-neighbourhood of the sub-ray of $\alpha$ between
  $\xi$ and $v$: otherwise a limiting argument shows that $\xi$ is in $C$.

  Since $g_i \to \xi$, the distance $\dist(v, [\xi, g_i]) \to \infty$ as
  $i\to\infty$. The triangle with vertices $\xi$, $g_i$ and $x$ is
  $\delta$-slim, so the geodesic path from $g_i$ to $x$ passes within a
  distance $\delta$ of $v$ for $i$ large enough. Therefore, since $\dist(g_i,
  x) = n_i$ for $i$ large enough, the following inequality holds for all $i$
  large enough.
  \begin{align*}
    0 \leq \dist(g_i, v) + \dist(v, x) - n_i \leq 2\delta.
  \end{align*}

  Let $\alpha'$ be a bi-infinite geodesic with $\alpha'(-\infty) = \xi$ and
  $\alpha'(\infty) \in C$ and let $x' \in \alpha' \intersection H$. The ideal
  triangle with vertices $\xi$, $\alpha(\infty)$ and $\alpha'(\infty)$ is
  $\delta$-slim, so the subray of $\alpha$ between $\xi$ and $v$ is contained
  in a $\delta$-neighbourhood of $\alpha'$.  Let $v' \in \alpha'$ be a point
  with $\dist(v, v') \leq \delta$.

  We split into cases according to the order of $\xi$, $v'$ and $x'$ on
  $\alpha'$.
  \begin{enumerate}
    \item
      First we suppose that $v'$ is between $x'$ and $\xi$ on $\alpha'$. Then as
      in the argument above, for $i$ sufficiently large we have the following
      inequality:
      \begin{align*}
        0 \leq \dist(g_i, v') + \dist(v', x') - n_i \leq 2\delta.
      \end{align*}
      And therefore,
      \begin{align*}
        -2\delta \leq \dist(g_i, v) + \dist(v, x') - n_i \leq 4\delta.
      \end{align*}
      Finally, putting these inequalities together,
      \begin{align*}
        \dist(v,x') \leq \dist(v,x) + 4\delta,
      \end{align*}
      and thus we can uniformly bound this distance in this case.
    \item
      Alternatively, $x'$ is between $v'$ and $\xi$ on $\alpha'$ and so (since
      the triangle with vertices $\xi$, $v$ and $v'$ is $\delta$-slim) $x'$ is
      within a distance $2\delta$ of the geodesic ray from $x$ to $\xi$. By
      considering the triangle with vertices $\xi$, $g_i$ and $x$ for $i$ large
      enough, a geodesic segment from $g_i$ to $x$ passes within a distance
      $3\delta$ of $x'$. Therefore we have the following inequality for all $i$
      sufficiently large:
      \begin{align*}
        0 \leq \dist(g_i, x') + \dist(x', x) - \dist(g_i, x) \leq 6\delta.
      \end{align*}
      Finally, for $i$ sufficiently large, $\dist(g_i, x') = \dist(g_i, x) = n_i$,
      so
      \begin{align*}
        \dist(x,x') \leq 6\delta.
      \end{align*}
  \end{enumerate}
\end{proof}

\begin{definition}
  Let $U_i \subset \boundary G$ be the (closed) preimage of $H_i$ under the map 
  $g_i \composed p^\infty_{n_i} \composed g_i^{-1} \from \boundary G \to X$.
  Denote by $q_i$ the restriction of this map to $U_i$.
\end{definition}

The following lemma is immediate from the definition of $p^\infty_i$.

\begin{lemma}\label{lem:describing_q_i}\todo{Check this}
  Let $\zeta \in \boundary G - \set\xi$ and suppose that $q_i(\zeta) \in H_i$
  is defined, so $\zeta \in U_i$, and $N_{4\delta+1} q_i(\zeta) \in H_i$. Then
  $q_i(\zeta)$ is contained in the minimal simplex of $H_i$ with vertex set
  \begin{align*}
    N_{2\delta+1} \set{\eta(n_i)\suchthat\text{$\eta$ a geodesic ray with
    $\eta(0) = g_i$ and $\eta(\infty) = \zeta$}}.
  \end{align*}\qed
\end{lemma}

\begin{lemma}
  Every compact subset of $\boundary G - \set\xi$ is contained in $U_i$ for 
  $i$ sufficiently large.
\end{lemma}

\begin{proof}
  Suppose that a compact subset $C$ of $\boundary G - \set\xi$ is not contained
  in $U_i$ for infinitely many $i$. Then after passing to a subsequence there
  exists for each $i$ a point $\zeta_i \in C\setminus U_i$.

  By assumption, $g_i^{-1}(H_i)$ contains the star in $K_{n_i}$ of 
  $g_i^{-1}(H_{i-1})$, so the definition of $p^\infty_{n_i}$ implies that a 
  geodesic ray $\alpha_i$ from $e$ to $g_i^{-1}(\zeta_i)$ does not pass through 
  $g_i^{-1}(H_{i-1})$. Equivalently, $g_i\composed\alpha_i$ is a geodesic from 
  $g_i$ to $\zeta_i$ that does not pass through $H_{i-1}$.

  After reparameterising and passing to a subsequence, the geodesic rays
  $g_i\composed\alpha_i$ converge uniformly on compact subsets to a bi-infinite
  geodesic from $\xi$ to some point $\zeta \in C$.  This geodesic does not pass
  through $H$, which contradicts \cref{lem:geodesicsmeethorosphere}.
\end{proof}

\begin{lemma}\label{lem:affinehomotopic}
  For any compact subset $C\subset\boundary G - \set\xi$, there exists $i_0$ 
  such that for all $i \geq i_0$ and any $\zeta \in C$, $\newdist(q_i(\zeta),
  q_{i_0}(\zeta)) \leq 8\delta + 2$, and, in particular, $q_i\restricted{C}$
  and $q_{i_0}\restricted{C}$ are related by an affine homotopy.
\end{lemma}

\begin{proof}
  Let $B\subset H$ be a bounded set containing all points where geodesics with
  one limit point equal to $\xi$ and the other in $C$ meet $H$; this set exists
  by \cref{lem:boundedintersection}.

  Fix $\alpha$ to be some geodesic with $\alpha(-\infty)=\xi$ and
  $\alpha(\infty)\in C$ and let $x$ be a point of intersection between $\alpha$
  and $B$. Since the triangle with vertcies $x$, $g_i$ and $\xi$ is
  $\delta$-slim, and $\dist(x, [\xi, g_i]) \to \infty$ as $i\to\infty$, for
  each $i$ there exists a point $y_i$ on $[g_i, x]$ with $\dist(y_i, \alpha)
  \leq \delta$ and so that $y_i \to \xi$ as $i\to\infty$. Let $z_i \in \alpha$
  be such that $\dist(y_i, z_i)\leq\delta$.

  Now fix $i_0$ such that the following conditions hold for all $i\geq 
  i_0$.
  \begin{enumerate}
    \item The distance $\dist(y_i,x)$ is greater than $7\delta + \Diam B$.
    \item The set $C$ is contained in $U_i$.
  \end{enumerate}

  Let $\zeta \in C$ and let $\alpha'$ be a geodesic from $\xi$ to $\zeta$. Let 
  $x'$ be a point in the intersection of $\alpha'$ and $B$.

  Now let $i\geq i_0$. Then by considering the ideal triangle with vertices
  $g_i$, $x$ and $x'$, and using the fact that $\dist(y_i, x) > \delta + \Diam
  B$, we deduce that there exists a point $y_i'$ on $[x', g_i]$ with
  $\dist(y_i, y_i') \leq \delta$.

  Similarly, since $\dist(z_i, x) > \delta + \Diam B$, consideration of the
  triangle with vertices $\xi$, $x$ and $x'$ reveals that there exists a point
  $z_i'$ on $\alpha'$ between $\xi$ and $x'$ with $\dist(z_i, z_i') \leq
  \delta$. Then $\dist(y_i', z_i') \leq 3\delta$.

  Since $\dist(z_i', x') > 2\delta$, the distance from $y_i'$ to the subray of
  $\alpha'$ from $x'$ to $\zeta$ is greater than $\delta$. Therefore by
  considering a triangle with vertices $g_i$, $x'$ and $\zeta$ we see that
  there exists a point $v_i$ on a geodesic ray $\eta_i$ from $g_i$ to $\zeta$
  with $\dist(v_i, y_i') \leq \delta$. It follows that $\dist(v_i, z_i') \leq
  4\delta$, and we know that $\dist(x', z_i') > 5\delta$, so $\dist(x', [z_i',
  v_i]) > \delta$ and therefore $\dist(x', \eta_i) \leq \delta$.

  In summary, any geodesic ray from $g_i$ to $\zeta$ passes within a distance 
  $\delta$ of $x'$, for $i\geq i_0$. Furthermore, $\dist(g_i,x') = n_i$, so 
  $\dist(\eta_i(n_i), x')\leq 2\delta$. It follows from the description of
  $q_i$ in \cref{lem:describing_q_i} that $q_i(\zeta)$ is contained in a
  simplex with all vertices within a distance $4\delta+1$ of $x'$. The set of
  all such vertices spans a simplex, so, in particular, $q_i\restricted{C}$ and
  $q_{i_0}\restricted{C}$ are related by an affine homotopy for $i \geq i_0$. 
\end{proof}

\begin{lemma}\label{lem:propermaps} 
  For any compact subset $C \subset H$ there exists $i_0$ such that
  \begin{align*}
    \bigunion_{i\geq i_0} q_i^{-1} C
  \end{align*}
  is a relatively compact subset of $\boundary G - \set\xi$.
\end{lemma}

\begin{proof}
  If not then there exists a sequence $\zeta_i$ of points with $\zeta_i \in U_i$ 
  for all $i$ such that $q_i(\zeta_i) \in C$ for all $i$ and $\zeta_i \to \xi$ 
  as $i \to \infty$.

  Then for each $i$ a geodesic from $g_i$ to $\zeta_i$ passes through the star 
  in $H$ of $C$.  After passing to a subsequence these geodesic rays converge to 
  a bi-infinite geodesic passing through the star in $H$ of $C$, both end points 
  of which must be $\xi$, which is a contradiction.
\end{proof}

Since $f$ is related by an affine homotopy to $q_i\composed g_i\composed
\gamma_i$ for every $i$, for each $i$ the image of $g_i\composed\gamma_i$ is
contained in $q_i^{-1} H_1$. By \cref{lem:propermaps} there exists $i_0$ and a
compact subset $C_0 \subset \boundary G - \set\xi$ such that the image of
$g_i\composed\gamma_i$ is contained in $C_0$ for $i\geq i_0$. By
\cref{lem:affinehomotopic} we can choose $i_1 \geq i_0$ such that
$q_i\restricted{C_0}$ is affine homotopic to $q_{i_1}\restricted{C_0}$ for
$i\geq i_1$.

Let $\gamma = g_{i_1}\composed\gamma_{i_1}$ and let $h \from
\Delta^{d+1}\to\boundary G - \set\xi$ be a continuous extension of $\gamma$;
this exists since $\boundary G - \set\xi$ is $\C{d}$. Let $C_1 \supset C_0$ be
a compact subset of $\boundary G - \set\xi$ containing the image of $h$ and let
$i_2 \geq i_1$ be chosen so that $C_1 \subset U_{i_2}$.

Then $q_{i_2}\composed h$ has image in $H_{i_2}$. Furthermore,
$q_{i_2}\composed h\restricted{\boundary\Delta^{d+1}} = q_{i_2}\composed
\gamma$ is related by an affine homotopy in $H_{i_2}$ to
$q_{i_1}\composed\gamma$, which is related by an affine homotopy to the affine
map $f$. Therefore $f$ is null-homotopic in $H_{i_2}$, and so by the Relative
Simplicial Approximation theorem~\cite{zeeman64} there is a number $k'$ and an
affine extension $h'\from\sd^{k'}\to H_{i_2}$ of $f$.

Then, for $i \geq i_2$ the map $g_i^{-1}\composed
h'\from\sd^{k'}\Delta^{d+1}\to K_{n_i}$ is an affine extension of $f_i$, which
contradicts the choice of maps $f_i$ if $i > k'$.

This completes the proof of \cref{thm:nocutpointimpliesdagger}.
\end{proof}

\subsection{Strengthening the condition: $\Sd{d}$}

We now strengthen the conclusion of \cref{thm:nocutpointimpliesdagger} 
under the assumption that $\boundary G$ is $\lLC{d}$:

\begin{theorem}\label{thm:lLCandnocutpointimpliesS}
  Suppose that $\boundary G - \set\xi$ is $\C{d}$ for any $\xi \in \boundary G$ 
  and that $\boundary G$ is $\lLC{d}$. Then $G$ satisfies $\Sd{d+1}$.
\end{theorem}

\begin{proof}

does not hold, and therefore there exists a number $k$, a sequence of affine 
maps $f_i\from \sd^k\boundary\Delta^{d+1}\to K_{n_i}$ and a sequence of 
continuous maps $\gamma_i\from \boundary\Delta^{d+1}\to\boundary G$ satisfying 
the following (modified) conditions.
\begin{enumerate}
  \item For each $i$, $(\sd^k\boundary\Delta^{d+1},\gamma_i,f_i)_{n_i}$ if a 
    factored triple.
  \item There is no pair $(F_i, \Gamma_i)$ where $F_i$ is an affine extension of 
    $f_i$ to $\sd^i\Delta^{d+1}$, $\Gamma_i$ is a continuous extension of 
    $\gamma_i$ to $\Delta^{d+1}$, and 
    $(\sd^i\boundary\Delta^{d+1},\Gamma_i,F_i)_{n_i}$ is a factored triple.
  \item The sequence $n_i$ tends to infinity as $i$ tends to infinity.
\end{enumerate}

As in the proof of \cref{thm:nocutpointimpliesdagger} we pass to a 
subsequence and define complexes $H_i$ and $H$, subsets $U_i = (g_i\composed 
p^\infty_{n_i}\composed g_i^{-1})^{-1} H_i\subset \boundary G 
- \set\xi$ and maps $q_i = g_i\composed p^\infty_{n_i}\composed 
g_i^{-1}\restricted{U_i}\from U_i\to H_i$. Then 
\cref{lem:geodesicsmeethorosphere}--\ref{lem:propermaps} apply to these maps
and spaces as in \cref{thm:nocutpointimpliesdagger} without modification.

It is now sufficient to prove the following claim.

\begin{claim} 
  There is a number $k$ such that, for infinitely many $i$, there is an 
  extension of $\gamma_i$ to $\sd^k\Delta^{d+1}$ whose composition with 
  $p^\infty_{n_i}$ is affine.
\end{claim}

Let $C_0$ be a compact subset of $\boundary G - \set\xi$ and $i_0$ be an
integer such that $g_i\composed\gamma_i$ is contained in $C_0$ for $i\geq i_0$
and $q_i\restricted{C_0}$ is affine homotopic to $q_j\restricted{C_0}$ for
$i\geq j\geq i_0$.

\begin{lemma}
  There exists $i_1\geq i_0$ and a number $P$ such that for $i\geq j\geq i_1$ 
  the maps $g_i\composed \gamma_i$ and $g_j\composed\gamma_j$ are joined by a 
  homotopy $h_{i,j}$ such that the image of $h_{i,j}$ is contained in $U_{i_1}$ 
  and  $q_i\composed h_{i,j}$ is a concatenation of at most $P$ affine 
  homotopies.
\end{lemma}

\begin{proof} 
  Let $i\geq j\geq i_0$. Each of $q_i\composed g_i\composed\gamma_i$ and
  $q_j\composed g_j\composed\gamma_j$ is affine homotopic to $f$, and
  $q_j\composed g_j\composed\gamma_j$ is affine homotopic to $q_i\composed
  g_j\composed\gamma_j$, so the distance between $q_i\composed
  g_i\composed\gamma_i$ and $q_i\composed g_j\composed\gamma_j$ is uniformly
  bounded. Therefore the distance between $p^\infty_{n_i}\composed
  g_i^{-1}\composed g_j\composed\gamma_j$ and $p^\infty_{n_i}\composed \gamma_i$ is
  uniformly bounded, so the distance between $g_i^{-1}\composed
  g_j\composed\gamma_j$ and $\gamma_i$ is bounded above by a constant multiple
  of $a^{-i}$. By 
  %\cref{lem:shorthomotopy}, if $i$ is large enough then there
  exists a homotopy $h'_{i,j}$ between these maps with width also bounded above
  by a constant multiple of $a^{-i}$.

  Therefore the width of $p^\infty_{n_i}\composed h'_{i,j}$ is uniformly bounded. 
  It follows that it is the concatenation of boundedly many affine homotopies. 
  For $i$ sufficiently large, $p^\infty_j\composed h'_{i,j}$ has image contained 
  in $H_i$. Define $h_{i,j} = g_i\composed h'_{i,j}$; then $h_{i,j}$ is a 
  homotopy from $g_i\composed\gamma_i$ to $g_i\composed\gamma_j$ such that 
  $q_j\composed h_{i,j}$ is a concatenation of boundedly many affine homotopies.
\end{proof}

Let $C_2$ be a compact subset of $\boundary G - \set\xi$ containing $U_{i_1}$ and 
also containing the image of a continuous extension 
$\Gamma\from\Delta^{d+1}\to\boundary G - \set\xi$ of $\gamma$. Take $i_2\geq 
i_1$ such that $C_2 \subset U_2$ and also so that $q_i\restricted{C_2}$ is 
affine homotopic to $q_j\restricted{C_2}$ for $i \geq j \geq i_2$.

Now, $q_{i_2}\composed \Gamma$ is affine homotopic to an affine 
map after some finite number of subdivisions. Since $q_i$ is affine homotopic to 
$q_{i_2}$ for $i\geq i_2$ it follows that for any $i\geq i_2$ the map 
$q_i\composed \Gamma$ is affine homotopic to an affine map after boundedly many 
subdivisions. Furthermore, for $i\geq i_2$, $h_{i,i_1}$ is a 
homotopy from $g_i\composed \gamma_i$ to $\gamma$, the composition of which with 
$q_i$ is affine homotopic to an affine map after boundedly many subdivisions. 
Therefore, for each $i\geq i_2$ there is a null-homotopy of 
$g_i\composed\gamma_i$ whose composition with $q_i$ is affine homotopic to an 
affine map after boundedly many subdivisions. The composition of this extension 
with $g_i^{-1}$ gives the required extension of $\gamma_i$ to $\Delta^{d+1}$.
\end{proof}

\section{The main theorem}\label{sec:assembling}

The results of the previous two sections may now be assembled to prove the main 
theorem:

\begin{theorem}\label{thm:maintheorem}
  Let $G$ be a hyperbolic group. Then $\boundary G$ is $\LC{d}$ if and only if 
  $\boundary G - \set\xi$ is $\C{d}$ for every point $\xi \in \boundary G$.
\end{theorem}

\begin{proof}
  We first prove that if $\boundary G - \set\xi$ is $\C{d}$ for every point $\xi 
  \in \boundary G$ then $\boundary G$ is $\LC{d}$ by induction. Suppose this 
  condition holds and also that $\boundary G$ is $\LC{d-1}$. Then 
  \cref{thm:lLCandnocutpointimpliesS} implies that $\Sd{d}$ is 
  satisfied, while \cref{thm:nocutpointimpliesdagger} implies that 
  $\dd{d+1}$ is satisfied, and so $\boundary G$ is $\LC{d}$ by 
  \cref{thm:ddagimpliesLCd}.

  Conversely, suppose that $\boundary G$ is $\LC{d}$ and let $\xi \in \boundary 
  G$; we aim to show that $\boundary G - \set\xi$ is $\C{d}$. Let $\gamma$ be a 
  continuous map $S^d \to \boundary G - \set\xi$ The point $\xi$ is a conical 
  limit point, so there exist distinct points $\zeta_1$ and $\zeta_2$ in 
  $\boundary G$ and a sequence of elements $(g_i)$ in $G$ such that $g_i\xi \to 
  \zeta_1$ as $i\to \infty$, and for any compact subset $C$ of $\boundary G - 
  \set\xi$ and any neighbourhood $U$ of $\zeta_2$, $g_i(C) \subset U$ for $i$ 
  sufficiently large.

  Let $V$ be a neighbourhood of $\zeta_2$ that does not contain any point 
  $g_i\xi$.  Let $U$ be a neighbourhood of $\zeta_2$ such that any map $S^d \to 
  U$ has an extension to the disk $D^{d+1}$ with image contained in $V$. Then 
  let $i$ be such that $g_i(\image\gamma)\subset U$. Let $h$ be an extension of 
  $\gamma$ to $D^{d+1}$ with image contained in $V$; then $g_i^{-1}\composed h$ 
  is a continuous extension of $\gamma$ with image contained in $\boundary G - 
  \set\xi$.
\end{proof}

\begin{corollary}
  Let $G$ be a hyperbolic group. Then the following conditions are equivalent.
  \begin{enumerate}
    \item\label{item:LCd} The boundary $\boundary G$ is $\LC{d}$.
    \item\label{item:Cd} For all points $\xi \in \boundary G$, $\boundary G - 
      \set\xi$ is $\C{d}$.
    \item\label{item:dd} The condition $\dd{d+1}$ is satisfied.
    \item\label{item:Sd} The condition $\Sd{d+1}$ is satisfied.
  \end{enumerate}
\end{corollary}

\begin{proof}
 The equivalence of conditions~\ref{item:LCd} and~\ref{item:Cd} is the content 
 of \cref{thm:maintheorem}.
 \todo{finish this}
\end{proof}

\subsection{Questions}

\begin{question}
  Suppose that $G$ is a hyperbolic group and $d\geq 1$ such that $\boundary G$ 
  is $\C{d}$.  Does it follow that $\boundary G - \set\xi$ is $\C{d}$ for every 
  $\xi$ in $\boundary G$, and therefore that $\boundary G$ is $\LC{d}$?
\end{question}

For $d = 0$ this question was originally asked by Bestvina and 
Mess~\cite{bestvinamess91} and answered in the affirmative by work of 
Bowditch~\cite{bowditch98b} and Swarup~\cite{swarup96}. The techniques of
Bowditch and Swarup are not applicable for $d\geq 1$, and new methods would be
required. On the other hand, there is no example in the literature of a group
that provides a negative answer to the question.

\begin{question}
  Conversely, suppose that $\boundary G - \set\xi$ is $\C{d}$ for every 
  $\xi\in\boundary G$, and therefore $\boundary G$ is $\LC{d}$. Is it true that 
  $\boundary G$ is either $\C{d}$ or homeomorphic to $S^d$?
\end{question}

\section{Locally contractible boundaries}

In this section we investigate the implications of local contractibility for
the boundary of a hyperbolic group. (Recall that a space is locally
contractible if any neighbourhood $U$ of any point admits a sub-neighbourhood
$V$ such that the inclusion $V\into U$ is null-homotopic in $U$.) This condition
is related to the conditions $\LC{n}$ investigated earlier in this paper by the
following well-known proposition.

\begin{proposition}%Mentioned in the Dugundji paper. Cited to Kuratowski's
  %Topologie II, chapter VII
  Let $X$ be a separable metric space of topological dimension $n$. If $X$ is
  $\LC{n}$ then it is locally contractible.
\end{proposition}

To begin, note the following lemma.

\begin{lemma}
  If $\boundary G$ is locally contractible then $\homology_\star(\boundary G;
  \integers)$ and $\homology^\star(\boundary G; \integers)$ are finitely
  generated.
\end{lemma}

\begin{proof}
  Take an finite cover of $\boundary G$ by contractible open subsets
  $\{U_i\}_{i \leq n}$. Let $K$ be the nerve of the covering. Then there is a
  spectral sequence with 
  \begin{align}
    E^1_{pq} = \bigoplus_\sigma\in\Skel^{p} K H_q(X_\sigma),
  \end{align}
  where $X_\sigma = \intersection_{i \in \sigma} X_i$, such that
  $E_{pq}\ssconverges \homology_{p+q}(X)$. The simplicial complex $K$ is finite
  and each group $H_q(X_\sigma)$
  \todo{Finish proving this lemma.}
\end{proof}

\bibliography{references}
\end{document}

### 2020-01-13 paper.tex
Wrote a skeleton

@@
 
-\section{The Rips complex and the Gromov boundary}\label{sec:approximating}
+\section{The Rips complex and the Gromov boundary}\label{sec:spheres}
 
@@
 
-\section{Connectivity and double dagger conditions}\label{sec:connectivity}
+\section{Horoballs in the Rips Complex}
 
-\subsection{Connectivity conditions}
+\section{The double dagger condition}
 
-Recall the following standard definitions of topological connectedness 
-properties.
+We begin this section by recalling results of Bestvina and Mess, Bowditch, and
+Swarup, which characterise the hyperbolic groups with locally (path) connected
+boundary. In~\cite{bestvinamess91}, Bestvina and Mess introduce the following
+condition that a hyperbolic group might satisfy.
 
 \begin{definition}
-  The space $M$ is \emph{$d$-locally-connected} (abbreviated $\LC{d}$) if for any 
-  point $p \in M$ and any neighbourhood $U$ of $p$, $U$ contains a 
-  subneighbourhood $V$ of $p$ such that any continuous map $S^i \to V$ for $i 
-  \leq d$ is homotopic in $U$ to a constant map.
-
-  A topological space $M$ is \emph{$d$-connected} (abbreviated $\C{d}$) if 
-  any continuous map $S^i \to M$ for $i \leq d$ is homotopic to a constant map.
+  Double dagger condition
 \end{definition}
 
-We also define a quantitative version of the condition $\LC{d}$.
+This property is linked to the connectedness of $\boundary G$ by the following
+propositions:
+
+\begin{proposition}
+  $\ddag$ implies locally path connected.
+\end{proposition}
+
+\begin{proposition}
+  no cut point implies $\ddag$.
+\end{proposition}
+
+Taken together with the following theorem of Bowditch~\cite{bowditch98b} and
+Swarup~\cite{swarup96}, these propositions show that $\boundary G$ is locally
+path connected if and only if it is connected.
+
+\begin{theorem}
+  If $\boundary G$ is connected then $\boundary G$ does not contain a cut
+  point.
+\end{theorem}
+
+\subsection{An equivalent condition}
+
+In this section we reinterpret the double dagger condition as a condition
+describing the existence of paths in the spheres $K_n$ of
+Section~\ref{sec:spheres}. This interpretation gives a more systematic method
+for constructing paths in $\boundary G$ from paths in the spheres $K_n$, and
+permits a generalisation to higher dimensional connectivity.
 
 \begin{definition}
-  A metric space $M$ is \emph{linearly-$d$-locally-connected} (abbreviated 
-  $\lLC{d}$) if there exists constants $\lambda$ and $r_0$ such that for any 
-  point $p \in M$ and any number $r \in (0,r_0)$, any continuous map $S^i \to 
-  \Ball_p(r)$ for $i \leq d$ is homotopic in $\Ball_p(\lambda r)$ to a constant 
-  map.
+  New double dagger condition. \todo{State condition.}
 \end{definition}
 
-\subsection{Combinatorial conditions}
+\todo{Prove things about this condition}
 
-In \cref{sec:criterion,sec:dd,sec:assembling} we relate local connectivity
-properties, applied to the boundary of a hyperbolic group, to certain
-combinatorial properties of spheres in the Rips complex of the group. We now
-define these conditions. Let $G$ be a hyperbolic group and let $K_n$ be the
-simplicial complex defined in \cref{sec:approximating}.
+\section{Local simple connectedness}
+
+In this section we introduce a new condition that a hyperbolic group might satisfy.
 
 \begin{definition}
-  Let $J$ be a simplicial complex. Let $\gamma \from J \to \boundary G$ be 
-  continuous and let $f\from J \to K_n$ be affine. We call the triple $(J, 
-  \gamma, f)_n$ a \emph{factored triple} or a \emph{factoring of $f$} if $f$ is 
-  affine homotopic to $p^\infty_n\composed\gamma$. In this case we say that $f$ 
-  \emph{admits a factoring}.
+  \todo{New condition}
 \end{definition}
 
-\begin{definition}
-  Let $d\geq -1$. We say that $X$ satisfies $\dd{d}$ if, for any $k$, there
-  exist $n_0$ and $k'$ with the following property. Let $n\geq n_0$ and let
-  $(\sd^k\boundary\Delta^{d+1}, \gamma, f)_n$ be a factored triple. If $d = 0$
-  then further assume that the diameter of the image of $f$ is at most $k$.
-  Then $f$ admits an affine extension to $\sd^{k'}\Delta^{d+1}$.
-\end{definition}
+\todo{If this condition is satisfied then the bounadry is locally simply
+connected.}
 
-We also introduce the following a priori stronger condition.
+\section{Simply connected point complements}
 
-\begin{definition}
-  Let $d\geq -1$. We say that $X$ satisfies $\Sd{d}$ if, for any $k$, there
-  exist $n_0$ and $k'$ with the following property. Let $n\geq n_0$ and let
-  $(\sd^k\boundary\Delta^{d+1}, \gamma, f)_n$ be a factored triple. If $d = 0$
-  then further assume that the diameter of the image of $f$ is at most $k$.
-  Then $\gamma$ admits a continuous extension $\gamma'$ to $\Delta^{d+1}$ and
-  $f$ admits an affine extension $f'$ to $\sd^{k'}\Delta^{d+1}$ such that
-  $(\sd^{k'}\Delta^{d+1}, \gamma', f')$ is a factored triple.
-\end{definition}
-
-\begin{remark}
-  The base cases $\dd{-1}$ and $\Sd{-1}$ are each equivalent to the statement
-  that $G$ is infinite.
-\end{remark}
-
-\begin{remark}
-  The condition $\dd{0}$ is related to the double dagger condition of 
-  Bestvina and Mess~\cite{bestvinamess91}. This is the reason for the choice 
-  of notation.
-\end{remark}
-
-\subsection{Extending maps between simplicial complexes}
-
-The conditions $\dd{-1}$ and $\Sd{-1}$ allow us to extend certain maps from
-subcomplexes of simplicial complexes into $K_n$ in a controlled way. We now
-prove a lemma to this effect.
-
-\begin{lemma}\label{lem:extendingaffinemaps1}
-  Suppose that $G$ satisfies $\Sd{d}$. Let $k \geq 0$. Then there exist numbers
-  $k'$ and $n_0$ with the following property. Let $n \geq n_0$, let $J$ be a
-  simplicial complex, let $J'$ be a subcomplex of $J$ containing all vertices
-  of $J$ and all simplices of $J$ with dimension greater than $d+1$ and let $f$
-  be a map $J' \to K_n$ satisfying the following conditions.
-  \begin{enumerate}
-    \item The map $f$ admits a factoring.
-    \item The map $f$ is affine on the subdivision $\sd^k J'$.
-    \item For any vertices $x$ and $y$ of $J'$ that are adjacent in $J$,
-      $\dist(f(x), f(y)) \leq k$.
-  \end{enumerate}
-  Then $f$ admits an extension to $J$ that is affine on the subdivision
-  $\sd^{k'} J$ and that admits a factoring.
-\end{lemma}
-
-\begin{proof}
-  We prove the statement by induction on the maximal dimension of a simplex of
-  $J$ that is not contained in $J'$. Let this dimension be $d'$, so $1 \leq d'
-  \leq d+1$.
-
-  By the inductive hypothesis there exist $k'$ and $n_0$ such that if $n \geq
-  n_0$ and $f\from J' \to K_n$ is a map satisfying the conditions of the lemma
-  then $f$ admits an extension $f'$ to $J' \union \Skel^{d'-1} J$ such that $f'$
-  admits a factoring and is affine on the subdivision $\sd^{k'} (J' \union
-  \Skel^{d'-1} J)$.
-
-  The condition $\Sd{d}$ tells us that there exists $n_0' \geq n_0$ and $k''$
-  such that for all $n \geq n_0'$ and any affine map $g \from
-  \sd^{k'}\boundary\Delta^{d'}\to K_n$ that admits a factoring, $g$ admits an
-  affine extension to $\sd^{k''}\Delta^{d+1}$ that extends the factoring.
-  For each $d$-simplex $\sigma$ of $J$ not contained in $J'$, apply this fact
-  to the map $f'\restricted{\boundary\sigma}$ to extend $f'$ to a map $f''\from
-  J\to K_n$ that admits a factoring and is affine on $\sd^{k''} J$.
-\end{proof}
-
-If we weaken the conclusion of \cref{lem:extendingaffinemaps1} by no
-longer insisting that the extension admit a factoring, then we can weaken the
-assumptions to obtain the following proposition.
-
-\begin{proposition}\label{prop:extendingaffinemaps2}
-  Suppose that $G$ satisfies $\Sd{d-1}$ and $\dd{d}$. Let $k \geq 0$. Then
-  there exist numbers $k'$ and $n_0$ with the following property. Let $n \geq
-  n_0$, let $J$ be a simplicial complex, let $J'$ be a subcomplex of $J$
-  containing all vertices of $J$ and all simplices of $J$ with dimension
-  greater than $d+1$ and let $f$ be a map $J' \to K_n$ satisfying the following
-  conditions.
-  \begin{enumerate}
-    \item The map $f$ admits a factoring.
-    \item The map $f$ is affine on the subdivision $\sd^k J'$.
-    \item For any vertices $x$ and $y$ of $J'$ that are adjacent in $J$,
-      $\dist(f(x), f(y)) \leq k$.
-  \end{enumerate}
-  Then $f$ admits an extension to $J$ that is affine on the subdivision
-  $\sd^{k'} J$. Furthermore $f\restricted{J' \union \Skel{d} J}$ admits a
-  factoring.
-\end{proposition}
-
-\begin{proof}
-  Apply \cref{lem:extendingaffinemaps1} until the final inductive step, which
-  can be proved exactly analogously to the proof of the inductive step in
-  \cref{lem:extendingaffinemaps1}.
-\end{proof}
-
-\section{A criterion for $d$-local-connectedness}\label{sec:criterion}
-
-The goal in this section is to prove the following theorem.
-
-\begin{restatable}{theorem}{ddagimpliesLCd}
-  \label{thm:ddagimpliesLCd}
-  Suppose that $G$ satisfies the conditions $\Sd{d-1}$ and $\dd{d}$. Then 
-  $\boundary G$ is $\lLC{d}$.
-\end{restatable}
-
-\subsection{Constructing maps to $\boundary G$}
-
-We will make frequent use of the following lemma, adapted 
-from~\cite{bestvinamess91}
-
-\begin{lemma}\cite{bestvinamess91}\label{lem:near_geod_rays}
-  Let $G$ be infinite. For any $x \in X$ there exists a geodesic ray $\alpha$ 
-  with $\alpha(0) = e$ and $\dist(x,\alpha) \leq 2\delta$.
-
-  Furthermore, $\dist(x, \alpha(\dist(e,x))) \leq 4\delta$.
-\end{lemma}
-
-\begin{proof}
-  For the first claim, see~\cite{bestvinamess91}. For the second, let $p$ be a 
-  point on $\alpha$ such that $\dist(x, p) \leq 2\delta$. Then the triangle 
-  inequality shows that $\abs{\dist(e,p), \dist(e,x)} \leq 2\delta$, and 
-  so $\dist(p, \alpha(\dist(e,x))) \leq 2\delta$. Then the result 
-  follows from another application of the triangle inequality.
-\end{proof}
-
-We begin the proof of \cref{thm:ddagimpliesLCd} by proving the following 
-proposition.
-
-\begin{proposition}\label{prop:ddag_implies_i}
-  Let $d \geq -1$. Suppose that $G$ satisfies the conditions $\Sd{d-1}$ and
-  $\dd{d}$. Then there are constants $n_0$, $k$ and $\epsilon$ such that for
-  each $n\geq n_0$ there is map $i^n_{n+1}\from\Skel_{d+1} K_n \to \Skel_{d+1}
-  K_{n+1}$ such that the following conditions hold.
-  \begin{enumerate}
-    \item For any $x \in \Vertices(K_n)$, $\dist(x, i_{n+1}^n(x)) \leq
-      \epsilon$.
-    \item The map $i^n_{n+1}$ is affine on the subdivision $\sd^k\Skel_{d+1}
-      K_n$ of $\Skel_{d+1}K_n$.
-    \item The map $i^n_{n+1}\restricted{\Skel_d K_n}$ admits a factoring.
-  \end{enumerate}
-\end{proposition}
-
-\begin{proof}
-  The condition $\dd{-1}$ implies the infinitude of $G$, so
-  \cref{lem:near_geod_rays} is applicable. For $x \in \Vertices{K_n}$ choose an
-  infinite geodesic ray $\alpha_x$ such that $\alpha(0) = 1$ and
-  $\dist(\alpha(n), x) \leq 4\delta$. Define $i^n_{n+1}(x) =
-  \alpha_x(n+1)$. Then $i^n_{n+1}$ satisfies the first requirement with
-  $\epsilon = 4\delta+2$ and satisfies the second requirement automatically.
-
-  Furthermore, $\alpha_x(\infty) \in V_{n+1}(\alpha_x(n+1))$, so 
-  $p^\infty_{n+1}(\alpha_x(\infty))$ lies in a simplex of $K_{n+1}$ that also 
-  contains $\alpha_x(n+1)$.  Therefore the map $i^n_{n+1}$ and a simplicial 
-  approximation to the map $x \mapsto \alpha_x(\infty) \mapsto p^\infty_{n+1} 
-  (\alpha_x(\infty))$ are related by an affine homotopy, so $i^n_{n+1}$ admits a 
-  factoring.
-
-  Now apply \cref{prop:extendingaffinemaps2} to extend $i^n_{n+1}$ from
-  $\Vertices(K_n)$ to $\Skel_{d+1} K_n$ to obtain a map with the required
-  properties.
-\end{proof}
-
-Throughout the remainder of this section we assume that $G$ satisfies $\dd{d-1}$ 
-and $\Sd{d}$. Let $n_0$, $k$ and $\epsilon$ be the constants given in 
-\cref{prop:ddag_implies_i}, and for $n\geq n_0$ let $i^n_{n+1} 
-\from \sd^k\Skel_{d+1} K_n \to \Skel_{d+1} K_{n+1}$ be the affine map given by 
-that proposition.  For $n \geq m \geq n_0$ let $i^m_n$ be the composition 
-$i^{n-1}_n \composed \dotsb \composed i^m_{m+1} \from \Skel_{d+1} K_m \to 
-\Skel_{d+1} K_n$.  This map is affine on a degree $k^{n-m}$ subdivision of 
-$\Skel_{d+1} K_m$.
-
-In what follows we require the following useful lemma.
-
-\begin{lemma}\label{lem:useful}
-  Let $(x_n)$ be a sequence of points in $G$ with $\dist(x_{n+1}, e) = 
-  \dist(x_n, e) + 1$ and $\dist(x_{n+1}, x_n)$ bounded. Then,
-  \begin{align*}
-    \gromov{e}{x_m}{x_n} \geq \dist(e,x_m) - C
-  \end{align*}
-  for some constant $C$ depending only on $\delta$ and the bound on 
-  $\dist(x_{n+1}, x_n)$.
-\end{lemma}
-
-\begin{proof}
-  We estimate the Gromov product using the visual metric $\vdistance$ on 
-  $\boundary G$; then the claimed inequality follows from the triangle 
-  inequality.
-
-  Let $i_n = \dist(x_n, e)$, so $i_n = i_0 + n$, and let 
-  $\dist(x_{n+1},x_n)$ be bounded by $C_0$. By 
-  \cref{lem:near_geod_rays} there exists a sequence $(\alpha_n)$ of 
-  geodesic rays with $\dist(\alpha_n(i_n), x_n) \leq 4\delta$. Then 
-  $\dist(\alpha_n(i_n), \alpha_{n+1}(i_{n+1})) \leq C_0 + 8\delta$. Then 
-  $\gromov{e}{\alpha_n(\infty)}{ \alpha_{n+1}(\infty)} \geq i_n - (C_0 + 
-  8\delta)/2$.
-
-  By the triangle inequality it follows that for $n\geq m$ we have the following 
-  inequality.
-  \begin{align*}
-    \vdistance(\alpha_n(\infty), \alpha_m(\infty)) \leq C_1 a^{-i_m}
-  \end{align*}
-  for some constants $C_1$ depending only on $\delta$ and $C_0$. Then, by
-  definition of the visual metric, there exists a constant $C_2$ such that
-  \begin{align*}
-    \gromov{e}{\alpha_n(\infty)}{\alpha_m(\infty)} \geq i_m - C_2.
-  \end{align*}
-
-  Now, by \cref{lem:boundary_gromov_product} there exists a constant $C_3$ such
-  that
-  \begin{align*}
-    \gromov{e}{\alpha_n(i_n)}{\alpha_m(i_m)} \geq i_m - C_3,\qedhere
-  \end{align*}
-  as required.
-\end{proof}
-
-\begin{lemma}\label{lem:linearproduct}
-  There is a constant $C$ such that if $x \in \Skel_{d+1} K_m$ then
-  \begin{align*}
-    \gromov{e}{i^m_n(x)}{x} \geq m - C
-  \end{align*}
-  for all $n\geq m\geq n_0$.
-\end{lemma}
-
-\begin{proof}
-  For $n \geq m$, let $y_n$ be a vertex of the minimal simplex of $K_n$
-  containing $i^m_n(x)$. Then, for each $n \geq m$, we have $\dist(e, y_{n+1})
-  = \dist(e, y_n)$.
-
-  We now bound the distance $\dist(y_n, y_{n+1}$. To start with, $\dist(y_n,
-  i^n_{n+1} y_n) \leq \epsilon$. Let $R$ be such that any two vertices in the
-  1-skeleton of $\sd^k \Delta^{d+1}$ are joined by a path traversing at most
-  $R$ edges. Let $\sigma$ be the minimal simplex of $K_n$ containing
-  $i^m_n(x)$. Then $y_n$ is a vertex of $\sigma$ and $y_{n+1}$ is a vertex of
-  the image of $\sigma$ under $i^n_{n+1}$, so $\dist(i^n_{n+1} y_n, y_{n+1})
-  \leq RD$.  Putting this together,
-  \begin{align*}
-      \dist(y_n, y_{n+1}) \leq \epsilon + RD
-  \end{align*}
-
-  It follows from \cref{lem:useful} that there exists a constant $C$ depending
-  only on $\delta$, $\epsilon$ and $k$ such that $\gromov{e}{y_n}{y_m} \geq m -
-  C$.
-
-  Finally, by applying the inequality in \cref{rem:dist_vs_newdist}, we deduce
-  that
-  \begin{align*}
-      \gromov{e}{i^m_n(x)}{x} \geq m - C - 3D.\qedhere
-  \end{align*}
-\end{proof}
-
-\begin{corollary}
-  For $m \geq n_0$ and $x \in \Skel_{d+1} K_m$, the sequence
-  $(i^m_n(x))_{n\geq m}$ converges to a point in $\boundary G$, which we shall
-  denote $i^m_\infty(x)$.
-\end{corollary}
-
-\begin{proof}
-  For $n_1$ and $n_2$ at least $m$, \cref{lem:linearproduct} implies that
-  $\gromov{e}{i^m_{n_1}(x)}{i^m_{n_2}(x)} \geq \min\{n_1,n_2\} - C$, which
-  tends to infinity as $n_1$ and $n_2$ tend to infinity.
-\end{proof}
-
-\begin{lemma}\label{lem:simplexproduct}
-  There is a constant $C$ such that if $m \geq n_0$ and $x$ and $y$ are in a
-  common simplex of $\Skel_{d+1} K_m$ then
-  \begin{align*}
-    \gromov{e}{i^m_n(x)}{i^m_n(y)} \geq m - C
-  \end{align*}
-  for all $n\geq m$.
-\end{lemma}
-
-\begin{proof}
-  The inequality of \cref{lem:linearproduct} is satisfied for each of $x$ 
-  and $y$. By~\cite{bridsonhaefliger99} there exist $\delta'$ depending only on 
-  $\delta$ such that
-  \begin{align*}
-    \gromov{e}{i^m_n(x)}{i^m_n(y)} &\geq \min\{\gromov{e}{i^m_n(x)}{x}, 
-    \gromov{e}{x}{y}, \gromov{e}{y}{i^m_n(y)}\} - 2\delta'\\
-    &\geq \min\{m - C, m - R/2, m - C\} - 2\delta' \\
-    &\geq m - C'
-  \end{align*}
-  for some constant $C'$.
-\end{proof}
-
-The following corollary immediately follows from \cref{lem:simplexproduct}.
-
-\begin{corollary}\label{cor:visualdiameter}
-  There is a constant $C$ such that for any $m\geq n_0$ and any simplex
-  $\sigma$ of $\Skel_{d+1} K_m$, the diameter of $i^m_{\infty}(\sigma)$ with
-  respect to the visual metric $\vdistance$ is bounded above by $Ca^{-m}$,
-  where $a$ is the visual parameter.
-\end{corollary}
-
-\begin{proposition}\label{prop:continuouslimit}
-  The map $i^m_\infty\from \Skel_{d+1} K_m \to \boundary G$ is continuous.
-\end{proposition}
-
-\begin{proof}
-  Fix $x \in \Skel_{d+1} K_m$. Let $k$ be the constant given in the definition 
-  of the map $i$. For $n\geq 0$ let $U_n$ be the star in $\beta^{nk} 
-  \Skel_{d+1}K_m$ of the minimal simplex of $\beta^{nk}\Skel_{d+1}K_m$ 
-  containing $x$. Then $U_n$ is a neighbourhood of $x$ for each $n$.
-
-  For each $n$, the restriction of $i^m_{m+n}$ to a simplex in 
-  $\beta^{nk}\Skel_{d+1}K_m$ is affine, and therefore has image contained in a 
-  simplex of $\Skel_{d+1} K_{m+n}$. The point $x$ is contained in every simplex 
-  of $U_n$, so for any $y \in U_n$ the points $i^m_{m+n}(x)$ and $i^m_{m+n}(y)$ 
-  are contained in a common simplex of $\Skel_{d+1}K_m$. Therefore, by 
-  \cref{cor:visualdiameter}, there is a constant $C$ such that 
-  $\vdistance(i^m_\infty(x), i^m_\infty(y)) \leq Ca^{-(m+n)}$ for every $y \in 
-  U_n$.
-\end{proof}
-
-\begin{remark}
-  In fact, if $K_m$ is endowed with a metric in which each simplex is 
-  isometrically identified with the standard simplex of the same dimension then 
-  the map $i^m_\infty$ can be shown to be H\"{o}lder continuous with exponent 
-  only depending on $\delta$ and the constants in the definition of the map $i$. 
-  We do not require this strengthening of \cref{prop:continuouslimit} 
-  here.
-\end{remark}
-
-Finally, we use the maps $i^n_\infty$ to construct homotopies between certain
-special maps to $\boundary G$.
-
-\begin{proposition}\label{prop:basic_homotopies}
-  Let $C$ be a constant. Then there exists a number $m_0$ and a function $\mu
-  \from \posreals\to\posreals$ such that $\mu(\eta)\to0$ as $\eta\to0$ with the following
-  property. Let $n \geq m_0$ and let $f_0$ and $f_1$ be any maps from
-  $\boundary\Delta^{d+1}$ to $K_n$ satisfying the following conditions:
-  \begin{enumerate}
-    \item the maps $f_0$ and $f_1$ are affine on some subdivision of
-      $\boundary\Delta^{d+1}$;
-    \item for any $x \in \boundary\Delta^{d+1}$, the distance 
-      $\newdist(f_0(x), f_1(x))$ is at most $C$;
-    \item each of $f_0$ and $f_1$ admits a factoring.
-  \end{enumerate}
-  Then there is a homotopy $h$ from $i^n_\infty\composed f_0$ to
-  $i^n_\infty\composed f_1$ satisfying a uniform continuity condition: for any
-  $x \in \boundary\Delta^{d+1}$ and any $s$ and $t$ in $[0,1]$,
-  \begin{align*}
-    \rho(h(x,s), h(x,t)) \leq \mu(\abs{s-t})a^{-n}.
-  \end{align*}
-\end{proposition}
-
-\begin{proof}
-  To start with, apply \cref{prop:extendingaffinemaps2} with $k = C + D$ to
-  obtain constants $k'$ and $m_0\geq n_0$ such that the conclusion of the
-  proposition holds.
-
-  Let $n \geq m_0$.  Let $J$ be a subdivision of $\boundary\Delta^{d+1}$ such
-  that $f_0$ and $f_1$ are both affine on $J$. Then the map 
-  \begin{align*}
-    f_0 \disjointunion f_1 \from J \times \{0\} \disjointunion J \times \{1\}
-          \to K_n,
-  \end{align*}
-  defined on a subset of the product simplicial complex $J \times [0,1]$,
-  satisfies the conditions of \cref{prop:extendingaffinemaps2}, and so admits
-  an affine extension $F \from \sd^{k'} (J \times [0,1]) \to K_n$. Let $h =
-  i^n_\infty \composed F$, so $h$ is a homotopy from $i^n_\infty\composed f_0$
-  to $i^n_\infty\composed f_1$ and it remains to prove the uniform continuity
-  assertion.
-
-  Let $\eta_0$ be such that for $\eta$ at most $\eta_0$, 
-  for any $x \in \Delta^d$, for any $s$ and $t$ in $[0,1]$ with
-  $\abs{s-t} \leq \eta$, the segment $\{x\} \times [s,t]$ is contained in a
-  union of at most two $(d+1)$-simplices of $\sd^{k'}(\Delta^d \times [0,1])$.
-  We first define the modulus of continuity $\mu(\eta)$ for $\eta > \eta_0$.
-
-  Let $M$ be the number of $(d+1)$-simplices in $\sd^{k'}(\Delta^d \times
-  [0,1])$.  \Cref{cor:visualdiameter} gives a constant $C_0$ such that any
-  $(d+1)$-simplex of $K_n$ is mapped to a subset of $\boundary G$ of diameter
-  at most $C_0 a^{-n}$, and so we can take $\mu(\eta) = C_0M$ for $\eta >
-  \eta_0$.
-
-  Now, for $\eta \leq \eta_0$, there exists a maximal number $\kappa(\eta) \geq
-  0$ such that for any $x \in \Delta^d$ and any $s$ and $t$ in $[0,1]$ with
-  $\abs{s-t} \leq \eta$, the segment $\{x\} \times [s,t]$ is contained in a
-  union of at most two $(d+1)$-simplices of
-  $\sd^{\kappa(\eta)}\sd^{k'}(\Delta^d\times[0,1])$. Note that $\kappa(\eta)
-  \to \infty$ as $\eta \to 0$. Now, if $N\in\naturals$ then a $(d+1)$-simplex of
-  $\sd^{k^N}K_n$ is mapped by $i^n_{n+N}$ into a $(d+1)$-simplex of $K_{n+N}$,
-  which is mapped by $i^{n+N}_\infty$ to a set of diameter at most
-  $C_0a^{-n+N}$. Therefore, if $N$ is such that $\kappa(\eta) \geq k^N$ then
-  for $x \in \boundary\Delta^{d+1}$ and $\abs{s-t} < \eta$, $\rho(h(x,s),
-  h(x,t)) \leq 2C_0a^{-n-N}$. It follows that we may take $\mu(\eta)$ as follows:
-  \begin{align*}
-    \mu(\eta) = 2C_0 a^{-\floor*{\frac{\log\kappa(\eta)}{\log k}}}.\qedhere
-  \end{align*}
-\end{proof}
-
-\subsection{Proving \Cref{thm:ddagimpliesLCd}}
-
-We now use the maps $(i^n_{n+1})$ to prove \cref{thm:ddagimpliesLCd}. We begin
-with two lemmas.
-
-\begin{lemma}\label{lem:convergestoidentity}
-  There is a constant $C$ such that the distance from $(i^m_\infty \composed 
-  p^\infty_m)$ to the identity map $\boundary G\to\boundary G$ is at most 
-  $Ca^{-m}$ for each $m$, where $a$ is the visual parameter.
-\end{lemma}
-
-\begin{proof}
-  Let $\xi \in \boundary G$. By \cref{lem:linearproduct} there is a 
-  constant $C$ such that 
-  \begin{align*}
-    \gromov{e}{i^m_n\composed p^\infty_m(\xi)}{p^\infty_m(\xi)} \geq m - C
-  \end{align*} 
-  for each $n\geq m\geq n_0$.
-
-  Let $\alpha$ be a geodesic ray with $\alpha(0) = e$ and $\alpha(\infty) = 
-  \xi$. Then $\alpha(m)$ is a vertex of a simplex in $\Skel_{d+1}K_m$ containing 
-  $p^\infty_m(\xi)$, and $\gromov{e}{\alpha(m)}{\alpha(n)} = m$ for $n\geq m$.
-  It follows that there is a constant $\delta'$ depending only on $\delta$ such 
-  that
-  \begin{align*}
-    \mathrlap{\gromov{e}{\alpha(n)}{i^m_n\composed p^\infty_m(\xi)}}\quad\quad &\\
-          & \geq \min\{\gromov{e}{\alpha(n)}{\alpha(m)}, 
-            \gromov{e}{\alpha(m)}{p^\infty_m(\xi)}, 
-            \gromov{e}{p^\infty_m(\xi)}{i^m_n\composed p^\infty_m(\xi)}\} 
-            - 2\delta' \\
-          &\geq \min\{m - C, m - R/2, m\} - 2\delta' \\
-          &\geq m - C'
-  \end{align*}
-  for some constant $C'$.
-
-  Therefore $\gromov{e}{\xi}{i^m_\infty\composed p^\infty_m(\xi)} \geq m - C'$, 
-  from which the claim follows.
-\end{proof}
-
-\begin{lemma}\label{lem:name_this}
-  There is a number $C$ such that, for any $\xi \in \boundary G$ and any $n
-  \geq 0$ and any vertices $x_1$ and $x_2$ of the minimal simplices containing
-  $i^n_{n+1}\composed p^\infty_n(\xi)$ and $p^\infty_{n+1}(\xi)$ respectively,
-  \begin{align*}
-    \dist(x_1, x_2) \leq C.
-  \end{align*}
-\end{lemma}
-
-\begin{proof}
-  By \cref{lem:close_projections} the distances $\newdist(p^\infty_n(\xi),
-  p^\infty_{n+1}(\xi))$ are bounded by $6\delta + 3 + 2D$. Let $y$ be a vertex
-  of a simplex containing $p^\infty_n(\xi)$; then $\newdist(y, p^\infty_n(\xi))$
-  is bounded by $D$.
-
-  Furthermore, $\dist(y, i^n_{n+1}(y))$ is uniformly bounded by the constant
-  $\epsilon$ from \cref{prop:ddag_implies_i}, and $\newdist(i^n_{n+1}(y),
-  i^n_{n+1}\composed p^\infty_n (\xi))$ is bounded by the product of $D$ and
-  the constant $k$ appearing in \cref{prop:ddag_implies_i}. By putting all this
-  together we obtain a bound $C$ on $\newdist(i^n_{n+1}\composed
-  p^\infty_n(\xi), p^\infty_{n+1}(\xi))$, and then $\dist(x_1, x_2) \leq C +
-  2D$.
-\end{proof}
-
-\begin{proposition}\label{prop:uniform_homotopies}
-  There exists a number $m_0$ and a function $\nu\from\posreals\to\posreals$ such
-  that $\nu(\eta)\to0$ as $\eta\to0$ with the following property. Let
-  $\gamma\from\boundary\Delta^{d+1}\to\boundary G$ be a continuous map. Let $n
-  \geq m_0$ and let $f$ be an affine approximation to
-  $p^\infty_n\composed\gamma$. Then there is a homotopy $h$ from $\gamma$ to
-  $i^n_\infty\composed f$ such that for any $x \in \boundary\Delta^{d+1}$ and
-  any $s$ and $t$ in $[0,1]$,
-  \begin{align*}
-    \rho(h(x,s), h(x,t)) \leq \nu(\abs{s-t}) a^{-n}.
-  \end{align*}
-\end{proposition}
-
-\begin{proof}
-  Let $C$ be as in \cref{lem:name_this} and apply \cref{prop:basic_homotopies}
-  to obtain a number $m_0\geq n_0$ and a function $\mu$.
-
-  Let $\gamma\from\boundary\Delta^{d+1}\to\boundary G$, $n\geq m_0$ and
-  $f\from\boundary\Delta^{d+1}\to K_n$ be as in the proposition. Let $f_0 = f$,
-  and for $m > 0$ let $f_m\from\boundary\Delta^{d+1}\to K_{n+m}$ be a
-  simplicial approximation to $p^\infty_{n+m}\composed\gamma$. For $m \geq 0$
-  let $\gamma_m = i^{m+n}_\infty\composed f_m$. For each $m\geq 0$ the
-  following observations are immediate:
-  \begin{enumerate}
-    \item the map $f_m$ admits a factoring;
-    \item the image of $f_m$ is contained in the $d$-skeleton of $K_{n+m}$, and
-      so $i^{n+m}_{n+m+1}\composed f_m$ admits a factoring;
-    \item by \cref{lem:name_this} we have $\newdist(i^{n+m}_{n+m+1}\composed
-      f_m(x), f_{m+1}(x)) \leq C$ for all $x \in \boundary\Delta^{d+1}$.
-  \end{enumerate}
-  Therefore, for each $m$, \cref{prop:basic_homotopies} gives a homotopy $h_m$
-  from $i^{n+m+1}_\infty\composed f_{m+1}$ to $i^{n+m}_\infty \composed f_m$
-  satisfying a uniform continuity condition. Define an infinite concatenation
-  of these homotopies:
-  \begin{align*}
-    h(x,t) = 
-    \begin{cases}
-      \gamma(x) & \text{if } t = 0\\
-      h_n\left(x,2^{m+1}\left(t-\frac{1}{2^{m+1}}\right)\right) 
-              & \text{if $t \in \left[\frac{1}{2^{m+1}}, \frac{1}{2^m}\right]$
-                    , $m\geq 0$}.
-    \end{cases}
-  \end{align*}
-  This function is clearly continuous except possibly on
-  $\boundary\Delta^{d+1}\times\{0\}$. We aim to show it is also continuous
-  there, but first we define the function $\nu$.
-
-  Let $m \in \naturals$. We aim to bound the distance $\rho(h(x,s), h(x,t))$
-  for $\abs{s,t} \leq 2^{-m}$ independently of $n$ and the particular path
-  $\gamma$. We first treat the case when one of $s$ and $t$ is $0$, then we
-  deal with the case when $s$ and $t$ are small, and finally we treat the case
-  when $s$ and $t$ are large. (Our ``small'' and ``large'' regions intersect,
-  to guarantee that this covers all possibilities.)
-
-  To begin, we bound the distance $\rho(h(x,0), h(x,t))$
-  where $x \in \boundary \Delta^{d+1}$ and $t < 2^{-m}$. Let $C'$ be the
-  constant appearing in \cref{lem:convergestoidentity}. Then 
-  \begin{align*}
-    \rho(h(x,0), h(x,2^{-m})) \leq C'a^{-m-n}.
-  \end{align*}
-  Furthermore, for any $m' \in \naturals$ and any $t \in [2^{-m'-1}, 2^{-m'}]$,
-  \begin{align*}
-    \rho(h(x,t), h(x,2^{-m'})) \leq \mu(1)a^{-m'-n}.
-  \end{align*}
-  It follows that for $t \leq 2^{-m}$,
-  \begin{align*}
-    \rho(h(x,0), h(x,t)) \leq a^{-n}\left(C'a^{-m} + \sum_{m' \geq m}
-          \mu(1)a^{-m'}\right).
-  \end{align*}
-
-  Similarly, we treat the ``small'' case. Here $s$ and $t$ are \emph{small} if
-  they are at most $2^{-m/2}$. If $s$ and $t$ are both at most this large
-  then
-  \begin{align*}
-    \rho(h(x,s), h(x,t)) \leq a^{-n} \sum_{m' \geq \floor{m/2}} \mu(1) a^{-m'}
-  \end{align*}
-
-  Finally, if $s$ and $t$ are such that $\abs{s-t} \leq 2^{-m}$ but at least
-  one of $s$ and $t$ is greater than $2^{-m/2}$ then both $s$ and $t$ are at
-  least $2^{-m/2}$. This is the ``large'' case. It follows that 
-  \begin{align*}
-    \rho(h(x,s), h(x,t)) &\leq a^{-n} \mu(\abs{s-t} 2^{m/2 + 1}) \\
-                         &\leq a^{-n} \mu(2^{1-m/2})
-  \end{align*}
-
-  Therefore for $\eta \in (2^{-m-1}, 2^{-m}]$ we define
-  \begin{align*}
-    \nu(\eta)  = \max\left\{
-      C'a^{-m} + \sum_{m' \geq m} \mu(1)a^{-m'},
-      \sum_{m' \geq \floor{m/2}} \mu(1) a^{-m'},
-      \mu(2^{1-m/2})
-    \right\},
-  \end{align*}
-  and we see that $\nu(\eta) \to 0$ as $\eta \to 0$, and also that
-  \begin{align*}
-    \rho(h(x,s), h(x,t)) \leq \nu(\abs{s-t})
-  \end{align*}
-  for any $x \in \boundary\Delta^{d+1}$ and $s$ and $t$ in $[0,1]$.
-
-  It remains to show that $h$ is continuous at $(x,0)$ for each $x$ in
-  $\boundary\Delta^{d+1}$. Let $\epsilon > 0$ and take a neighbourhood $U$ of
-  $x$ in $\boundary\Delta^{d+1}$ such that $\rho(\gamma(x), \gamma(y)) \leq
-  \epsilon/2$ for $y$ in $U$. Let $\eta > 0$ be so that $\nu(\eta) <
-  \epsilon/2$. Then for any $(y, t) \in U \times [0, \eta]$, $\rho(h(x,0),
-  h(y,t)) < \epsilon$.
-\end{proof}
-
-\Cref{thm:ddagimpliesLCd} follows as a corollary of this proposition.
-
-\ddagimpliesLCd*
-
-\begin{proof}
-  To begin, let $\nu$ and $m_0 \geq n_0$ be as in
-  \cref{prop:uniform_homotopies}. Let $r_0 =
-  k_1a^{-m_0}$, so that, by \cref{lem:projectstoasimplex},
-  $p^\infty_{m_0}\composed\gamma$ has image contained in the star of a single
-  vertex of $K_{m_0}$ for any map $\gamma\from\boundary\Delta^{d+1}\to\boundary
-  G$ with $\Diam\image(\gamma)\leq r_0$.
-
-  Let $\gamma\from\boundary\Delta^{d+1}\to\boundary G$ be such a map. Let 
-  \begin{align*}
-    m = \floor{\log_a(k_1/\Diam\image\gamma)} \geq m_0,
-  \end{align*}
-  so that by \cref{lem:projectstoasimplex} $p^\infty_{m}\composed\gamma$ has
-  image contained in a single vertex of $K_m$. Then a constant map
-  $\boundary\Delta^{d+1} \to K_m$ is a simplicial approximation to
-  $p^\infty_m\composed\gamma$; applying \cref{prop:uniform_homotopies} to
-  this map immediately gives a homotopy $h$ from $\gamma$ to the constant map.
-
-  Furthermore,
-  \begin{align*}
-    \Diam\image h &\leq \Diam\image\gamma + \sup_{x \in\boundary\Delta^{d+1}, s,t \in [0,1]} \rho(h(x,s), h(x,t)) \\
-                  &\leq \Diam\image\gamma + a^{-m} \nu(1) \\
-                  &\leq (1 + a\nu(1)/k_1) \Diam\image\gamma \qedhere
-  \end{align*}
-\end{proof}
-
-\section{Criteria for $\dd{d}$ and $\Sd{d}$}\label{sec:dd}
-
-In this section we establish sufficient conditions for $\dd{d}$ and $\Sd{d}$ to 
-hold.
-
-\subsection{A criterion for $\dd{d}$}
-
-This section is devoted to the proof of the following theorem.
-
-\begin{theorem}\label{thm:nocutpointimpliesdagger}
-  Suppose that $\boundary G - \set\xi$ is $\C{d}$ for any $\xi \in \boundary G$. 
-  Then $G$ satisfies $\dd{d+1}$.
-\end{theorem}
-
-\begin{proof}
-
-Suppose that the conclusion of \cref{thm:nocutpointimpliesdagger} 
-does not hold. Then there exists a number $k$, a sequence of affine maps 
-$f_i\from\sd^k\boundary\Delta^{d+1}\to K_{n_i}$ and a sequence of continuous 
-maps $\gamma_i\from\boundary\Delta^{d+1}\to\boundary G$ satisfying the following 
-conditions.
-\begin{enumerate}
-  \item For each $i$, $(\sd^k\boundary\Delta^{d+1}, f_i, \gamma_i)_{n_i}$ is a 
-    factored triple.
-  \item There is no affine extension of $f_i$ to $\sd^i\Delta^{d+1}$.
-  \item The sequence $n_i$ tends to infinity as $i$ tends to infinity.
-\end{enumerate}
-
-By passing to a subsequence, we may assume that the sequence $(f_i)$ has the 
-following properties, where we denote by $J$ the simplicial complex 
-$\sd^k\boundary\Delta^{d+1}$.
-\begin{enumerate}
-  \item There exist group elements $g_i$ such that $g_i(f_i(v)) = g_j(f_j(v))$ 
-    for all $i$ and $j$ and for all $v \in \Vertices(J)$.
-  \item Large neighbourhoods of translates by $g_i$ of the images of the vertex 
-    set of $J$ under $f_i$ are identical: we have the following equality for all 
-    $i$ and $j$:
-    \begin{align*}
-      g_i\left(N_{\min\set{i,j}}\left(f_i(\Vertices(J))\right) \intersection 
-      S_{n_i}\right) = g_j\left(N_{\min\set{i,j}}\left(f_j(\Vertices(J))\right) 
-      \intersection S_{n_j}\right).
-    \end{align*}
-  \item The restrictions of the pullbacks $g_i^\star\dist$ and 
-    $g_j^\star\dist$ of the distance function to the vertex set of this 
-    simplicial complex agree.
-  \item The sequence $g_i = g_i\cdot 1$ of vertices of $K$ converges to a point 
-    $\xi\in\boundary G$ as $i\to\infty$.
-\end{enumerate}
-
-\begin{definition}
-  Let $H_i$ be the full subcomplex of $K_{n_i}$ with vertex set
-  \begin{align*}
-    g_i\left(N_i\left(f_i(\Vertices (J))\right)\intersection S_{n_i}\right).
-  \end{align*}
-  Note that $H_i$ contains $H_j$ for $i \geq j$. It will be convenient to pass 
-  to a further subsequence such that for each $i$ the complex $H_{i+1}$ contains 
-  all vertices of $g_i(S_{n_i})$ adjacent to $H_i$. Let $H$ be the direct
-  limit of the complexes $H_i$.  We view $H$ as a horosphere, the topology of
-  which approximates that of $\boundary G - \set\xi$.
-  \cref{lem:geodesicsmeethorosphere}--\ref{lem:propermaps} below justify 
-  this point of view.
-
-  All of the maps $g_i \composed f_i \from J \to H$ are equal; call this map
-  $f$. 
-\end{definition}
-
-\begin{lemma}\label{lem:geodesicsmeethorosphere}
-  Every bi-infinite geodesic with $\xi$ in its limit set meets $H$.
-\end{lemma}
-
-\begin{proof}
-  Let $\alpha$ be a bi-infinite geodesic with $\xi$ as a limit pint. Pick a
-  point $w \in f(\Vertices(J))$ and let the distance $\dist(w,\alpha)$ be
-  realised by a point $x \in \alpha$.
-
-  The points $g_i$ converge to $\xi$ as $i\to\infty$, so the distances
-  $\dist(x, [\xi, g_i])$ tend to infinity as $i$ tends to infinity. The
-  triangle with vertices $x$, $\xi$ and $g_i$ is $\delta$-slim, so for each $i$
-  there exists a point $y_i$ on $[x, g_i]$ with $\dist(y_i, \alpha) \leq
-  \delta$ and $y_i\to\xi$ as $i\to\infty$.  For each $i$ let $z_i$ be a point
-  on $\alpha$ with $\dist(y_i, z_i) \delta$.
-
-  Since $\dist(g_i, x) = n_i$ for $i$ sufficiently large and $\dist(x,y_i) \to
-  \infty$ as $i\to\infty$, we have the following limit.
-  \begin{align*}\label{eqn:zi_closer_to_gi_than_x}
-    \dist(g_i,z_i) - n_i &\leq \dist(g_i,y_i) + \delta - n_i \text{ for $i$
-                                        sufficiently large} \\
-                         &= - \dist(x,y_i) + \delta \\
-                         &\to -\infty\text{ as $i \to \infty$} \tag{$\star$}
-  \end{align*}
-  Therefore, for $i$ sufficiently large, there exists a point $p_i$ on $\alpha$
-  such that $z_i$ lies between $\xi$ and $p_i$ on $\alpha$ and so that
-  $\dist(g_i,p_i)=n_i$. We now show that $\dist(p_i, x)$ is uniformly bounded.
-
-  The limit~\eqref{eqn:zi_closer_to_gi_than_x}, taken together with the fact
-  that $\dist(g_i, x) = \dist(g_i, p_i) = n_i$, shows that the distances
-  $\dist([z_i, g_i], x)$ and $\dist([z_i, g_i], p_i)$ tend to infinity as
-  $i\to\infty$.  We now divide into cases according to which of $x$ and $p_i$
-  is closer to $z_i$.
-  \begin{enumerate}
-    \item If $x$ is between $z_i$ and $p_i$ on $\alpha$ then by considering a
-      geodesic triangle with vertices $g_i$, $z_i$ and $p_i$ we see that for
-      $i$ sufficiently large, $x$ is within a distance $\delta$ of a point
-      $q_i$ on the geodesic from $g_i$ to $p_i$.  Therefore,
-      \begin{align*}
-        \dist(g_i,x)&\leq \dist(g_i,q_i)+\delta\\
-                        &\leq \dist(g_i,p_i)-\dist(p_i,q_i)+\delta\\
-                        &\leq \dist(g_i,p_i)-\dist(x,p_i)+2\delta.
-      \end{align*}
-      It follows that $\dist(x,p_i) \leq \dist(g_i,p_i)-\dist(g_i,x)+2\delta
-      = 2\delta$.
-    \item If $p_i$ is between $z_i$ and $x$ on $\alpha$ then by an identical 
-      argument with the r\^oles of $x$ and $p_i$ reversed we can similarly 
-      deduce that 
-      \begin{align*}
-        \dist(x,p_i)\leq\dist(g_i,x) - \dist(g_i,p_i) + 2\delta =2\delta.
-      \end{align*}
-  \end{enumerate}
-
-  Either way, $\dist(w, p_i) \leq \dist(x,w) + 2\delta$. In summary, we have
-  shown that for $i$ sufficiently large there is a point $p_i\in\alpha$ with
-  $\dist(g_i,p_i)=n_i$ and $\dist(p_i,f(\Vertices J))$ bounded by $\dist(x,w) +
-  2\delta$. Then $p_i \in H_i$ whenever $i$ is at least $\dist(x,w) + 2\delta$.
-\end{proof}
-
-\begin{lemma}\label{lem:boundedintersection}
-  Let $C$ be a compact subset of $\boundary G - \set\xi$. Then the set of points 
-  of intersection between $H$ and bi-infinite geodesics with one end point equal 
-  to $\xi$ and the other in $C$ is bounded.
-\end{lemma}
-
-\begin{proof}
-  Let $\alpha$ be any bi-infinite geodesic with $\alpha(-\infty)=\xi$ and 
-  $\alpha(\infty)\in C$. Let $x \in \alpha \intersection H$. Since $C$ is
-  compact, there exists a point $v \in \alpha$, between $\xi$ and $x$ on
-  $\alpha$, such for that any bi-infinite geodesic $\beta$ with
-  $\beta(-\infty)$ in $C$ and $\beta(\infty) = \alpha(\infty)$, $\beta$ does
-  not meet the $100\delta$-neighbourhood of the sub-ray of $\alpha$ between
-  $\xi$ and $v$: otherwise a limiting argument shows that $\xi$ is in $C$.
-
-  Since $g_i \to \xi$, the distance $\dist(v, [\xi, g_i]) \to \infty$ as
-  $i\to\infty$. The triangle with vertices $\xi$, $g_i$ and $x$ is
-  $\delta$-slim, so the geodesic path from $g_i$ to $x$ passes within a
-  distance $\delta$ of $v$ for $i$ large enough. Therefore, since $\dist(g_i,
-  x) = n_i$ for $i$ large enough, the following inequality holds for all $i$
-  large enough.
-  \begin{align*}
-    0 \leq \dist(g_i, v) + \dist(v, x) - n_i \leq 2\delta.
-  \end{align*}
-
-  Let $\alpha'$ be a bi-infinite geodesic with $\alpha'(-\infty) = \xi$ and
-  $\alpha'(\infty) \in C$ and let $x' \in \alpha' \intersection H$. The ideal
-  triangle with vertices $\xi$, $\alpha(\infty)$ and $\alpha'(\infty)$ is
-  $\delta$-slim, so the subray of $\alpha$ between $\xi$ and $v$ is contained
-  in a $\delta$-neighbourhood of $\alpha'$.  Let $v' \in \alpha'$ be a point
-  with $\dist(v, v') \leq \delta$.
-
-  We split into cases according to the order of $\xi$, $v'$ and $x'$ on
-  $\alpha'$.
-  \begin{enumerate}
-    \item
-      First we suppose that $v'$ is between $x'$ and $\xi$ on $\alpha'$. Then as
-      in the argument above, for $i$ sufficiently large we have the following
-      inequality:
-      \begin{align*}
-        0 \leq \dist(g_i, v') + \dist(v', x') - n_i \leq 2\delta.
-      \end{align*}
-      And therefore,
-      \begin{align*}
-        -2\delta \leq \dist(g_i, v) + \dist(v, x') - n_i \leq 4\delta.
-      \end{align*}
-      Finally, putting these inequalities together,
-      \begin{align*}
-        \dist(v,x') \leq \dist(v,x) + 4\delta,
-      \end{align*}
-      and thus we can uniformly bound this distance in this case.
-    \item
-      Alternatively, $x'$ is between $v'$ and $\xi$ on $\alpha'$ and so (since
-      the triangle with vertices $\xi$, $v$ and $v'$ is $\delta$-slim) $x'$ is
-      within a distance $2\delta$ of the geodesic ray from $x$ to $\xi$. By
-      considering the triangle with vertices $\xi$, $g_i$ and $x$ for $i$ large
-      enough, a geodesic segment from $g_i$ to $x$ passes within a distance
-      $3\delta$ of $x'$. Therefore we have the following inequality for all $i$
-      sufficiently large:
-      \begin{align*}
-        0 \leq \dist(g_i, x') + \dist(x', x) - \dist(g_i, x) \leq 6\delta.
-      \end{align*}
-      Finally, for $i$ sufficiently large, $\dist(g_i, x') = \dist(g_i, x) = n_i$,
-      so
-      \begin{align*}
-        \dist(x,x') \leq 6\delta.
-      \end{align*}
-  \end{enumerate}
-\end{proof}
-
-\begin{definition}
-  Let $U_i \subset \boundary G$ be the (closed) preimage of $H_i$ under the map 
-  $g_i \composed p^\infty_{n_i} \composed g_i^{-1} \from \boundary G \to X$.
-  Denote by $q_i$ the restriction of this map to $U_i$.
-\end{definition}
-
-The following lemma is immediate from the definition of $p^\infty_i$.
-
-\begin{lemma}\label{lem:describing_q_i}\todo{Check this}
-  Let $\zeta \in \boundary G - \set\xi$ and suppose that $q_i(\zeta) \in H_i$
-  is defined, so $\zeta \in U_i$, and $N_{4\delta+1} q_i(\zeta) \in H_i$. Then
-  $q_i(\zeta)$ is contained in the minimal simplex of $H_i$ with vertex set
-  \begin{align*}
-    N_{2\delta+1} \set{\eta(n_i)\suchthat\text{$\eta$ a geodesic ray with
-    $\eta(0) = g_i$ and $\eta(\infty) = \zeta$}}.
-  \end{align*}\qed
-\end{lemma}
-
-\begin{lemma}
-  Every compact subset of $\boundary G - \set\xi$ is contained in $U_i$ for 
-  $i$ sufficiently large.
-\end{lemma}
-
-\begin{proof}
-  Suppose that a compact subset $C$ of $\boundary G - \set\xi$ is not contained
-  in $U_i$ for infinitely many $i$. Then after passing to a subsequence there
-  exists for each $i$ a point $\zeta_i \in C\setminus U_i$.
-
-  By assumption, $g_i^{-1}(H_i)$ contains the star in $K_{n_i}$ of 
-  $g_i^{-1}(H_{i-1})$, so the definition of $p^\infty_{n_i}$ implies that a 
-  geodesic ray $\alpha_i$ from $e$ to $g_i^{-1}(\zeta_i)$ does not pass through 
-  $g_i^{-1}(H_{i-1})$. Equivalently, $g_i\composed\alpha_i$ is a geodesic from 
-  $g_i$ to $\zeta_i$ that does not pass through $H_{i-1}$.
-
-  After reparameterising and passing to a subsequence, the geodesic rays
-  $g_i\composed\alpha_i$ converge uniformly on compact subsets to a bi-infinite
-  geodesic from $\xi$ to some point $\zeta \in C$.  This geodesic does not pass
-  through $H$, which contradicts \cref{lem:geodesicsmeethorosphere}.
-\end{proof}
-
-\begin{lemma}\label{lem:affinehomotopic}
-  For any compact subset $C\subset\boundary G - \set\xi$, there exists $i_0$ 
-  such that for all $i \geq i_0$ and any $\zeta \in C$, $\newdist(q_i(\zeta),
-  q_{i_0}(\zeta)) \leq 8\delta + 2$, and, in particular, $q_i\restricted{C}$
-  and $q_{i_0}\restricted{C}$ are related by an affine homotopy.
-\end{lemma}
-
-\begin{proof}
-  Let $B\subset H$ be a bounded set containing all points where geodesics with
-  one limit point equal to $\xi$ and the other in $C$ meet $H$; this set exists
-  by \cref{lem:boundedintersection}.
-
-  Fix $\alpha$ to be some geodesic with $\alpha(-\infty)=\xi$ and
-  $\alpha(\infty)\in C$ and let $x$ be a point of intersection between $\alpha$
-  and $B$. Since the triangle with vertcies $x$, $g_i$ and $\xi$ is
-  $\delta$-slim, and $\dist(x, [\xi, g_i]) \to \infty$ as $i\to\infty$, for
-  each $i$ there exists a point $y_i$ on $[g_i, x]$ with $\dist(y_i, \alpha)
-  \leq \delta$ and so that $y_i \to \xi$ as $i\to\infty$. Let $z_i \in \alpha$
-  be such that $\dist(y_i, z_i)\leq\delta$.
-
-  Now fix $i_0$ such that the following conditions hold for all $i\geq 
-  i_0$.
-  \begin{enumerate}
-    \item The distance $\dist(y_i,x)$ is greater than $7\delta + \Diam B$.
-    \item The set $C$ is contained in $U_i$.
-  \end{enumerate}
-
-  Let $\zeta \in C$ and let $\alpha'$ be a geodesic from $\xi$ to $\zeta$. Let 
-  $x'$ be a point in the intersection of $\alpha'$ and $B$.
-
-  Now let $i\geq i_0$. Then by considering the ideal triangle with vertices
-  $g_i$, $x$ and $x'$, and using the fact that $\dist(y_i, x) > \delta + \Diam
-  B$, we deduce that there exists a point $y_i'$ on $[x', g_i]$ with
-  $\dist(y_i, y_i') \leq \delta$.
-
-  Similarly, since $\dist(z_i, x) > \delta + \Diam B$, consideration of the
-  triangle with vertices $\xi$, $x$ and $x'$ reveals that there exists a point
-  $z_i'$ on $\alpha'$ between $\xi$ and $x'$ with $\dist(z_i, z_i') \leq
-  \delta$. Then $\dist(y_i', z_i') \leq 3\delta$.
-
-  Since $\dist(z_i', x') > 2\delta$, the distance from $y_i'$ to the subray of
-  $\alpha'$ from $x'$ to $\zeta$ is greater than $\delta$. Therefore by
-  considering a triangle with vertices $g_i$, $x'$ and $\zeta$ we see that
-  there exists a point $v_i$ on a geodesic ray $\eta_i$ from $g_i$ to $\zeta$
-  with $\dist(v_i, y_i') \leq \delta$. It follows that $\dist(v_i, z_i') \leq
-  4\delta$, and we know that $\dist(x', z_i') > 5\delta$, so $\dist(x', [z_i',
-  v_i]) > \delta$ and therefore $\dist(x', \eta_i) \leq \delta$.
-
-  In summary, any geodesic ray from $g_i$ to $\zeta$ passes within a distance 
-  $\delta$ of $x'$, for $i\geq i_0$. Furthermore, $\dist(g_i,x') = n_i$, so 
-  $\dist(\eta_i(n_i), x')\leq 2\delta$. It follows from the description of
-  $q_i$ in \cref{lem:describing_q_i} that $q_i(\zeta)$ is contained in a
-  simplex with all vertices within a distance $4\delta+1$ of $x'$. The set of
-  all such vertices spans a simplex, so, in particular, $q_i\restricted{C}$ and
-  $q_{i_0}\restricted{C}$ are related by an affine homotopy for $i \geq i_0$. 
-\end{proof}
-
-\begin{lemma}\label{lem:propermaps} 
-  For any compact subset $C \subset H$ there exists $i_0$ such that
-  \begin{align*}
-    \bigunion_{i\geq i_0} q_i^{-1} C
-  \end{align*}
-  is a relatively compact subset of $\boundary G - \set\xi$.
-\end{lemma}
-
-\begin{proof}
-  If not then there exists a sequence $\zeta_i$ of points with $\zeta_i \in U_i$ 
-  for all $i$ such that $q_i(\zeta_i) \in C$ for all $i$ and $\zeta_i \to \xi$ 
-  as $i \to \infty$.
-
-  Then for each $i$ a geodesic from $g_i$ to $\zeta_i$ passes through the star 
-  in $H$ of $C$.  After passing to a subsequence these geodesic rays converge to 
-  a bi-infinite geodesic passing through the star in $H$ of $C$, both end points 
-  of which must be $\xi$, which is a contradiction.
-\end{proof}
-
-Since $f$ is related by an affine homotopy to $q_i\composed g_i\composed
-\gamma_i$ for every $i$, for each $i$ the image of $g_i\composed\gamma_i$ is
-contained in $q_i^{-1} H_1$. By \cref{lem:propermaps} there exists $i_0$ and a
-compact subset $C_0 \subset \boundary G - \set\xi$ such that the image of
-$g_i\composed\gamma_i$ is contained in $C_0$ for $i\geq i_0$. By
-\cref{lem:affinehomotopic} we can choose $i_1 \geq i_0$ such that
-$q_i\restricted{C_0}$ is affine homotopic to $q_{i_1}\restricted{C_0}$ for
-$i\geq i_1$.
-
-Let $\gamma = g_{i_1}\composed\gamma_{i_1}$ and let $h \from
-\Delta^{d+1}\to\boundary G - \set\xi$ be a continuous extension of $\gamma$;
-this exists since $\boundary G - \set\xi$ is $\C{d}$. Let $C_1 \supset C_0$ be
-a compact subset of $\boundary G - \set\xi$ containing the image of $h$ and let
-$i_2 \geq i_1$ be chosen so that $C_1 \subset U_{i_2}$.
-
-Then $q_{i_2}\composed h$ has image in $H_{i_2}$. Furthermore,
-$q_{i_2}\composed h\restricted{\boundary\Delta^{d+1}} = q_{i_2}\composed
-\gamma$ is related by an affine homotopy in $H_{i_2}$ to
-$q_{i_1}\composed\gamma$, which is related by an affine homotopy to the affine
-map $f$. Therefore $f$ is null-homotopic in $H_{i_2}$, and so by the Relative
-Simplicial Approximation theorem~\cite{zeeman64} there is a number $k'$ and an
-affine extension $h'\from\sd^{k'}\to H_{i_2}$ of $f$.
-
-Then, for $i \geq i_2$ the map $g_i^{-1}\composed
-h'\from\sd^{k'}\Delta^{d+1}\to K_{n_i}$ is an affine extension of $f_i$, which
-contradicts the choice of maps $f_i$ if $i > k'$.
-
-This completes the proof of \cref{thm:nocutpointimpliesdagger}.
-\end{proof}
-
-\subsection{Strengthening the condition: $\Sd{d}$}
-
-We now strengthen the conclusion of \cref{thm:nocutpointimpliesdagger} 
-under the assumption that $\boundary G$ is $\lLC{d}$:
-
-\begin{theorem}\label{thm:lLCandnocutpointimpliesS}
-  Suppose that $\boundary G - \set\xi$ is $\C{d}$ for any $\xi \in \boundary G$ 
-  and that $\boundary G$ is $\lLC{d}$. Then $G$ satisfies $\Sd{d+1}$.
-\end{theorem}
-
-\begin{proof}
-
-does not hold, and therefore there exists a number $k$, a sequence of affine 
-maps $f_i\from \sd^k\boundary\Delta^{d+1}\to K_{n_i}$ and a sequence of 
-continuous maps $\gamma_i\from \boundary\Delta^{d+1}\to\boundary G$ satisfying 
-the following (modified) conditions.
-\begin{enumerate}
-  \item For each $i$, $(\sd^k\boundary\Delta^{d+1},\gamma_i,f_i)_{n_i}$ if a 
-    factored triple.
-  \item There is no pair $(F_i, \Gamma_i)$ where $F_i$ is an affine extension of 
-    $f_i$ to $\sd^i\Delta^{d+1}$, $\Gamma_i$ is a continuous extension of 
-    $\gamma_i$ to $\Delta^{d+1}$, and 
-    $(\sd^i\boundary\Delta^{d+1},\Gamma_i,F_i)_{n_i}$ is a factored triple.
-  \item The sequence $n_i$ tends to infinity as $i$ tends to infinity.
-\end{enumerate}
-
-As in the proof of \cref{thm:nocutpointimpliesdagger} we pass to a 
-subsequence and define complexes $H_i$ and $H$, subsets $U_i = (g_i\composed 
-p^\infty_{n_i}\composed g_i^{-1})^{-1} H_i\subset \boundary G 
-- \set\xi$ and maps $q_i = g_i\composed p^\infty_{n_i}\composed 
-g_i^{-1}\restricted{U_i}\from U_i\to H_i$. Then 
-\cref{lem:geodesicsmeethorosphere}--\ref{lem:propermaps} apply to these maps
-and spaces as in \cref{thm:nocutpointimpliesdagger} without modification.
-
-It is now sufficient to prove the following claim.
-
-\begin{claim} 
-  There is a number $k$ such that, for infinitely many $i$, there is an 
-  extension of $\gamma_i$ to $\sd^k\Delta^{d+1}$ whose composition with 
-  $p^\infty_{n_i}$ is affine.
-\end{claim}
-
-Let $C_0$ be a compact subset of $\boundary G - \set\xi$ and $i_0$ be an
-integer such that $g_i\composed\gamma_i$ is contained in $C_0$ for $i\geq i_0$
-and $q_i\restricted{C_0}$ is affine homotopic to $q_j\restricted{C_0}$ for
-$i\geq j\geq i_0$.
-
-\begin{lemma}
-  There exists $i_1\geq i_0$ and a number $P$ such that for $i\geq j\geq i_1$ 
-  the maps $g_i\composed \gamma_i$ and $g_j\composed\gamma_j$ are joined by a 
-  homotopy $h_{i,j}$ such that the image of $h_{i,j}$ is contained in $U_{i_1}$ 
-  and  $q_i\composed h_{i,j}$ is a concatenation of at most $P$ affine 
-  homotopies.
-\end{lemma}
-
-\begin{proof} 
-  Let $i\geq j\geq i_0$. Each of $q_i\composed g_i\composed\gamma_i$ and
-  $q_j\composed g_j\composed\gamma_j$ is affine homotopic to $f$, and
-  $q_j\composed g_j\composed\gamma_j$ is affine homotopic to $q_i\composed
-  g_j\composed\gamma_j$, so the distance between $q_i\composed
-  g_i\composed\gamma_i$ and $q_i\composed g_j\composed\gamma_j$ is uniformly
-  bounded. Therefore the distance between $p^\infty_{n_i}\composed
-  g_i^{-1}\composed g_j\composed\gamma_j$ and $p^\infty_{n_i}\composed \gamma_i$ is
-  uniformly bounded, so the distance between $g_i^{-1}\composed
-  g_j\composed\gamma_j$ and $\gamma_i$ is bounded above by a constant multiple
-  of $a^{-i}$. By 
-  %\cref{lem:shorthomotopy}, if $i$ is large enough then there
-  exists a homotopy $h'_{i,j}$ between these maps with width also bounded above
-  by a constant multiple of $a^{-i}$.
-
-  Therefore the width of $p^\infty_{n_i}\composed h'_{i,j}$ is uniformly bounded. 
-  It follows that it is the concatenation of boundedly many affine homotopies. 
-  For $i$ sufficiently large, $p^\infty_j\composed h'_{i,j}$ has image contained 
-  in $H_i$. Define $h_{i,j} = g_i\composed h'_{i,j}$; then $h_{i,j}$ is a 
-  homotopy from $g_i\composed\gamma_i$ to $g_i\composed\gamma_j$ such that 
-  $q_j\composed h_{i,j}$ is a concatenation of boundedly many affine homotopies.
-\end{proof}
-
-Let $C_2$ be a compact subset of $\boundary G - \set\xi$ containing $U_{i_1}$ and 
-also containing the image of a continuous extension 
-$\Gamma\from\Delta^{d+1}\to\boundary G - \set\xi$ of $\gamma$. Take $i_2\geq 
-i_1$ such that $C_2 \subset U_2$ and also so that $q_i\restricted{C_2}$ is 
-affine homotopic to $q_j\restricted{C_2}$ for $i \geq j \geq i_2$.
-
-Now, $q_{i_2}\composed \Gamma$ is affine homotopic to an affine 
-map after some finite number of subdivisions. Since $q_i$ is affine homotopic to 
-$q_{i_2}$ for $i\geq i_2$ it follows that for any $i\geq i_2$ the map 
-$q_i\composed \Gamma$ is affine homotopic to an affine map after boundedly many 
-subdivisions. Furthermore, for $i\geq i_2$, $h_{i,i_1}$ is a 
-homotopy from $g_i\composed \gamma_i$ to $\gamma$, the composition of which with 
-$q_i$ is affine homotopic to an affine map after boundedly many subdivisions. 
-Therefore, for each $i\geq i_2$ there is a null-homotopy of 
-$g_i\composed\gamma_i$ whose composition with $q_i$ is affine homotopic to an 
-affine map after boundedly many subdivisions. The composition of this extension 
-with $g_i^{-1}$ gives the required extension of $\gamma_i$ to $\Delta^{d+1}$.
-\end{proof}
-
-\section{The main theorem}\label{sec:assembling}
-
-The results of the previous two sections may now be assembled to prove the main 
-theorem:
-
-\begin{theorem}\label{thm:maintheorem}
-  Let $G$ be a hyperbolic group. Then $\boundary G$ is $\LC{d}$ if and only if 
-  $\boundary G - \set\xi$ is $\C{d}$ for every point $\xi \in \boundary G$.
-\end{theorem}
-
-\begin{proof}
-  We first prove that if $\boundary G - \set\xi$ is $\C{d}$ for every point $\xi 
-  \in \boundary G$ then $\boundary G$ is $\LC{d}$ by induction. Suppose this 
-  condition holds and also that $\boundary G$ is $\LC{d-1}$. Then 
-  \cref{thm:lLCandnocutpointimpliesS} implies that $\Sd{d}$ is 
-  satisfied, while \cref{thm:nocutpointimpliesdagger} implies that 
-  $\dd{d+1}$ is satisfied, and so $\boundary G$ is $\LC{d}$ by 
-  \cref{thm:ddagimpliesLCd}.
-
-  Conversely, suppose that $\boundary G$ is $\LC{d}$ and let $\xi \in \boundary 
-  G$; we aim to show that $\boundary G - \set\xi$ is $\C{d}$. Let $\gamma$ be a 
-  continuous map $S^d \to \boundary G - \set\xi$ The point $\xi$ is a conical 
-  limit point, so there exist distinct points $\zeta_1$ and $\zeta_2$ in 
-  $\boundary G$ and a sequence of elements $(g_i)$ in $G$ such that $g_i\xi \to 
-  \zeta_1$ as $i\to \infty$, and for any compact subset $C$ of $\boundary G - 
-  \set\xi$ and any neighbourhood $U$ of $\zeta_2$, $g_i(C) \subset U$ for $i$ 
-  sufficiently large.
-
-  Let $V$ be a neighbourhood of $\zeta_2$ that does not contain any point 
-  $g_i\xi$.  Let $U$ be a neighbourhood of $\zeta_2$ such that any map $S^d \to 
-  U$ has an extension to the disk $D^{d+1}$ with image contained in $V$. Then 
-  let $i$ be such that $g_i(\image\gamma)\subset U$. Let $h$ be an extension of 
-  $\gamma$ to $D^{d+1}$ with image contained in $V$; then $g_i^{-1}\composed h$ 
-  is a continuous extension of $\gamma$ with image contained in $\boundary G - 
-  \set\xi$.
-\end{proof}
-
-\begin{corollary}
-  Let $G$ be a hyperbolic group. Then the following conditions are equivalent.
-  \begin{enumerate}
-    \item\label{item:LCd} The boundary $\boundary G$ is $\LC{d}$.
-    \item\label{item:Cd} For all points $\xi \in \boundary G$, $\boundary G - 
-      \set\xi$ is $\C{d}$.
-    \item\label{item:dd} The condition $\dd{d+1}$ is satisfied.
-    \item\label{item:Sd} The condition $\Sd{d+1}$ is satisfied.
-  \end{enumerate}
-\end{corollary}
-
-\begin{proof}
- The equivalence of conditions~\ref{item:LCd} and~\ref{item:Cd} is the content 
- of \cref{thm:maintheorem}.
- \todo{finish this}
-\end{proof}
-
-\subsection{Questions}
-
-\begin{question}
-  Suppose that $G$ is a hyperbolic group and $d\geq 1$ such that $\boundary G$ 
-  is $\C{d}$.  Does it follow that $\boundary G - \set\xi$ is $\C{d}$ for every 
-  $\xi$ in $\boundary G$, and therefore that $\boundary G$ is $\LC{d}$?
-\end{question}
-
-For $d = 0$ this question was originally asked by Bestvina and 
-Mess~\cite{bestvinamess91} and answered in the affirmative by work of 
-Bowditch~\cite{bowditch98b} and Swarup~\cite{swarup96}. The techniques of
-Bowditch and Swarup are not applicable for $d\geq 1$, and new methods would be
-required. On the other hand, there is no example in the literature of a group
-that provides a negative answer to the question.
-
-\begin{question}
-  Conversely, suppose that $\boundary G - \set\xi$ is $\C{d}$ for every 
-  $\xi\in\boundary G$, and therefore $\boundary G$ is $\LC{d}$. Is it true that 
-  $\boundary G$ is either $\C{d}$ or homeomorphic to $S^d$?
-\end{question}
-
-\section{Locally contractible boundaries}
-
-In this section we investigate the implications of local contractibility for
-the boundary of a hyperbolic group. (Recall that a space is locally
-contractible if any neighbourhood $U$ of any point admits a sub-neighbourhood
-$V$ such that the inclusion $V\into U$ is null-homotopic in $U$.) This condition
-is related to the conditions $\LC{n}$ investigated earlier in this paper by the
-following well-known proposition.
-
-\begin{proposition}%Mentioned in the Dugundji paper. Cited to Kuratowski's
-  %Topologie II, chapter VII
-  Let $X$ be a separable metric space of topological dimension $n$. If $X$ is
-  $\LC{n}$ then it is locally contractible.
-\end{proposition}
-
-To begin, note the following lemma.
-
-\begin{lemma}
-  If $\boundary G$ is locally contractible then $\homology_\star(\boundary G;
-  \integers)$ and $\homology^\star(\boundary G; \integers)$ are finitely
-  generated.
-\end{lemma}
-
-\begin{proof}
-  Take an finite cover of $\boundary G$ by contractible open subsets
-  $\{U_i\}_{i \leq n}$. Let $K$ be the nerve of the covering. Then there is a
-  spectral sequence with 
-  \begin{align}
-    E^1_{pq} = \bigoplus_\sigma\in\Skel^{p} K H_q(X_\sigma),
-  \end{align}
-  where $X_\sigma = \intersection_{i \in \sigma} X_i$, such that
-  $E_{pq}\ssconverges \homology_{p+q}(X)$. The simplicial complex $K$ is finite
-  and each group $H_q(X_\sigma)$
-  \todo{Finish proving this lemma.}
-\end{proof}
+In this section we give a sufficient condition for our condition
+\todo{condition} to be satisfied.
 

### 2020-01-14 paper.tex
Added the horoball section

@@
 
+In future sections we will make use of a limiting argument, which will relate
+the topology of the complement of a point in the boundary $\boundary G$ to a
+particular complex built from $K$, which we will think of as a horoball in $K$.
+In this section we prove that this construction possesses certain properties
+that we will need later.
+
+\subsection{Defining the horoball}\label{sec:horoball}
+
+For each $n$, let $v_n$ be a vertex of $K_n$ and let $g_n$ be an element of $G$
+taken so that $g_n\cdot v_n$ is independent of $n$.  Since $K$ is locally
+finite, we can pass to a subsequence so that now $v_i \in K_{n_i}$ satisfying
+the following conditions:
+\begin{enumerate}
+  \item
+    The translates by $g_i$ of large neighbourhoods of $v_i$ in the sphere
+    $S_{n_i} \subset G$ are equal: for any $i \geq j$,
+    \begin{equation*}
+      g_i\left(N_j(v_i) \intersection S_{n_i}\right) 
+            = g_j\left(N_j(v_j) \intersection S_{n_j}\right).
+    \end{equation*}
+    (Here $N$ denotes a neighbourhood taken with respect to the word metric on
+    $G$.)
+  \item
+    The sequence $g_i = g_i\cdot 1$ of vertices of $K$ converges to a point
+    $\xi \in \boundary G$ as $i\to\infty$.
+\end{enumerate}
+
+Let $H_i$ be the full subcomplex of $K$ with vertex set
+\begin{equation*}
+  g_i\left(N_i(v_i) \intersection S_{n_i}\right);
+\end{equation*}
+notice that $H_i$ contains $H_j$ for $i \geq j$, and also that $g_i$ maps the
+full subcomplex of $K_{n_i}$ with vertex set $N_i(v_i) \intersection S_{n_i}$
+isometrically onto $H_i$.
+
+Let $H$ be the union of the complexes $H_i \subset K$. We view $H$ as a
+horosphere, the topology of which approximates that of $\boundary G - \set\xi$.
+The rest of~\ref{sec:horoball} will be spent justifying this point of view.
+
+\subsection{Geodesics and and the horosphere}
+
+\begin{lemma}\label{lem:geodesicsmeethorosphere}
+  Every bi-infinite geodesic with $\xi$ in its limit set meets $H$.
+\end{lemma}
+
+\begin{proof}
+  Let $\alpha$ be a bi-infinite geodesic with $\xi$ as a limit pint. Pick a
+  point $w \in f(\Vertices(J))$ and let the distance $\dist(w,\alpha)$ be
+  realised by a point $x \in \alpha$.
+
+  The points $g_i$ converge to $\xi$ as $i\to\infty$, so the distances
+  $\dist(x, [\xi, g_i])$ tend to infinity as $i$ tends to infinity. The
+  triangle with vertices $x$, $\xi$ and $g_i$ is $\delta$-slim, so for each $i$
+  there exists a point $y_i$ on $[x, g_i]$ with $\dist(y_i, \alpha) \leq
+  \delta$ and $y_i\to\xi$ as $i\to\infty$.  For each $i$ let $z_i$ be a point
+  on $\alpha$ with $\dist(y_i, z_i) \delta$.
+
+  Since $\dist(g_i, x) = n_i$ for $i$ sufficiently large and $\dist(x,y_i) \to
+  \infty$ as $i\to\infty$, we have the following limit.
+  \begin{align*}\label{eqn:zi_closer_to_gi_than_x}
+    \dist(g_i,z_i) - n_i &\leq \dist(g_i,y_i) + \delta - n_i \text{ for $i$
+                                        sufficiently large} \\
+                         &= - \dist(x,y_i) + \delta \\
+                         &\to -\infty\text{ as $i \to \infty$} \tag{$\star$}
+  \end{align*}
+  Therefore, for $i$ sufficiently large, there exists a point $p_i$ on $\alpha$
+  such that $z_i$ lies between $\xi$ and $p_i$ on $\alpha$ and so that
+  $\dist(g_i,p_i)=n_i$. We now show that $\dist(p_i, x)$ is uniformly bounded.
+
+  The limit~\eqref{eqn:zi_closer_to_gi_than_x}, taken together with the fact
+  that $\dist(g_i, x) = \dist(g_i, p_i) = n_i$, shows that the distances
+  $\dist([z_i, g_i], x)$ and $\dist([z_i, g_i], p_i)$ tend to infinity as
+  $i\to\infty$.  We now divide into cases according to which of $x$ and $p_i$
+  is closer to $z_i$.
+  \begin{enumerate}
+    \item If $x$ is between $z_i$ and $p_i$ on $\alpha$ then by considering a
+      geodesic triangle with vertices $g_i$, $z_i$ and $p_i$ we see that for
+      $i$ sufficiently large, $x$ is within a distance $\delta$ of a point
+      $q_i$ on the geodesic from $g_i$ to $p_i$.  Therefore,
+      \begin{align*}
+        \dist(g_i,x)&\leq \dist(g_i,q_i)+\delta\\
+                        &\leq \dist(g_i,p_i)-\dist(p_i,q_i)+\delta\\
+                        &\leq \dist(g_i,p_i)-\dist(x,p_i)+2\delta.
+      \end{align*}
+      It follows that $\dist(x,p_i) \leq \dist(g_i,p_i)-\dist(g_i,x)+2\delta
+      = 2\delta$.
+    \item If $p_i$ is between $z_i$ and $x$ on $\alpha$ then by an identical 
+      argument with the r\^oles of $x$ and $p_i$ reversed we can similarly 
+      deduce that 
+      \begin{align*}
+        \dist(x,p_i)\leq\dist(g_i,x) - \dist(g_i,p_i) + 2\delta =2\delta.
+      \end{align*}
+  \end{enumerate}
+
+  Either way, $\dist(w, p_i) \leq \dist(x,w) + 2\delta$. In summary, we have
+  shown that for $i$ sufficiently large there is a point $p_i\in\alpha$ with
+  $\dist(g_i,p_i)=n_i$ and $\dist(p_i,f(\Vertices J))$ bounded by $\dist(x,w) +
+  2\delta$. Then $p_i \in H_i$ whenever $i$ is at least $\dist(x,w) + 2\delta$.
+\end{proof}
+
+\begin{lemma}\label{lem:boundedintersection}
+  Let $C$ be a compact subset of $\boundary G - \set\xi$. Then the set of points 
+  of intersection between $H$ and bi-infinite geodesics with one end point equal 
+  to $\xi$ and the other in $C$ is bounded.
+\end{lemma}
+
+\begin{proof}
+  Let $\alpha$ be any bi-infinite geodesic with $\alpha(-\infty)=\xi$ and 
+  $\alpha(\infty)\in C$. Let $x \in \alpha \intersection H$. Since $C$ is
+  compact, there exists a point $v \in \alpha$, between $\xi$ and $x$ on
+  $\alpha$, such for that any bi-infinite geodesic $\beta$ with
+  $\beta(-\infty)$ in $C$ and $\beta(\infty) = \alpha(\infty)$, $\beta$ does
+  not meet the $100\delta$-neighbourhood of the sub-ray of $\alpha$ between
+  $\xi$ and $v$: otherwise a limiting argument shows that $\xi$ is in $C$.
+
+  Since $g_i \to \xi$, the distance $\dist(v, [\xi, g_i]) \to \infty$ as
+  $i\to\infty$. The triangle with vertices $\xi$, $g_i$ and $x$ is
+  $\delta$-slim, so the geodesic path from $g_i$ to $x$ passes within a
+  distance $\delta$ of $v$ for $i$ large enough. Therefore, since $\dist(g_i,
+  x) = n_i$ for $i$ large enough, the following inequality holds for all $i$
+  large enough.
+  \begin{align*}
+    0 \leq \dist(g_i, v) + \dist(v, x) - n_i \leq 2\delta.
+  \end{align*}
+
+  Let $\alpha'$ be a bi-infinite geodesic with $\alpha'(-\infty) = \xi$ and
+  $\alpha'(\infty) \in C$ and let $x' \in \alpha' \intersection H$. The ideal
+  triangle with vertices $\xi$, $\alpha(\infty)$ and $\alpha'(\infty)$ is
+  $\delta$-slim, so the subray of $\alpha$ between $\xi$ and $v$ is contained
+  in a $\delta$-neighbourhood of $\alpha'$.  Let $v' \in \alpha'$ be a point
+  with $\dist(v, v') \leq \delta$.
+
+  We split into cases according to the order of $\xi$, $v'$ and $x'$ on
+  $\alpha'$.
+  \begin{enumerate}
+    \item
+      First we suppose that $v'$ is between $x'$ and $\xi$ on $\alpha'$. Then as
+      in the argument above, for $i$ sufficiently large we have the following
+      inequality:
+      \begin{align*}
+        0 \leq \dist(g_i, v') + \dist(v', x') - n_i \leq 2\delta.
+      \end{align*}
+      And therefore,
+      \begin{align*}
+        -2\delta \leq \dist(g_i, v) + \dist(v, x') - n_i \leq 4\delta.
+      \end{align*}
+      Finally, putting these inequalities together,
+      \begin{align*}
+        \dist(v,x') \leq \dist(v,x) + 4\delta,
+      \end{align*}
+      and thus we can uniformly bound this distance in this case.
+    \item
+      Alternatively, $x'$ is between $v'$ and $\xi$ on $\alpha'$ and so (since
+      the triangle with vertices $\xi$, $v$ and $v'$ is $\delta$-slim) $x'$ is
+      within a distance $2\delta$ of the geodesic ray from $x$ to $\xi$. By
+      considering the triangle with vertices $\xi$, $g_i$ and $x$ for $i$ large
+      enough, a geodesic segment from $g_i$ to $x$ passes within a distance
+      $3\delta$ of $x'$. Therefore we have the following inequality for all $i$
+      sufficiently large:
+      \begin{align*}
+        0 \leq \dist(g_i, x') + \dist(x', x) - \dist(g_i, x) \leq 6\delta.
+      \end{align*}
+      Finally, for $i$ sufficiently large, $\dist(g_i, x') = \dist(g_i, x) = n_i$,
+      so
+      \begin{align*}
+        \dist(x,x') \leq 6\delta.
+      \end{align*}
+  \end{enumerate}
+\end{proof}
+
+\subsection{Projections to the horosphere}
+
+\begin{definition}
+  Let $U_i \subset \boundary G$ be the (closed) preimage of $H_i$ under the map 
+  $g_i \composed p^\infty_{n_i} \composed g_i^{-1} \from \boundary G \to X$.
+  Denote by $q_i$ the restriction of this map to $U_i$.
+\end{definition}
+
+The following lemma is immediate from the definition of $p^\infty_i$.
+
+\begin{lemma}\label{lem:describing_q_i}\todo{Check this}
+  Let $\zeta \in \boundary G - \set\xi$ and suppose that $q_i(\zeta) \in H_i$
+  is defined, so $\zeta \in U_i$, and $N_{4\delta+1} q_i(\zeta) \in H_i$. Then
+  $q_i(\zeta)$ is contained in the minimal simplex of $H_i$ with vertex set
+  \begin{align*}
+    N_{2\delta+1} \set{\eta(n_i)\suchthat\text{$\eta$ a geodesic ray with
+    $\eta(0) = g_i$ and $\eta(\infty) = \zeta$}}.
+  \end{align*}\qed
+\end{lemma}
+
+\begin{lemma}
+  Every compact subset of $\boundary G - \set\xi$ is contained in $U_i$ for 
+  $i$ sufficiently large.
+\end{lemma}
+
+\begin{proof}
+  Suppose that a compact subset $C$ of $\boundary G - \set\xi$ is not contained
+  in $U_i$ for infinitely many $i$. Then after passing to a subsequence there
+  exists for each $i$ a point $\zeta_i \in C\setminus U_i$.
+
+  By assumption, $g_i^{-1}(H_i)$ contains the star in $K_{n_i}$ of 
+  $g_i^{-1}(H_{i-1})$, so the definition of $p^\infty_{n_i}$ implies that a 
+  geodesic ray $\alpha_i$ from $e$ to $g_i^{-1}(\zeta_i)$ does not pass through 
+  $g_i^{-1}(H_{i-1})$. Equivalently, $g_i\composed\alpha_i$ is a geodesic from 
+  $g_i$ to $\zeta_i$ that does not pass through $H_{i-1}$.
+
+  After reparameterising and passing to a subsequence, the geodesic rays
+  $g_i\composed\alpha_i$ converge uniformly on compact subsets to a bi-infinite
+  geodesic from $\xi$ to some point $\zeta \in C$.  This geodesic does not pass
+  through $H$, which contradicts \cref{lem:geodesicsmeethorosphere}.
+\end{proof}
+
+\begin{lemma}\label{lem:affinehomotopic}
+  For any compact subset $C\subset\boundary G - \set\xi$, there exists $i_0$ 
+  such that for all $i \geq i_0$ and any $\zeta \in C$, $\newdist(q_i(\zeta),
+  q_{i_0}(\zeta)) \leq 8\delta + 2$, and, in particular, $q_i\restricted{C}$
+  and $q_{i_0}\restricted{C}$ are related by an affine homotopy.
+\end{lemma}
+
+\begin{proof}
+  Let $B\subset H$ be a bounded set containing all points where geodesics with
+  one limit point equal to $\xi$ and the other in $C$ meet $H$; this set exists
+  by \cref{lem:boundedintersection}.
+
+  Fix $\alpha$ to be some geodesic with $\alpha(-\infty)=\xi$ and
+  $\alpha(\infty)\in C$ and let $x$ be a point of intersection between $\alpha$
+  and $B$. Since the triangle with vertcies $x$, $g_i$ and $\xi$ is
+  $\delta$-slim, and $\dist(x, [\xi, g_i]) \to \infty$ as $i\to\infty$, for
+  each $i$ there exists a point $y_i$ on $[g_i, x]$ with $\dist(y_i, \alpha)
+  \leq \delta$ and so that $y_i \to \xi$ as $i\to\infty$. Let $z_i \in \alpha$
+  be such that $\dist(y_i, z_i)\leq\delta$.
+
+  Now fix $i_0$ such that the following conditions hold for all $i\geq 
+  i_0$.
+  \begin{enumerate}
+    \item The distance $\dist(y_i,x)$ is greater than $7\delta + \Diam B$.
+    \item The set $C$ is contained in $U_i$.
+  \end{enumerate}
+
+  Let $\zeta \in C$ and let $\alpha'$ be a geodesic from $\xi$ to $\zeta$. Let 
+  $x'$ be a point in the intersection of $\alpha'$ and $B$.
+
+  Now let $i\geq i_0$. Then by considering the ideal triangle with vertices
+  $g_i$, $x$ and $x'$, and using the fact that $\dist(y_i, x) > \delta + \Diam
+  B$, we deduce that there exists a point $y_i'$ on $[x', g_i]$ with
+  $\dist(y_i, y_i') \leq \delta$.
+
+  Similarly, since $\dist(z_i, x) > \delta + \Diam B$, consideration of the
+  triangle with vertices $\xi$, $x$ and $x'$ reveals that there exists a point
+  $z_i'$ on $\alpha'$ between $\xi$ and $x'$ with $\dist(z_i, z_i') \leq
+  \delta$. Then $\dist(y_i', z_i') \leq 3\delta$.
+
+  Since $\dist(z_i', x') > 2\delta$, the distance from $y_i'$ to the subray of
+  $\alpha'$ from $x'$ to $\zeta$ is greater than $\delta$. Therefore by
+  considering a triangle with vertices $g_i$, $x'$ and $\zeta$ we see that
+  there exists a point $w_i$ on a geodesic ray $\eta_i$ from $g_i$ to $\zeta$
+  with $\dist(w_i, y_i') \leq \delta$. It follows that $\dist(w_i, z_i') \leq
+  4\delta$, and we know that $\dist(x', z_i') > 5\delta$, so $\dist(x', [z_i',
+  w_i]) > \delta$ and therefore $\dist(x', \eta_i) \leq \delta$.
+
+  In summary, any geodesic ray from $g_i$ to $\zeta$ passes within a distance 
+  $\delta$ of $x'$, for $i\geq i_0$. Furthermore, $\dist(g_i,x') = n_i$, so 
+  $\dist(\eta_i(n_i), x')\leq 2\delta$. It follows from the description of
+  $q_i$ in \cref{lem:describing_q_i} that $q_i(\zeta)$ is contained in a
+  simplex with all vertices within a distance $4\delta+1$ of $x'$. The set of
+  all such vertices spans a simplex, so, in particular, $q_i\restricted{C}$ and
+  $q_{i_0}\restricted{C}$ are related by an affine homotopy for $i \geq i_0$. 
+\end{proof}
+
+\begin{lemma}\label{lem:propermaps} 
+  For any compact subset $C \subset H$ there exists $i_0$ such that
+  \begin{align*}
+    \bigunion_{i\geq i_0} q_i^{-1} C
+  \end{align*}
+  is a relatively compact subset of $\boundary G - \set\xi$.
+\end{lemma}
+
+\begin{proof}
+  If not then there exists a sequence $\zeta_i$ of points with $\zeta_i \in U_i$ 
+  for all $i$ such that $q_i(\zeta_i) \in C$ for all $i$ and $\zeta_i \to \xi$ 
+  as $i \to \infty$.
+
+  Then for each $i$ a geodesic from $g_i$ to $\zeta_i$ passes through the star 
+  in $H$ of $C$.  After passing to a subsequence these geodesic rays converge to 
+  a bi-infinite geodesic passing through the star in $H$ of $C$, both end points 
+  of which must be $\xi$, which is a contradiction.
+\end{proof}
+
 \section{The double dagger condition}

### 2020-01-14 paper.tex
Added a couple of points to come back to

@@
 
+  \todo{This assumption is gone.}
   By assumption, $g_i^{-1}(H_i)$ contains the star in $K_{n_i}$ of 
@@
 
+  \todo{Is star actually the right word?}
   Then for each $i$ a geodesic from $g_i$ to $\zeta_i$ passes through the star 

### 2020-01-14 paper.tex
Wrote some double dagger stuff

@@
 \begin{definition}
-  Double dagger condition
+  We say that $G$ satisfies $\ddag_M$ if there exists a number $L$ such that,
+  for any $n$ and any $x$ and $y$ in $S_n$ with $\dist(x,y) \leq M$, $x$ and
+  $y$ are connected by a path of length at most $L$ in the complement of the
+  ball with radius $\dist(x,y) - 3\delta$ with centre $1 \in G$.
+  \todo{$3\delta$?}
 \end{definition}
@@
 
-\begin{proposition}
-  $\ddag$ implies locally path connected.
+\begin{proposition}\cite[Proposition 3.2]{bestvinamess91}
+  If $G$ satisfies $\ddag_{11\delta + 3}$ then $\boundary G$ is locally path
+  connected.
 \end{proposition}
@@
 \begin{proposition}
-  no cut point implies $\ddag$.
+  If $\boundary G - \set\xi$ is connected for any $\xi \in \boundary G$ then
+  $G$ satisfies $\ddag_M$ for any $M$.
 \end{proposition}
 
-Taken together with the following theorem of Bowditch~\cite{bowditch98b} and
-Swarup~\cite{swarup96}, these propositions show that $\boundary G$ is locally
-path connected if and only if it is connected.
+Taken together with the following theorem, first proved by
+Bowditch~\cite{bowditch98b} when $G$ is strongly accessible and then by
+Swarup~\cite{swarup96} in the general case, these propositions show that
+$\boundary G$ is locally path connected if and only if it is connected.
 
-\begin{theorem}
+\begin{theorem}\cite{bowditch98b,swarup96}
   If $\boundary G$ is connected then $\boundary G$ does not contain a cut
@@
 
-\subsection{An equivalent condition}
+\subsection{An modified condition}
 
-In this section we reinterpret the double dagger condition as a condition
-describing the existence of paths in the spheres $K_n$ of
-Section~\ref{sec:spheres}. This interpretation gives a more systematic method
-for constructing paths in $\boundary G$ from paths in the spheres $K_n$, and
-permits a generalisation to higher dimensional connectivity.
+In this section we introduce a related condition. This condition is stronger
+than $\ddag_M$, but, using Bestvina and Mess's result, we show that it holds
+under the same assumption. This condition reinterprets the paths in $\ddag_M$
+as paths in the complexes $K_n$, with the additional assumption that these
+paths approximate paths that factor through the projection map $p^\infty_n$.
+This interpretation gives a more systematic method for constructing paths in
+$\boundary G$ from paths in the spheres $K_n$, and permits a generalisation to
+higher dimensional connectivity.
 
 \begin{definition}
-  New double dagger condition. \todo{State condition.}
+  We say that $G$ satisfies $\ddag'_M$ if there exists a number $L$ such that,
+  for any $n$ sufficiently large any $\zeta_1$ and $\zeta_2$ in $\boundary G$
+  such that $\newdist(p^\infty_n(\zeta_1), p^\infty_n(\zeta_2)) \leq M$, and
+  any points $x_1$ and $x_2$ in $K_n$ adjacent to $p^\infty_n(\zeta_1)$ and
+  $p^\infty_n(\zeta_2)$, there is a path $\alpha\from I\to \boundary G$ from
+  $\zeta_1$ to $\zeta_2$ in $\boundary G$ such that $p^\infty_n\composed\alpha$
+  admits a simplicial approximation connecting $x_1$ to $x_2$ in $K_n$ after at
+  most $L$ barycentric subdivisions of $I$.
 \end{definition}
 
-\todo{Prove things about this condition}
+\begin{proposition}
+  If $\boundary G - \set\xi$ is path connected then $G$ satisfies $\ddag'_M$
+  for any $M$.
+\end{proposition}
+
+\begin{proof}
+  Suppose $\ddag'_M$ does not hold. Then for any $i$ there exists a number $n_i
+  \geq i$, points $\zeta_1^i$ and $\zeta_2^i$ in $\boundary G$ and vertices
+  $x_1^i$ and $y_1^i$ of $K_{n_i}$ adjacent in $K_{n_i}$ to
+  $p^\infty_{n_i}(\zeta^i_1)$ and $p^\infty_{n_i}(\zeta^i_2)$ such that there
+  is no path $\alpha$ from $\zeta_1^i$ to $\zeta_2^i$ in $\boundary G$ where
+  $p^\infty_{n_i}\composed\alpha$ admits a simplicial approximation after at
+  most $i$ barycentric subdivisions of the interval.
+
+  Take group elements $g_i$ such that $g_i\cdot x_1^i$ is equal to some vertex
+  $x_1$ for all $i$ vertices and pass to a subsequence as in
+  Section~\ref{sec:horoball}, so that $g_i\to\xi$ as $i \to\infty$. Since
+  $\dist(x_1^i, x_2^i)$ is bounded we can pass to a deeper subsequence so that
+  $g_i\cdot x_2^i$ is constant equal to $x_2$ for all $i$, and $x_2$ is
+  contained in $H_i$ for all $i$.
+
+  Now, $g_i\cdot \zeta_1^i$ and $g_i\cdot\zeta_2^i$ map by $q_i$ to points in
+  simplices adjacent to $x_1$ and $x_2$, so by Lemma~\ref{lem:propermaps} the
+  sequences we can pass to a subsequence so that the sequences $g_i\cdot
+  \zeta_1^i$ and $g_i\cdot\zeta_2^i$ converge to points $\zeta_1$ and $\zeta_2$
+  in $\boundary G - \set\xi$ as $i \to \infty$.
+  \todo{finish this}
+\end{proof}
+
+Using this property we define maps $i^n_{n+1}\from \Sk^1 K_n$ to $\Sk^1K_{n+1}$
+as follows.
+
+\begin{proposition}
+  Suppose that $G$ satisfies $\ddag'_M$ for $M = D+2$. Then there exists $k$
+  such that for $n$ sufficiently large there is a map
+  $i^n_{n+1}\from \Sk_1 K_n \to \Sk_1 K_{n+1}$ satisfying the following
+  conditions:
+  \begin{enumerate}
+    \item for each $n$, $i^n_{n+1}$ is an affine map on the subdivision
+      $\sd_k\Sk_1 K_n$,
+    \item for any vertex $x$ of $K_n$, $\dist(x, i^n_{n+1}(x)) \leq ?$, and
+    \item for each $n$, $i^n_{n+1}$ is affine homotopic to a map that factors
+      through $p^\infty_{n+1}\from \boundary G \to K_{n+1}$.
+  \end{enumerate}
+\end{proposition}
+
+\begin{proof}
+  \todo{Prove this}
+\end{proof}
 
@@
 \begin{definition}
-  \todo{New condition}
+  We say that $G$ satisfies $\Sd_M$ if there exists $k$ such that for any $n$
+  sufficiently large and any affine map $f\from \boundary\Delta^2$ \todo{Do
+  this}
 \end{definition}

### 2020-01-14 paper.tex
Copied in results about the boundary being locally simply connected

@@
 
-\todo{If this condition is satisfied then the bounadry is locally simply
-connected.}
+Our goal in this section is to prove the following theorem.
+
+\begin{theorem}
+  If $G$ satisfies $\Sd_M$ for all $M$ then $\boundary G$ is locally simply
+  connected.
+\end{theorem}
+
+\subsection{Constructing maps to $\boundary G$}
+
+We will make frequent use of the following lemma, adapted 
+from~\cite{bestvinamess91}
+
+\begin{lemma}\cite{bestvinamess91}\label{lem:near_geod_rays}
+  Let $G$ be infinite. For any $x \in X$ there exists a geodesic ray $\alpha$ 
+  with $\alpha(0) = e$ and $\dist(x,\alpha) \leq 2\delta$.
+
+  Furthermore, $\dist(x, \alpha(\dist(e,x))) \leq 4\delta$.
+\end{lemma}
+
+\begin{proof}
+  For the first claim, see~\cite{bestvinamess91}. For the second, let $p$ be a 
+  point on $\alpha$ such that $\dist(x, p) \leq 2\delta$. Then the triangle 
+  inequality shows that $\abs{\dist(e,p), \dist(e,x)} \leq 2\delta$, and 
+  so $\dist(p, \alpha(\dist(e,x))) \leq 2\delta$. Then the result 
+  follows from another application of the triangle inequality.
+\end{proof}
+
+We begin the proof of \cref{thm:ddagimpliesLCd} by proving the following 
+proposition.
+
+\begin{proposition}\label{prop:ddag_implies_i}
+  Let $d \geq -1$. Suppose that $G$ satisfies the conditions $\Sd{d-1}$ and
+  $\dd{d}$. Then there are constants $n_0$, $k$ and $\epsilon$ such that for
+  each $n\geq n_0$ there is map $i^n_{n+1}\from\Skel_{d+1} K_n \to \Skel_{d+1}
+  K_{n+1}$ such that the following conditions hold.
+  \begin{enumerate}
+    \item For any $x \in \Vertices(K_n)$, $\dist(x, i_{n+1}^n(x)) \leq
+      \epsilon$.
+    \item The map $i^n_{n+1}$ is affine on the subdivision $\sd^k\Skel_{d+1}
+      K_n$ of $\Skel_{d+1}K_n$.
+    \item The map $i^n_{n+1}\restricted{\Skel_d K_n}$ admits a factoring.
+  \end{enumerate}
+\end{proposition}
+
+\begin{proof}
+  The condition $\dd{-1}$ implies the infinitude of $G$, so
+  \cref{lem:near_geod_rays} is applicable. For $x \in \Vertices{K_n}$ choose an
+  infinite geodesic ray $\alpha_x$ such that $\alpha(0) = 1$ and
+  $\dist(\alpha(n), x) \leq 4\delta$. Define $i^n_{n+1}(x) =
+  \alpha_x(n+1)$. Then $i^n_{n+1}$ satisfies the first requirement with
+  $\epsilon = 4\delta+2$ and satisfies the second requirement automatically.
+
+  Furthermore, $\alpha_x(\infty) \in V_{n+1}(\alpha_x(n+1))$, so 
+  $p^\infty_{n+1}(\alpha_x(\infty))$ lies in a simplex of $K_{n+1}$ that also 
+  contains $\alpha_x(n+1)$.  Therefore the map $i^n_{n+1}$ and a simplicial 
+  approximation to the map $x \mapsto \alpha_x(\infty) \mapsto p^\infty_{n+1} 
+  (\alpha_x(\infty))$ are related by an affine homotopy, so $i^n_{n+1}$ admits a 
+  factoring.
+
+  Now apply \cref{prop:extendingaffinemaps2} to extend $i^n_{n+1}$ from
+  $\Vertices(K_n)$ to $\Skel_{d+1} K_n$ to obtain a map with the required
+  properties.
+\end{proof}
+
+Throughout the remainder of this section we assume that $G$ satisfies $\dd{d-1}$ 
+and $\Sd{d}$. Let $n_0$, $k$ and $\epsilon$ be the constants given in 
+\cref{prop:ddag_implies_i}, and for $n\geq n_0$ let $i^n_{n+1} 
+\from \sd^k\Skel_{d+1} K_n \to \Skel_{d+1} K_{n+1}$ be the affine map given by 
+that proposition.  For $n \geq m \geq n_0$ let $i^m_n$ be the composition 
+$i^{n-1}_n \composed \dotsb \composed i^m_{m+1} \from \Skel_{d+1} K_m \to 
+\Skel_{d+1} K_n$.  This map is affine on a degree $k^{n-m}$ subdivision of 
+$\Skel_{d+1} K_m$.
+
+In what follows we require the following useful lemma.
+
+\begin{lemma}\label{lem:useful}
+  Let $(x_n)$ be a sequence of points in $G$ with $\dist(x_{n+1}, e) = 
+  \dist(x_n, e) + 1$ and $\dist(x_{n+1}, x_n)$ bounded. Then,
+  \begin{align*}
+    \gromov{e}{x_m}{x_n} \geq \dist(e,x_m) - C
+  \end{align*}
+  for some constant $C$ depending only on $\delta$ and the bound on 
+  $\dist(x_{n+1}, x_n)$.
+\end{lemma}
+
+\begin{proof}
+  We estimate the Gromov product using the visual metric $\vdistance$ on 
+  $\boundary G$; then the claimed inequality follows from the triangle 
+  inequality.
+
+  Let $i_n = \dist(x_n, e)$, so $i_n = i_0 + n$, and let 
+  $\dist(x_{n+1},x_n)$ be bounded by $C_0$. By 
+  \cref{lem:near_geod_rays} there exists a sequence $(\alpha_n)$ of 
+  geodesic rays with $\dist(\alpha_n(i_n), x_n) \leq 4\delta$. Then 
+  $\dist(\alpha_n(i_n), \alpha_{n+1}(i_{n+1})) \leq C_0 + 8\delta$. Then 
+  $\gromov{e}{\alpha_n(\infty)}{ \alpha_{n+1}(\infty)} \geq i_n - (C_0 + 
+  8\delta)/2$.
+
+  By the triangle inequality it follows that for $n\geq m$ we have the following 
+  inequality.
+  \begin{align*}
+    \vdistance(\alpha_n(\infty), \alpha_m(\infty)) \leq C_1 a^{-i_m}
+  \end{align*}
+  for some constants $C_1$ depending only on $\delta$ and $C_0$. Then, by
+  definition of the visual metric, there exists a constant $C_2$ such that
+  \begin{align*}
+    \gromov{e}{\alpha_n(\infty)}{\alpha_m(\infty)} \geq i_m - C_2.
+  \end{align*}
+
+  Now, by \cref{lem:boundary_gromov_product} there exists a constant $C_3$ such
+  that
+  \begin{align*}
+    \gromov{e}{\alpha_n(i_n)}{\alpha_m(i_m)} \geq i_m - C_3,\qedhere
+  \end{align*}
+  as required.
+\end{proof}
+
+\begin{lemma}\label{lem:linearproduct}
+  There is a constant $C$ such that if $x \in \Skel_{d+1} K_m$ then
+  \begin{align*}
+    \gromov{e}{i^m_n(x)}{x} \geq m - C
+  \end{align*}
+  for all $n\geq m\geq n_0$.
+\end{lemma}
+
+\begin{proof}
+  For $n \geq m$, let $y_n$ be a vertex of the minimal simplex of $K_n$
+  containing $i^m_n(x)$. Then, for each $n \geq m$, we have $\dist(e, y_{n+1})
+  = \dist(e, y_n)$.
+
+  We now bound the distance $\dist(y_n, y_{n+1}$. To start with, $\dist(y_n,
+  i^n_{n+1} y_n) \leq \epsilon$. Let $R$ be such that any two vertices in the
+  1-skeleton of $\sd^k \Delta^{d+1}$ are joined by a path traversing at most
+  $R$ edges. Let $\sigma$ be the minimal simplex of $K_n$ containing
+  $i^m_n(x)$. Then $y_n$ is a vertex of $\sigma$ and $y_{n+1}$ is a vertex of
+  the image of $\sigma$ under $i^n_{n+1}$, so $\dist(i^n_{n+1} y_n, y_{n+1})
+  \leq RD$.  Putting this together,
+  \begin{align*}
+      \dist(y_n, y_{n+1}) \leq \epsilon + RD
+  \end{align*}
+
+  It follows from \cref{lem:useful} that there exists a constant $C$ depending
+  only on $\delta$, $\epsilon$ and $k$ such that $\gromov{e}{y_n}{y_m} \geq m -
+  C$.
+
+  Finally, by applying the inequality in \cref{rem:dist_vs_newdist}, we deduce
+  that
+  \begin{align*}
+      \gromov{e}{i^m_n(x)}{x} \geq m - C - 3D.\qedhere
+  \end{align*}
+\end{proof}
+
+\begin{corollary}
+  For $m \geq n_0$ and $x \in \Skel_{d+1} K_m$, the sequence
+  $(i^m_n(x))_{n\geq m}$ converges to a point in $\boundary G$, which we shall
+  denote $i^m_\infty(x)$.
+\end{corollary}
+
+\begin{proof}
+  For $n_1$ and $n_2$ at least $m$, \cref{lem:linearproduct} implies that
+  $\gromov{e}{i^m_{n_1}(x)}{i^m_{n_2}(x)} \geq \min\{n_1,n_2\} - C$, which
+  tends to infinity as $n_1$ and $n_2$ tend to infinity.
+\end{proof}
+
+\begin{lemma}\label{lem:simplexproduct}
+  There is a constant $C$ such that if $m \geq n_0$ and $x$ and $y$ are in a
+  common simplex of $\Skel_{d+1} K_m$ then
+  \begin{align*}
+    \gromov{e}{i^m_n(x)}{i^m_n(y)} \geq m - C
+  \end{align*}
+  for all $n\geq m$.
+\end{lemma}
+
+\begin{proof}
+  The inequality of \cref{lem:linearproduct} is satisfied for each of $x$ 
+  and $y$. By~\cite{bridsonhaefliger99} there exist $\delta'$ depending only on 
+  $\delta$ such that
+  \begin{align*}
+    \gromov{e}{i^m_n(x)}{i^m_n(y)} &\geq \min\{\gromov{e}{i^m_n(x)}{x}, 
+    \gromov{e}{x}{y}, \gromov{e}{y}{i^m_n(y)}\} - 2\delta'\\
+    &\geq \min\{m - C, m - R/2, m - C\} - 2\delta' \\
+    &\geq m - C'
+  \end{align*}
+  for some constant $C'$.
+\end{proof}
+
+The following corollary immediately follows from \cref{lem:simplexproduct}.
+
+\begin{corollary}\label{cor:visualdiameter}
+  There is a constant $C$ such that for any $m\geq n_0$ and any simplex
+  $\sigma$ of $\Skel_{d+1} K_m$, the diameter of $i^m_{\infty}(\sigma)$ with
+  respect to the visual metric $\vdistance$ is bounded above by $Ca^{-m}$,
+  where $a$ is the visual parameter.
+\end{corollary}
+
+\begin{proposition}\label{prop:continuouslimit}
+  The map $i^m_\infty\from \Skel_{d+1} K_m \to \boundary G$ is continuous.
+\end{proposition}
+
+\begin{proof}
+  Fix $x \in \Skel_{d+1} K_m$. Let $k$ be the constant given in the definition 
+  of the map $i$. For $n\geq 0$ let $U_n$ be the star in $\beta^{nk} 
+  \Skel_{d+1}K_m$ of the minimal simplex of $\beta^{nk}\Skel_{d+1}K_m$ 
+  containing $x$. Then $U_n$ is a neighbourhood of $x$ for each $n$.
+
+  For each $n$, the restriction of $i^m_{m+n}$ to a simplex in 
+  $\beta^{nk}\Skel_{d+1}K_m$ is affine, and therefore has image contained in a 
+  simplex of $\Skel_{d+1} K_{m+n}$. The point $x$ is contained in every simplex 
+  of $U_n$, so for any $y \in U_n$ the points $i^m_{m+n}(x)$ and $i^m_{m+n}(y)$ 
+  are contained in a common simplex of $\Skel_{d+1}K_m$. Therefore, by 
+  \cref{cor:visualdiameter}, there is a constant $C$ such that 
+  $\vdistance(i^m_\infty(x), i^m_\infty(y)) \leq Ca^{-(m+n)}$ for every $y \in 
+  U_n$.
+\end{proof}
+
+\begin{remark}
+  In fact, if $K_m$ is endowed with a metric in which each simplex is 
+  isometrically identified with the standard simplex of the same dimension then 
+  the map $i^m_\infty$ can be shown to be H\"{o}lder continuous with exponent 
+  only depending on $\delta$ and the constants in the definition of the map $i$. 
+  We do not require this strengthening of \cref{prop:continuouslimit} 
+  here.
+\end{remark}
+
+Finally, we use the maps $i^n_\infty$ to construct homotopies between certain
+special maps to $\boundary G$.
+
+\begin{proposition}\label{prop:basic_homotopies}
+  Let $C$ be a constant. Then there exists a number $m_0$ and a function $\mu
+  \from \posreals\to\posreals$ such that $\mu(\eta)\to0$ as $\eta\to0$ with the following
+  property. Let $n \geq m_0$ and let $f_0$ and $f_1$ be any maps from
+  $\boundary\Delta^{d+1}$ to $K_n$ satisfying the following conditions:
+  \begin{enumerate}
+    \item the maps $f_0$ and $f_1$ are affine on some subdivision of
+      $\boundary\Delta^{d+1}$;
+    \item for any $x \in \boundary\Delta^{d+1}$, the distance 
+      $\newdist(f_0(x), f_1(x))$ is at most $C$;
+    \item each of $f_0$ and $f_1$ admits a factoring.
+  \end{enumerate}
+  Then there is a homotopy $h$ from $i^n_\infty\composed f_0$ to
+  $i^n_\infty\composed f_1$ satisfying a uniform continuity condition: for any
+  $x \in \boundary\Delta^{d+1}$ and any $s$ and $t$ in $[0,1]$,
+  \begin{align*}
+    \rho(h(x,s), h(x,t)) \leq \mu(\abs{s-t})a^{-n}.
+  \end{align*}
+\end{proposition}
+
+\begin{proof}
+  To start with, apply \cref{prop:extendingaffinemaps2} with $k = C + D$ to
+  obtain constants $k'$ and $m_0\geq n_0$ such that the conclusion of the
+  proposition holds.
+
+  Let $n \geq m_0$.  Let $J$ be a subdivision of $\boundary\Delta^{d+1}$ such
+  that $f_0$ and $f_1$ are both affine on $J$. Then the map 
+  \begin{align*}
+    f_0 \disjointunion f_1 \from J \times \{0\} \disjointunion J \times \{1\}
+          \to K_n,
+  \end{align*}
+  defined on a subset of the product simplicial complex $J \times [0,1]$,
+  satisfies the conditions of \cref{prop:extendingaffinemaps2}, and so admits
+  an affine extension $F \from \sd^{k'} (J \times [0,1]) \to K_n$. Let $h =
+  i^n_\infty \composed F$, so $h$ is a homotopy from $i^n_\infty\composed f_0$
+  to $i^n_\infty\composed f_1$ and it remains to prove the uniform continuity
+  assertion.
+
+  Let $\eta_0$ be such that for $\eta$ at most $\eta_0$, 
+  for any $x \in \Delta^d$, for any $s$ and $t$ in $[0,1]$ with
+  $\abs{s-t} \leq \eta$, the segment $\{x\} \times [s,t]$ is contained in a
+  union of at most two $(d+1)$-simplices of $\sd^{k'}(\Delta^d \times [0,1])$.
+  We first define the modulus of continuity $\mu(\eta)$ for $\eta > \eta_0$.
+
+  Let $M$ be the number of $(d+1)$-simplices in $\sd^{k'}(\Delta^d \times
+  [0,1])$.  \Cref{cor:visualdiameter} gives a constant $C_0$ such that any
+  $(d+1)$-simplex of $K_n$ is mapped to a subset of $\boundary G$ of diameter
+  at most $C_0 a^{-n}$, and so we can take $\mu(\eta) = C_0M$ for $\eta >
+  \eta_0$.
+
+  Now, for $\eta \leq \eta_0$, there exists a maximal number $\kappa(\eta) \geq
+  0$ such that for any $x \in \Delta^d$ and any $s$ and $t$ in $[0,1]$ with
+  $\abs{s-t} \leq \eta$, the segment $\{x\} \times [s,t]$ is contained in a
+  union of at most two $(d+1)$-simplices of
+  $\sd^{\kappa(\eta)}\sd^{k'}(\Delta^d\times[0,1])$. Note that $\kappa(\eta)
+  \to \infty$ as $\eta \to 0$. Now, if $N\in\naturals$ then a $(d+1)$-simplex of
+  $\sd^{k^N}K_n$ is mapped by $i^n_{n+N}$ into a $(d+1)$-simplex of $K_{n+N}$,
+  which is mapped by $i^{n+N}_\infty$ to a set of diameter at most
+  $C_0a^{-n+N}$. Therefore, if $N$ is such that $\kappa(\eta) \geq k^N$ then
+  for $x \in \boundary\Delta^{d+1}$ and $\abs{s-t} < \eta$, $\rho(h(x,s),
+  h(x,t)) \leq 2C_0a^{-n-N}$. It follows that we may take $\mu(\eta)$ as follows:
+  \begin{align*}
+    \mu(\eta) = 2C_0 a^{-\floor*{\frac{\log\kappa(\eta)}{\log k}}}.\qedhere
+  \end{align*}
+\end{proof}
+
+\subsection{Proving \Cref{thm:ddagimpliesLCd}}
+
+We now use the maps $(i^n_{n+1})$ to prove \cref{thm:ddagimpliesLCd}. We begin
+with two lemmas.
+
+\begin{lemma}\label{lem:convergestoidentity}
+  There is a constant $C$ such that the distance from $(i^m_\infty \composed 
+  p^\infty_m)$ to the identity map $\boundary G\to\boundary G$ is at most 
+  $Ca^{-m}$ for each $m$, where $a$ is the visual parameter.
+\end{lemma}
+
+\begin{proof}
+  Let $\xi \in \boundary G$. By \cref{lem:linearproduct} there is a 
+  constant $C$ such that 
+  \begin{align*}
+    \gromov{e}{i^m_n\composed p^\infty_m(\xi)}{p^\infty_m(\xi)} \geq m - C
+  \end{align*} 
+  for each $n\geq m\geq n_0$.
+
+  Let $\alpha$ be a geodesic ray with $\alpha(0) = e$ and $\alpha(\infty) = 
+  \xi$. Then $\alpha(m)$ is a vertex of a simplex in $\Skel_{d+1}K_m$ containing 
+  $p^\infty_m(\xi)$, and $\gromov{e}{\alpha(m)}{\alpha(n)} = m$ for $n\geq m$.
+  It follows that there is a constant $\delta'$ depending only on $\delta$ such 
+  that
+  \begin{align*}
+    \mathrlap{\gromov{e}{\alpha(n)}{i^m_n\composed p^\infty_m(\xi)}}\quad\quad &\\
+          & \geq \min\{\gromov{e}{\alpha(n)}{\alpha(m)}, 
+            \gromov{e}{\alpha(m)}{p^\infty_m(\xi)}, 
+            \gromov{e}{p^\infty_m(\xi)}{i^m_n\composed p^\infty_m(\xi)}\} 
+            - 2\delta' \\
+          &\geq \min\{m - C, m - R/2, m\} - 2\delta' \\
+          &\geq m - C'
+  \end{align*}
+  for some constant $C'$.
+
+  Therefore $\gromov{e}{\xi}{i^m_\infty\composed p^\infty_m(\xi)} \geq m - C'$, 
+  from which the claim follows.
+\end{proof}
+
+\begin{lemma}\label{lem:name_this}
+  There is a number $C$ such that, for any $\xi \in \boundary G$ and any $n
+  \geq 0$ and any vertices $x_1$ and $x_2$ of the minimal simplices containing
+  $i^n_{n+1}\composed p^\infty_n(\xi)$ and $p^\infty_{n+1}(\xi)$ respectively,
+  \begin{align*}
+    \dist(x_1, x_2) \leq C.
+  \end{align*}
+\end{lemma}
+
+\begin{proof}
+  By \cref{lem:close_projections} the distances $\newdist(p^\infty_n(\xi),
+  p^\infty_{n+1}(\xi))$ are bounded by $6\delta + 3 + 2D$. Let $y$ be a vertex
+  of a simplex containing $p^\infty_n(\xi)$; then $\newdist(y, p^\infty_n(\xi))$
+  is bounded by $D$.
+
+  Furthermore, $\dist(y, i^n_{n+1}(y))$ is uniformly bounded by the constant
+  $\epsilon$ from \cref{prop:ddag_implies_i}, and $\newdist(i^n_{n+1}(y),
+  i^n_{n+1}\composed p^\infty_n (\xi))$ is bounded by the product of $D$ and
+  the constant $k$ appearing in \cref{prop:ddag_implies_i}. By putting all this
+  together we obtain a bound $C$ on $\newdist(i^n_{n+1}\composed
+  p^\infty_n(\xi), p^\infty_{n+1}(\xi))$, and then $\dist(x_1, x_2) \leq C +
+  2D$.
+\end{proof}
+
+\begin{proposition}\label{prop:uniform_homotopies}
+  There exists a number $m_0$ and a function $\nu\from\posreals\to\posreals$ such
+  that $\nu(\eta)\to0$ as $\eta\to0$ with the following property. Let
+  $\gamma\from\boundary\Delta^{d+1}\to\boundary G$ be a continuous map. Let $n
+  \geq m_0$ and let $f$ be an affine approximation to
+  $p^\infty_n\composed\gamma$. Then there is a homotopy $h$ from $\gamma$ to
+  $i^n_\infty\composed f$ such that for any $x \in \boundary\Delta^{d+1}$ and
+  any $s$ and $t$ in $[0,1]$,
+  \begin{align*}
+    \rho(h(x,s), h(x,t)) \leq \nu(\abs{s-t}) a^{-n}.
+  \end{align*}
+\end{proposition}
+
+\begin{proof}
+  Let $C$ be as in \cref{lem:name_this} and apply \cref{prop:basic_homotopies}
+  to obtain a number $m_0\geq n_0$ and a function $\mu$.
+
+  Let $\gamma\from\boundary\Delta^{d+1}\to\boundary G$, $n\geq m_0$ and
+  $f\from\boundary\Delta^{d+1}\to K_n$ be as in the proposition. Let $f_0 = f$,
+  and for $m > 0$ let $f_m\from\boundary\Delta^{d+1}\to K_{n+m}$ be a
+  simplicial approximation to $p^\infty_{n+m}\composed\gamma$. For $m \geq 0$
+  let $\gamma_m = i^{m+n}_\infty\composed f_m$. For each $m\geq 0$ the
+  following observations are immediate:
+  \begin{enumerate}
+    \item the map $f_m$ admits a factoring;
+    \item the image of $f_m$ is contained in the $d$-skeleton of $K_{n+m}$, and
+      so $i^{n+m}_{n+m+1}\composed f_m$ admits a factoring;
+    \item by \cref{lem:name_this} we have $\newdist(i^{n+m}_{n+m+1}\composed
+      f_m(x), f_{m+1}(x)) \leq C$ for all $x \in \boundary\Delta^{d+1}$.
+  \end{enumerate}
+  Therefore, for each $m$, \cref{prop:basic_homotopies} gives a homotopy $h_m$
+  from $i^{n+m+1}_\infty\composed f_{m+1}$ to $i^{n+m}_\infty \composed f_m$
+  satisfying a uniform continuity condition. Define an infinite concatenation
+  of these homotopies:
+  \begin{align*}
+    h(x,t) = 
+    \begin{cases}
+      \gamma(x) & \text{if } t = 0\\
+      h_n\left(x,2^{m+1}\left(t-\frac{1}{2^{m+1}}\right)\right) 
+              & \text{if $t \in \left[\frac{1}{2^{m+1}}, \frac{1}{2^m}\right]$
+                    , $m\geq 0$}.
+    \end{cases}
+  \end{align*}
+  This function is clearly continuous except possibly on
+  $\boundary\Delta^{d+1}\times\{0\}$. We aim to show it is also continuous
+  there, but first we define the function $\nu$.
+
+  Let $m \in \naturals$. We aim to bound the distance $\rho(h(x,s), h(x,t))$
+  for $\abs{s,t} \leq 2^{-m}$ independently of $n$ and the particular path
+  $\gamma$. We first treat the case when one of $s$ and $t$ is $0$, then we
+  deal with the case when $s$ and $t$ are small, and finally we treat the case
+  when $s$ and $t$ are large. (Our ``small'' and ``large'' regions intersect,
+  to guarantee that this covers all possibilities.)
+
+  To begin, we bound the distance $\rho(h(x,0), h(x,t))$
+  where $x \in \boundary \Delta^{d+1}$ and $t < 2^{-m}$. Let $C'$ be the
+  constant appearing in \cref{lem:convergestoidentity}. Then 
+  \begin{align*}
+    \rho(h(x,0), h(x,2^{-m})) \leq C'a^{-m-n}.
+  \end{align*}
+  Furthermore, for any $m' \in \naturals$ and any $t \in [2^{-m'-1}, 2^{-m'}]$,
+  \begin{align*}
+    \rho(h(x,t), h(x,2^{-m'})) \leq \mu(1)a^{-m'-n}.
+  \end{align*}
+  It follows that for $t \leq 2^{-m}$,
+  \begin{align*}
+    \rho(h(x,0), h(x,t)) \leq a^{-n}\left(C'a^{-m} + \sum_{m' \geq m}
+          \mu(1)a^{-m'}\right).
+  \end{align*}
+
+  Similarly, we treat the ``small'' case. Here $s$ and $t$ are \emph{small} if
+  they are at most $2^{-m/2}$. If $s$ and $t$ are both at most this large
+  then
+  \begin{align*}
+    \rho(h(x,s), h(x,t)) \leq a^{-n} \sum_{m' \geq \floor{m/2}} \mu(1) a^{-m'}
+  \end{align*}
+
+  Finally, if $s$ and $t$ are such that $\abs{s-t} \leq 2^{-m}$ but at least
+  one of $s$ and $t$ is greater than $2^{-m/2}$ then both $s$ and $t$ are at
+  least $2^{-m/2}$. This is the ``large'' case. It follows that 
+  \begin{align*}
+    \rho(h(x,s), h(x,t)) &\leq a^{-n} \mu(\abs{s-t} 2^{m/2 + 1}) \\
+                         &\leq a^{-n} \mu(2^{1-m/2})
+  \end{align*}
+
+  Therefore for $\eta \in (2^{-m-1}, 2^{-m}]$ we define
+  \begin{align*}
+    \nu(\eta)  = \max\left\{
+      C'a^{-m} + \sum_{m' \geq m} \mu(1)a^{-m'},
+      \sum_{m' \geq \floor{m/2}} \mu(1) a^{-m'},
+      \mu(2^{1-m/2})
+    \right\},
+  \end{align*}
+  and we see that $\nu(\eta) \to 0$ as $\eta \to 0$, and also that
+  \begin{align*}
+    \rho(h(x,s), h(x,t)) \leq \nu(\abs{s-t})
+  \end{align*}
+  for any $x \in \boundary\Delta^{d+1}$ and $s$ and $t$ in $[0,1]$.
+
+  It remains to show that $h$ is continuous at $(x,0)$ for each $x$ in
+  $\boundary\Delta^{d+1}$. Let $\epsilon > 0$ and take a neighbourhood $U$ of
+  $x$ in $\boundary\Delta^{d+1}$ such that $\rho(\gamma(x), \gamma(y)) \leq
+  \epsilon/2$ for $y$ in $U$. Let $\eta > 0$ be so that $\nu(\eta) <
+  \epsilon/2$. Then for any $(y, t) \in U \times [0, \eta]$, $\rho(h(x,0),
+  h(y,t)) < \epsilon$.
+\end{proof}
+
+\Cref{thm:ddagimpliesLCd} follows as a corollary of this proposition.
+
+\ddagimpliesLCd*
+
+\begin{proof}
+  To begin, let $\nu$ and $m_0 \geq n_0$ be as in
+  \cref{prop:uniform_homotopies}. Let $r_0 =
+  k_1a^{-m_0}$, so that, by \cref{lem:projectstoasimplex},
+  $p^\infty_{m_0}\composed\gamma$ has image contained in the star of a single
+  vertex of $K_{m_0}$ for any map $\gamma\from\boundary\Delta^{d+1}\to\boundary
+  G$ with $\Diam\image(\gamma)\leq r_0$.
+
+  Let $\gamma\from\boundary\Delta^{d+1}\to\boundary G$ be such a map. Let 
+  \begin{align*}
+    m = \floor{\log_a(k_1/\Diam\image\gamma)} \geq m_0,
+  \end{align*}
+  so that by \cref{lem:projectstoasimplex} $p^\infty_{m}\composed\gamma$ has
+  image contained in a single vertex of $K_m$. Then a constant map
+  $\boundary\Delta^{d+1} \to K_m$ is a simplicial approximation to
+  $p^\infty_m\composed\gamma$; applying \cref{prop:uniform_homotopies} to
+  this map immediately gives a homotopy $h$ from $\gamma$ to the constant map.
+
+  Furthermore,
+  \begin{align*}
+    \Diam\image h &\leq \Diam\image\gamma + \sup_{x \in\boundary\Delta^{d+1}, s,t \in [0,1]} \rho(h(x,s), h(x,t)) \\
+                  &\leq \Diam\image\gamma + a^{-m} \nu(1) \\
+                  &\leq (1 + a\nu(1)/k_1) \Diam\image\gamma \qedhere
+  \end{align*}
+\end{proof}
 

### 2020-01-14 paper.tex
Corrected a macro

@@
   such that for $n$ sufficiently large there is a map
-  $i^n_{n+1}\from \Sk_1 K_n \to \Sk_1 K_{n+1}$ satisfying the following
+  $i^n_{n+1}\from \Skel_1 K_n \to \Skel_1 K_{n+1}$ satisfying the following
   conditions:
@@
     \item for each $n$, $i^n_{n+1}$ is an affine map on the subdivision
-      $\sd_k\Sk_1 K_n$,
+      $\sd_k\Skel_1 K_n$,
     \item for any vertex $x$ of $K_n$, $\dist(x, i^n_{n+1}(x)) \leq ?$, and

### 2020-01-14 paper.tex
Various bug fixes

@@
 
-Using this property we define maps $i^n_{n+1}\from \Sk^1 K_n$ to $\Sk^1K_{n+1}$
-as follows.
+Using this property we define maps $i^n_{n+1}\from \Skel_1 K_n$ to
+$\Skel_1K_{n+1}$ as follows.
 
@@
 
-\begin{theorem}
+\begin{restatable}{theorem}{ddagimpliesLCd}
   If $G$ satisfies $\Sd_M$ for all $M$ then $\boundary G$ is locally simply
   connected.
-\end{theorem}
+\end{restatable}
 

### 2020-01-15 paper.tex
Changed align*s to equation*s
To make qedhere work

@@
   containing $x$ and $y$ respectively, then
-  \begin{align*}
+  \begin{equation*}
     \abs{\newdist(x,y) - \dist(x^\star, y^\star)} \leq 2D
-  \end{align*}
+  \end{equation*}
 \end{remark}
@@
   $\gromov{x}{y}{z}$ of $x$, $y$ and $z$} as follows.
-  \begin{align*}
+  \begin{equation*}
     \gromov{x}{y}{z} = \frac{1}{2}\left(\newdist(x,y) + \newdist(x,z) -
           \newdist(y,z)\right)
-  \end{align*}
+  \end{equation*}
 \end{definition}
@@
     \item For $\xi \in \boundary G$, the set
-      \begin{align*}
+      \begin{equation*}
         \set{x \in K \union \boundary G \suchthat \gromov{e}{x}{\xi} \geq N}_{N\in\naturals}
-      \end{align*}
+      \end{equation*}
       is a fundamental system of neighbourhoods for the point $x$.
@@
   follows that
-  \begin{align*}
+  \begin{equation*}
     \Diam\{g_1, \dotsc, g_k\} \leq 6\delta+ 2 \leq D.\qedhere
-  \end{align*}
+  \end{equation*}
 \end{proof}
@@
 For each $n$, fix a partition of unity subordinate to the open covering 
-\begin{align*}
+\begin{equation*}
   \set{V_n(x) \suchthat x \in S_n}
-\end{align*} 
+\end{equation*} 
 of $\boundary G$. This is equivalent to a continuous map $\pi_n \from \boundary
@@
   \alpha_2(0) = e$. Then for any $m_1$ and $m_2$,
-  \begin{align*}
+  \begin{equation*}
     \gromov{e}{\alpha_1(m_1)}{\alpha_2(m_2)} \geq 
         \min\{m_1 - 3\delta, m_2 - 3\delta, \gromov{e}{\alpha_1(\infty)}{\alpha_2(\infty)} - 6\delta\}
-  \end{align*}
+  \end{equation*}
 \end{lemma}
@@
   By~\cite{bridsonhaefliger99},
-  \begin{align*}
+  \begin{equation*}
     \gromov{e}{\alpha_1(\infty)}{\alpha_2(\infty)} \leq \liminf_{n_1, n_2}
         \gromov{e}{\alpha_1(n_1)}{\alpha_2(n_2)} + 2\delta.
-  \end{align*}
+  \end{equation*}
   Let $n_1 \geq m_1$ and $n_2 \geq m_2$.
@@
   2\delta$. Therefore $\dist(\alpha_1(m_1), \alpha_2) \leq 3\delta$, and so
-  \begin{align*}
+  \begin{equation*}
     \gromov{e}{\alpha_1(m_1)}{\alpha_2(m_2)} \geq \min\{m_1, m_2\} - 3\delta
-  \end{align*}
+  \end{equation*}
   and the result follows.
@@
   Otherwise,
-  \begin{align*}
+  \begin{equation*}
     \dist(\alpha_1(n_1), \alpha_2(n_2)) = \dist(\alpha_1(n_1), p_1) +
         \dist(p_1, p_2) + \dist(p_2, \alpha_2(n_2)).
-  \end{align*}
+  \end{equation*}
   Therefore,
@@
   It follows that
-  \begin{align*}
+  \begin{equation*}
     \gromov{e}{\alpha_1(\infty)}{\alpha_2(\infty)} \leq \gromov{e}{\alpha_1(m_1)}{\alpha_2(m_2)} + 6\delta,
-  \end{align*}
+  \end{equation*}
   which completes the proof.
@@
   \log_a(k_1/\rho_0)$. Therefore, by \cref{lem:boundary_gromov_product},
-  \begin{align*}
+  \begin{equation*}
     \gromov{e}{\alpha_1(n)}{\alpha_2(n)} \geq \min\{n - 3\delta, \log_a(k_1/\rho_0) - 6\delta\}.
-  \end{align*}
+  \end{equation*}
   In particular,
-  \begin{align*}
+  \begin{equation*}
     \dist(\alpha_1(n), \alpha_2(n)) \leq \max\{6\delta, 12\delta - 2(\log(k_1/\rho_0) - n)\}
-  \end{align*}
+  \end{equation*}
   and the result follows.
@@
   and } \xi \in V_n(g)\}$.  We show that the union
-  \begin{align*}
+  \begin{equation*}
     \set{g \in S_m \suchthat \xi \in V_m(g)} \union \{p^n_m(g) \suchthat g \in S_n \text{ and } \xi \in V_n(g)\}
-  \end{align*}
+  \end{equation*}
   of these sets spans a simplex in $K_n$; this simplex then contains
@@
       deduce that 
-      \begin{align*}
+      \begin{equation*}
         \dist(x,p_i)\leq\dist(g_i,x) - \dist(g_i,p_i) + 2\delta =2\delta.
-      \end{align*}
+      \end{equation*}
   \end{enumerate}
@@
   large enough.
-  \begin{align*}
+  \begin{equation*}
     0 \leq \dist(g_i, v) + \dist(v, x) - n_i \leq 2\delta.
-  \end{align*}
+  \end{equation*}
 
@@
       inequality:
-      \begin{align*}
+      \begin{equation*}
         0 \leq \dist(g_i, v') + \dist(v', x') - n_i \leq 2\delta.
-      \end{align*}
+      \end{equation*}
       And therefore,
-      \begin{align*}
+      \begin{equation*}
         -2\delta \leq \dist(g_i, v) + \dist(v, x') - n_i \leq 4\delta.
-      \end{align*}
+      \end{equation*}
       Finally, putting these inequalities together,
-      \begin{align*}
+      \begin{equation*}
         \dist(v,x') \leq \dist(v,x) + 4\delta,
-      \end{align*}
+      \end{equation*}
       and thus we can uniformly bound this distance in this case.
@@
       sufficiently large:
-      \begin{align*}
+      \begin{equation*}
         0 \leq \dist(g_i, x') + \dist(x', x) - \dist(g_i, x) \leq 6\delta.
-      \end{align*}
+      \end{equation*}
       Finally, for $i$ sufficiently large, $\dist(g_i, x') = \dist(g_i, x) = n_i$,
       so
-      \begin{align*}
+      \begin{equation*}
         \dist(x,x') \leq 6\delta.
-      \end{align*}
+      \end{equation*}
   \end{enumerate}
@@
   $q_i(\zeta)$ is contained in the minimal simplex of $H_i$ with vertex set
-  \begin{align*}
+  \begin{equation*}
     N_{2\delta+1} \set{\eta(n_i)\suchthat\text{$\eta$ a geodesic ray with
     $\eta(0) = g_i$ and $\eta(\infty) = \zeta$}}.
-  \end{align*}\qed
+  \end{equation*}\qed
 \end{lemma}
@@
   For any compact subset $C \subset H$ there exists $i_0$ such that
-  \begin{align*}
+  \begin{equation*}
     \bigunion_{i\geq i_0} q_i^{-1} C
-  \end{align*}
+  \end{equation*}
   is a relatively compact subset of $\boundary G - \set\xi$.
@@
 
-\begin{restatable}{theorem}{ddagimpliesLCd}
+\begin{restatable}{theorem}{ddagimpliesLCd}\label{thm:ddagimpliesLCd}
   If $G$ satisfies $\Sd_M$ for all $M$ then $\boundary G$ is locally simply
@@
   \dist(x_n, e) + 1$ and $\dist(x_{n+1}, x_n)$ bounded. Then,
-  \begin{align*}
+  \begin{equation*}
     \gromov{e}{x_m}{x_n} \geq \dist(e,x_m) - C
-  \end{align*}
+  \end{equation*}
   for some constant $C$ depending only on $\delta$ and the bound on 
@@
   inequality.
-  \begin{align*}
+  \begin{equation*}
     \vdistance(\alpha_n(\infty), \alpha_m(\infty)) \leq C_1 a^{-i_m}
-  \end{align*}
+  \end{equation*}
   for some constants $C_1$ depending only on $\delta$ and $C_0$. Then, by
   definition of the visual metric, there exists a constant $C_2$ such that
-  \begin{align*}
+  \begin{equation*}
     \gromov{e}{\alpha_n(\infty)}{\alpha_m(\infty)} \geq i_m - C_2.
-  \end{align*}
+  \end{equation*}
 
@@
   that
-  \begin{align*}
-    \gromov{e}{\alpha_n(i_n)}{\alpha_m(i_m)} \geq i_m - C_3,\qedhere
-  \end{align*}
+  \begin{equation*}
+    \gromov{e}{\alpha_n(i_n)}{\alpha_m(i_m)} \geq i_m - C_3,
+  \end{equation*}
   as required.
@@
   There is a constant $C$ such that if $x \in \Skel_{d+1} K_m$ then
-  \begin{align*}
+  \begin{equation*}
     \gromov{e}{i^m_n(x)}{x} \geq m - C
-  \end{align*}
+  \end{equation*}
   for all $n\geq m\geq n_0$.
@@
   \leq RD$.  Putting this together,
-  \begin{align*}
+  \begin{equation*}
       \dist(y_n, y_{n+1}) \leq \epsilon + RD
-  \end{align*}
+  \end{equation*}
 
@@
   that
-  \begin{align*}
+  \begin{equation*}
       \gromov{e}{i^m_n(x)}{x} \geq m - C - 3D.\qedhere
-  \end{align*}
+  \end{equation*}
 \end{proof}
@@
   common simplex of $\Skel_{d+1} K_m$ then
-  \begin{align*}
+  \begin{equation*}
     \gromov{e}{i^m_n(x)}{i^m_n(y)} \geq m - C
-  \end{align*}
+  \end{equation*}
   for all $n\geq m$.
@@
   $x \in \boundary\Delta^{d+1}$ and any $s$ and $t$ in $[0,1]$,
-  \begin{align*}
+  \begin{equation*}
     \rho(h(x,s), h(x,t)) \leq \mu(\abs{s-t})a^{-n}.
-  \end{align*}
+  \end{equation*}
 \end{proposition}
@@
   that $f_0$ and $f_1$ are both affine on $J$. Then the map 
-  \begin{align*}
+  \begin{equation*}
     f_0 \disjointunion f_1 \from J \times \{0\} \disjointunion J \times \{1\}
           \to K_n,
-  \end{align*}
+  \end{equation*}
   defined on a subset of the product simplicial complex $J \times [0,1]$,
@@
   h(x,t)) \leq 2C_0a^{-n-N}$. It follows that we may take $\mu(\eta)$ as follows:
-  \begin{align*}
+  \begin{equation*}
     \mu(\eta) = 2C_0 a^{-\floor*{\frac{\log\kappa(\eta)}{\log k}}}.\qedhere
-  \end{align*}
+  \end{equation*}
 \end{proof}
@@
   constant $C$ such that 
-  \begin{align*}
+  \begin{equation*}
     \gromov{e}{i^m_n\composed p^\infty_m(\xi)}{p^\infty_m(\xi)} \geq m - C
-  \end{align*} 
+  \end{equation*} 
   for each $n\geq m\geq n_0$.
@@
   $i^n_{n+1}\composed p^\infty_n(\xi)$ and $p^\infty_{n+1}(\xi)$ respectively,
-  \begin{align*}
+  \begin{equation*}
     \dist(x_1, x_2) \leq C.
-  \end{align*}
+  \end{equation*}
 \end{lemma}
@@
   any $s$ and $t$ in $[0,1]$,
-  \begin{align*}
+  \begin{equation*}
     \rho(h(x,s), h(x,t)) \leq \nu(\abs{s-t}) a^{-n}.
-  \end{align*}
+  \end{equation*}
 \end{proposition}
@@
   of these homotopies:
-  \begin{align*}
+  \begin{equation*}
     h(x,t) = 
@@
     \end{cases}
-  \end{align*}
+  \end{equation*}
   This function is clearly continuous except possibly on
@@
   constant appearing in \cref{lem:convergestoidentity}. Then 
-  \begin{align*}
+  \begin{equation*}
     \rho(h(x,0), h(x,2^{-m})) \leq C'a^{-m-n}.
-  \end{align*}
+  \end{equation*}
   Furthermore, for any $m' \in \naturals$ and any $t \in [2^{-m'-1}, 2^{-m'}]$,
-  \begin{align*}
+  \begin{equation*}
     \rho(h(x,t), h(x,2^{-m'})) \leq \mu(1)a^{-m'-n}.
-  \end{align*}
+  \end{equation*}
   It follows that for $t \leq 2^{-m}$,
-  \begin{align*}
+  \begin{equation*}
     \rho(h(x,0), h(x,t)) \leq a^{-n}\left(C'a^{-m} + \sum_{m' \geq m}
           \mu(1)a^{-m'}\right).
-  \end{align*}
+  \end{equation*}
 
@@
   then
-  \begin{align*}
+  \begin{equation*}
     \rho(h(x,s), h(x,t)) \leq a^{-n} \sum_{m' \geq \floor{m/2}} \mu(1) a^{-m'}
-  \end{align*}
+  \end{equation*}
 
@@
   Therefore for $\eta \in (2^{-m-1}, 2^{-m}]$ we define
-  \begin{align*}
+  \begin{equation*}
     \nu(\eta)  = \max\left\{
@@
     \right\},
-  \end{align*}
+  \end{equation*}
   and we see that $\nu(\eta) \to 0$ as $\eta \to 0$, and also that
-  \begin{align*}
+  \begin{equation*}
     \rho(h(x,s), h(x,t)) \leq \nu(\abs{s-t})
-  \end{align*}
+  \end{equation*}
   for any $x \in \boundary\Delta^{d+1}$ and $s$ and $t$ in $[0,1]$.
@@
   Let $\gamma\from\boundary\Delta^{d+1}\to\boundary G$ be such a map. Let 
-  \begin{align*}
+  \begin{equation*}
     m = \floor{\log_a(k_1/\Diam\image\gamma)} \geq m_0,
-  \end{align*}
+  \end{equation*}
   so that by \cref{lem:projectstoasimplex} $p^\infty_{m}\composed\gamma$ has

### 2020-01-21 paper.tex
Altered the ddag and Sd symbols.

@@
     \item for any vertex $x$ of $K_n$, $\dist(x, i^n_{n+1}(x)) \leq ?$, and
-    \item for each $n$, $i^n_{n+1}$ is affine homotopic to a map that factors
-      through $p^\infty_{n+1}\from \boundary G \to K_{n+1}$.
+    \item for each $n$, the map $i^n_{n+1}$ is affine homotopic to a map that
+      factors through $p^\infty_{n+1}\from \boundary G \to K_{n+1}$.
   \end{enumerate}
@@
 
-In this section we introduce a new condition that a hyperbolic group might satisfy.
+\todo{Proposition below}
+
+\begin{proposition}\label{prop:extendingaffinemaps2}
+  Something about extending affine maps.
+\end{proposition}
+
+In this section we introduce a new condition that a hyperbolic group might
+satisfy.
 
 \begin{definition}
-  We say that $G$ satisfies $\Sd_M$ if there exists $k$ such that for any $n$
+  We say that $G$ satisfies $\S_M$ if there exists $k$ such that for any $n$
   sufficiently large and any affine map $f\from \boundary\Delta^2$ \todo{Do
@@
 \begin{restatable}{theorem}{ddagimpliesLCd}\label{thm:ddagimpliesLCd}
-  If $G$ satisfies $\Sd_M$ for all $M$ then $\boundary G$ is locally simply
+  If $G$ satisfies $\S_M$ for all $M$ then $\boundary G$ is locally simply
   connected.
@@
 \begin{proposition}\label{prop:ddag_implies_i}
-  Let $d \geq -1$. Suppose that $G$ satisfies the conditions $\Sd{d-1}$ and
-  $\dd{d}$. Then there are constants $n_0$, $k$ and $\epsilon$ such that for
+  Let $d \geq -1$. Suppose that $G$ satisfies the conditions $\S^{d-1}$ and
+  $\ddag^{d}$. Then there are constants $n_0$, $k$ and $\epsilon$ such that for
   each $n\geq n_0$ there is map $i^n_{n+1}\from\Skel_{d+1} K_n \to \Skel_{d+1}
@@
 \begin{proof}
-  The condition $\dd{-1}$ implies the infinitude of $G$, so
+  The condition $\ddag^{-1}$ implies the infinitude of $G$, so
   \cref{lem:near_geod_rays} is applicable. For $x \in \Vertices{K_n}$ choose an
@@
 
-Throughout the remainder of this section we assume that $G$ satisfies $\dd{d-1}$ 
-and $\Sd{d}$. Let $n_0$, $k$ and $\epsilon$ be the constants given in 
+Throughout the remainder of this section we assume that $G$ satisfies $\ddag^{d-1}$ 
+and $\S^{d}$. Let $n_0$, $k$ and $\epsilon$ be the constants given in 
 \cref{prop:ddag_implies_i}, and for $n\geq n_0$ let $i^n_{n+1} 

### 2020-01-21 paper.tex
Mostly proved the double dagger thing

@@
 
+\begin{lemma}\label{lem:uniform_continuity}
+  For any compact subset $C \subset \boundary G - \set\xi$ there exists $i_0$
+  and $\epsilon > 0$ such that $C \in U_i$ for $i \geq i_0$, and so that
+  $\newdist(q_i(\zeta_1), q_i(\zeta_2)) \leq ?$ whenever $i \geq i_0$ and
+  $\zeta_1$ and $\zeta_2$ are points in $C$ with $\rho(\zeta_1, \zeta_2) \leq
+  \epsilon$.
+\end{lemma}
+
+\begin{proof}
+  \todo{Prove this uniform continuity statement.}
+\end{proof}
+
 \section{The double dagger condition}
@@
   in $\boundary G - \set\xi$ as $i \to \infty$.
-  \todo{finish this}
+
+  Let $C$ be a compact subset of $\boundary G - \set\xi$ containing a path
+  $\beta$ from $\zeta_1$ to $\zeta_2$ and also a neighbourhood of each of the
+  points $\zeta_1$ and $\zeta_2$. Let $\epsilon$ and $i_0$ be as in
+  Lemma~\ref{lem:uniform_continuity}. By increasing $i_0$ we may also assume
+  that $\zeta_1^i$ and $\zeta_2^i$ are contained in $C$ for $i \geq i_0$. By
+  decreasing $\epsilon$ we may assume that the $\epsilon$-neighbourhoods of
+  $\zeta_1$ and $\zeta_2$ are contained in $C$.
+
+  Since $\boundary G$ is locally path connected, there exists a neighbourhood
+  of $\zeta_1$ (repsectively $\zeta_2$) such that any point in this
+  neighbourhood is joined to $\zeta_1$ (respectively $\zeta_2$) by a path
+  contained in the $\epsilon$-neighbourhood of $\zeta_1$. Now increase $i_0$ to
+  ensure that $\zeta_1^i$ and $\zeta_2^i$ are contained in these neighbourhoods
+  for $i \geq i_0$. Let $\alpha_1^i$ (respectively $\alpha_2^i$) be a path in
+  the ball of radius $\epsilon$ centred at $\zeta_1$ (respectively $\zeta_2$)
+  connecting $\zeta_1^i$ (repsectively $\zeta_2^i$) to $\zeta_1$ (respectively
+  $\zeta_2$.)
+
+  Then the concatenation of $\alpha_1^i$, $\beta$ and $\alpha_2^i$ gives a path
+  in $C$ from $\zeta_1^i$ to $\zeta_2^i$ that can be cut into boundedly many
+  subpaths of diameter at most $\epsilon$. It follows that the composition of
+  this path with $q_i$ is a path that admits a simplicial approximation
+  connecting $x_1$ to $x_2$ after boundedly many subdivisions of the interval.
+  For $i \geq i_0$ sufficiently large this gives a contradiction.
+  \todo{Check this paragraph.}
 \end{proof}
@@
 
+In what follows we will make use of the following lemma, adapted from
+from~\cite{bestvinamess91}
+
+\begin{lemma}\cite{bestvinamess91}\label{lem:near_geod_rays}
+  Let $G$ be infinite. For any $x \in X$ there exists a geodesic ray $\alpha$ 
+  with $\alpha(0) = e$ and $\dist(x,\alpha) \leq 2\delta$.
+
+  Furthermore, $\dist(x, \alpha(\dist(e,x))) \leq 4\delta$.
+\end{lemma}
+
+\begin{proof}
+  For the first claim, see~\cite{bestvinamess91}. For the second, let $p$ be a 
+  point on $\alpha$ such that $\dist(x, p) \leq 2\delta$. Then the triangle 
+  inequality shows that $\abs{\dist(e,p), \dist(e,x)} \leq 2\delta$, and 
+  so $\dist(p, \alpha(\dist(e,x))) \leq 2\delta$. Then the result 
+  follows from another application of the triangle inequality.
+\end{proof}
+
 \begin{proposition}
-  Suppose that $G$ satisfies $\ddag'_M$ for $M = D+2$. Then there exists $k$
+  Suppose that $G$ satisfies $\ddag'_M$ for $M = ?$. Then there exists $k$
   such that for $n$ sufficiently large there is a map
@@
 \begin{proof}
-  \todo{Prove this}
+  First we define $i^n_{n+1}$ on the vertex set of $K_n$. For a vertex $x$ of
+  $K_n$, let $\alpha$ be a geodesic with $\dist(x, \alpha(n)) \leq 4\delta$ and
+  let $i^n_{n+1}(x)$ be any vertex of the minimal simplex of $K_{n+1}$
+  containing $p^\infty_{n+1}(\gamma_x(\infty))$. Then the second claimed
+  property follows from \todo{why?}
+
+  For an edge $e$ of $K_n$, the distance between the images of the end points
+  of $e$ under $i^n_{n+1}$ is at most \todo{?} and it follows that \todo{prove
+  this}.
 \end{proof}
@@
 
-\todo{Proposition below}
-
 \begin{proposition}\label{prop:extendingaffinemaps2}
-  Something about extending affine maps.
+  \todo{Proposition about extending affine maps.}
 \end{proposition}
@@
 \subsection{Constructing maps to $\boundary G$}
-
-We will make frequent use of the following lemma, adapted 
-from~\cite{bestvinamess91}
-
-\begin{lemma}\cite{bestvinamess91}\label{lem:near_geod_rays}
-  Let $G$ be infinite. For any $x \in X$ there exists a geodesic ray $\alpha$ 
-  with $\alpha(0) = e$ and $\dist(x,\alpha) \leq 2\delta$.
-
-  Furthermore, $\dist(x, \alpha(\dist(e,x))) \leq 4\delta$.
-\end{lemma}
-
-\begin{proof}
-  For the first claim, see~\cite{bestvinamess91}. For the second, let $p$ be a 
-  point on $\alpha$ such that $\dist(x, p) \leq 2\delta$. Then the triangle 
-  inequality shows that $\abs{\dist(e,p), \dist(e,x)} \leq 2\delta$, and 
-  so $\dist(p, \alpha(\dist(e,x))) \leq 2\delta$. Then the result 
-  follows from another application of the triangle inequality.
-\end{proof}
 

### 2020-01-22 paper.tex
Wrote down a S condition

@@
 
-In this section we introduce a new condition that a hyperbolic group might
-satisfy.
+We now introduce a new condition, which should be thought of as a version of
+$\ddag_M$ one dimension higher.
 
@@
   We say that $G$ satisfies $\S_M$ if there exists $k$ such that for any $n$
-  sufficiently large and any affine map $f\from \boundary\Delta^2$ \todo{Do
-  this}
+  sufficiently large and any simplicial map $f\from \sd^M\boundary\Delta^2 \to
+  K_n$ that is a simplicial approximation to a map that factors through
+  $p^\infty_n \from \boundary G \to K_n$, $f$ admits an extension to $\Delta^2$
+  that is affine on $\sd^k \Delta^2$.
 \end{definition}

### 2020-01-22 paper.tex
Proved the existence of i^n_n+1 on the 1-skeleton

@@
 \boundary G$. Using $\newdist$ we extend the Gromov product to $K$:
+\todo{This looks shit.}
 
@@
       \begin{equation*}
-        \set{x \in K \union \boundary G \suchthat \gromov{e}{x}{\xi} \geq N}_{N\in\naturals}
+        \set{x \in K \union \boundary G 
+              \suchthat \gromov{e}{x}{\xi} \geq N}_{N\in\naturals}
       \end{equation*}
@@
   $y$ are connected by a path of length at most $L$ in the complement of the
-  ball with radius $\dist(x,y) - 3\delta$ with centre $1 \in G$.
-  \todo{$3\delta$?}
+  ball with radius $\dist(x,y) - \delta$ with centre $1 \in G$.
 \end{definition}
@@
   Furthermore, $\dist(x, \alpha(\dist(e,x))) \leq 4\delta$.
+  \todo{Since I'm assuming ideal triangles are delta-slim, 2delta should be
+  delta and 4delta should be 2delta.}
 \end{lemma}
@@
 \begin{proposition}
-  Suppose that $G$ satisfies $\ddag'_M$ for $M = ?$. Then there exists $k$
-  such that for $n$ sufficiently large there is a map
-  $i^n_{n+1}\from \Skel_1 K_n \to \Skel_1 K_{n+1}$ satisfying the following
-  conditions:
+  Suppose that $G$ satisfies $\ddag'_{D + 8\delta+2}$. Then there exists $L$
+  such that for $n$ sufficiently large there is a map $i^n_{n+1}\from \Skel_1
+  K_n \to \Skel_1 K_{n+1}$ satisfying the following conditions:
   \begin{enumerate}
     \item for each $n$, $i^n_{n+1}$ is an affine map on the subdivision
-      $\sd_k\Skel_1 K_n$,
-    \item for any vertex $x$ of $K_n$, $\dist(x, i^n_{n+1}(x)) \leq ?$, and
+      $\sd_L\Skel_1 K_n$,
+    \item for any vertex $x$ of $K_n$, $\dist(x, i^n_{n+1}(x)) \leq 4\delta+1$,
+      and
     \item for each $n$, the map $i^n_{n+1}$ is affine homotopic to a map that
@@
 \begin{proof}
+  Let $n_0$ and $L$ be the numbers given by the condition $\ddag'_{D + 8\delta
+  + 2}$ and let $n \geq n_0$.
+
   First we define $i^n_{n+1}$ on the vertex set of $K_n$. For a vertex $x$ of
-  $K_n$, let $\alpha$ be a geodesic with $\dist(x, \alpha(n)) \leq 4\delta$ and
-  let $i^n_{n+1}(x)$ be any vertex of the minimal simplex of $K_{n+1}$
-  containing $p^\infty_{n+1}(\gamma_x(\infty))$. Then the second claimed
-  property follows from \todo{why?}
-
-  For an edge $e$ of $K_n$, the distance between the images of the end points
-  of $e$ under $i^n_{n+1}$ is at most \todo{?} and it follows that \todo{prove
-  this}.
+  $K_n$, let $\gamma_x$ be a geodesic with $\dist(x, \gamma_x(n)) \leq 4\delta$
+  and let $i^n_{n+1}(x)$ be $\gamma_x(n+1)$, which is a vertex of a simplex
+  containing $p^\infty_{n+1}(\gamma_n(\infty))$. Then $\dist(x, i^n_{n+1}(x))
+  \leq 4\delta + 1$, as required by the second condition.
+
+  For an edge $e$ of $K_n$ with end points $x_1$ and $x_2$, the distance
+  $\dist(x_1, x_2)$ is at most $D + 8\delta + 2$. It follows that there is a
+  path $\alpha$ from $\gamma_{x_1}(\infty)$ to $\gamma_{x_2}(\infty)$ in
+  $\boundary G$ so that $p^\infty_{n+1}\composed\alpha$ admits a simplicial
+  approximation connecting $i^n_{n+1}(x_1)$ to $i^n_{n+1}(x_2)$ after at most
+  $L$ subdivisions. Define $i^n_{n+1}$ to be this simplicial map on $\sd^L e$.
+
+  This process defines a map $i^n_{n+1}\from \Skel_1 K_n\to \Skel_1 K_{n+1}$
+  with the required properties.
 \end{proof}

### 2020-01-24 paper.tex
typos
Mostly proved something

@@
 
-We denote by $\gromov{{-}}{{-}}{{-}}$ the Gromov product on $G \union
-\boundary G$. Using $\newdist$ we extend the Gromov product to $K$:
-\todo{This looks shit.}
+We denote by $\gromov{a}{b}{c}$ the Gromov product of $b$ and $c$ in $G \union
+\boundary$ with respect to base point $a \in G$. Using $\newdist$ we extend the
+Gromov product to $K$:
 
@@
   \delta$ and $y_i\to\xi$ as $i\to\infty$.  For each $i$ let $z_i$ be a point
-  on $\alpha$ with $\dist(y_i, z_i) \delta$.
+  on $\alpha$ with $\dist(y_i, z_i) \leq \delta$.
 
@@
       \begin{equation*}
-        \dist(x,x') \leq 6\delta.
+        \dist(x,x') \leq 6\delta.\qedhere
       \end{equation*}
@@
 
-\begin{lemma}\label{lem:describing_q_i}\todo{Check this}
+\begin{lemma}\label{lem:describing_q_i}\todo{Check this and state uniform continuity lemma as appropriate}
   Let $\zeta \in \boundary G - \set\xi$ and suppose that $q_i(\zeta) \in H_i$
@@
     $\eta(0) = g_i$ and $\eta(\infty) = \zeta$}}.
-  \end{equation*}\qed
+  \end{equation*}
 \end{lemma}
@@
 
-  \todo{Is star actually the right word?}
-  Then for each $i$ a geodesic from $g_i$ to $\zeta_i$ passes through the star 
-  in $H$ of $C$.  After passing to a subsequence these geodesic rays converge to 
-  a bi-infinite geodesic passing through the star in $H$ of $C$, both end points 
-  of which must be $\xi$, which is a contradiction.
+  Then for each $i$ a geodesic from $g_i$ to $\zeta_i$ passes through the subcomplex
+  of $H$ comprising all simplices that meet $C$.  After passing to a
+  subsequence these geodesic rays converge to a bi-infinite geodesic passing
+  through the star in $H$ of $C$, both end points of which must be $\xi$, which
+  is a contradiction.
 \end{proof}
@@
 \begin{lemma}\label{lem:uniform_continuity}
-  For any compact subset $C \subset \boundary G - \set\xi$ there exists $i_0$
-  and $\epsilon > 0$ such that $C \in U_i$ for $i \geq i_0$, and so that
-  $\newdist(q_i(\zeta_1), q_i(\zeta_2)) \leq ?$ whenever $i \geq i_0$ and
-  $\zeta_1$ and $\zeta_2$ are points in $C$ with $\rho(\zeta_1, \zeta_2) \leq
-  \epsilon$.
-\end{lemma}
-
-\begin{proof}
-  \todo{Prove this uniform continuity statement.}
+  For any point $\zeta \in \boundary G - \set\xi$, there is a neighbourhood $V$
+  of $\zeta$ and a number $i_0$ such that $V \subset U_i$ for all $i \geq i_0$,
+  and the diameter of $q_i(V)$ with respect to $\newdist$ is at most $?$.
+\end{lemma}
+
+\begin{proof}
+  Let $\zeta \in \boundary G - \set\xi$ and let $\alpha$ be a bi-infinite
+  geodesic from $\xi$ to $\zeta$. Let $x$ be a point on $\alpha$ so that the
+  distance between the sub-ray of $\alpha$ from $x$ to $\zeta$ and the set $H$
+  is at least $9\delta+2$.
+
+  Let $V$ be the following set. It is easy to check that this is a
+  neighbourhood of $\zeta$.
+  \begin{equation*}
+    V = \set{\beta(\infty) \suchthat \text{$\beta$ a geodesic with
+            $\beta(-\infty) = \xi$ and $\dist(\beta, x) \leq 3\delta+1$}}
+  \end{equation*}
+  The neighbourhood $V$ is relatively compact in $\boundary G - \set\xi$ so
+  there we may take $i_0$ such that $V \subset U_i$ for $i \geq i_0$. Enlarge
+  $i_0$ so that for any $i \geq i_0$, $\dist([\xi, g_i], x) \geq ?$.
+
+  Now let $\zeta_1$ and $\zeta_2$ be points in $V$ and let $i \geq i_0$. For
+  $j$ equal to $1$ or $2$ let $\gamma_j$ be any geodesic ray from $g_i$ to
+  $\zeta_j$ and let $\beta_j$ be a bi-infinite geodesic with $\beta_j(-\infty) =
+  \xi$, $\beta_j(\infty) = \zeta_j$ and $\dist(\beta_j, x) \leq 3\delta+1$; let
+  this minimal distance be realised by a point $y_j \in \beta_j$. By
+  considering a triangle with vertices $\xi$, $g_i$ and $\zeta_j$, $\dist(y_j,
+  \gamma_j) \leq \delta$, so $\dist(\gamma_j, x) \leq 4\delta+1$; let $z_j \in
+  \gamma_j$ minimise this minimal distance. Then $\dist(z_1, z_2) \leq
+  8\delta+2$.
+
+  Now, $\dist(x, H) \geq 9\delta+2$, so $\dist(z_j, H) \geq 5\delta+1$.
+  Furthermore, $\beta_j(n_i) \in H$. It follows that $\dist(\beta_j(n_i), [z_1,
+  z_2]) > \delta$ and so by considering a triangle with vertices $g_i$, $z_1$
+  and $z_2$, $\dist(\beta_1(n_i), \beta_2(n_i)) \leq 2\delta$. The result
+  follows by lemma~\ref{lem:describing_q_i}. 
 \end{proof}

### 2020-01-29 paper.tex
Improvements to the horoball section.

@@
 \begin{definition}
-  Let $U_i \subset \boundary G$ be the (closed) preimage of $H_i$ under the map 
-  $g_i \composed p^\infty_{n_i} \composed g_i^{-1} \from \boundary G \to X$.
-  Denote by $q_i$ the restriction of this map to $U_i$.
+  Let $U_i \subset \boundary G$ be the set of all points in $\boundary G -
+  \set\xi$ such that all geodesic rays from $g_i \in G$ to points in $U_i$ pass
+  through $H_i$. Let $q_i$ be the restriction of the map $g_i \composed
+  p^\infty_{n_i} \composed g_i^{-1}$ to $U_i$.
 \end{definition}
@@
 
-\begin{lemma}\label{lem:describing_q_i}\todo{Check this and state uniform continuity lemma as appropriate}
-  Let $\zeta \in \boundary G - \set\xi$ and suppose that $q_i(\zeta) \in H_i$
-  is defined, so $\zeta \in U_i$, and $N_{4\delta+1} q_i(\zeta) \in H_i$. Then
+\begin{lemma}\label{lem:describing_q_i}
+  The set $q_i(U_i)$ is contained in $H_i$.
+  Furthermore, let $\zeta \in U_i$ so that $q_i(\zeta) \in H_i$.  Then
   $q_i(\zeta)$ is contained in the minimal simplex of $H_i$ with vertex set
@@
     N_{2\delta+1} \set{\eta(n_i)\suchthat\text{$\eta$ a geodesic ray with
-    $\eta(0) = g_i$ and $\eta(\infty) = \zeta$}}.
+    $\eta(0) = g_i$ and $\eta(\infty) = \zeta$}} \intersection H_i
+  \end{equation*}
+  In particular, if $\eta$ is any geodesic ray with $\eta(0) = g_i$ and
+  $\eta(\infty) = \zeta$ then $q_i(\zeta)$ is contained in the minimal simplex
+  of $H_i$ with vertex set
+  \begin{equation*}
+    N_{4\delta + 1}(\eta(n_i)) \intersection H_i.
   \end{equation*}
@@
   in $U_i$ for infinitely many $i$. Then after passing to a subsequence there
-  exists for each $i$ a point $\zeta_i \in C\setminus U_i$.
-
-  \todo{This assumption is gone.}
-  By assumption, $g_i^{-1}(H_i)$ contains the star in $K_{n_i}$ of 
-  $g_i^{-1}(H_{i-1})$, so the definition of $p^\infty_{n_i}$ implies that a 
-  geodesic ray $\alpha_i$ from $e$ to $g_i^{-1}(\zeta_i)$ does not pass through 
-  $g_i^{-1}(H_{i-1})$. Equivalently, $g_i\composed\alpha_i$ is a geodesic from 
-  $g_i$ to $\zeta_i$ that does not pass through $H_{i-1}$.
-
-  After reparameterising and passing to a subsequence, the geodesic rays
-  $g_i\composed\alpha_i$ converge uniformly on compact subsets to a bi-infinite
-  geodesic from $\xi$ to some point $\zeta \in C$.  This geodesic does not pass
-  through $H$, which contradicts \cref{lem:geodesicsmeethorosphere}.
+  exists for each $i$ a point $\zeta_i \in C\setminus U_i$, so for each $i$
+  there is a geodesic ray $\alpha_i$ from $g_i$ to $\zeta_i$ that does not pass
+  through $H_i$.
+After passing to a subsequence, the rays $\alpha_i$ converge uniformly on compact susbets to a bi-infinite geodesic from $\xi$ to some $\zeta \in C$ that does not meet $H$, contardicting Lemma~\ref{lem:geodesicsmeethorosphere}.
 \end{proof}
@@
   such that for all $i \geq i_0$ and any $\zeta \in C$, $\newdist(q_i(\zeta),
-  q_{i_0}(\zeta)) \leq 8\delta + 2$, and, in particular, $q_i\restricted{C}$
+  q_{i_0}(\zeta)) \leq 10\delta + 2$, and, in particular, $q_i\restricted{C}$
   and $q_{i_0}\restricted{C}$ are related by an affine homotopy.
@@
 
-  Then for each $i$ a geodesic from $g_i$ to $\zeta_i$ passes through the subcomplex
-  of $H$ comprising all simplices that meet $C$.  After passing to a
-  subsequence these geodesic rays converge to a bi-infinite geodesic passing
-  through the star in $H$ of $C$, both end points of which must be $\xi$, which
-  is a contradiction.
+  Then for each $i$ a geodesic from $g_i$ to $\zeta_i$ passes within a bounded
+  distance of $C$. After passing to a subsequence these geodesic rays converge
+  to a bi-infinite geodesic passing within a bounded distance of $C$, both end
+  points of which must be $\xi$. This is a contradiction.
 \end{proof}
@@
   For any point $\zeta \in \boundary G - \set\xi$, there is a neighbourhood $V$
-  of $\zeta$ and a number $i_0$ such that $V \subset U_i$ for all $i \geq i_0$,
-  and the diameter of $q_i(V)$ with respect to $\newdist$ is at most $?$.
+  of $\zeta$ and a number $i_0$ such that, for all $i \geq i_0$, $V \subset U_i$ 
+  and the diameter of $q_i(V)$ with respect to $\newdist$ is at most $6\delta+2$.
 \end{lemma}
@@
   The neighbourhood $V$ is relatively compact in $\boundary G - \set\xi$ so
-  there we may take $i_0$ such that $V \subset U_i$ for $i \geq i_0$. Enlarge
-  $i_0$ so that for any $i \geq i_0$, $\dist([\xi, g_i], x) \geq ?$.
+  we may take $i_0$ such that $V \subset U_i$ for $i \geq i_0$. Enlarge $i_0$
+  so that for any $i \geq i_0$, $\dist([\xi, g_i], x) \geq 4\delta+1$.
 
@@
   Now, $\dist(x, H) \geq 9\delta+2$, so $\dist(z_j, H) \geq 5\delta+1$.
-  Furthermore, $\beta_j(n_i) \in H$. It follows that $\dist(\beta_j(n_i), [z_1,
+  Furthermore, $\gamma_j(n_i) \in H$. It follows that $\dist(\gamma_j(n_i), [z_1,
   z_2]) > \delta$ and so by considering a triangle with vertices $g_i$, $z_1$
-  and $z_2$, $\dist(\beta_1(n_i), \beta_2(n_i)) \leq 2\delta$. The result
+  and $z_2$, $\dist(\gamma_1(n_i), \gamma_2(n_i)) \leq 2\delta$. The result
   follows by lemma~\ref{lem:describing_q_i}. 

### 2020-01-30 paper.tex
Corrections to section 3

@@
 
-We begin this section by recalling results of Bestvina and Mess, Bowditch, and
-Swarup, which characterise the hyperbolic groups with locally (path) connected
+We begin this section by recalling work of Bestvina and Mess, Bowditch, and
+Swarup, which characterise the hyperbolic groups with locally path connected
 boundary. In~\cite{bestvinamess91}, Bestvina and Mess introduce the following
@@
 \begin{definition}
-  We say that $G$ satisfies $\ddag'_M$ if there exists a number $L$ such that,
-  for any $n$ sufficiently large any $\zeta_1$ and $\zeta_2$ in $\boundary G$
+  We say that $G$ satisfies $\ddag'_M$ if there exist numbers $L$ and $n_0$ such that,
+  for any $n \geq n_0$, any $\zeta_1$ and $\zeta_2$ in $\boundary G$
   such that $\newdist(p^\infty_n(\zeta_1), p^\infty_n(\zeta_2)) \leq M$, and
-  any points $x_1$ and $x_2$ in $K_n$ adjacent to $p^\infty_n(\zeta_1)$ and
+  any vertices $x_1$ and $x_2$ of $K_n$ adjacent to $p^\infty_n(\zeta_1)$ and
   $p^\infty_n(\zeta_2)$, there is a path $\alpha\from I\to \boundary G$ from
@@
   Now, $g_i\cdot \zeta_1^i$ and $g_i\cdot\zeta_2^i$ map by $q_i$ to points in
-  simplices adjacent to $x_1$ and $x_2$, so by Lemma~\ref{lem:propermaps} the
-  sequences we can pass to a subsequence so that the sequences $g_i\cdot
-  \zeta_1^i$ and $g_i\cdot\zeta_2^i$ converge to points $\zeta_1$ and $\zeta_2$
-  in $\boundary G - \set\xi$ as $i \to \infty$.
+  simplices adjacent to $x_1$ and $x_2$, so by Lemma~\ref{lem:propermaps} we
+  can pass to a subsequence so that the sequences $g_i\cdot \zeta_1^i$ and
+  $g_i\cdot\zeta_2^i$ converge to points $\zeta_1$ and $\zeta_2$ in $\boundary
+  G - \set\xi$ as $i \to \infty$.
 
@@
   $\beta$ from $\zeta_1$ to $\zeta_2$ and also a neighbourhood of each of the
-  points $\zeta_1$ and $\zeta_2$. Let $\epsilon$ and $i_0$ be as in
-  Lemma~\ref{lem:uniform_continuity}. By increasing $i_0$ we may also assume
-  that $\zeta_1^i$ and $\zeta_2^i$ are contained in $C$ for $i \geq i_0$. By
-  decreasing $\epsilon$ we may assume that the $\epsilon$-neighbourhoods of
-  $\zeta_1$ and $\zeta_2$ are contained in $C$.
-
-  Since $\boundary G$ is locally path connected, there exists a neighbourhood
-  of $\zeta_1$ (repsectively $\zeta_2$) such that any point in this
-  neighbourhood is joined to $\zeta_1$ (respectively $\zeta_2$) by a path
-  contained in the $\epsilon$-neighbourhood of $\zeta_1$. Now increase $i_0$ to
-  ensure that $\zeta_1^i$ and $\zeta_2^i$ are contained in these neighbourhoods
-  for $i \geq i_0$. Let $\alpha_1^i$ (respectively $\alpha_2^i$) be a path in
-  the ball of radius $\epsilon$ centred at $\zeta_1$ (respectively $\zeta_2$)
-  connecting $\zeta_1^i$ (repsectively $\zeta_2^i$) to $\zeta_1$ (respectively
-  $\zeta_2$.)
-
-  Then the concatenation of $\alpha_1^i$, $\beta$ and $\alpha_2^i$ gives a path
-  in $C$ from $\zeta_1^i$ to $\zeta_2^i$ that can be cut into boundedly many
-  subpaths of diameter at most $\epsilon$. It follows that the composition of
-  this path with $q_i$ is a path that admits a simplicial approximation
-  connecting $x_1$ to $x_2$ after boundedly many subdivisions of the interval.
-  For $i \geq i_0$ sufficiently large this gives a contradiction.
-  \todo{Check this paragraph.}
+  points $\zeta_1$ and $\zeta_2$. By Lemma~\ref{lem:uniform_continuity} and
+  compactness of $C$, there exists $\epsilon > 0$ and $i_0 \in \naturals$ such
+  that for subset $V$ of $C$ of diameter at most $\epsilon$ and any $i \geq
+  i_0$, $q_i(V)$ has diameter (with respect to $\newdist$) at most $6\delta+2$.
+  By increasing $i_0$ we may also assume that $\zeta_1^i$ and $\zeta_2^i$ are
+  contained in $C$ for $i \geq i_0$. By decreasing $\epsilon$ we may assume
+  that the $\epsilon$-neighbourhoods of $\zeta_1$ and $\zeta_2$ are contained
+  in $C$.
+
+  Since $\boundary G$ is locally path connected, for $j$ equal to $1$ or $2$
+  there exists a neighbourhood of $\zeta_j$ such that any point in this
+  neighbourhood is joined to $\zeta_j$ by a path contained in the
+  $\epsilon$-neighbourhood of $\zeta_j$. Now increase $i_0$ to ensure that
+  $\zeta_1^i$ and $\zeta_2^i$ are contained in these neighbourhoods for $i \geq
+  i_0$. Let $\alpha_1^j$ be a path in the ball of radius $\epsilon$ centred at
+  $\zeta_j$ connecting $\zeta_j^i$ to $\zeta_j$.
+
+  Then the concatenation $\alpha^i\from[0,1]\to \boundary G$ of $\alpha_1^i$,
+  $\beta$ and $\alpha_2^i$ gives a path in $C$ from $\zeta_1^i$ to $\zeta_2^i$
+  such that $I$ can be covered by boundedly many open intervals, each of which
+  has image under $\alpha^i$ with diameter at most $\epsilon$. It follows that
+  the composition of $\alpha^i$ with $q_i$ is a path that admits a simplicial
+  approximation connecting $x_1$ to $x_2$ after boundedly many subdivisions of
+  the interval. For $i \geq i_0$ large enough this gives a contradiction.
 \end{proof}
@@
 Using this property we define maps $i^n_{n+1}\from \Skel_1 K_n$ to
-$\Skel_1K_{n+1}$ as follows.
-
-In what follows we will make use of the following lemma, adapted from
-from~\cite{bestvinamess91}
+$\Skel_1K_{n+1}$ as follows.  We will make use of the following lemma, adapted
+from from~\cite{bestvinamess91}
 
@@
   Let $G$ be infinite. For any $x \in X$ there exists a geodesic ray $\alpha$ 
-  with $\alpha(0) = e$ and $\dist(x,\alpha) \leq 2\delta$.
-
-  Furthermore, $\dist(x, \alpha(\dist(e,x))) \leq 4\delta$.
-  \todo{Since I'm assuming ideal triangles are delta-slim, 2delta should be
-  delta and 4delta should be 2delta.}
+  with $\alpha(0) = e$ and $\dist(x,\alpha) \leq \delta$.
+
+  Furthermore, $\dist(x, \alpha(\dist(e,x))) \leq 2\delta$.
 \end{lemma}
@@
   For the first claim, see~\cite{bestvinamess91}. For the second, let $p$ be a 
-  point on $\alpha$ such that $\dist(x, p) \leq 2\delta$. Then the triangle 
-  inequality shows that $\abs{\dist(e,p), \dist(e,x)} \leq 2\delta$, and 
-  so $\dist(p, \alpha(\dist(e,x))) \leq 2\delta$. Then the result 
+  point on $\alpha$ such that $\dist(x, p) \leq \delta$. Then the triangle 
+  inequality shows that $\abs{\dist(e,p) - \dist(e,x)} \leq \delta$, and 
+  so $\dist(p, \alpha(\dist(e,x))) \leq \delta$. Then the result 
   follows from another application of the triangle inequality.
@@
 \begin{proposition}
-  Suppose that $G$ satisfies $\ddag'_{D + 8\delta+2}$. Then there exists $L$
+  Suppose that $G$ satisfies $\ddag'_{D + 4\delta+2}$. Then there exists $L$
   such that for $n$ sufficiently large there is a map $i^n_{n+1}\from \Skel_1
@@
       $\sd_L\Skel_1 K_n$,
-    \item for any vertex $x$ of $K_n$, $\dist(x, i^n_{n+1}(x)) \leq 4\delta+1$,
+    \item for any vertex $x$ of $K_n$, $\dist(x, i^n_{n+1}(x)) \leq 2\delta+1$,
       and
@@
   First we define $i^n_{n+1}$ on the vertex set of $K_n$. For a vertex $x$ of
-  $K_n$, let $\gamma_x$ be a geodesic with $\dist(x, \gamma_x(n)) \leq 4\delta$
+  $K_n$, let $\gamma_x$ be a geodesic with $\dist(x, \gamma_x(n)) \leq 2\delta$
   and let $i^n_{n+1}(x)$ be $\gamma_x(n+1)$, which is a vertex of a simplex
   containing $p^\infty_{n+1}(\gamma_n(\infty))$. Then $\dist(x, i^n_{n+1}(x))
-  \leq 4\delta + 1$, as required by the second condition.
-
-  For an edge $e$ of $K_n$ with end points $x_1$ and $x_2$, the distance
-  $\dist(x_1, x_2)$ is at most $D + 8\delta + 2$. It follows that there is a
-  path $\alpha$ from $\gamma_{x_1}(\infty)$ to $\gamma_{x_2}(\infty)$ in
-  $\boundary G$ so that $p^\infty_{n+1}\composed\alpha$ admits a simplicial
-  approximation connecting $i^n_{n+1}(x_1)$ to $i^n_{n+1}(x_2)$ after at most
-  $L$ subdivisions. Define $i^n_{n+1}$ to be this simplicial map on $\sd^L e$.
+  \leq 2\delta + 1$, as required by the second condition.
+
+  For an edge $e$ of $K_n$ connecting vertices $x_1$ and $x_2$,
+  $\dist(i^n_{n+1}(x_1), i^n_{n+1}(x_2))$ is at most $D + 4\delta + 2$. It
+  follows that there is a path $\alpha$ from $\gamma_{x_1}(\infty)$ to
+  $\gamma_{x_2}(\infty)$ in $\boundary G$ so that
+  $p^\infty_{n+1}\composed\alpha$ admits a simplicial approximation connecting
+  $i^n_{n+1}(x_1)$ to $i^n_{n+1}(x_2)$ after at most $L$ subdivisions. Define
+  $i^n_{n+1}$ to be this simplicial map on $\sd^L e$.
 

### 2020-01-31 paper.tex
Minor changes to section 4

@@
 
-\begin{proposition}
-  Suppose that $G$ satisfies $\ddag'_{D + 4\delta+2}$. Then there exists $L$
-  such that for $n$ sufficiently large there is a map $i^n_{n+1}\from \Skel_1
-  K_n \to \Skel_1 K_{n+1}$ satisfying the following conditions:
+\begin{proposition}\label{prop:i_in_dimension_1}
+  Suppose that $G$ satisfies $\ddag'_{D + 4\delta+2}$. Then there exist $L$ and
+  $n_0$ such that for $n\geq n_0$ there is a map $i^n_{n+1}\from \Skel_1 K_n
+  \to \Skel_1 K_{n+1}$ satisfying the following conditions:
   \begin{enumerate}
@@
 \begin{proof}
-  Let $n_0$ and $L$ be the numbers given by the condition $\ddag'_{D + 8\delta
+  Let $n_0$ and $L$ be the numbers given by the condition $\ddag'_{D + 4\delta
   + 2}$ and let $n \geq n_0$.
@@
 
-\begin{proposition}\label{prop:extendingaffinemaps2}
-  \todo{Proposition about extending affine maps.}
-\end{proposition}
-
 We now introduce a new condition, which should be thought of as a version of
@@
 \begin{definition}
-  We say that $G$ satisfies $\S_M$ if there exists $k$ such that for any $n$
-  sufficiently large and any simplicial map $f\from \sd^M\boundary\Delta^2 \to
-  K_n$ that is a simplicial approximation to a map that factors through
-  $p^\infty_n \from \boundary G \to K_n$, $f$ admits an extension to $\Delta^2$
-  that is affine on $\sd^k \Delta^2$.
+  Let $\Delta$ be the standard 2-simplex.  We say that $G$ satisfies $\S_M$ if
+  there exist $L$ and $n_0$ such that for any $n\geq n_0$ and any simplicial
+  map $f\from \sd^M\boundary\Delta \to K_n$ that is a simplicial approximation
+  to a map that factors through $p^\infty_n \from \boundary G \to K_n$, $f$
+  admits an extension to $\Delta$ that is affine on $\sd^L \Delta$.
 \end{definition}
@@
 
+Thrououghout the rest of this section we assume that $G$ satisfies
+\todo{conditions.}
+
 \subsection{Constructing maps to $\boundary G$}
@@
 We begin the proof of \cref{thm:ddagimpliesLCd} by proving the following 
-proposition.
-
-\begin{proposition}\label{prop:ddag_implies_i}
-  Let $d \geq -1$. Suppose that $G$ satisfies the conditions $\S^{d-1}$ and
-  $\ddag^{d}$. Then there are constants $n_0$, $k$ and $\epsilon$ such that for
-  each $n\geq n_0$ there is map $i^n_{n+1}\from\Skel_{d+1} K_n \to \Skel_{d+1}
-  K_{n+1}$ such that the following conditions hold.
+proposition, which extends the maps constructed in
+Proposition~\ref{prop:i_in_dimension_1}.
+
+\begin{proposition}\label{prop:i_in_dimension_2}
+  There are constants $n_0$ and $L$ such that for each $n\geq n_0$ there is map
+  $i^n_{n+1}\from\Skel_{d+1} K_n \to \Skel_{d+1} K_{n+1}$ such that the
+  following conditions hold.
   \begin{enumerate}
-    \item For any $x \in \Vertices(K_n)$, $\dist(x, i_{n+1}^n(x)) \leq
-      \epsilon$.
-    \item The map $i^n_{n+1}$ is affine on the subdivision $\sd^k\Skel_{d+1}
-      K_n$ of $\Skel_{d+1}K_n$.
-    \item The map $i^n_{n+1}\restricted{\Skel_d K_n}$ admits a factoring.
+    \item for each $n$, $i^n_{n+1}$ is an affine map on the subdivision
+      $\sd_L\Skel_2 K_n$,
+    \item for any vertex $x$ of $K_n$, $\dist(x, i^n_{n+1}(x)) \leq 2\delta+1$,
+      and
   \end{enumerate}
@@
 \begin{proof}
-  The condition $\ddag^{-1}$ implies the infinitude of $G$, so
-  \cref{lem:near_geod_rays} is applicable. For $x \in \Vertices{K_n}$ choose an
-  infinite geodesic ray $\alpha_x$ such that $\alpha(0) = 1$ and
-  $\dist(\alpha(n), x) \leq 4\delta$. Define $i^n_{n+1}(x) =
-  \alpha_x(n+1)$. Then $i^n_{n+1}$ satisfies the first requirement with
-  $\epsilon = 4\delta+2$ and satisfies the second requirement automatically.
-
-  Furthermore, $\alpha_x(\infty) \in V_{n+1}(\alpha_x(n+1))$, so 
-  $p^\infty_{n+1}(\alpha_x(\infty))$ lies in a simplex of $K_{n+1}$ that also 
-  contains $\alpha_x(n+1)$.  Therefore the map $i^n_{n+1}$ and a simplicial 
-  approximation to the map $x \mapsto \alpha_x(\infty) \mapsto p^\infty_{n+1} 
-  (\alpha_x(\infty))$ are related by an affine homotopy, so $i^n_{n+1}$ admits a 
-  factoring.
-
-  Now apply \cref{prop:extendingaffinemaps2} to extend $i^n_{n+1}$ from
-  $\Vertices(K_n)$ to $\Skel_{d+1} K_n$ to obtain a map with the required
-  properties.
-\end{proof}
-
-Throughout the remainder of this section we assume that $G$ satisfies $\ddag^{d-1}$ 
-and $\S^{d}$. Let $n_0$, $k$ and $\epsilon$ be the constants given in 
-\cref{prop:ddag_implies_i}, and for $n\geq n_0$ let $i^n_{n+1} 
-\from \sd^k\Skel_{d+1} K_n \to \Skel_{d+1} K_{n+1}$ be the affine map given by 
-that proposition.  For $n \geq m \geq n_0$ let $i^m_n$ be the composition 
+  \todo{Prove this}
+\end{proof}
+
+\begin{definition}
+  With the notation of Proposition~\ref{prop:i_in_dimension_2}, for $n \geq m
+  \geq n_0$ let $i^n_m \from \Skel_2 K_m \to \Skel_2 K_n$ be the composition
   $i^{n-1}_n \composed \dotsb \composed i^m_{m+1} \from \Skel_{d+1} K_m \to 
-\Skel_{d+1} K_n$.  This map is affine on a degree $k^{n-m}$ subdivision of 
+  \Skel_{d+1} K_n$.  This map is affine on a degree $L^{n-m}$ subdivision of 
   $\Skel_{d+1} K_m$.
+\end{definition}
 
@@
 \begin{lemma}\label{lem:useful}
+  \todo{Or quasi-geodesics?}
   Let $(x_n)$ be a sequence of points in $G$ with $\dist(x_{n+1}, e) = 
@@
   \end{equation*}
-
   Now, by \cref{lem:boundary_gromov_product} there exists a constant $C_3$ such
@@
 
-  We now bound the distance $\dist(y_n, y_{n+1}$. To start with, $\dist(y_n,
-  i^n_{n+1} y_n) \leq \epsilon$. Let $R$ be such that any two vertices in the
-  1-skeleton of $\sd^k \Delta^{d+1}$ are joined by a path traversing at most
-  $R$ edges. Let $\sigma$ be the minimal simplex of $K_n$ containing
-  $i^m_n(x)$. Then $y_n$ is a vertex of $\sigma$ and $y_{n+1}$ is a vertex of
-  the image of $\sigma$ under $i^n_{n+1}$, so $\dist(i^n_{n+1} y_n, y_{n+1})
-  \leq RD$.  Putting this together,
-  \begin{equation*}
-      \dist(y_n, y_{n+1}) \leq \epsilon + RD
+  We now bound the distance $\dist(y_n, y_{n+1})$. To start with, $\dist(y_n,
+  i^n_{n+1} y_n) \leq 2\delta+1$. Let $R$ be $3\cdot 2^{k-1}$, so that any two
+  vertices in the 1-skeleton of $\sd^k \Delta^{d+1}$ are joined by a path
+  traversing at most $R$ edges. Let $\sigma$ be the minimal simplex of $K_n$
+  containing $i^m_n(x)$. Then $y_n$ is a vertex of $\sigma$ and $y_{n+1}$ is a
+  vertex of the image of $\sigma$ under $i^n_{n+1}$, so $\dist(i^n_{n+1} y_n,
+  y_{n+1}) \leq RD$.  Putting this together,
+  \begin{equation*}
+      \dist(y_n, y_{n+1}) \leq 2\delta + 1 + RD
   \end{equation*}
@@
   It follows from \cref{lem:useful} that there exists a constant $C$ depending
-  only on $\delta$, $\epsilon$ and $k$ such that $\gromov{e}{y_n}{y_m} \geq m -
+  only on $\delta$ and $k$ such that $\gromov{e}{y_n}{y_m} \geq m -
   C$.
@@
 \begin{proof}
-  To start with, apply \cref{prop:extendingaffinemaps2} with $k = C + D$ to
-  obtain constants $k'$ and $m_0\geq n_0$ such that the conclusion of the
+  To start with, apply Proposition \todo{extending affine maps} with $k = C +
+  D$ to obtain constants $k'$ and $m_0\geq n_0$ such that the conclusion of the
   proposition holds.
@@
   defined on a subset of the product simplicial complex $J \times [0,1]$,
-  satisfies the conditions of \cref{prop:extendingaffinemaps2}, and so admits
+  satisfies the conditions of Proposition~\todo{extending maps}, and so admits
   an affine extension $F \from \sd^{k'} (J \times [0,1]) \to K_n$. Let $h =
@@
 
-  Furthermore, $\dist(y, i^n_{n+1}(y))$ is uniformly bounded by the constant
-  $\epsilon$ from \cref{prop:ddag_implies_i}, and $\newdist(i^n_{n+1}(y),
-  i^n_{n+1}\composed p^\infty_n (\xi))$ is bounded by the product of $D$ and
-  the constant $k$ appearing in \cref{prop:ddag_implies_i}. By putting all this
-  together we obtain a bound $C$ on $\newdist(i^n_{n+1}\composed
-  p^\infty_n(\xi), p^\infty_{n+1}(\xi))$, and then $\dist(x_1, x_2) \leq C +
-  2D$.
+  Furthermore, $\dist(y, i^n_{n+1}(y))$ is bounded by $2\delta+1$, and
+  $\newdist(i^n_{n+1}(y), i^n_{n+1}\composed p^\infty_n (\xi))$ is bounded by
+  the product of $D$ and the constant $k$ appearing in
+  \cref{prop:i_in_dimension_2}. By putting all this together we obtain a bound
+  $C$ on $\newdist(i^n_{n+1}\composed p^\infty_n(\xi), p^\infty_{n+1}(\xi))$,
+  and then $\dist(x_1, x_2) \leq C + 2D$.
 \end{proof}

### 2020-02-04 paper.tex
Minor punctuation changes

@@
   simplices adjacent to $x_1$ and $x_2$, so by Lemma~\ref{lem:propermaps} we
-  can pass to a subsequence so that the sequences $g_i\cdot \zeta_1^i$ and
+  can pass to a subsequence so that the sequences $g_i\cdot \zeta_1^i$ anl
   $g_i\cdot\zeta_2^i$ converge to points $\zeta_1$ and $\zeta_2$ in $\boundary
@@
 $\Skel_1K_{n+1}$ as follows.  We will make use of the following lemma, adapted
-from from~\cite{bestvinamess91}
+from from~\cite{bestvinamess91}.
 

### 2020-02-05 paper.tex
Changed Delta^d+1 to Delta^2 in section 4

@@
   i^n_{n+1} y_n) \leq 2\delta+1$. Let $R$ be $3\cdot 2^{k-1}$, so that any two
-  vertices in the 1-skeleton of $\sd^k \Delta^{d+1}$ are joined by a path
+  vertices in the 1-skeleton of $\sd^k \Delta^2$ are joined by a path
   traversing at most $R$ edges. Let $\sigma$ be the minimal simplex of $K_n$
@@
   property. Let $n \geq m_0$ and let $f_0$ and $f_1$ be any maps from
-  $\boundary\Delta^{d+1}$ to $K_n$ satisfying the following conditions:
+  $\boundary\Delta^2$ to $K_n$ satisfying the following conditions:
   \begin{enumerate}
     \item the maps $f_0$ and $f_1$ are affine on some subdivision of
-      $\boundary\Delta^{d+1}$;
-    \item for any $x \in \boundary\Delta^{d+1}$, the distance 
+      $\boundary\Delta^2$;
+    \item for any $x \in \boundary\Delta^2$, the distance 
       $\newdist(f_0(x), f_1(x))$ is at most $C$;
@@
   $i^n_\infty\composed f_1$ satisfying a uniform continuity condition: for any
-  $x \in \boundary\Delta^{d+1}$ and any $s$ and $t$ in $[0,1]$,
+  $x \in \boundary\Delta^2$ and any $s$ and $t$ in $[0,1]$,
   \begin{equation*}
@@
 
-  Let $n \geq m_0$.  Let $J$ be a subdivision of $\boundary\Delta^{d+1}$ such
+  Let $n \geq m_0$.  Let $J$ be a subdivision of $\boundary\Delta^2$ such
   that $f_0$ and $f_1$ are both affine on $J$. Then the map 
@@
   $C_0a^{-n+N}$. Therefore, if $N$ is such that $\kappa(\eta) \geq k^N$ then
-  for $x \in \boundary\Delta^{d+1}$ and $\abs{s-t} < \eta$, $\rho(h(x,s),
+  for $x \in \boundary\Delta^2$ and $\abs{s-t} < \eta$, $\rho(h(x,s),
   h(x,t)) \leq 2C_0a^{-n-N}$. It follows that we may take $\mu(\eta)$ as follows:
@@
   that $\nu(\eta)\to0$ as $\eta\to0$ with the following property. Let
-  $\gamma\from\boundary\Delta^{d+1}\to\boundary G$ be a continuous map. Let $n
+  $\gamma\from\boundary\Delta^2\to\boundary G$ be a continuous map. Let $n
   \geq m_0$ and let $f$ be an affine approximation to
   $p^\infty_n\composed\gamma$. Then there is a homotopy $h$ from $\gamma$ to
-  $i^n_\infty\composed f$ such that for any $x \in \boundary\Delta^{d+1}$ and
+  $i^n_\infty\composed f$ such that for any $x \in \boundary\Delta^2$ and
   any $s$ and $t$ in $[0,1]$,
@@
 
-  Let $\gamma\from\boundary\Delta^{d+1}\to\boundary G$, $n\geq m_0$ and
-  $f\from\boundary\Delta^{d+1}\to K_n$ be as in the proposition. Let $f_0 = f$,
-  and for $m > 0$ let $f_m\from\boundary\Delta^{d+1}\to K_{n+m}$ be a
+  Let $\gamma\from\boundary\Delta^2\to\boundary G$, $n\geq m_0$ and
+  $f\from\boundary\Delta^2\to K_n$ be as in the proposition. Let $f_0 = f$,
+  and for $m > 0$ let $f_m\from\boundary\Delta^2\to K_{n+m}$ be a
   simplicial approximation to $p^\infty_{n+m}\composed\gamma$. For $m \geq 0$
@@
     \item by \cref{lem:name_this} we have $\newdist(i^{n+m}_{n+m+1}\composed
-      f_m(x), f_{m+1}(x)) \leq C$ for all $x \in \boundary\Delta^{d+1}$.
+      f_m(x), f_{m+1}(x)) \leq C$ for all $x \in \boundary\Delta^2$.
   \end{enumerate}
@@
   This function is clearly continuous except possibly on
-  $\boundary\Delta^{d+1}\times\{0\}$. We aim to show it is also continuous
+  $\boundary\Delta^2\times\{0\}$. We aim to show it is also continuous
   there, but first we define the function $\nu$.
@@
   To begin, we bound the distance $\rho(h(x,0), h(x,t))$
-  where $x \in \boundary \Delta^{d+1}$ and $t < 2^{-m}$. Let $C'$ be the
+  where $x \in \boundary \Delta^2$ and $t < 2^{-m}$. Let $C'$ be the
   constant appearing in \cref{lem:convergestoidentity}. Then 
@@
   \end{equation*}
-  for any $x \in \boundary\Delta^{d+1}$ and $s$ and $t$ in $[0,1]$.
+  for any $x \in \boundary\Delta^2$ and $s$ and $t$ in $[0,1]$.
 
   It remains to show that $h$ is continuous at $(x,0)$ for each $x$ in
-  $\boundary\Delta^{d+1}$. Let $\epsilon > 0$ and take a neighbourhood $U$ of
-  $x$ in $\boundary\Delta^{d+1}$ such that $\rho(\gamma(x), \gamma(y)) \leq
+  $\boundary\Delta^2$. Let $\epsilon > 0$ and take a neighbourhood $U$ of
+  $x$ in $\boundary\Delta^2$ such that $\rho(\gamma(x), \gamma(y)) \leq
   \epsilon/2$ for $y$ in $U$. Let $\eta > 0$ be so that $\nu(\eta) <
@@
   $p^\infty_{m_0}\composed\gamma$ has image contained in the star of a single
-  vertex of $K_{m_0}$ for any map $\gamma\from\boundary\Delta^{d+1}\to\boundary
+  vertex of $K_{m_0}$ for any map $\gamma\from\boundary\Delta^2\to\boundary
   G$ with $\Diam\image(\gamma)\leq r_0$.
 
-  Let $\gamma\from\boundary\Delta^{d+1}\to\boundary G$ be such a map. Let 
+  Let $\gamma\from\boundary\Delta^2\to\boundary G$ be such a map. Let 
   \begin{equation*}
@@
   image contained in a single vertex of $K_m$. Then a constant map
-  $\boundary\Delta^{d+1} \to K_m$ is a simplicial approximation to
+  $\boundary\Delta^2 \to K_m$ is a simplicial approximation to
   $p^\infty_m\composed\gamma$; applying \cref{prop:uniform_homotopies} to
@@
   \begin{align*}
-    \Diam\image h &\leq \Diam\image\gamma + \sup_{x \in\boundary\Delta^{d+1}, s,t \in [0,1]} \rho(h(x,s), h(x,t)) \\
+    \Diam\image h &\leq \Diam\image\gamma + \sup_{x \in\boundary\Delta^2, s,t \in [0,1]} \rho(h(x,s), h(x,t)) \\
                   &\leq \Diam\image\gamma + a^{-m} \nu(1) \\

### 2020-02-05 paper.tex
Skel_d+1 to Skel_2 and minor changes

@@
   There are constants $n_0$ and $L$ such that for each $n\geq n_0$ there is map
-  $i^n_{n+1}\from\Skel_{d+1} K_n \to \Skel_{d+1} K_{n+1}$ such that the
+  $i^n_{n+1}\from\Skel_2 K_n \to \Skel_2 K_{n+1}$ such that the
   following conditions hold.
@@
   \geq n_0$ let $i^n_m \from \Skel_2 K_m \to \Skel_2 K_n$ be the composition
-  $i^{n-1}_n \composed \dotsb \composed i^m_{m+1} \from \Skel_{d+1} K_m \to 
-  \Skel_{d+1} K_n$.  This map is affine on a degree $L^{n-m}$ subdivision of 
-  $\Skel_{d+1} K_m$.
+  $i^{n-1}_n \composed \dotsb \composed i^m_{m+1} \from \Skel_2 K_m \to 
+  \Skel_2 K_n$.  This map is affine on a degree $L^{n-m}$ subdivision of 
+  $\Skel_2 K_m$.
 \end{definition}
@@
 \begin{lemma}\label{lem:linearproduct}
-  There is a constant $C$ such that if $x \in \Skel_{d+1} K_m$ then
+  There is a constant $C$ such that if $x \in \Skel_2 K_m$ then
   \begin{equation*}
@@
   \begin{equation*}
-      \dist(y_n, y_{n+1}) \leq 2\delta + 1 + RD
+    \dist(y_n, y_{n+1}) \leq (2\delta + 1) + RD
   \end{equation*}
@@
 \begin{corollary}
-  For $m \geq n_0$ and $x \in \Skel_{d+1} K_m$, the sequence
+  For $m \geq n_0$ and $x \in \Skel_2 K_m$, the sequence
   $(i^m_n(x))_{n\geq m}$ converges to a point in $\boundary G$, which we shall
@@
   There is a constant $C$ such that if $m \geq n_0$ and $x$ and $y$ are in a
-  common simplex of $\Skel_{d+1} K_m$ then
+  common simplex of $\Skel_2 K_m$ then
   \begin{equation*}
@@
   There is a constant $C$ such that for any $m\geq n_0$ and any simplex
-  $\sigma$ of $\Skel_{d+1} K_m$, the diameter of $i^m_{\infty}(\sigma)$ with
+  $\sigma$ of $\Skel_2 K_m$, the diameter of $i^m_{\infty}(\sigma)$ with
   respect to the visual metric $\vdistance$ is bounded above by $Ca^{-m}$,
@@
 \begin{proposition}\label{prop:continuouslimit}
-  The map $i^m_\infty\from \Skel_{d+1} K_m \to \boundary G$ is continuous.
+  The map $i^m_\infty\from \Skel_2 K_m \to \boundary G$ is continuous.
 \end{proposition}
@@
 \begin{proof}
-  Fix $x \in \Skel_{d+1} K_m$. Let $k$ be the constant given in the definition 
+  Fix $x \in \Skel_2 K_m$. Let $k$ be the constant given in the definition 
   of the map $i$. For $n\geq 0$ let $U_n$ be the star in $\beta^{nk} 
-  \Skel_{d+1}K_m$ of the minimal simplex of $\beta^{nk}\Skel_{d+1}K_m$ 
+  \Skel_2K_m$ of the minimal simplex of $\beta^{nk}\Skel_2K_m$ 
   containing $x$. Then $U_n$ is a neighbourhood of $x$ for each $n$.
@@
   For each $n$, the restriction of $i^m_{m+n}$ to a simplex in 
-  $\beta^{nk}\Skel_{d+1}K_m$ is affine, and therefore has image contained in a 
-  simplex of $\Skel_{d+1} K_{m+n}$. The point $x$ is contained in every simplex 
+  $\beta^{nk}\Skel_2K_m$ is affine, and therefore has image contained in a 
+  simplex of $\Skel_2 K_{m+n}$. The point $x$ is contained in every simplex 
   of $U_n$, so for any $y \in U_n$ the points $i^m_{m+n}(x)$ and $i^m_{m+n}(y)$ 
-  are contained in a common simplex of $\Skel_{d+1}K_m$. Therefore, by 
+  are contained in a common simplex of $\Skel_2K_m$. Therefore, by 
   \cref{cor:visualdiameter}, there is a constant $C$ such that 
@@
   Let $\alpha$ be a geodesic ray with $\alpha(0) = e$ and $\alpha(\infty) = 
-  \xi$. Then $\alpha(m)$ is a vertex of a simplex in $\Skel_{d+1}K_m$ containing 
+  \xi$. Then $\alpha(m)$ is a vertex of a simplex in $\Skel_2K_m$ containing 
   $p^\infty_m(\xi)$, and $\gromov{e}{\alpha(m)}{\alpha(n)} = m$ for $n\geq m$.

### 2020-02-05 paper.tex
Startedmaking changes, up to most of the way through section 4.1

@@
   The inequality of \cref{lem:linearproduct} is satisfied for each of $x$ 
-  and $y$. By~\cite{bridsonhaefliger99} there exist $\delta'$ depending only on 
-  $\delta$ such that
+  and $y$. By~\cite[Proposition III.H.1.22]{bridsonhaefliger99} there exist
+  $\delta'$ depending only on $\delta$ such that
   \begin{align*}
@@
   respect to the visual metric $\vdistance$ is bounded above by $Ca^{-m}$,
-  where $a$ is the visual parameter.
+  where $a$ is the visual parameter.\qed
 \end{corollary}
@@
 \begin{proposition}\label{prop:continuouslimit}
-  The map $i^m_\infty\from \Skel_2 K_m \to \boundary G$ is continuous.
+  For $m\geq n_0$ the map $i^m_\infty\from \Skel_2 K_m \to \boundary G$ is
+  continuous.
 \end{proposition}
@@
 \begin{proof}
-  Fix $x \in \Skel_2 K_m$. Let $k$ be the constant given in the definition 
-  of the map $i$. For $n\geq 0$ let $U_n$ be the star in $\beta^{nk} 
-  \Skel_2K_m$ of the minimal simplex of $\beta^{nk}\Skel_2K_m$ 
-  containing $x$. Then $U_n$ is a neighbourhood of $x$ for each $n$.
+  Fix $x \in \Skel_2 K_m$. For $n\geq 0$ let $U_n$ be the minimal subcomplex of
+  $\sd^{nk}\Skel_2 K_m$ containing a neighbourhood of $x$.
 
   For each $n$, the restriction of $i^m_{m+n}$ to a simplex in 
-  $\beta^{nk}\Skel_2K_m$ is affine, and therefore has image contained in a 
-  simplex of $\Skel_2 K_{m+n}$. The point $x$ is contained in every simplex 
+  $\sd^{nk}\Skel_2K_m$ is affine, and therefore has image contained in a 
+  simplex of $\Skel_2 K_{m+n}$. The point $x$ is contained in every maximal simplex 
   of $U_n$, so for any $y \in U_n$ the points $i^m_{m+n}(x)$ and $i^m_{m+n}(y)$ 
@@
   \cref{cor:visualdiameter}, there is a constant $C$ such that 
-  $\vdistance(i^m_\infty(x), i^m_\infty(y)) \leq Ca^{-(m+n)}$ for every $y \in 
-  U_n$.
+  $\vdistance(i^m_\infty(x), i^m_\infty(y)) \leq Ca^{-(m+n)}$ for every $n \geq
+  0$ and every $y \in U_n$.
 \end{proof}
@@
   the map $i^m_\infty$ can be shown to be H\"{o}lder continuous with exponent 
-  only depending on $\delta$ and the constants in the definition of the map $i$. 
-  We do not require this strengthening of \cref{prop:continuouslimit} 
-  here.
+  only depending on $\delta$ and $k$.  We do not require this strengthening of
+  \cref{prop:continuouslimit} here.
 \end{remark}
@@
   Let $C$ be a constant. Then there exists a number $m_0$ and a function $\mu
-  \from \posreals\to\posreals$ such that $\mu(\eta)\to0$ as $\eta\to0$ with the following
-  property. Let $n \geq m_0$ and let $f_0$ and $f_1$ be any maps from
-  $\boundary\Delta^2$ to $K_n$ satisfying the following conditions:
-  \begin{enumerate}
-    \item the maps $f_0$ and $f_1$ are affine on some subdivision of
-      $\boundary\Delta^2$;
-    \item for any $x \in \boundary\Delta^2$, the distance 
-      $\newdist(f_0(x), f_1(x))$ is at most $C$;
-    \item each of $f_0$ and $f_1$ admits a factoring.
-  \end{enumerate}
-  Then there is a homotopy $h$ from $i^n_\infty\composed f_0$ to
-  $i^n_\infty\composed f_1$ satisfying a uniform continuity condition: for any
-  $x \in \boundary\Delta^2$ and any $s$ and $t$ in $[0,1]$,
+  \from \posreals\to\posreals$ such that $\mu(\eta)\to0$ as $\eta\to0$ with the
+  following property. Let $n \geq m_0$ and let $\gamma_0$ and $\gamma_1$ be
+  maps from $\boundary\Delta\to\boundary G$. Let $f_0$ and $f_1$ be simplicial
+  approximations to $p^\infty_n\composed \gamma_0$ and
+  $p^\infty_n\composed\gamma_1$. Suppose that $\newdist(f_0(x), f_1(x))\leq C$
+  for every $x \in \boundary \Delta$. Then there is a homotopy $h$ from
+  $i^n_\infty\composed f_0$ to $i^n_\infty\composed f_1$ satisfying a uniform
+  continuity condition: for any $x \in \boundary\Delta^2$ and any $s$ and $t$
+  in $[0,1]$,
   \begin{equation*}
@@
 \begin{proof}
-  To start with, apply Proposition \todo{extending affine maps} with $k = C +
-  D$ to obtain constants $k'$ and $m_0\geq n_0$ such that the conclusion of the
-  proposition holds.
-
+  \todo{constant on ddag}
+  Let $G$ satisfy $\ddag'_?$ with constants $L$ and $m_0 \geq n_0$.
   Let $n \geq m_0$.  Let $J$ be a subdivision of $\boundary\Delta^2$ such
-  that $f_0$ and $f_1$ are both affine on $J$. Then the map 
+  that $f_0$ and $f_1$ are both affine on $J$. Then we have a map 
   \begin{equation*}
@@
   \end{equation*}
-  defined on a subset of the product simplicial complex $J \times [0,1]$,
+  defined on a subset of the product simplicial complex $J \times [0,1]$ and
+  this map is a simplicial approximation to the map $\gamma_0 \disjointunion
+  \gamma_1$ from $J\times\{0\} \disjointunion \{1\}$ to $\boundary G$. Using
+  $\ddag'_?$ we can extend $\gamma_0\disjointunion\gamma_1$ along $x \times
+  [0,1]$ for each vertex $x$ of $J$ in such a way that the extension along each
+  edge $x\times [0,1]$, when composed with $p^\infty_n$ admits a simplicial
+  approximation connecting $f_0(x)$ to $f_1(x)$ after at most $L$ subdivisions
+  of the interval.
+
+  \todo{Continue here!}
+  ,
   satisfies the conditions of Proposition~\todo{extending maps}, and so admits

### 2020-02-06 paper.tex
substantial changes to section 4
Brought it in line with the new "dimension 2" situation

@@
   i^n_{n+1} y_n) \leq 2\delta+1$. Let $R$ be $3\cdot 2^{k-1}$, so that any two
-  vertices in the 1-skeleton of $\sd^k \Delta^2$ are joined by a path
+  vertices in the 1-skeleton of $\sd^k \Delta$ are joined by a path
   traversing at most $R$ edges. Let $\sigma$ be the minimal simplex of $K_n$
@@
 \begin{proposition}\label{prop:basic_homotopies}
-  Let $C$ be a constant. Then there exists a number $m_0$ and a function $\mu
-  \from \posreals\to\posreals$ such that $\mu(\eta)\to0$ as $\eta\to0$ with the
-  following property. Let $n \geq m_0$ and let $\gamma_0$ and $\gamma_1$ be
-  maps from $\boundary\Delta\to\boundary G$. Let $f_0$ and $f_1$ be simplicial
-  approximations to $p^\infty_n\composed \gamma_0$ and
+  Let $C$ be a constant. Then there exist numbers $m_0$ and $\mu$
+  with the following property. Let $n \geq m_0$ and let $\gamma_0$ and
+  $\gamma_1$ be maps from $\boundary\Delta\to\boundary G$. Let $f_0$ and $f_1$
+  be simplicial approximations to $p^\infty_n\composed \gamma_0$ and
   $p^\infty_n\composed\gamma_1$. Suppose that $\newdist(f_0(x), f_1(x))\leq C$
@@
   $i^n_\infty\composed f_0$ to $i^n_\infty\composed f_1$ satisfying a uniform
-  continuity condition: for any $x \in \boundary\Delta^2$ and any $s$ and $t$
-  in $[0,1]$,
-  \begin{equation*}
-    \rho(h(x,s), h(x,t)) \leq \mu(\abs{s-t})a^{-n}.
-  \end{equation*}
+  continuity condition: for any $x \in \boundary\Delta$,
+  \begin{equation*}
+    \Diam(h(\{x\} \times [0,1])) \leq \mu a^{-n},
+  \end{equation*}
+  where the diameter is taken with respect to the visual metric.
 \end{proposition}
@@
   Let $G$ satisfy $\ddag'_?$ with constants $L$ and $m_0 \geq n_0$.
-  Let $n \geq m_0$.  Let $J$ be a subdivision of $\boundary\Delta^2$ such
+  Let $n \geq m_0$.  Let $J$ be a subdivision of $\boundary\Delta$ such
   that $f_0$ and $f_1$ are both affine on $J$. Then we have a map 
@@
   this map is a simplicial approximation to the map $\gamma_0 \disjointunion
-  \gamma_1$ from $J\times\{0\} \disjointunion \{1\}$ to $\boundary G$. Using
-  $\ddag'_?$ we can extend $\gamma_0\disjointunion\gamma_1$ along $x \times
-  [0,1]$ for each vertex $x$ of $J$ in such a way that the extension along each
-  edge $x\times [0,1]$, when composed with $p^\infty_n$ admits a simplicial
-  approximation connecting $f_0(x)$ to $f_1(x)$ after at most $L$ subdivisions
-  of the interval.
-
-  \todo{Continue here!}
-  ,
-  satisfies the conditions of Proposition~\todo{extending maps}, and so admits
-  an affine extension $F \from \sd^{k'} (J \times [0,1]) \to K_n$. Let $h =
-  i^n_\infty \composed F$, so $h$ is a homotopy from $i^n_\infty\composed f_0$
-  to $i^n_\infty\composed f_1$ and it remains to prove the uniform continuity
+  \gamma_1$ from $J\times\{0\} \disjointunion \{1\}$ to $\boundary G$.
+
+  Using $\ddag'_?$ we can extend $\gamma_0\disjointunion\gamma_1$ along $x
+  \times [0,1]$ for each vertex $x$ of $J$ in such a way that the extension
+  along each edge $x\times [0,1]$, when composed with $p^\infty_n$ admits a
+  simplicial approximation connecting $f_0(x)$ to $f_1(x)$ after at most $L$
+  subdivisions of the interval. Finally, using the condition $\S_?$, we deduce
+  that $f_0 \disjointunion f_1$ admints an extension to $J \times [0,1]$ after
+  only $k'$ barycentric subdivisions. Call the extension $F$ and let $h =
+  i^n_\infty \composed F$, so that $h$ is a homotopy from $i^n_\infty\composed
+  f_0$ to $i^n_\infty\composed f_1$. It remains to prove the bounded distance
   assertion.
 
-  Let $\eta_0$ be such that for $\eta$ at most $\eta_0$, 
-  for any $x \in \Delta^d$, for any $s$ and $t$ in $[0,1]$ with
-  $\abs{s-t} \leq \eta$, the segment $\{x\} \times [s,t]$ is contained in a
-  union of at most two $(d+1)$-simplices of $\sd^{k'}(\Delta^d \times [0,1])$.
-  We first define the modulus of continuity $\mu(\eta)$ for $\eta > \eta_0$.
-
-  Let $M$ be the number of $(d+1)$-simplices in $\sd^{k'}(\Delta^d \times
-  [0,1])$.  \Cref{cor:visualdiameter} gives a constant $C_0$ such that any
-  $(d+1)$-simplex of $K_n$ is mapped to a subset of $\boundary G$ of diameter
-  at most $C_0 a^{-n}$, and so we can take $\mu(\eta) = C_0M$ for $\eta >
-  \eta_0$.
-
-  Now, for $\eta \leq \eta_0$, there exists a maximal number $\kappa(\eta) \geq
-  0$ such that for any $x \in \Delta^d$ and any $s$ and $t$ in $[0,1]$ with
-  $\abs{s-t} \leq \eta$, the segment $\{x\} \times [s,t]$ is contained in a
-  union of at most two $(d+1)$-simplices of
-  $\sd^{\kappa(\eta)}\sd^{k'}(\Delta^d\times[0,1])$. Note that $\kappa(\eta)
-  \to \infty$ as $\eta \to 0$. Now, if $N\in\naturals$ then a $(d+1)$-simplex of
-  $\sd^{k^N}K_n$ is mapped by $i^n_{n+N}$ into a $(d+1)$-simplex of $K_{n+N}$,
-  which is mapped by $i^{n+N}_\infty$ to a set of diameter at most
-  $C_0a^{-n+N}$. Therefore, if $N$ is such that $\kappa(\eta) \geq k^N$ then
-  for $x \in \boundary\Delta^2$ and $\abs{s-t} < \eta$, $\rho(h(x,s),
-  h(x,t)) \leq 2C_0a^{-n-N}$. It follows that we may take $\mu(\eta)$ as follows:
-  \begin{equation*}
-    \mu(\eta) = 2C_0 a^{-\floor*{\frac{\log\kappa(\eta)}{\log k}}}.\qedhere
-  \end{equation*}
+  Let $M$ be the number of $2$-simplices in $\sd^{k'}([0,1]^2)$.
+  Corollary~\ref{cor:visualdiameter} gives a constant $C_0$ so that any
+  $2$-simplex is mapped by $i^n_\infty$ to a set of diameter at most $C_0
+  a^{-n}$, and so we can take $\mu = MC_0$.
 \end{proof}
@@
   p^\infty_m)$ to the identity map $\boundary G\to\boundary G$ is at most 
-  $Ca^{-m}$ for each $m$, where $a$ is the visual parameter.
+  $Ca^{-m}$ for each $m \geq n_0$.
 \end{lemma}
@@
 \begin{proposition}\label{prop:uniform_homotopies}
-  There exists a number $m_0$ and a function $\nu\from\posreals\to\posreals$ such
-  that $\nu(\eta)\to0$ as $\eta\to0$ with the following property. Let
-  $\gamma\from\boundary\Delta^2\to\boundary G$ be a continuous map. Let $n
-  \geq m_0$ and let $f$ be an affine approximation to
-  $p^\infty_n\composed\gamma$. Then there is a homotopy $h$ from $\gamma$ to
-  $i^n_\infty\composed f$ such that for any $x \in \boundary\Delta^2$ and
-  any $s$ and $t$ in $[0,1]$,
-  \begin{equation*}
-    \rho(h(x,s), h(x,t)) \leq \nu(\abs{s-t}) a^{-n}.
+  There exists numbers $m_0$ and $\nu$ with the following property. Let
+  $\gamma\from\boundary\Delta\to\boundary G$ be a continuous map. Let $n \geq
+  m_0$ and let $f$ be an affine approximation to $p^\infty_n\composed\gamma$.
+  Then there is a homotopy $h$ from $\gamma$ to $i^n_\infty\composed f$ such
+  that for any $x \in \boundary\Delta$,
+  \begin{equation*}
+    \Diam(h(\{x\}\times [0,1])) \leq \nu a^{-n}.
   \end{equation*}
@@
 \begin{proof}
-  Let $C$ be as in \cref{lem:name_this} and apply \cref{prop:basic_homotopies}
-  to obtain a number $m_0\geq n_0$ and a function $\mu$.
-
-  Let $\gamma\from\boundary\Delta^2\to\boundary G$, $n\geq m_0$ and
-  $f\from\boundary\Delta^2\to K_n$ be as in the proposition. Let $f_0 = f$,
-  and for $m > 0$ let $f_m\from\boundary\Delta^2\to K_{n+m}$ be a
+  Apply Proposition~\ref{prop:basic_homotopies} with $C$ as in
+  Lemma~\ref{lem:name_this} to obtain numbers $m_0$ and $\mu$.
+
+  Let $\gamma\from\boundary\Delta\to\boundary G$, $n\geq m_0$ and
+  $f\from\boundary\Delta\to K_n$ be as in the proposition. Let $f_0 = f$,
+  and for $m > 0$ let $f_m\from\boundary\Delta\to K_{n+m}$ be a
   simplicial approximation to $p^\infty_{n+m}\composed\gamma$. For $m \geq 0$
-  let $\gamma_m = i^{m+n}_\infty\composed f_m$. For each $m\geq 0$ the
-  following observations are immediate:
-  \begin{enumerate}
-    \item the map $f_m$ admits a factoring;
-    \item the image of $f_m$ is contained in the $d$-skeleton of $K_{n+m}$, and
-      so $i^{n+m}_{n+m+1}\composed f_m$ admits a factoring;
-    \item by \cref{lem:name_this} we have $\newdist(i^{n+m}_{n+m+1}\composed
-      f_m(x), f_{m+1}(x)) \leq C$ for all $x \in \boundary\Delta^2$.
-  \end{enumerate}
+  let $\gamma_m = i^{m+n}_\infty\composed f_m$.
+
+  \todo{Justify the application of the proposition.}
+
   Therefore, for each $m$, \cref{prop:basic_homotopies} gives a homotopy $h_m$
@@
       \gamma(x) & \text{if } t = 0\\
-      h_n\left(x,2^{m+1}\left(t-\frac{1}{2^{m+1}}\right)\right) 
+      h_m\left(x,2^{m+1}\left(t-\frac{1}{2^{m+1}}\right)\right) 
               & \text{if $t \in \left[\frac{1}{2^{m+1}}, \frac{1}{2^m}\right]$
@@
   This function is clearly continuous except possibly on
-  $\boundary\Delta^2\times\{0\}$. We aim to show it is also continuous
-  there, but first we define the function $\nu$.
-
-  Let $m \in \naturals$. We aim to bound the distance $\rho(h(x,s), h(x,t))$
-  for $\abs{s,t} \leq 2^{-m}$ independently of $n$ and the particular path
-  $\gamma$. We first treat the case when one of $s$ and $t$ is $0$, then we
-  deal with the case when $s$ and $t$ are small, and finally we treat the case
-  when $s$ and $t$ are large. (Our ``small'' and ``large'' regions intersect,
-  to guarantee that this covers all possibilities.)
-
-  To begin, we bound the distance $\rho(h(x,0), h(x,t))$
-  where $x \in \boundary \Delta^2$ and $t < 2^{-m}$. Let $C'$ be the
-  constant appearing in \cref{lem:convergestoidentity}. Then 
-  \begin{equation*}
-    \rho(h(x,0), h(x,2^{-m})) \leq C'a^{-m-n}.
-  \end{equation*}
-  Furthermore, for any $m' \in \naturals$ and any $t \in [2^{-m'-1}, 2^{-m'}]$,
-  \begin{equation*}
-    \rho(h(x,t), h(x,2^{-m'})) \leq \mu(1)a^{-m'-n}.
-  \end{equation*}
-  It follows that for $t \leq 2^{-m}$,
-  \begin{equation*}
-    \rho(h(x,0), h(x,t)) \leq a^{-n}\left(C'a^{-m} + \sum_{m' \geq m}
-          \mu(1)a^{-m'}\right).
-  \end{equation*}
-
-  Similarly, we treat the ``small'' case. Here $s$ and $t$ are \emph{small} if
-  they are at most $2^{-m/2}$. If $s$ and $t$ are both at most this large
-  then
-  \begin{equation*}
-    \rho(h(x,s), h(x,t)) \leq a^{-n} \sum_{m' \geq \floor{m/2}} \mu(1) a^{-m'}
-  \end{equation*}
-
-  Finally, if $s$ and $t$ are such that $\abs{s-t} \leq 2^{-m}$ but at least
-  one of $s$ and $t$ is greater than $2^{-m/2}$ then both $s$ and $t$ are at
-  least $2^{-m/2}$. This is the ``large'' case. It follows that 
+  $\boundary\Delta\times\{0\}$. We now show that it is continuous there, too.
+
+  Let $x \in \boundary\Delta$ and let $\epsilon > 0$. There exists $M$ such
+  that for $m \geq M$ and $y \in \boundary \Delta$, $\rho(\gamma(y),
+  \gamma_m(y)) \leq \epsilon/3$. Increasing $M$ if necessary we may assume that
   \begin{align*}
-    \rho(h(x,s), h(x,t)) &\leq a^{-n} \mu(\abs{s-t} 2^{m/2 + 1}) \\
-                         &\leq a^{-n} \mu(2^{1-m/2})
+    \sum_m \geq M \mu a^{-m-n} \leq \epsilon/3.
   \end{align*}
-
-  Therefore for $\eta \in (2^{-m-1}, 2^{-m}]$ we define
-  \begin{equation*}
-    \nu(\eta)  = \max\left\{
-      C'a^{-m} + \sum_{m' \geq m} \mu(1)a^{-m'},
-      \sum_{m' \geq \floor{m/2}} \mu(1) a^{-m'},
-      \mu(2^{1-m/2})
-    \right\},
-  \end{equation*}
-  and we see that $\nu(\eta) \to 0$ as $\eta \to 0$, and also that
-  \begin{equation*}
-    \rho(h(x,s), h(x,t)) \leq \nu(\abs{s-t})
-  \end{equation*}
-  for any $x \in \boundary\Delta^2$ and $s$ and $t$ in $[0,1]$.
-
-  It remains to show that $h$ is continuous at $(x,0)$ for each $x$ in
-  $\boundary\Delta^2$. Let $\epsilon > 0$ and take a neighbourhood $U$ of
-  $x$ in $\boundary\Delta^2$ such that $\rho(\gamma(x), \gamma(y)) \leq
-  \epsilon/2$ for $y$ in $U$. Let $\eta > 0$ be so that $\nu(\eta) <
-  \epsilon/2$. Then for any $(y, t) \in U \times [0, \eta]$, $\rho(h(x,0),
-  h(y,t)) < \epsilon$.
+  Finally, let $U$ be a neighbourhood of $x$ such that $\rho(\gamma(x),
+  \gamma(y)) \leq \epsilon/3$ for $y \in U$. Now, for any $y \in U$ and $t \in (0, 2^{-M}$,
+  \begin{equation*}
+    \rho{h(x,0), h(y,t)} \leq \frac{\epsilon}{3} + \frac{\epsilon}{3} +
+        \frac{\epsilon}{3} = \epsilon.
+  \end{equation*}
+  Therefore $h$ is continuous.
+
+  Finally, we immediately see that for any $x \in \boundary\Delta$,
+  \begin{equation*}
+    \Diam(h(\{x\}\times (0,1])) \leq \mu \left(\sum_{m\geq 0} a^{-m}\right)a^{-n},
+  \end{equation*}
+  and then $\Diam(h(\{x\}\times [0,1]))$ satisfies the same inequality by
+  continuity of $h$.
 \end{proof}
@@
   $p^\infty_{m_0}\composed\gamma$ has image contained in the star of a single
-  vertex of $K_{m_0}$ for any map $\gamma\from\boundary\Delta^2\to\boundary
+  vertex of $K_{m_0}$ for any map $\gamma\from\boundary\Delta\to\boundary
   G$ with $\Diam\image(\gamma)\leq r_0$.
 
-  Let $\gamma\from\boundary\Delta^2\to\boundary G$ be such a map. Let 
+  Let $\gamma\from\boundary\Delta\to\boundary G$ be such a map. Let 
   \begin{equation*}
@@
   image contained in a single vertex of $K_m$. Then a constant map
-  $\boundary\Delta^2 \to K_m$ is a simplicial approximation to
+  $\boundary\Delta \to K_m$ is a simplicial approximation to
   $p^\infty_m\composed\gamma$; applying \cref{prop:uniform_homotopies} to
@@
   \begin{align*}
-    \Diam\image h &\leq \Diam\image\gamma + \sup_{x \in\boundary\Delta^2, s,t \in [0,1]} \rho(h(x,s), h(x,t)) \\
-                  &\leq \Diam\image\gamma + a^{-m} \nu(1) \\
-                  &\leq (1 + a\nu(1)/k_1) \Diam\image\gamma \qedhere
+    \Diam\image h &\leq \Diam\image\gamma + \sup_{x \in\boundary\Delta} \Diam(h(\{x\} \times [0,1])) \\
+                  &\leq \Diam\image\gamma + a^{-m} \nu \\
+                  &\leq (1 + a\nu/k_1) \Diam\image\gamma \qedhere
   \end{align*}

### 2020-02-10 paper.tex
Proved taht simply connected implies S

@@
   \begin{align*}
-    \Diam\image h &\leq \Diam\image\gamma + \sup_{x \in\boundary\Delta} \Diam(h(\{x\} \times [0,1])) \\
+    \Diam\image h &\leq \Diam\image\gamma + \sup_{x \in\boundary\Delta}
+                                    \Diam(h(\{x\} \times [0,1])) \\
                   &\leq \Diam\image\gamma + a^{-m} \nu \\
@@
 
-In this section we give a sufficient condition for our condition
-\todo{condition} to be satisfied.
+In this section we give a sufficient condition for the condition $\S_M$ to be
+satisfied.
+
+\begin{proposition}
+  Suppose that $\boundary G - \set\xi$ is simply connected for any point $\xi
+  \in \boundary G$. Then $\S_M$ is satisfied for all $M$.
+\end{proposition}
+
+\begin{proof}
+  Suppose that the condition is not satisfied. Then for each $i$ there exists a
+  number $n_i \geq i$, a map $\gamma_i \from \boundary\Delta \to \boundary G$
+  and a simplicial map $f_i \from \sd^M \boundary\Delta \to K_{n_i}$ that is a
+  simplicial approimxation to $p^\infty_{n_i}\composed\gamma_i$ such that $f_i$
+  does not admit an extension to $\Delta$ that is affine on $\sd^i\Delta$.
+
+  Fix a vertex $v$ of $\boundary\Delta$; then there exist group elements $g_i
+  \in G$ such that $g_i\cdot f_i(v)$ is a fixed vertex of $K$. Pass to a
+  subsequence as in Section~\ref{sec:horoball}, and to a deeper subsequence so
+  that $g_i\cdot f_i(w)$ is independent of $i$ for all vertices $w \in \sd^M
+  \boundary\Delta$. Then the map $g_i\composed f_i$ is independent of $i$; call
+  this map $f$. It remains to show that $f$ is nullhomotopic in $H$; then it is
+  nullhomotopic by a simplicial map, and this gives a contradiction for $i$
+  sufficiently large.
+
+  By Lemma~\ref{lem:propermaps} there exists $i_0$ and a 
+  compact set $C_0 \subset \boundary G - \set\xi$ such that $C_0$ contains the
+  image of $\gamma_i$ for every $i \geq i_0$. By
+  Lemma~\ref{lem:affinehomotopic} there exists $i_1 \geq i_0$ such that
+  $q_i\restricted{C_0}$ is affine homotopic to $q_{i_1}\restricted{C_0}$ for
+  every $i \geq i_1$.
+
+  Let $h$ be a nullhomotopy of $\gamma_{i_1}$ in
+  $\boundary G - \set\xi$ and let $C_1$ be a compact subset of $\boundary G -
+  \set\xi$ containing $C_0$ and the image of $h$. Let $i_2$ be so that $C_1
+  \subset U_{i_2}$.
+
+  Then $f$ is homotopic to $q_{i_1}\composed\gamma_{i_1}$, which is homotopic
+  to $q_{i_2}\composed\gamma_{i_1}$, which is homotopic by $q_{i_2}\composed h$
+  to a point.
+  \todo{would just $i_0$ and $i_1$ have been enough?}
+\end{proof}
 

### 2020-02-14 paper.tex
Proof reading of sections 3-4

@@
       and
-    \item for each $n$, the map $i^n_{n+1}$ is affine homotopic to a map that
-      factors through $p^\infty_{n+1}\from \boundary G \to K_{n+1}$.
+    \item for each $n$, the map $i^n_{n+1}$ is a simplicial approximation a map
+      that factors through $p^\infty_{n+1}\from \boundary G \to K_{n+1}$.
   \end{enumerate}
@@
 We now introduce a new condition, which should be thought of as a version of
-$\ddag_M$ one dimension higher.
+$\ddag_M$ describing connectedness one dimension higher.
 
@@
 \begin{restatable}{theorem}{ddagimpliesLCd}\label{thm:ddagimpliesLCd}
-  If $G$ satisfies $\S_M$ for all $M$ then $\boundary G$ is locally simply
-  connected.
+  If $G$ satisfies $\ddag'_M$ and $\S_M$ for all $M$ then $\boundary G$ is
+  locally simply connected.
 \end{restatable}
@@
 Thrououghout the rest of this section we assume that $G$ satisfies
-\todo{conditions.}
+$\ddag'_M$ and $\S_M$ for all $M$.
 
@@
 \begin{proof} 
-  \todo{Prove this}
+  Let $n_0$ be as in Proposition~\ref{prop:i_in_dimension_1} and for $n \geq
+  n_0$ let $i^n_{n+1} \from \Skel_1 K_n \to \Skel_1 K_{n+1}$ be the maps given
+  by that proposition, so there exists $M$ such that $i^n_{n+1}$ is a
+  simplicial map on $\sd^M\Skel_1 K_n$, and this map is a simplicial
+  approximation to a map that factors through $p^\infty_{n+1} \from \boundary G
+  \to K_{n+1}$.
+
+  Then $\S_M$ gives numbers $L$ and $n_0' \geq n_0$ such that for $n \geq
+  n_0'$, for any 2-simplex $\sigma$ of $K_n$, $i^n_{n+1}\restricted\boundary
+  \sigma$ admits an extension to $\sigma$ that is affine on $\sd^L\sigma$.
+  Gluing these extensions together extends $i^n_{n+1}$ to a map $\sd^2 K_n \to
+  \sd_2 K_{n+1}$ with the required properties.
 \end{proof}
@@
 \begin{lemma}\label{lem:useful}
-  \todo{Or quasi-geodesics?}
   Let $(x_n)$ be a sequence of points in $G$ with $\dist(x_{n+1}, e) = 
-  \dist(x_n, e) + 1$ and $\dist(x_{n+1}, x_n)$ bounded. Then,
+  \dist(x_n, e) + 1$ and $\dist(x_{n+1}, x_n)$ bounded. Then for $n \geq m$,
   \begin{equation*}
@@
 \begin{proof}
-  We estimate the Gromov product using the visual metric $\vdistance$ on 
-  $\boundary G$; then the claimed inequality follows from the triangle 
-  inequality.
-
-  Let $i_n = \dist(x_n, e)$, so $i_n = i_0 + n$, and let 
-  $\dist(x_{n+1},x_n)$ be bounded by $C_0$. By 
-  \cref{lem:near_geod_rays} there exists a sequence $(\alpha_n)$ of 
-  geodesic rays with $\dist(\alpha_n(i_n), x_n) \leq 4\delta$. Then 
-  $\dist(\alpha_n(i_n), \alpha_{n+1}(i_{n+1})) \leq C_0 + 8\delta$. Then 
-  $\gromov{e}{\alpha_n(\infty)}{ \alpha_{n+1}(\infty)} \geq i_n - (C_0 + 
-  8\delta)/2$.
-
-  By the triangle inequality it follows that for $n\geq m$ we have the following 
-  inequality.
-  \begin{equation*}
-    \vdistance(\alpha_n(\infty), \alpha_m(\infty)) \leq C_1 a^{-i_m}
-  \end{equation*}
-  for some constants $C_1$ depending only on $\delta$ and $C_0$. Then, by
-  definition of the visual metric, there exists a constant $C_2$ such that
-  \begin{equation*}
-    \gromov{e}{\alpha_n(\infty)}{\alpha_m(\infty)} \geq i_m - C_2.
-  \end{equation*}
-  Now, by \cref{lem:boundary_gromov_product} there exists a constant $C_3$ such
-  that
-  \begin{equation*}
-    \gromov{e}{\alpha_n(i_n)}{\alpha_m(i_m)} \geq i_m - C_3,
-  \end{equation*}
-  as required.
+  By the triangle inequality, for any $n$ and $m$ we have $\dist(x_n, x_m) \geq
+  \abs{n - m}$.  On the other hand, let $B$ be the bound on $\dist(x_{n+1},
+  x_n)$. Then for any $n$ and $m$ we have $\dist(x_n, x_m) \leq B\abs{n - m}$. 
+  Finally, $\dist(e, x_n) = \dist(e, x_0) + n$.
+
+  It follows that the concatenation of a geodesic $[e, x_0]$ with the sequence
+  $(x_n)_{n = 0}^\infty$ is a quasi-geodesic with constants depending only on
+  $B$. Therefore by~\cite[Theorem III.H.1.7]{bridsonhaefliger99} there is a
+  number $R$ depending only on $B$ and $\delta$ such that the sequence $(x_n)$
+  is contained in an $R$-neighbourhood of a ray starting at $e$; let $(y_n)$ be
+  a sequence of points on this geodesic with $\dist(y_n, x_n) \leq R$. Then
+  $\gromov{e}{y_m}{y_n} = \min\{\dist(e, y_m), \dist(e, y_n)\}$, and the result
+  follows with $C = 5R/2$.
 \end{proof}
@@
   containing $i^m_n(x)$. Then, for each $n \geq m$, we have $\dist(e, y_{n+1})
-  = \dist(e, y_n)$.
-
-  We now bound the distance $\dist(y_n, y_{n+1})$. To start with, $\dist(y_n,
-  i^n_{n+1} y_n) \leq 2\delta+1$. Let $R$ be $3\cdot 2^{k-1}$, so that any two
-  vertices in the 1-skeleton of $\sd^k \Delta$ are joined by a path
-  traversing at most $R$ edges. Let $\sigma$ be the minimal simplex of $K_n$
-  containing $i^m_n(x)$. Then $y_n$ is a vertex of $\sigma$ and $y_{n+1}$ is a
-  vertex of the image of $\sigma$ under $i^n_{n+1}$, so $\dist(i^n_{n+1} y_n,
-  y_{n+1}) \leq RD$.  Putting this together,
+  = \dist(e, y_n)$.  We now bound the distance $\dist(y_n, y_{n+1})$. To start
+  with, $\dist(y_n, i^n_{n+1} (y_n)) \leq 2\delta+1$. Let $R$ be $3\cdot
+  2^{k-1}$, so that any two vertices in the 1-skeleton of $\sd^k \Delta$ are
+  joined by a path traversing at most $R$ edges. Let $\sigma$ be the minimal
+  simplex of $K_n$ containing $i^m_n(x)$. Then $y_n$ is a vertex of $\sigma$
+  and $y_{n+1}$ is a vertex of the image of $\sigma$ under $i^n_{n+1}$, so
+  $\dist(i^n_{n+1} y_n, y_{n+1}) \leq RD$.  Putting this together,
   \begin{equation*}
@@
   only on $\delta$ and $k$ such that $\gromov{e}{y_n}{y_m} \geq m -
-  C$.
-
-  Finally, by applying the inequality in \cref{rem:dist_vs_newdist}, we deduce
-  that
+  C$.  By applying the inequality in \cref{rem:dist_vs_newdist}, we deduce that
   \begin{equation*}
@@
   $\gromov{e}{i^m_{n_1}(x)}{i^m_{n_2}(x)} \geq \min\{n_1,n_2\} - C$, which
-  tends to infinity as $n_1$ and $n_2$ tend to infinity.
+  tends to infinity as $n_1$ and $n_2$ tend to infinity. Therefore
+  $(i^m_n(x))_{n=m}^\infty$ converges to a point in $\boundary G$,
+  by~\cite[Lemma III.H.3.13]{bridsonhaefliger99}.
 \end{proof}
@@
     \gromov{e}{x}{y}, \gromov{e}{y}{i^m_n(y)}\} - 2\delta'\\
-    &\geq \min\{m - C, m - R/2, m - C\} - 2\delta' \\
+    &\geq \min\{m - C, m - D/2, m - C\} - 2\delta' \\
     &\geq m - C'
@@
   $\sigma$ of $\Skel_2 K_m$, the diameter of $i^m_{\infty}(\sigma)$ with
-  respect to the visual metric $\vdistance$ is bounded above by $Ca^{-m}$,
-  where $a$ is the visual parameter.\qed
+  respect to the visual metric $\vdistance$ is bounded above by $Ca^{-m}$.
 \end{corollary}
@@
 \begin{remark}
-  In fact, if $K_m$ is endowed with a metric in which each simplex is 
-  isometrically identified with the standard simplex of the same dimension then 
-  the map $i^m_\infty$ can be shown to be H\"{o}lder continuous with exponent 
-  only depending on $\delta$ and $k$.  We do not require this strengthening of
+  In fact, if a 2-simplex of $K_m$ is metrically identified with the standard
+  2-simplex then the restriction of $i^m_\infty$ to this simplex can be shown
+  to be H\"{o}lder continuous.  We do not require this strengthening of
   \cref{prop:continuouslimit} here.
@@
 
-Finally, we use the maps $i^n_\infty$ to construct homotopies between certain
-special maps to $\boundary G$.
+\subsection{Homotopies in $\boundary G$}
+
+We now use the maps $i^n_\infty$ to construct homotopies in $\boudndary G$. To
+begin, we prove the following proposition, which constructs homotopies between
+certain special maps.
 
 \begin{proposition}\label{prop:basic_homotopies}
-  Let $C$ be a constant. Then there exist numbers $m_0$ and $\mu$
+  Let $C$ be a positive number. Then there exist numbers $m_0$ and $\mu$
   with the following property. Let $n \geq m_0$ and let $\gamma_0$ and
@@
   for every $x \in \boundary \Delta$. Then there is a homotopy $h$ from
-  $i^n_\infty\composed f_0$ to $i^n_\infty\composed f_1$ satisfying a uniform
-  continuity condition: for any $x \in \boundary\Delta$,
+  $i^n_\infty\composed f_0$ to $i^n_\infty\composed f_1$ satisfying a bounded
+  length condition: for any $x \in \boundary\Delta$,
   \begin{equation*}
@@
 \begin{proof}
-  \todo{constant on ddag}
-  Let $G$ satisfy $\ddag'_?$ with constants $L$ and $m_0 \geq n_0$.
+  \todo{Think about condition for apply Sd}
+  Let $G$ satisfy $\ddag'_C$ with constants $L$ and $m_0 \geq n_0$.
+  By increasing $m_0$ we can also assume that $G$ satisfies $\S_?$ with
+  constants $L'$ and $m_0$.
+
   Let $n \geq m_0$.  Let $J$ be a subdivision of $\boundary\Delta$ such
@@
   this map is a simplicial approximation to the map $\gamma_0 \disjointunion
-  \gamma_1$ from $J\times\{0\} \disjointunion \{1\}$ to $\boundary G$.
-
-  Using $\ddag'_?$ we can extend $\gamma_0\disjointunion\gamma_1$ along $x
+  \gamma_1$ from $J\times\{0\} \disjointunion J \times\{1\}$ to $\boundary G$.
+
+  Using $\ddag'_C$ we can extend $\gamma_0\disjointunion\gamma_1$ along $x
   \times [0,1]$ for each vertex $x$ of $J$ in such a way that the extension
-  along each edge $x\times [0,1]$, when composed with $p^\infty_n$ admits a
+  along each edge $x\times [0,1]$, when composed with $p^\infty_n$, admits a
   simplicial approximation connecting $f_0(x)$ to $f_1(x)$ after at most $L$
   subdivisions of the interval. Finally, using the condition $\S_?$, we deduce
-  that $f_0 \disjointunion f_1$ admints an extension to $J \times [0,1]$ after
-  only $k'$ barycentric subdivisions. Call the extension $F$ and let $h =
-  i^n_\infty \composed F$, so that $h$ is a homotopy from $i^n_\infty\composed
-  f_0$ to $i^n_\infty\composed f_1$. It remains to prove the bounded distance
-  assertion.
-
-  Let $M$ be the number of $2$-simplices in $\sd^{k'}([0,1]^2)$.
-  Corollary~\ref{cor:visualdiameter} gives a constant $C_0$ so that any
-  $2$-simplex is mapped by $i^n_\infty$ to a set of diameter at most $C_0
-  a^{-n}$, and so we can take $\mu = MC_0$.
-\end{proof}
-
-\subsection{Proving \Cref{thm:ddagimpliesLCd}}
-
-We now use the maps $(i^n_{n+1})$ to prove \cref{thm:ddagimpliesLCd}. We begin
-with two lemmas.
+  that $f_0 \disjointunion f_1$ admints an affine extension to $\sd^{L'}(J
+  \times [0,1])$ after Call the extension $F$ and let $h = i^n_\infty \composed
+  F$, so that $h$ is a homotopy from $i^n_\infty\composed f_0$ to
+  $i^n_\infty\composed f_1$.
+
+  It remains to prove the bounded length assertion.  Let $M$ be the number of
+  $2$-simplices in $\sd^{L'}([0,1]^2)$.  Corollary~\ref{cor:visualdiameter}
+  gives a constant $C_0$ so that any $2$-simplex is mapped by $i^n_\infty$ to a
+  set of diameter at most $C_0 a^{-n}$, and so we can take $\mu = MC_0$.
+\end{proof}
+
+We now need two more lemmas.
 
 \begin{lemma}\label{lem:convergestoidentity}
-  There is a constant $C$ such that the distance from $(i^m_\infty \composed 
-  p^\infty_m)$ to the identity map $\boundary G\to\boundary G$ is at most 
+  There is a constant $C$ such that the distance from $i^m_\infty \composed 
+  p^\infty_m$ to the identity map $\boundary G\to\boundary G$ is at most 
   $Ca^{-m}$ for each $m \geq n_0$.
@@
 \begin{proof}
-  Let $\xi \in \boundary G$. By \cref{lem:linearproduct} there is a 
-  constant $C$ such that 
+  By \cref{lem:linearproduct} there is a constant $C$ such that  for $\xi \in
+  \boundary G$,
   \begin{equation*}
@@
             - 2\delta' \\
-          &\geq \min\{m - C, m - R/2, m\} - 2\delta' \\
+          &\geq \min\{m, m - D/2, m - C\} - 2\delta' \\
           &\geq m - C'
@@
   p^\infty_{n+1}(\xi))$ are bounded by $6\delta + 3 + 2D$. Let $y$ be a vertex
-  of a simplex containing $p^\infty_n(\xi)$; then $\newdist(y, p^\infty_n(\xi))$
-  is bounded by $D$.
+  of a minimal simplex containing $p^\infty_n(\xi)$; then $\newdist(y,
+  p^\infty_n(\xi))$ is bounded by $D$.
 
@@
   $\newdist(i^n_{n+1}(y), i^n_{n+1}\composed p^\infty_n (\xi))$ is bounded by
-  the product of $D$ and the constant $k$ appearing in
-  \cref{prop:i_in_dimension_2}. By putting all this together we obtain a bound
-  $C$ on $\newdist(i^n_{n+1}\composed p^\infty_n(\xi), p^\infty_{n+1}(\xi))$,
-  and then $\dist(x_1, x_2) \leq C + 2D$.
+  the product of $D$ and the the number of 2-simpices in $\sd^L\Delta$, where
+  $L$ is the number appearing in Proposition~\ref{prop:i_in_dimension_2}.  By
+  putting all this together we obtain a bound $C$ on
+  $\newdist(i^n_{n+1}\composed p^\infty_n(\xi), p^\infty_{n+1}(\xi))$, and then
+  $\dist(x_1, x_2) \leq C + 2D$.
 \end{proof}
@@
   $\gamma\from\boundary\Delta\to\boundary G$ be a continuous map. Let $n \geq
-  m_0$ and let $f$ be an affine approximation to $p^\infty_n\composed\gamma$.
+  m_0$ and let $f$ a simplicial approximation to $p^\infty_n\composed\gamma$.
   Then there is a homotopy $h$ from $\gamma$ to $i^n_\infty\composed f$ such
@@
 
-  \todo{Justify the application of the proposition.}
+  \todo{This still doesn't feel quite there yet.}
+  For each $m$ we can apply Proposition~\ref{prop:basic_homotopies} to the maps
+  $f_{m+1}$ and $i^{n+m}_{n+m+1}\composed f_m$: Lemma~\ref{lem:name_this} gives
+  the bounded distance assumption, $f_{m+1}$ is a simplicial approximation to
+  $p^\infty_{n+m+1}\composed\gamma$, and $i^{n+m}_{n+m+1}\composed f_{m+1}$ is
+  also a simplicial approximation to a map that factors through
+  $p^\infty_{n+m+1}$ because the restriction of $i^{n+m}_{n+m+1}$ to $\Skel_1
+  K_{n+m}$ has this property.
 
@@
   \gamma_m(y)) \leq \epsilon/3$. Increasing $M$ if necessary we may assume that
-  \begin{align*}
-    \sum_m \geq M \mu a^{-m-n} \leq \epsilon/3.
-  \end{align*}
+  $\mu a^{-m-n} \leq \epsilon/3$.
   Finally, let $U$ be a neighbourhood of $x$ such that $\rho(\gamma(x),
-  \gamma(y)) \leq \epsilon/3$ for $y \in U$. Now, for any $y \in U$ and $t \in (0, 2^{-M}$,
-  \begin{equation*}
-    \rho{h(x,0), h(y,t)} \leq \frac{\epsilon}{3} + \frac{\epsilon}{3} +
+  \gamma(y)) \leq \epsilon/3$ for $y \in U$. Now, for any $y \in U$ and $t \in (0, 2^{-M}]$,
+  \begin{equation*}
+    \rho(h(x,0), h(y,t)) \leq \frac{\epsilon}{3} + \frac{\epsilon}{3} +
         \frac{\epsilon}{3} = \epsilon.
@@
 
-  Finally, we immediately see that for any $x \in \boundary\Delta$,
+  To prove the final claim, we immediately see that for any $x \in
+  \boundary\Delta$,
   \begin{equation*}
@@
 
-\Cref{thm:ddagimpliesLCd} follows as a corollary of this proposition.
+\Cref{thm:ddagimpliesLCd} follows from this proposition:
 
@@
   \begin{equation*}
-    m = \floor{\log_a(k_1/\Diam\image\gamma)} \geq m_0,
-  \end{equation*}
-  so that by \cref{lem:projectstoasimplex} $p^\infty_{m}\composed\gamma$ has
-  image contained in a single vertex of $K_m$. Then a constant map
-  $\boundary\Delta \to K_m$ is a simplicial approximation to
-  $p^\infty_m\composed\gamma$; applying \cref{prop:uniform_homotopies} to
+    m = \floor{\log_a(k_1/\Diam\image\gamma)} \geq m_0.
+  \end{equation*}
+  Then a constant map $\boundary\Delta \to K_m$ is a simplicial approximation
+  to $p^\infty_m\composed\gamma$; applying \cref{prop:uniform_homotopies} to
   this map immediately gives a homotopy $h$ from $\gamma$ to the constant map.
@@
 \section{Simply connected point complements}
+\todo{Move this section into section 3}
 
@@
   number $n_i \geq i$, a map $\gamma_i \from \boundary\Delta \to \boundary G$
-  and a simplicial map $f_i \from \sd^M \boundary\Delta \to K_{n_i}$ that is a
-  simplicial approimxation to $p^\infty_{n_i}\composed\gamma_i$ such that $f_i$
-  does not admit an extension to $\Delta$ that is affine on $\sd^i\Delta$.
+  and a simplicial approximation $f_i \from \sd^M \boundary\Delta \to K_{n_i}$
+  to $p^\infty_{n_i}\composed\gamma_i$ such that $f_i$ does not admit an
+  extension to $\Delta$ that is affine on $\sd^i\Delta$.
 
@@
   this map $f$. It remains to show that $f$ is nullhomotopic in $H$; then it is
-  nullhomotopic by a simplicial map, and this gives a contradiction for $i$
-  sufficiently large.
+  nullhomotopic by an affine map by~\cite{zeeman64}, and this gives a
+  contradiction for $i$ sufficiently large.
 
@@
   Lemma~\ref{lem:affinehomotopic} there exists $i_1 \geq i_0$ such that
-  $q_i\restricted{C_0}$ is affine homotopic to $q_{i_1}\restricted{C_0}$ for
-  every $i \geq i_1$.
-
-  Let $h$ be a nullhomotopy of $\gamma_{i_1}$ in
-  $\boundary G - \set\xi$ and let $C_1$ be a compact subset of $\boundary G -
-  \set\xi$ containing $C_0$ and the image of $h$. Let $i_2$ be so that $C_1
-  \subset U_{i_2}$.
+  $q_i\restricted{C_0}$ is homotopic to $q_{i_1}\restricted{C_0}$ for every $i
+  \geq i_1$.
+
+  Let $h$ be a contracting homotopy of $\gamma_{i_1}$ in $\boundary G -
+  \set\xi$ and let $C_1$ be a compact subset of $\boundary G - \set\xi$
+  containing $C_0$ and the image of $h$. Let $i_2$ be so that $C_1 \subset
+  U_{i_2}$.
 
@@
   to a point.
-  \todo{would just $i_0$ and $i_1$ have been enough?}
 \end{proof}

### 2020-02-18 paper.tex
Moved (dG - xi simply connected => loc simp con)

@@
 
-\begin{proposition}
+\begin{proposition}\cite[Proposition ?]{bestvinamess91}\label{prop:BM2}
   If $\boundary G - \set\xi$ is connected for any $\xi \in \boundary G$ then
@@
 
-\section{Local simple connectedness}
+\subsection{A two-dimensional version}
 
@@
 \end{definition}
+
+We can immediately give a sufficient condition for $\S_M$ to be satisfied. This
+result is analagous to Proposition~\ref{prop:BM2}.
+
+\begin{proposition}
+  Suppose that $\boundary G - \set\xi$ is simply connected for any point $\xi
+  \in \boundary G$. Then $\S_M$ is satisfied for all $M$.
+\end{proposition}
+
+\begin{proof}
+  Suppose that the condition is not satisfied. Then for each $i$ there exists a
+  number $n_i \geq i$, a map $\gamma_i \from \boundary\Delta \to \boundary G$
+  and a simplicial approximation $f_i \from \sd^M \boundary\Delta \to K_{n_i}$
+  to $p^\infty_{n_i}\composed\gamma_i$ such that $f_i$ does not admit an
+  extension to $\Delta$ that is affine on $\sd^i\Delta$.
+
+  Fix a vertex $v$ of $\boundary\Delta$; then there exist group elements $g_i
+  \in G$ such that $g_i\cdot f_i(v)$ is a fixed vertex of $K$. Pass to a
+  subsequence as in Section~\ref{sec:horoball}, and to a deeper subsequence so
+  that $g_i\cdot f_i(w)$ is independent of $i$ for all vertices $w \in \sd^M
+  \boundary\Delta$. Then the map $g_i\composed f_i$ is independent of $i$; call
+  this map $f$. It remains to show that $f$ is nullhomotopic in $H$; then it is
+  nullhomotopic by an affine map by~\cite{zeeman64}, and this gives a
+  contradiction for $i$ sufficiently large.
+
+  By Lemma~\ref{lem:propermaps} there exists $i_0$ and a 
+  compact set $C_0 \subset \boundary G - \set\xi$ such that $C_0$ contains the
+  image of $\gamma_i$ for every $i \geq i_0$. By
+  Lemma~\ref{lem:affinehomotopic} there exists $i_1 \geq i_0$ such that
+  $q_i\restricted{C_0}$ is homotopic to $q_{i_1}\restricted{C_0}$ for every $i
+  \geq i_1$.
+
+  Let $h$ be a contracting homotopy of $\gamma_{i_1}$ in $\boundary G -
+  \set\xi$ and let $C_1$ be a compact subset of $\boundary G - \set\xi$
+  containing $C_0$ and the image of $h$. Let $i_2$ be so that $C_1 \subset
+  U_{i_2}$.
+
+  Then $f$ is homotopic to $q_{i_1}\composed\gamma_{i_1}$, which is homotopic
+  to $q_{i_2}\composed\gamma_{i_1}$, which is homotopic by $q_{i_2}\composed h$
+  to a point.
+\end{proof}
+
+\section{Local simple connectedness}
 
@@
 
-We now use the maps $i^n_\infty$ to construct homotopies in $\boudndary G$. To
+We now use the maps $i^n_\infty$ to construct homotopies in $\boundary G$. To
 begin, we prove the following proposition, which constructs homotopies between
@@
 
-\section{Simply connected point complements}
-\todo{Move this section into section 3}
-
-In this section we give a sufficient condition for the condition $\S_M$ to be
-satisfied.
-
-\begin{proposition}
-  Suppose that $\boundary G - \set\xi$ is simply connected for any point $\xi
-  \in \boundary G$. Then $\S_M$ is satisfied for all $M$.
-\end{proposition}
-
-\begin{proof}
-  Suppose that the condition is not satisfied. Then for each $i$ there exists a
-  number $n_i \geq i$, a map $\gamma_i \from \boundary\Delta \to \boundary G$
-  and a simplicial approximation $f_i \from \sd^M \boundary\Delta \to K_{n_i}$
-  to $p^\infty_{n_i}\composed\gamma_i$ such that $f_i$ does not admit an
-  extension to $\Delta$ that is affine on $\sd^i\Delta$.
-
-  Fix a vertex $v$ of $\boundary\Delta$; then there exist group elements $g_i
-  \in G$ such that $g_i\cdot f_i(v)$ is a fixed vertex of $K$. Pass to a
-  subsequence as in Section~\ref{sec:horoball}, and to a deeper subsequence so
-  that $g_i\cdot f_i(w)$ is independent of $i$ for all vertices $w \in \sd^M
-  \boundary\Delta$. Then the map $g_i\composed f_i$ is independent of $i$; call
-  this map $f$. It remains to show that $f$ is nullhomotopic in $H$; then it is
-  nullhomotopic by an affine map by~\cite{zeeman64}, and this gives a
-  contradiction for $i$ sufficiently large.
-
-  By Lemma~\ref{lem:propermaps} there exists $i_0$ and a 
-  compact set $C_0 \subset \boundary G - \set\xi$ such that $C_0$ contains the
-  image of $\gamma_i$ for every $i \geq i_0$. By
-  Lemma~\ref{lem:affinehomotopic} there exists $i_1 \geq i_0$ such that
-  $q_i\restricted{C_0}$ is homotopic to $q_{i_1}\restricted{C_0}$ for every $i
-  \geq i_1$.
-
-  Let $h$ be a contracting homotopy of $\gamma_{i_1}$ in $\boundary G -
-  \set\xi$ and let $C_1$ be a compact subset of $\boundary G - \set\xi$
-  containing $C_0$ and the image of $h$. Let $i_2$ be so that $C_1 \subset
-  U_{i_2}$.
-
-  Then $f$ is homotopic to $q_{i_1}\composed\gamma_{i_1}$, which is homotopic
-  to $q_{i_2}\composed\gamma_{i_1}$, which is homotopic by $q_{i_2}\composed h$
-  to a point.
-\end{proof}
-
 \bibliography{references}

### 2020-02-18 paper.tex
Fixed the stuff about common subdivisions

@@
 \begin{proof}
-  \todo{Think about condition for apply Sd}
-  Let $G$ satisfy $\ddag'_C$ with constants $L$ and $m_0 \geq n_0$.
+  \todo{proof read the first htree paragraphs}
+  Let $G$ satisfy $\ddag'_{C+D}$ with constants $L$ and $m_0 \geq n_0$.
   By increasing $m_0$ we can also assume that $G$ satisfies $\S_?$ with
@@
 
-  Let $n \geq m_0$.  Let $J$ be a subdivision of $\boundary\Delta$ such
-  that $f_0$ and $f_1$ are both affine on $J$. Then we have a map 
+  Let $n \geq m_0$ and let $f_0$ and $f_1$ be as in the statement of the
+  proposition, so there exist $k_0$ and $k_1$ such that $f_0$ is simplicial on
+  $\sd^{k_0}\boundary\Delta$ and $f_1$ is simplicial on
+  $\sd^{k_1}\boundary\Delta$. We first show that we may assume that $k_0$ and
+  $k_1$ are equal. If not, suppose $k_0 < k_1$.
+
+  Let $f_0'$ be the simplicial map on $\sd^{k_1}$ defined as follows. For each
+  edge $e$ of $\sd^{k_0}\boundary\Delta$, choose an orientation of $e$ define
+  $f_0'\restricted{\sd^{k_1-k_0}e}$ to be given by $f_0\restricted{e}$ on the
+  initial edge of $\sd^{k_1-k_0}e$ and constant equal to the image under $f_0$
+  of the terminal vertex of $e$ on the rest of $\sd^{k_1-k_0}$. Then there is a
+  homotopy from $f_0$ to $f_0'$ such that for any $x \in \boundary\Delta$, the
+  path traced by $x$ under the homotopy is contained in a single edge of $K_n$.
+  It follows that, when composed with $i^n_\infty$, this homotopy gives a
+  homotopy from $i^n_\infty\composed f_0$ to $i^n_\infty \composed f_0'$ such
+  that the path traced by any point in $\boundary\Delta$ has diameter at most
+  some multiple of $a^{-n}$ as given by Corollary~\ref{cor:visualdiameter}.
+  Therefore we may replace $f_0$ by $f_0'$ and assume that $f_0$ and $f_1$ are
+  simplicial maps on a common subdivision $J$ of $\boundary\Delta$, and
+  $\newdist(f_0(x), f_1(x))\leq C+D$ for any $x \in \boundary\Delta$.
+
+  Then we have a map 
   \begin{equation*}

### 2020-02-18 paper.tex
Made clearer the application of the special homotopy proposition

@@
 
-  \todo{This still doesn't feel quite there yet.}
   For each $m$ we can apply Proposition~\ref{prop:basic_homotopies} to the maps
-  $f_{m+1}$ and $i^{n+m}_{n+m+1}\composed f_m$: Lemma~\ref{lem:name_this} gives
-  the bounded distance assumption, $f_{m+1}$ is a simplicial approximation to
-  $p^\infty_{n+m+1}\composed\gamma$, and $i^{n+m}_{n+m+1}\composed f_{m+1}$ is
-  also a simplicial approximation to a map that factors through
-  $p^\infty_{n+m+1}$ because the restriction of $i^{n+m}_{n+m+1}$ to $\Skel_1
-  K_{n+m}$ has this property.
+  $f_{m+1}$ and $i^{n+m}_{n+m+1}\composed f_m$. To see this, firstly
+  Lemma~\ref{lem:name_this} gives the uniformly bounded distance assumption.
+  Secondly, $f_{m+1}$ is a simplicial approximation to
+  $p^\infty_{n+m+1}\composed\gamma$. Finally,
+  $i^{n+m}_{n+m+1}\restricted{\Skel_1 K_{n+m}}$ is a simplicial approximation
+  to a map $p^\infty_{n+m+1}\composed j_m$ for some map $j_m\from\Skel_1
+  K_{n+m}\to \boundary G$, and then $i^{n+m}_{n+m+1}\composed g_m$ is a
+  simplicial approximation to $p^\infty_{n+m+1}\composed j_m\composed f_m$.
 

### 2020-03-05 paper.tex
Changed the title
Improvements to section 1

@@
 \input{header.tex}
-\title{Conditions for $d$-local-connectedness of boundaries of hyperbolic groups}
+\title{Local simple connectedness of boundaries of hyperbolic groups}
 \author{Benjamin Barrett}
@@
 \maketitle
+
+\todo{Worry about when $p^n_m$ is not defined.}
 
@@
 \begin{definition}
-  We denote by $K(G)$ the \emph{Rips complex} of $G$; this is the simplicial
+  We denote by $K$ the \emph{Rips complex} of $G$; this is the simplicial
   complex with vertex set $G$ such that a finite set of elements of $G$ spans a
@@
 
-We will sometimes want to refer to distances between points in $K(G)$. The
-precise means by which we extend the metric on $G$ to $K(G)$ will not matter
+We will sometimes want to refer to distances between points in $K$. The
+precise means by which we extend the metric on $G$ to $K$ will not matter
 very much, so we make the following simple definition.
@@
 \begin{definition}
-  For $x$ and $y$ in $K(G)$, choose vertices $x^\star$ and $y^\star$ of the
+  For $x$ and $y$ in $K$, choose vertices $x^\star$ and $y^\star$ of the
   minimal simplices containing $x$ and $y$ respectively. Then define
@@
 We denote by $\gromov{a}{b}{c}$ the Gromov product of $b$ and $c$ in $G \union
-\boundary$ with respect to base point $a \in G$. Using $\newdist$ we extend the
+\boundary G$ with respect to base point $a \in G$. Using $\newdist$ we extend the
 Gromov product to $K$:
@@
 
-We now define a sequence of subcomplexes in $K(G)$. We will use the topology of
+We now define a sequence of subcomplexes in $K$. We will use the topology of
 these complexes to approximate the topology of $\boundary G$.
@@
 
-  Let $K_n$ be the full subcomplex of the Rips complex $K(G)$ with vertex set
+  Let $K_n$ be the full subcomplex of the Rips complex $K$ with vertex set
   $S_n$.
@@
   For $n \geq m$ define a map $p^n_m \from S_n \to S_m$ as follows.
-  Given an element $g$ of $S_n$ let $w_g \in S^\star$ be the lex-least 
-  representative of $g$; note that this word necessarily has length $n$.
-  Then define $p^n_m(g)$ to be the element of $G$ given by truncating $w_g$ to a 
-  word of length $m$.
+  Given an element $g$ of $S_n$ let $w_g \in S^\star$ be the lexicographically
+  first representative of $g$; note that this word in $S^\star$ necessarily has
+  length $n$.  Then define $p^n_m(g)$ to be the element of $G$ given by
+  truncating $w_g$ to a word of length $m$.
 \end{definition}
@@
 \begin{proof}
-  Let $\set{g_1, \dotsc, g_k}$ span a simplex in $K_n$.
-  Then for $g_i$ and $g_j$ in $\set{g_1, \dotsc, g_k}$, $\dist([g_i, g_j], 
-  p^n_m(g_i)) \geq n - m - D > \delta$, so $\dist(p^n_m(g_i), [e, g_j]) \leq 
-  \delta$.  But $p^n_m(g_j) \in [e, g_j]$ and $\dist(e, p^n_m(g_i)) = 
-  \dist(e, p^n_m(g_j))$ so $\dist(p^n_m(g_i), p^n_m(g_j)) \leq 2\delta 
-  \leq D$. It follows that the diameter of $\set{p^n_m(g_1), \dotsc, 
+  Let $\set{g_1, \dotsc, g_k}$ span a simplex in $K_n$.  Then for $g_i$ and
+  $g_j$ in $\set{g_1, \dotsc, g_k}$, the distance from $p^n_m(g_i))$ to a
+  geodesic from $g_i$ to $g_j$ is at least $n - m - D$, which is greater than
+  $\delta$, so by hyperbolicity of a triangle with vertices $e$, $g_i$ and $g_j$,
+  the distance from $p^n_m(g_i)$ to any geodesic from $e$ to $g_j$ is at most
+  $\delta$. We may choose this geodesic to contain $p^n_m(g_j)$, and $\dist(e,
+  p^n_m(g_i)) = \dist(e, p^n_m(g_j))$, so $\dist(p^n_m(g_i), p^n_m(g_j)) \leq
+  2\delta \leq D$.  It follows that the diameter of $\set{p^n_m(g_1), \dotsc,
   p^n_m(g_k)}$ is at most $D$ and therefore the set spans a simplex in $K_m$.
@@
 In order to define projections from $\boundary G$ into our system $(K_n)$, we
-first describe a closely related system of simplicial complexes.
+first describe a sequence of open covers of $\boundary G$.
 
@@
 
-  By~\cite{bridsonhaefliger99} $U_n(x)$ is a fundamental system of 
-  neighbourhoods in $\boundary G$ of the set of limit points in $\boundary G$ of 
-  geodesic rays $\gamma$ with $\gamma(0) = e$ and $\gamma(n) = x$, and therefore 
-  $U_n(x)$ contains an open set $V_n(x) \subset \boundary G$ containing this 
-  set. Then $\set{V_n(x)}_{x \in S_n}$ is an open cover of $\boundary G$.
-
-  Let $L_n$ be the nerve of this cover, so $\Vertices(L_n)$ is naturally 
-  identified with a subset of $S_n$.
+  By~\cite[III.H.3.6]{bridsonhaefliger99} $U_n(x)$ is a (not necessarily open)
+  neighbourhood in $\boundary G$ of the set of limit points in $\boundary G$ of
+  geodesic rays $\gamma$ with $\gamma(0) = e$ and $\gamma(n) = x$.
 \end{definition}
@@
 \begin{lemma}\label{lem:L_Ksimplicial}
-  The inclusion $\Skel_0 L_n \into \Skel_0 K_n^D$ is a simplicial map.
-\end{lemma}
-
-\begin{proof}
-  Let $g_1, \dotsc, g_k \subset \Vertices(L_n)$ span a simplex in $L_n$, so 
-  there exists a point $\xi \in \bigintersection_{i=1}^k V_n(g_i)$.  Let
-  $\gamma_1, \dotsc, \gamma_n$ be geodesic rays with $\gamma_i(0) = e$,
-  $\gamma_i(\infty) = \xi$ and $\dist(\gamma_i(n), g_i) \leq 2\delta+1$.
-  Then $\Diam\set{\gamma_i(n) \suchthat i=1, \dotsc, n} \leq 2\delta$, and it
-  follows that
+  The nerve of $\{U_n(x)\}_{x \in S_n}$ is a subcomplex of $K_n$.
+\end{lemma}
+
+\begin{proof}
+  Let $g_1, \dotsc, g_k \in S_n$ span a simplex in the nerve of
+  $\{U_n(x)\}_{x \in S_n}$, so there exists a point $\xi \in
+  \bigintersection_{i=1}^k U_n(g_i)$.  Let $\gamma_1, \dotsc, \gamma_n$ be
+  geodesic rays with $\gamma_i(0) = e$, $\gamma_i(\infty) = \xi$ and
+  $\dist(\gamma_i(n), g_i) \leq 2\delta+1$.  Then $\Diam\set{\gamma_i(n)
+  \suchthat i=1, \dotsc, n} \leq 2\delta$, and it follows that
   \begin{equation*}
@@
 
-For each $n$, fix a partition of unity subordinate to the open covering 
-\begin{equation*}
-  \set{V_n(x) \suchthat x \in S_n}
-\end{equation*} 
-of $\boundary G$. This is equivalent to a continuous map $\pi_n \from \boundary
-G \to L_n$. Let $p^\infty_n\from\boundary G\to K_n$ be the composition of
-$\pi_n$ with the simplicial map $L_n \to K_n$ given by
-\cref{lem:L_Ksimplicial}.
+\begin{definition}
+  For each $n$, fix a partition of unity subordinate to the covering
+  $\set{U_n(x)}_{x \in S_n}$ of $\boundary G$. This is gives a
+  continuous map from $\boundary G$ to the nerve of the covering. Denote by
+  $p^\infty_n\from \boundary G \to K_n$ the composition of this map with the
+  inclusion of the nerve into $K_n$, as given by Lemma~\ref{lem:L_Ksimplicial}.
+\end{definition}
 
@@
 
+\begin{proposition}\label{prop:projectstoasimplex}
+  Let $U$ be a subset of $\boundary G$ with diameter $\rho_0$ with respect to
+  the visual metric $\rho$. Let $n \leq \log_a(k_1/\rho_0)$. Then
+  $p^\infty_n(U)$ is contained in a single simplex of $K_n$
+\end{proposition}
+
+To prove this proposition we first prove the following lemma.
+
 \begin{lemma}\label{lem:boundary_gromov_product}
@@
 \begin{proof}
-  By~\cite{bridsonhaefliger99},
+  By~\cite[III.H.3.17]{bridsonhaefliger99},
   \begin{equation*}
@@
 
-  If $p_1$ lies between $\alpha_2(n_2)$ and $p_1$ on $[\alpha_1(n_1),
+  If $p_1$ lies between $\alpha_2(n_2)$ and $p_2$ on $[\alpha_1(n_1),
   \alpha_2(n_2)]$ then, by considering the triangle with vertices $p_2$,
@@
 
-\begin{lemma}\label{lem:projectstoasimplex}
-  Let $U$ be a subset of $\boundary G$ with diameter $\rho_0$ with respect to
-  the visual metric. Let $n \leq \log_a(k_1/\rho_0)$. Then $p^\infty_n(U)$ is
-  contained in a single simplex of $K_n$
-\end{lemma}
-
-\begin{proof} 
+\begin{proof}[Proof of Proposition~\ref{prop:projectstoasimplex}] 
   Let $\xi_1$ and $\xi_2$ be points in $U$, so $\rho(\xi_1, \xi_2)
@@
   \begin{equation*}
-    \dist(\alpha_1(n), \alpha_2(n)) \leq \max\{6\delta, 12\delta - 2(\log(k_1/\rho_0) - n)\}
+    \dist(\alpha_1(n), \alpha_2(n)) \leq \max\{6\delta, 12\delta + 2(n - \log(k_1/\rho_0))\}
   \end{equation*}
@@
 \begin{lemma}
+  \todo{Should this be used somewhere?}
   For $\xi \in \boundary G$ and $n - m \geq D + \delta$ the points $p^n_m
@@
   \cref{prop:uniform_homotopies}. Let $r_0 =
-  k_1a^{-m_0}$, so that, by \cref{lem:projectstoasimplex},
+  k_1a^{-m_0}$, so that, by \cref{prop:projectstoasimplex},
   $p^\infty_{m_0}\composed\gamma$ has image contained in the star of a single

### 2020-03-05 paper.tex
Section 2.2 improved

@@
 \begin{lemma}
-  \todo{Should this be used somewhere?}
+  \todo{Orphaned}
   For $\xi \in \boundary G$ and $n - m \geq D + \delta$ the points $p^n_m
@@
 
-\section{Horoballs in the Rips Complex}
-
-In future sections we will make use of a limiting argument, which will relate
-the topology of the complement of a point in the boundary $\boundary G$ to a
-particular complex built from $K$, which we will think of as a horoball in $K$.
-In this section we prove that this construction possesses certain properties
-that we will need later.
-
-\subsection{Defining the horoball}\label{sec:horoball}
+\section{Horoballs in the Rips Complex}\label{sec:horoballs}
+
+In Section~\ref{sec:double_dagger} we will make use of a limiting argument,
+which will relate the topology of the complement of a point in the boundary
+$\boundary G$ to a particular subcomplex of $K$, which we will think of as
+a horoball in $K$.  In this section we prove that this subcomplex possesses
+certain properties that we will apply later.
+
+\subsection{Defining the horoball}
 
 For each $n$, let $v_n$ be a vertex of $K_n$ and let $g_n$ be an element of $G$
-taken so that $g_n\cdot v_n$ is independent of $n$.  Since $K$ is locally
-finite, we can pass to a subsequence so that now $v_i \in K_{n_i}$ satisfying
-the following conditions:
+taken so that $g_n\cdot v_n$ is a point $v \in K_n$ independent of $n$.  Since
+$K$ is locally finite, we can pass to a subsequence so that $v_i \in
+K_{n_i}$ satisfies the following conditions:
 \begin{enumerate}
@@
 horosphere, the topology of which approximates that of $\boundary G - \set\xi$.
-The rest of~\ref{sec:horoball} will be spent justifying this point of view.
+The rest Section of~\ref{sec:horoballs} will be spent justifying this point of view.
 
@@
 \begin{proof}
-  Let $\alpha$ be a bi-infinite geodesic with $\xi$ as a limit pint. Pick a
-  point $w \in f(\Vertices(J))$ and let the distance $\dist(w,\alpha)$ be
-  realised by a point $x \in \alpha$.
+  Let $\alpha$ be a bi-infinite geodesic with $\xi$ as a limit point. 
+  Let the distance $\dist(w,\alpha)$ be realised by a point $x \in \alpha$.
 
@@
 
-  Since $\dist(g_i, x) = n_i$ for $i$ sufficiently large and $\dist(x,y_i) \to
+  Since $\dist(g_i, v) = n_i$ for all $i$ and $\dist(x,y_i) \to
   \infty$ as $i\to\infty$, we have the following limit.
   \begin{align*}\label{eqn:zi_closer_to_gi_than_x}
-    \dist(g_i,z_i) - n_i &\leq \dist(g_i,y_i) + \delta - n_i \text{ for $i$
-                                        sufficiently large} \\
-                         &= - \dist(x,y_i) + \delta \\
-                         &\to -\infty\text{ as $i \to \infty$} \tag{$\star$}
+    n_i - \dist(g_i, z_i) & \geq n_i - \dist(g_i, y_i) - \delta \\
+                          &= n_i - \dist(g_i, x) + \dist(x, y_i) - \delta\\
+                          &\geq \dist(x, y_i) - \dist(v,x) - \delta\\
+                          &\to \infty\text{ as $i \to \infty$}\tab{$\star$}
   \end{align*}
@@
   such that $z_i$ lies between $\xi$ and $p_i$ on $\alpha$ and so that
-  $\dist(g_i,p_i)=n_i$. We now show that $\dist(p_i, x)$ is uniformly bounded.
+  $\dist(g_i,p_i)=n_i$. We now show that $\dist(v, p_i)$ is uniformly bounded.
 
   The limit~\eqref{eqn:zi_closer_to_gi_than_x}, taken together with the fact
-  that $\dist(g_i, x) = \dist(g_i, p_i) = n_i$, shows that the distances
-  $\dist([z_i, g_i], x)$ and $\dist([z_i, g_i], p_i)$ tend to infinity as
-  $i\to\infty$.  We now divide into cases according to which of $x$ and $p_i$
-  is closer to $z_i$.
+  that $\dist(g_i, p_i) = n_i$ and $\dist(g_i, x) \geq n_i - \dist(x, v)$,
+  shows that the distances $\dist([z_i, g_i], x)$ and $\dist([z_i, g_i], p_i)$
+  tend to infinity as $i\to\infty$.  We now divide into cases according to
+  which of $x$ and $p_i$ is closer to $z_i$.
   \begin{enumerate}
@@
 
-  Either way, $\dist(w, p_i) \leq \dist(x,w) + 2\delta$. In summary, we have
+  Either way, $\dist(v, p_i) \leq \dist(v, x) + 2\delta$. In summary, we have
   shown that for $i$ sufficiently large there is a point $p_i\in\alpha$ with
@@
   $\alpha(\infty)\in C$. Let $x \in \alpha \intersection H$. Since $C$ is
-  compact, there exists a point $v \in \alpha$, between $\xi$ and $x$ on
+  compact, there exists a point $w \in \alpha$, between $\xi$ and $x$ on
   $\alpha$, such for that any bi-infinite geodesic $\beta$ with
@@
   not meet the $100\delta$-neighbourhood of the sub-ray of $\alpha$ between
-  $\xi$ and $v$: otherwise a limiting argument shows that $\xi$ is in $C$.
-
-  Since $g_i \to \xi$, the distance $\dist(v, [\xi, g_i]) \to \infty$ as
+  $\xi$ and $w$: otherwise a limiting argument shows that $\xi$ is in $C$.
+
+  Since $g_i \to \xi$, the distance $\dist(w, [\xi, g_i]) \to \infty$ as
   $i\to\infty$. The triangle with vertices $\xi$, $g_i$ and $x$ is
   $\delta$-slim, so the geodesic path from $g_i$ to $x$ passes within a
-  distance $\delta$ of $v$ for $i$ large enough. Therefore, since $\dist(g_i,
+  distance $\delta$ of $w$ for $i$ large enough. Therefore, since $\dist(g_i,
   x) = n_i$ for $i$ large enough, the following inequality holds for all $i$
@@
   \begin{equation*}
-    0 \leq \dist(g_i, v) + \dist(v, x) - n_i \leq 2\delta.
+    0 \leq \dist(g_i, w) + \dist(w, x) - n_i \leq 2\delta.
   \end{equation*}
@@
   triangle with vertices $\xi$, $\alpha(\infty)$ and $\alpha'(\infty)$ is
-  $\delta$-slim, so the subray of $\alpha$ between $\xi$ and $v$ is contained
-  in a $\delta$-neighbourhood of $\alpha'$.  Let $v' \in \alpha'$ be a point
-  with $\dist(v, v') \leq \delta$.
-
-  We split into cases according to the order of $\xi$, $v'$ and $x'$ on
+  $\delta$-slim, so the subray of $\alpha$ between $\xi$ and $w$ is contained
+  in a $\delta$-neighbourhood of $\alpha'$.  Let $w' \in \alpha'$ be a point
+  with $\dist(w, w') \leq \delta$.
+
+  We split into cases according to the order of $\xi$, $w'$ and $x'$ on
   $\alpha'$.
@@
     \item
-      First we suppose that $v'$ is between $x'$ and $\xi$ on $\alpha'$. Then as
+      First we suppose that $w'$ is between $x'$ and $\xi$ on $\alpha'$. Then as
       in the argument above, for $i$ sufficiently large we have the following
@@
       \begin{equation*}
-        0 \leq \dist(g_i, v') + \dist(v', x') - n_i \leq 2\delta.
+        0 \leq \dist(g_i, w') + \dist(w', x') - n_i \leq 2\delta.
       \end{equation*}
@@
       \begin{equation*}
-        -2\delta \leq \dist(g_i, v) + \dist(v, x') - n_i \leq 4\delta.
+        -2\delta \leq \dist(g_i, w) + \dist(w, x') - n_i \leq 4\delta.
       \end{equation*}
@@
       \begin{equation*}
-        \dist(v,x') \leq \dist(v,x) + 4\delta,
-      \end{equation*}
-      and thus we can uniformly bound this distance in this case.
+        \dist(x, x') \leq 2\dist(w, x) + 4\delta,
+      \end{equation*}
+      and so we uniformly bound this distance in this case.
     \item
-      Alternatively, $x'$ is between $v'$ and $\xi$ on $\alpha'$ and so (since
-      the triangle with vertices $\xi$, $v$ and $v'$ is $\delta$-slim) $x'$ is
+      Alternatively, $x'$ is between $w'$ and $\xi$ on $\alpha'$ and so (since
+      the triangle with vertices $\xi$, $w$ and $w'$ is $\delta$-slim) $x'$ is
       within a distance $2\delta$ of the geodesic ray from $x$ to $\xi$. By
@@
   \end{enumerate}
+  Either way, $\dist(x, x')$ is bounded over all points $x'$ in the
+  intersections between $H$ and geodesics with one end point equal to $\xi$ and
+  the other in $C$.
 \end{proof}
@@
 
-\section{The double dagger condition}
+\section{The double dagger condition}\label{sec:double_dagger}
 

### 2020-03-05 paper.tex
Proof reading section 2.3

@@
 \begin{definition}
-  Let $U_i \subset \boundary G$ be the set of all points in $\boundary G -
-  \set\xi$ such that all geodesic rays from $g_i \in G$ to points in $U_i$ pass
-  through $H_i$. Let $q_i$ be the restriction of the map $g_i \composed
-  p^\infty_{n_i} \composed g_i^{-1}$ to $U_i$.
+  For each $i$, let $U_i \subset \boundary G$ be the set $\left(g_i \composed
+  p^\infty_{n_i} \composed g_i^{-1}\right)^{-1} H_i$ and let $q_i \from U_i \to
+  H_i$ be the restriction of $g_i \composed p^\infty_{n_i}\composed g_i^{-1}$
+  to this set.
 \end{definition}
 
-The following lemma is immediate from the definition of $p^\infty_i$.
+The maps $q_i$ are described by the following lemma, which is immediate from
+the definition of $p^\infty_i$.
 
 \begin{lemma}\label{lem:describing_q_i}
-  The set $q_i(U_i)$ is contained in $H_i$.
-  Furthermore, let $\zeta \in U_i$ so that $q_i(\zeta) \in H_i$.  Then
-  $q_i(\zeta)$ is contained in the minimal simplex of $H_i$ with vertex set
-  \begin{equation*}
-    N_{2\delta+1} \set{\eta(n_i)\suchthat\text{$\eta$ a geodesic ray with
-    $\eta(0) = g_i$ and $\eta(\infty) = \zeta$}} \intersection H_i
-  \end{equation*}
-  In particular, if $\eta$ is any geodesic ray with $\eta(0) = g_i$ and
-  $\eta(\infty) = \zeta$ then $q_i(\zeta)$ is contained in the minimal simplex
-  of $H_i$ with vertex set
-  \begin{equation*}
-    N_{4\delta + 1}(\eta(n_i)) \intersection H_i.
-  \end{equation*}
+  \todo{Check this version is strong enough.}
+  Let $\zeta \in \boundary G$ be a point such that
+  \begin{equation*}
+    N_{2\delta+1}^{g_i\cdot S_{n_i}} \set{\eta(n_i)\suchthat\text{$\eta$ a geodesic ray with
+        $\eta(0) = g_i$ and $\eta(\infty) = \zeta$}} \subset H_i,
+  \end{equation*}
+  where $N_{2\delta+1}^{g_i\cdot S_{n_i}}$ denotes a $2\delta+1$-neighbourhood
+  in $g_i\cdot S_{n_i}$ taken with respect to the metrid $\dist$.
+  Then $\zeta \in U_i$ and $q_i(\zeta)$ is contained in the simplex of $H_i$
+  spanned by this set of vertices.
 \end{lemma}
@@
   in $U_i$ for infinitely many $i$. Then after passing to a subsequence there
-  exists for each $i$ a point $\zeta_i \in C\setminus U_i$, so for each $i$
-  there is a geodesic ray $\alpha_i$ from $g_i$ to $\zeta_i$ that does not pass
-  through $H_i$.
-After passing to a subsequence, the rays $\alpha_i$ converge uniformly on compact susbets to a bi-infinite geodesic from $\xi$ to some $\zeta \in C$ that does not meet $H$, contardicting Lemma~\ref{lem:geodesicsmeethorosphere}.
+  exists for each $i$ a point $\zeta_i \in C\setminus U_i$, so by
+  Lemma~\ref{lem:describing_q_i} for each $i$ there is a geodesic ray
+  $\alpha_i$ from $g_i$ to $\zeta_i$ that meets $N_{2\delta+1}^{g_i\cdot
+  S_{n_i}}(g_i\cdot S_{n_i} - H_i)$. After passing to a subsequence, the rays
+  $\alpha_i$ converge uniformly on compact subsets toa bi-infinite geodesic
+  from $\xi$ to some pint $\zeta \in C$ that does not meet $H$, contradicting
+  Lemma~\ref{lem:geodesicsmeethorosphere}.
 \end{proof}
@@
   q_{i_0}(\zeta)) \leq 10\delta + 2$, and, in particular, $q_i\restricted{C}$
-  and $q_{i_0}\restricted{C}$ are related by an affine homotopy.
+  and $q_{i_0}\restricted{C}$ are related by an homotopy.
 \end{lemma}

### 2020-03-10 paper.tex
Stopped worrying about something
Rearranged some todos

@@
 \maketitle
-
-\todo{Worry about when $p^n_m$ is not defined.}
 
@@
 \begin{lemma}\label{lem:describing_q_i}
-  \todo{Check this version is strong enough.}
   Let $\zeta \in \boundary G$ be a point such that
@@
   where $N_{2\delta+1}^{g_i\cdot S_{n_i}}$ denotes a $2\delta+1$-neighbourhood
-  in $g_i\cdot S_{n_i}$ taken with respect to the metrid $\dist$.
+  in $g_i\cdot S_{n_i}$ taken with respect to the metric $\dist$.
   Then $\zeta \in U_i$ and $q_i(\zeta)$ is contained in the simplex of $H_i$
@@
 
+  \todo{Is the lemma strong enough?}
   In summary, any geodesic ray from $g_i$ to $\zeta$ passes within a distance 
@@
   follows by lemma~\ref{lem:describing_q_i}. 
+  \todo{Is the lemma strong enough?}
 \end{proof}
@@
 \begin{proof}
-  \todo{proof read the first htree paragraphs}
+  \todo{proof read the first three paragraphs}
   Let $G$ satisfy $\ddag'_{C+D}$ with constants $L$ and $m_0 \geq n_0$.

### 2020-03-10 paper.tex
Spellcheck

@@
   triangle with vertices $\xi$, $\alpha(\infty)$ and $\alpha'(\infty)$ is
-  $\delta$-slim, so the subray of $\alpha$ between $\xi$ and $w$ is contained
+  $\delta$-slim, so the sub-ray of $\alpha$ between $\xi$ and $w$ is contained
   in a $\delta$-neighbourhood of $\alpha'$.  Let $w' \in \alpha'$ be a point
@@
   S_{n_i}}(g_i\cdot S_{n_i} - H_i)$. After passing to a subsequence, the rays
-  $\alpha_i$ converge uniformly on compact subsets toa bi-infinite geodesic
+  $\alpha_i$ converge uniformly on compact subsets to a bi-infinite geodesic
   from $\xi$ to some pint $\zeta \in C$ that does not meet $H$, contradicting
@@
   one limit point equal to $\xi$ and the other in $C$ meet $H$; this set exists
-  by \cref{lem:boundedintersection}.
+  by \cref{lem:bounded_intersection}.
 
@@
   $\alpha(\infty)\in C$ and let $x$ be a point of intersection between $\alpha$
-  and $B$. Since the triangle with vertcies $x$, $g_i$ and $\xi$ is
+  and $B$. Since the triangle with vertices $x$, $g_i$ and $\xi$ is
   $\delta$-slim, and $\dist(x, [\xi, g_i]) \to \infty$ as $i\to\infty$, for
@@
 
-  Since $\dist(z_i', x') > 2\delta$, the distance from $y_i'$ to the subray of
+  Since $\dist(z_i', x') > 2\delta$, the distance from $y_i'$ to the sub-ray of
   $\alpha'$ from $x'$ to $\zeta$ is greater than $\delta$. Therefore by
@@
   simplices adjacent to $x_1$ and $x_2$, so by Lemma~\ref{lem:propermaps} we
-  can pass to a subsequence so that the sequences $g_i\cdot \zeta_1^i$ anl
+  can pass to a subsequence so that the sequences $g_i\cdot \zeta_1^i$ and
   $g_i\cdot\zeta_2^i$ converge to points $\zeta_1$ and $\zeta_2$ in $\boundary
@@
 We can immediately give a sufficient condition for $\S_M$ to be satisfied. This
-result is analagous to Proposition~\ref{prop:BM2}.
+result is analogous to Proposition~\ref{prop:BM2}.
 
@@
   \boundary\Delta$. Then the map $g_i\composed f_i$ is independent of $i$; call
-  this map $f$. It remains to show that $f$ is nullhomotopic in $H$; then it is
-  nullhomotopic by an affine map by~\cite{zeeman64}, and this gives a
+  this map $f$. It remains to show that $f$ is null-homotopic in $H$; then it is
+  null-homotopic by an affine map by~\cite{zeeman64}, and this gives a
   contradiction for $i$ sufficiently large.
@@
 
-Thrououghout the rest of this section we assume that $G$ satisfies
+Throughout the rest of this section we assume that $G$ satisfies
 $\ddag'_M$ and $\S_M$ for all $M$.
@@
   subdivisions of the interval. Finally, using the condition $\S_?$, we deduce
-  that $f_0 \disjointunion f_1$ admints an affine extension to $\sd^{L'}(J
+  that $f_0 \disjointunion f_1$ admits an affine extension to $\sd^{L'}(J
   \times [0,1])$ after Call the extension $F$ and let $h = i^n_\infty \composed
@@
   $\newdist(i^n_{n+1}(y), i^n_{n+1}\composed p^\infty_n (\xi))$ is bounded by
-  the product of $D$ and the the number of 2-simpices in $\sd^L\Delta$, where
+  the product of $D$ and the the number of 2-simplices in $\sd^L\Delta$, where
   $L$ is the number appearing in Proposition~\ref{prop:i_in_dimension_2}.  By

### 2020-03-10 paper.tex
Added some todos
Added another todo
typo

@@
 \maketitle
+
+\todo{Affine vs simplicial}
+\todo{Write introduction}
+\todo{Hyperbolicity conventions}
+\todo{Proofread section 3}
 
@@
                           &\geq \dist(x, y_i) - \dist(v,x) - \delta\\
-                          &\to \infty\text{ as $i \to \infty$}\tab{$\star$}
+                          &\to \infty\text{ as $i \to \infty$}\tag{$\star$}
   \end{align*}

### 2020-03-10 paper.tex
Fixed some todos in section 2.3

@@
 
-\begin{lemma}\label{lem:boundedintersection}
+\begin{lemma}\label{lem:bounded_intersection}
   Let $C$ be a compact subset of $\boundary G - \set\xi$. Then the set of points 
@@
 
-The maps $q_i$ are described by the following lemma, which is immediate from
-the definition of $p^\infty_i$.
+The maps $q_i$ are described by the following lemma.
 
@@
 
+\begin{proof}
+  This is immediate from the definition of the maps $p^\infty_{n_i}$. Note that
+  the set has diameter at most $6\delta+1$, so does indeed span a simplex.
+\end{proof}
+
 \begin{lemma}
@@
 \begin{proof}
+  \todo{Check the claim about neighbourhoods being equal.}
   Suppose that a compact subset $C$ of $\boundary G - \set\xi$ is not contained
@@
   $\alpha_i$ from $g_i$ to $\zeta_i$ that meets $N_{2\delta+1}^{g_i\cdot
-  S_{n_i}}(g_i\cdot S_{n_i} - H_i)$. After passing to a subsequence, the rays
-  $\alpha_i$ converge uniformly on compact subsets to a bi-infinite geodesic
-  from $\xi$ to some pint $\zeta \in C$ that does not meet $H$, contradicting
+  S_{n_i}}(g_i\cdot S_{n_i} - H_i)$, and so does not meet $H_i\intersection
+  N_{i-4\delta-1}(v)$, which is equal to $H \intersection N_{i-4\delta-1}(v)$.
+  After passing to a subsequence, the rays $\alpha_i$ converge uniformly on
+  compact subsets to a bi-infinite geodesic from $\xi$ to some point $\zeta \in
+  C$ that does not meet $H$, contradicting
   Lemma~\ref{lem:geodesicsmeethorosphere}.
@@
 
-  \todo{Is the lemma strong enough?}
   In summary, any geodesic ray from $g_i$ to $\zeta$ passes within a distance 
@@
   follows by lemma~\ref{lem:describing_q_i}. 
-  \todo{Is the lemma strong enough?}
 \end{proof}

### 2020-03-11 paper.tex
Modified the definition of the H_i
This makes some later things work better, and I don't think it breaks
anything.

@@
 
-\section{Horoballs in the Rips Complex}\label{sec:horoballs}
+\section{Horoballs in the Rips Complex}\label{sec:horoball}
 
@@
     \begin{equation*}
-      g_i\left(N_j(v_i) \intersection S_{n_i}\right) 
-            = g_j\left(N_j(v_j) \intersection S_{n_j}\right).
+      N_j(v) \intersection g_i(S_{n_i}) = N_j(v) \intersection g_j(S_{n_j})
     \end{equation*}
@@
 
-Let $H_i$ be the full subcomplex of $K$ with vertex set
-\begin{equation*}
-  g_i\left(N_i(v_i) \intersection S_{n_i}\right);
-\end{equation*}
-notice that $H_i$ contains $H_j$ for $i \geq j$, and also that $g_i$ maps the
-full subcomplex of $K_{n_i}$ with vertex set $N_i(v_i) \intersection S_{n_i}$
-isometrically onto $H_i$.
+Let $H_i$ be the full subcomplex of $K$ with vertex set $N_i(v) \intersection
+g_i(S_{n_i})$; notice that $H_i$ contains $H_j$ for $i \geq j$, and also that
+$g_i$ maps the full subcomplex of $K_{n_i}$ with vertex set $N_i(v_i)
+\intersection S_{n_i}$ isometrically onto $H_i$.
 
@@
 horosphere, the topology of which approximates that of $\boundary G - \set\xi$.
-The rest Section of~\ref{sec:horoballs} will be spent justifying this point of view.
+The rest Section of~\ref{sec:horoball} will be spent justifying this point of view.
 
@@
 \begin{proof}
-  \todo{Check the claim about neighbourhoods being equal.}
   Suppose that a compact subset $C$ of $\boundary G - \set\xi$ is not contained

### 2020-03-11 paper.tex
Deleted an orphaned lemma
Lemma: p^infty_m = p_n_m\composed p^\infty_n
Also made lots of other changes

@@
 \todo{Write introduction}
-\todo{Hyperbolicity conventions}
-\todo{Proofread section 3}
+\todo{Proofread all}
 
@@
 
-Let $G$ be a hyperbolic group and let $S$ be a symmetric generating set for $G$.
+\subsection{Hyperbolic groups and the Rips complex}
+
+Let $G$ be a hyperbolic group and let $S$ be a symmetric generating set for
+$G$.  Let $\dist(\cdot, \cdot)$ be the natural metric on the Cayley graph of
+$G$ with respect to $S$; on $G$ this metric agrees with the word metric.
+
 Let $\delta \geq 0$ be such that the Cayley graph of $G$ with respect to $S$ is
-$\delta$-hyperbolic. Let $\dist(\cdot, \cdot)$ be the natural metric on the
-Cayley graph.
+$\delta$-hyperbolic, meaning that all geodesic triangles in the Cayley graph of
+$G$ are $\delta$-thin. To ameliorate the growth of constants later on we in
+fact assume that all \emph{ideal} triangles (with vertices in $G \union
+\boundary G$) are $\delta$-hyperbolic; this can be guaranteed by multiplying
+$\delta$ by $4$.
 
@@
   and the result follows.
-\end{proof}
-
-\begin{lemma}
-  \todo{Orphaned}
-  For $\xi \in \boundary G$ and $n - m \geq D + \delta$ the points $p^n_m
-  \composed p^\infty_n (\xi)$ and $p^\infty_m(\xi)$ lie in a common simplex of
-  $K_n^D$.
-\end{lemma}
-
-\begin{proof}
-  By definition, $p^\infty_m(\xi)$ is contained in the simplex spanned by the set
-  $\set{g \in S_m \suchthat \xi \in V_m(g)}$ and $p^n_m\composed p^\infty_n(\xi)$ is
-  contained in the simplex spanned by $\{p^n_m(g) \suchthat g \in S_n \text{
-  and } \xi \in V_n(g)\}$.  We show that the union
-  \begin{equation*}
-    \set{g \in S_m \suchthat \xi \in V_m(g)} \union \{p^n_m(g) \suchthat g \in S_n \text{ and } \xi \in V_n(g)\}
-  \end{equation*}
-  of these sets spans a simplex in $K_n$; this simplex then contains
-  $p^\infty_m(\xi)$ and $p^n_m\composed p^\infty_n(\xi)$.  It is sufficient to
-  prove that if $\xi \in V_m(g_1) \intersection V_n(g_2)$ for $g_1 \in S_m$ and
-  $g_2 \in S_n$ then $\dist(g_1, p^n_m(g_2)) \leq D$.
-
-  For $i = 1$ or $2$ let $\gamma_i$ be a geodesic ray with $\gamma_i(0) = e$ and
-  $\gamma_i(\infty) = \xi$ such that $\dist(g_1, \gamma_1(m)) \leq 2\delta
-  + 1$ and $\dist(g_2, \gamma_2(n)) \leq 2\delta+1$.  As in
-  \cref{lem:psimplicial}, $\dist(p^n_m(g_2), \gamma_2(m)) \leq
-  2\delta$, since $n-m \geq 3\delta+1$.  Then $\dist(p^n_m(g_2), g_1) \leq
-  2\delta + 2\delta + 2\delta+1 \leq D$.
 \end{proof}
@@
   q_{i_0}(\zeta)) \leq 10\delta + 2$, and, in particular, $q_i\restricted{C}$
-  and $q_{i_0}\restricted{C}$ are related by an homotopy.
+  and $q_{i_0}\restricted{C}$ are homotopic.
 \end{lemma}
@@
   all such vertices spans a simplex, so, in particular, $q_i\restricted{C}$ and
-  $q_{i_0}\restricted{C}$ are related by an affine homotopy for $i \geq i_0$. 
+  $q_{i_0}\restricted{C}$ are homotopic for $i \geq i_0$. 
 \end{proof}

### 2020-03-11 paper.tex
Added intro secion
Chose a resolution to the whole affine business.

@@
 
-\todo{Affine vs simplicial}
+\todo{Proof-read all}
+
+\section{Introduction}
+
 \todo{Write introduction}
-\todo{Proofread all}
 
@@
   to a map that factors through $p^\infty_n \from \boundary G \to K_n$, $f$
-  admits an extension to $\Delta$ that is affine on $\sd^L \Delta$.
+  admits an extension to $\Delta$ that is affine on $\sd^L \Delta$. (We say
+  that a map between simplicial complexes is affine if its restriction to any
+  simplex of the domain is affine.)
 \end{definition}
 
-We can immediately give a sufficient condition for $\S_M$ to be satisfied. This
-result is analogous to Proposition~\ref{prop:BM2}.
-
-\begin{proposition}
+We now give a sufficient condition for $\S_M$ to be satisfied. This result is
+analogous to Proposition~\ref{prop:BM2}.
+
+\begin{proposition}\label{prop:sufficient_condition}
   Suppose that $\boundary G - \set\xi$ is simply connected for any point $\xi
@@
 
-\begin{proof}
+We will use the following lemma:
+
+\begin{lemma}\label{lem:relative_approximation}
+  Let $X$ be a simplicial complex and let $f\from\sd^M\boundary\Delta\to X$ be
+  a simplicial map. Suppose that $f$ admits a continuous extension to $\Delta$.
+  Then there exists $L$ such that $f$ admits an extension to $\Delta$ that is
+  affine on $\sd^L\Delta$. 
+\end{lemma}
+
+\begin{proof}
+  This follows from the main theorem of~\cite{zeeman64}: note that the degree
+  $L$ subdivision of a complex can be obtained from any degree $L$ relative
+  subdivision by further subdividing some simplices, so any map that is affine
+  on the relative subdivision is also affine on the full subdivision.
+\end{proof}
+
+\begin{proof}[Proof of Proposition~\ref{prop:sufficient_condition}]
   Suppose that the condition is not satisfied. Then for each $i$ there exists a
@@
   this map $f$. It remains to show that $f$ is null-homotopic in $H$; then it is
-  null-homotopic by an affine map by~\cite{zeeman64}, and this gives a
-  contradiction for $i$ sufficiently large.
+  null-homotopic by an affine map by Lemma~\ref{lem:relative_approximation},
+  and this gives a contradiction for $i$ sufficiently large.
 

### 2020-03-12 paper.tex
Added a definition of a visual metric.
Fixed the proposition about homotopies

@@
   \end{enumerate}
+\end{definition}
+
+Finally, we endow $\boundary G$ with a visual metric in the usual way.
+
+\begin{definition}
+  Let $\rho$ be a visual metric on $\boundary G$, so that there exist constants
+  $k_1 \in (0,1]$, $k_2 \geq 1$ and $a > 1$ such that for any $\xi_1$ and
+  $\xi_2$ in $\boundary G$,
+  \begin{equation*}
+    \rho(\xi_1, \xi_2) \in \left[k_1 a^{-\gromov{e}{\xi_1}{\xi_2}}, k_2 a^{-\gromov{e}{\xi_1}{\xi_2}}\right]
+  \end{equation*}
 \end{definition}
@@
   $p^\infty_n\composed\gamma_1$. Suppose that $\newdist(f_0(x), f_1(x))\leq C$
-  for every $x \in \boundary \Delta$. Then there is a homotopy $h$ from
-  $i^n_\infty\composed f_0$ to $i^n_\infty\composed f_1$ satisfying a bounded
-  length condition: for any $x \in \boundary\Delta$,
+  for all $x \in \boundary \Delta$. Then there is a homotopy
+  $h\from\boundary\Delta\times[0,1]\to\boundary G$ from $i^n_\infty\composed
+  f_0$ to $i^n_\infty\composed f_1$ satisfying a bounded length condition: for
+  any $x \in \boundary\Delta$,
   \begin{equation*}
@@
 \begin{proof}
-  \todo{proof read the first three paragraphs}
   Let $G$ satisfy $\ddag'_{C+D}$ with constants $L$ and $m_0 \geq n_0$.
-  By increasing $m_0$ we can also assume that $G$ satisfies $\S_?$ with
-  constants $L'$ and $m_0$.
+  Let $M$ be such that $3\cdot2^M \geq 2L+2$, so that $\sd^M\boundary\Delta$
+  has at least $2L+2$ edges.  By increasing $m_0$ we can also assume that $G$
+  satisfies $\S_M$ with constants $L'$ and $m_0$.
 
@@
   $\sd^{k_1}\boundary\Delta$. We first show that we may assume that $k_0$ and
-  $k_1$ are equal. If not, suppose $k_0 < k_1$.
+  $k_1$ are equal, at the cost of increasing the distance between $f_0$ and
+  $f_1$ slightly. If they are not already equal, assume $k_0 < k_1$.
 
   Let $f_0'$ be the simplicial map on $\sd^{k_1}$ defined as follows. For each
-  edge $e$ of $\sd^{k_0}\boundary\Delta$, choose an orientation of $e$ define
-  $f_0'\restricted{\sd^{k_1-k_0}e}$ to be given by $f_0\restricted{e}$ on the
-  initial edge of $\sd^{k_1-k_0}e$ and constant equal to the image under $f_0$
-  of the terminal vertex of $e$ on the rest of $\sd^{k_1-k_0}$. Then there is a
-  homotopy from $f_0$ to $f_0'$ such that for any $x \in \boundary\Delta$, the
-  path traced by $x$ under the homotopy is contained in a single edge of $K_n$.
-  It follows that, when composed with $i^n_\infty$, this homotopy gives a
-  homotopy from $i^n_\infty\composed f_0$ to $i^n_\infty \composed f_0'$ such
-  that the path traced by any point in $\boundary\Delta$ has diameter at most
-  some multiple of $a^{-n}$ as given by Corollary~\ref{cor:visualdiameter}.
-  Therefore we may replace $f_0$ by $f_0'$ and assume that $f_0$ and $f_1$ are
-  simplicial maps on a common subdivision $J$ of $\boundary\Delta$, and
-  $\newdist(f_0(x), f_1(x))\leq C+D$ for any $x \in \boundary\Delta$.
+  edge $I$ of $\sd^{k_0}\boundary\Delta$, choose an orientation of $I$ and
+  define $f_0'\restricted{\sd^{k_1-k_0}I}$ to be given by $f_0\restricted{I}$
+  on the initial edge of $\sd^{k_1-k_0}I$ and constant equal to the image under
+  $f_0$ of the terminal vertex of $I$ on the rest of $\sd^{k_1-k_0}I$. Then
+  there is a homotopy from $f_0$ to $f_0'$ such that for any $x \in
+  \boundary\Delta$, the path traced by $x$ under the homotopy is contained in a
+  single edge of $K_n$.  It follows that, when composed with $i^n_\infty$, this
+  homotopy gives a homotopy from $i^n_\infty\composed f_0$ to $i^n_\infty
+  \composed f_0'$ such that the path traced by any point in $\boundary\Delta$
+  has diameter at most some multiple of $a^{-n}$ as given by
+  Corollary~\ref{cor:visualdiameter}.  Notice also that $f_0'$ is still a
+  simplicial approximation to $p^\infty_n\composed\gamma_0$.  Therefore we may
+  replace $f_0$ by $f_0'$ and assume that $f_0$ and $f_1$ are simplicial maps
+  on a common subdivision $J$ of $\boundary\Delta$, where now $\newdist(f_0(x),
+  f_1(x))\leq C+D$ for any $x \in \boundary\Delta$.
 
@@
   \end{equation*}
-  defined on a subset of the product simplicial complex $J \times [0,1]$ and
-  this map is a simplicial approximation to the map $\gamma_0 \disjointunion
-  \gamma_1$ from $J\times\{0\} \disjointunion J \times\{1\}$ to $\boundary G$.
-
-  Using $\ddag'_C$ we can extend $\gamma_0\disjointunion\gamma_1$ along $x
-  \times [0,1]$ for each vertex $x$ of $J$ in such a way that the extension
-  along each edge $x\times [0,1]$, when composed with $p^\infty_n$, admits a
-  simplicial approximation connecting $f_0(x)$ to $f_1(x)$ after at most $L$
-  subdivisions of the interval. Finally, using the condition $\S_?$, we deduce
-  that $f_0 \disjointunion f_1$ admits an affine extension to $\sd^{L'}(J
-  \times [0,1])$ after Call the extension $F$ and let $h = i^n_\infty \composed
-  F$, so that $h$ is a homotopy from $i^n_\infty\composed f_0$ to
-  $i^n_\infty\composed f_1$.
-
-  It remains to prove the bounded length assertion.  Let $M$ be the number of
-  $2$-simplices in $\sd^{L'}([0,1]^2)$.  Corollary~\ref{cor:visualdiameter}
-  gives a constant $C_0$ so that any $2$-simplex is mapped by $i^n_\infty$ to a
-  set of diameter at most $C_0 a^{-n}$, and so we can take $\mu = MC_0$.
+  the domain of which is a simplicial complex that we think of as a subspace of
+  the topological space $\boundary\Delta\times[0,1]$. This map is a
+  simplicial approximation to the map $\gamma_0 \disjointunion \gamma_1$ from
+  $J\times\{0\} \disjointunion J \times\{1\}$ to $\boundary G$.
+
+  Using $\ddag'_{C+D}$ we can extend $\gamma_0\disjointunion\gamma_1$ to a simplicial map
+  \begin{equation*}
+    J\times\{0\} \union(\Vert J \times \sd^L [0,1]) \union J\times\{1\} \to K_n,
+  \end{equation*}
+  again thinking of the domain of this map as a subspace of
+  $\boundary\Delta\times[0,1]$ in the same way. Each component of the
+  complement of this subspace in $\boundary\Delta\times[0,1]$ is a $2$-cell
+  whose boundary is an edge path of length $2L+2$. Identifying this edge path
+  with a copy of $\sd^M\boundary\Delta$ with some edges collapsed to a point,
+  we can use the condition $\S_M$ to extend the map to the full $2$-simplex
+  $\Delta$ in such a way that it is affine on $\sd^{L'}\Delta$, and use this
+  extension to extend the map to all of $\boundary\Delta\times[0,1]$.
+
+  It remains to prove the bounded length assertion.  Let $N$ be the number of
+  $2$-simplices in $\sd^M\Delta$.  Corollary~\ref{cor:visualdiameter} gives a
+  constant $C_0$ so that any $2$-simplex is mapped by $i^n_\infty$ to a set of
+  diameter at most $C_0 a^{-n}$, and so we can take $\mu = NC_0$.
 \end{proof}

### 2020-03-26 paper.tex
Proof read 4.1

@@
 Let $G$ be a hyperbolic group and let $S$ be a symmetric generating set for
-$G$.  Let $\dist(\cdot, \cdot)$ be the natural metric on the Cayley graph of
-$G$ with respect to $S$; on $G$ this metric agrees with the word metric.
+$G$. Let $\dist(\cdot, \cdot)$ be the natural metric on the Cayley graph of $G$
+with respect to $S$; on $G$ this metric agrees with the word metric.
 
@@
 We denote by $\gromov{a}{b}{c}$ the Gromov product of $b$ and $c$ in $G \union
-\boundary G$ with respect to base point $a \in G$. Using $\newdist$ we extend the
-Gromov product to $K$:
+\boundary G$ with respect to base point $a \in G$. Using $\newdist$ we extend
+the Gromov product to $K$:
 
@@
 boundary. In~\cite{bestvinamess91}, Bestvina and Mess introduce the following
-condition that a hyperbolic group might satisfy.
+condition that a hyperbolic group might satisfy. (Regarding the constants,
+note that with our convention that ideal triangles are $\delta$-hyperbolic,
+$C$ in the cited paper can be taken to be equal to $\delta$.)
 
@@
 \begin{proposition}\cite[Proposition 3.2]{bestvinamess91}
-  If $G$ satisfies $\ddag_{11\delta + 3}$ then $\boundary G$ is locally path
+  If $G$ satisfies $\ddag_{8\delta + 3}$ then $\boundary G$ is locally path
   connected.
@@
 
-\begin{proposition}\cite[Proposition ?]{bestvinamess91}\label{prop:BM2}
-  If $\boundary G - \set\xi$ is connected for any $\xi \in \boundary G$ then
+\begin{proposition}\cite[Proposition 3.3]{bestvinamess91}\label{prop:BM2}
+  If $\boundary G - \set\xi$ is connected for all $\xi \in \boundary G$ then
   $G$ satisfies $\ddag_M$ for any $M$.
@@
 under the same assumption. This condition reinterprets the paths in $\ddag_M$
-as paths in the complexes $K_n$, with the additional assumption that these
-paths approximate paths that factor through the projection map $p^\infty_n$.
-This interpretation gives a more systematic method for constructing paths in
-$\boundary G$ from paths in the spheres $K_n$, and permits a generalisation to
-higher dimensional connectivity.
-
-\begin{definition}
-  We say that $G$ satisfies $\ddag'_M$ if there exist numbers $L$ and $n_0$ such that,
-  for any $n \geq n_0$, any $\zeta_1$ and $\zeta_2$ in $\boundary G$
-  such that $\newdist(p^\infty_n(\zeta_1), p^\infty_n(\zeta_2)) \leq M$, and
-  any vertices $x_1$ and $x_2$ of $K_n$ adjacent to $p^\infty_n(\zeta_1)$ and
-  $p^\infty_n(\zeta_2)$, there is a path $\alpha\from I\to \boundary G$ from
-  $\zeta_1$ to $\zeta_2$ in $\boundary G$ such that $p^\infty_n\composed\alpha$
-  admits a simplicial approximation connecting $x_1$ to $x_2$ in $K_n$ after at
-  most $L$ barycentric subdivisions of $I$.
+as edge paths in the complexes $K_n$, with the additional assumption that
+these paths approximate paths that factor through the projection map
+$p^\infty_n$. This interpretation strengthens the link between
+path-connectedness of the boundary and connectedness of the complexes $K_n$.
+
+\begin{definition}
+  We say that $G$ satisfies $\ddag'_M$ if there exist numbers $L$ and $n_0$
+  such that, for any $n \geq n_0$, any $\zeta_1$ and $\zeta_2$ in $\boundary
+  G$ such that $\newdist(p^\infty_n(\zeta_1), p^\infty_n(\zeta_2)) \leq M$,
+  and any vertices $x_1$ and $x_2$ of the minimal simplices of $K_n$
+  containing $p^\infty_n(\zeta_1)$ and $p^\infty_n(\zeta_2)$, there is a path
+  $\alpha\from I\to \boundary G$ from $\zeta_1$ to $\zeta_2$ in $\boundary G$
+  such that $p^\infty_n\composed\alpha$ admits a simplicial approximation
+  connecting $x_1$ to $x_2$ in $K_n$ after at most $L$ barycentric
+  subdivisions of $I$.
 \end{definition}
@@
   \geq i$, points $\zeta_1^i$ and $\zeta_2^i$ in $\boundary G$ and vertices
-  $x_1^i$ and $y_1^i$ of $K_{n_i}$ adjacent in $K_{n_i}$ to
+  $x_1^i$ and $y_1^i$ of the minimal simplex of $K_{n_i}$ containing 
   $p^\infty_{n_i}(\zeta^i_1)$ and $p^\infty_{n_i}(\zeta^i_2)$ such that there
@@
   $\dist(x_1^i, x_2^i)$ is bounded we can pass to a deeper subsequence so that
-  $g_i\cdot x_2^i$ is constant equal to $x_2$ for all $i$, and $x_2$ is
-  contained in $H_i$ for all $i$.
+  $g_i\cdot x_2^i$ is constant equal to some vertex $x_2$ for all $i$, and
+  $x_2$ is contained in $H_i$ for all $i$.
 
   Now, $g_i\cdot \zeta_1^i$ and $g_i\cdot\zeta_2^i$ map by $q_i$ to points in
-  simplices adjacent to $x_1$ and $x_2$, so by Lemma~\ref{lem:propermaps} we
+  simplices containing $x_1$ and $x_2$, so by Lemma~\ref{lem:propermaps} we
   can pass to a subsequence so that the sequences $g_i\cdot \zeta_1^i$ and
@@
   $\beta$ from $\zeta_1$ to $\zeta_2$ and also a neighbourhood of each of the
-  points $\zeta_1$ and $\zeta_2$. By Lemma~\ref{lem:uniform_continuity} and
-  compactness of $C$, there exists $\epsilon > 0$ and $i_0 \in \naturals$ such
-  that for subset $V$ of $C$ of diameter at most $\epsilon$ and any $i \geq
-  i_0$, $q_i(V)$ has diameter (with respect to $\newdist$) at most $6\delta+2$.
-  By increasing $i_0$ we may also assume that $\zeta_1^i$ and $\zeta_2^i$ are
-  contained in $C$ for $i \geq i_0$. By decreasing $\epsilon$ we may assume
-  that the $\epsilon$-neighbourhoods of $\zeta_1$ and $\zeta_2$ are contained
-  in $C$.
+  points $\zeta_1$ and $\zeta_2$. By Lemma~\ref{lem:uniform_continuity}, there
+  exists $\epsilon > 0$ and $i_0 \in \naturals$ such that for subset $V$ of
+  $C$ of diameter at most $\epsilon$ and any $i \geq i_0$, $q_i(V)$ has
+  diameter (with respect to $\newdist$) at most $6\delta+2$. By increasing
+  $i_0$ we may also assume that $\zeta_1^i$ and $\zeta_2^i$ are contained in
+  $C$ for $i \geq i_0$. By decreasing $\epsilon$ we may assume that the
+  $\epsilon$-neighbourhoods of $\zeta_1$ and $\zeta_2$ are contained in $C$.
 
@@
 \begin{proof}
-  For the first claim, see~\cite{bestvinamess91}. For the second, let $p$ be a 
-  point on $\alpha$ such that $\dist(x, p) \leq \delta$. Then the triangle 
-  inequality shows that $\abs{\dist(e,p) - \dist(e,x)} \leq \delta$, and 
-  so $\dist(p, \alpha(\dist(e,x))) \leq \delta$. Then the result 
-  follows from another application of the triangle inequality.
+  For the first claim, see~\cite{bestvinamess91} and recall that ideal
+  triangles are assumed to be $\delta$-hyperbolic. For the second, let $p$ be
+  a point on $\alpha$ such that $\dist(x, p) \leq \delta$. Then the triangle
+  inequality shows that $\abs{\dist(e,p) - \dist(e,x)} \leq \delta$, and so
+  $\dist(p, \alpha(\dist(e,x))) \leq \delta$. Then the result follows from
+  another application of the triangle inequality.
 \end{proof}
@@
   \begin{enumerate}
-    \item for each $n$, $i^n_{n+1}$ is an affine map on the subdivision
+    \item for each $n$, $i^n_{n+1}$ is a simplicial map on the subdivision
       $\sd_L\Skel_1 K_n$,
@@
   For an edge $e$ of $K_n$ connecting vertices $x_1$ and $x_2$,
-  $\dist(i^n_{n+1}(x_1), i^n_{n+1}(x_2))$ is at most $D + 4\delta + 2$. It
-  follows that there is a path $\alpha$ from $\gamma_{x_1}(\infty)$ to
-  $\gamma_{x_2}(\infty)$ in $\boundary G$ so that
-  $p^\infty_{n+1}\composed\alpha$ admits a simplicial approximation connecting
-  $i^n_{n+1}(x_1)$ to $i^n_{n+1}(x_2)$ after at most $L$ subdivisions. Define
-  $i^n_{n+1}$ to be this simplicial map on $\sd^L e$.
+  $\dist(i^n_{n+1}(x_1), i^n_{n+1}(x_2))$ is at most $2(2\delta + 1) + D = D +
+  4\delta + 2$. It follows from $\ddag'_{D+4\delta+2}$ that there is a path
+  $\alpha$ from $\gamma_{x_1}(\infty)$ to $\gamma_{x_2}(\infty)$ in $\boundary
+  G$ so that $p^\infty_{n+1}\composed\alpha$ admits a simplicial approximation
+  connecting $i^n_{n+1}(x_1)$ to $i^n_{n+1}(x_2)$ after $L$ subdivisions.
+  Define $i^n_{n+1}$ to be this simplicial map on $\sd^L e$.
 
@@
   Finally, let $U$ be a neighbourhood of $x$ such that $\rho(\gamma(x),
-  \gamma(y)) \leq \epsilon/3$ for $y \in U$. Now, for any $y \in U$ and $t \in (0, 2^{-M}]$,
+  \gamma(y)) \leq \epsilon/3$ for $y \in U$. Now, for any $y \in U$ and 
+  $t \in (0, 2^{-M}]$,
   \begin{equation*}
@@
   \begin{equation*}
-    \Diam(h(\{x\}\times (0,1])) \leq \mu \left(\sum_{m\geq 0} a^{-m}\right)a^{-n},
+    \Diam(h(\{x\}\times (0,1])) 
+            \leq \mu \left(\sum_{m\geq 0} a^{-m}\right)a^{-n},
   \end{equation*}

### 2020-04-01 paper.tex
Minor changes to 4.2
Wrote a conclusion section and started work on the introduction

@@
 
-\todo{Write introduction}
+\begin{enumerate}
+  \item Introduce boundaries. What are they, why are they important.
+  \item Kapovich's question. Not much flexibility, not very many restrictions
+    either.
+  \item Partial answers.
+\end{enumerate}
+
+The goal of this paper is to prove the following theorem, which restricts the
+local complexity of the boundary of a hyperbolic group in terms of its global
+complexity.
+
+\begin{theorem}\label{thm:main_theorem}
+  Let $G$ be a one-ended hyperbolic group. Then $\boundary G$ is locally simply
+  connected if and only if $\boundary G - \set\xi$ is simply connected for any
+  point $\xi \in \boundary G$.
+\end{theorem}
+
+In Section~\ref{sec:spheres} we use the Rips complex of a group $G$ to build a
+sequence of simplicial complexes $(K_n)_{n \geq 0}$ that give successively
+better approximations to the boundary $\boundary G$. These simplicial complexes
+are spheres in the Rips complex. There exist natural simplicial maps
+$p^n_m\from K_n\to K_m$ for $n - m$ large enough, and there exist natural
+continuous maps $p^\infty_n\from\boundary G \to K_n$ for all $n$.  The
+remainder of Section~\ref{sec:spheres} will be spent proving quantitative
+statements about these maps.
+
+In Section~\ref{sec:horoball} we prove a compactness result: given a sequence
+of vertices $v_n \in K_n$, there exist group elements $g_n$ and a subcomplex
+$H$ of the Rips complex such that translation by $g_n$ maps a large
+neighbourhood in $K_n$ of $v_n$ onto a large neighbourhood in $H$ of $g_n\cdot
+v_n$.  We may further assume that $(g_n)$ converges to a point $\xi \in
+\boundary G$, and then we think of $H$ as a horoball in $G$ asymptotic to
+$\xi$. We then spend the remainder of Section~\ref{sec:horoball} describing
+projection maps $\boundary G - \set\xi \to H$.
+
+In Section~\ref{sec:double_dagger} we begin by recalling the so-called
+double-dagger condition $\ddag$ of Bestvina and Mess. This condition is
+guaranteed to hold if $\boundary G$ does not contain a cut point, and implies
+that $\boundary G$ is locally path connected. We then modify the condition to
+allow for easier generalisation, and introduce a new condition $\S$, which we
+will see to be related the local simple connectedness of $\boundary G$. Using
+the compactness results from Section~\ref{sec:horoball} we show that this
+condition is satisfied whenever we have that $\boundary G - \set\xi$ is simply
+connected for any $\xi$ in $\boundary G$.
+
+Then, in Section~\ref{sec:local_simple_connectedness} we show that our new
+condition $\S$ implies the local simple connectedness of $\boundary G$. We
+begin by using $\S$ to construct a sequence of maps $(i^n_\infty)_n$ from the
+2-skeleton of $K_n$ to $\boundary G$. These maps can be thought of as
+approximate sections of $p^\infty_n$, in that $i^n_\infty\composed p^\infty_n$
+converges uniformly to the identity map $\boundary G \to \boundary G$ as $n$
+tends to $\infty$. By controlling the diameter of the image under $i^n_\infty$
+of a simplex in $K_n$ we are able to prove the local simple connectedness of
+$\boundary G$.
+
+Finally, in Section~\ref{sec:conclusion} we put the results of the previous
+sections together to prove Theorem~\ref{thm:main_theorem}, and conclude the
+paper with some questions about strengthenings and generalisations.
 
@@
 $\delta$-hyperbolic, meaning that all geodesic triangles in the Cayley graph of
-$G$ are $\delta$-thin. To ameliorate the growth of constants later on we in
+$G$ are $\delta$-thin. To reduce the growth of constants later on we in
 fact assume that all \emph{ideal} triangles (with vertices in $G \union
@@
   \set\xi$ and let $C_1$ be a compact subset of $\boundary G - \set\xi$
-  containing $C_0$ and the image of $h$. Let $i_2$ be so that $C_1 \subset
-  U_{i_2}$.
+  containing $C_0$ and the image of $h$. Let $i_2 \geq i_1$ be so that $C_1
+  \subset U_{i_2}$.
 
@@
 
-\section{Local simple connectedness}
+\section{Local simple connectedness}\label{sec:local_simple_connectedness}
 
@@
 
-\begin{restatable}{theorem}{ddagimpliesLCd}\label{thm:ddagimpliesLCd}
+\begin{restatable}{theorem}{ddagimpliesLCtwo}\label{thm:ddagimpliesLCtwo}
   If $G$ satisfies $\ddag'_M$ and $\S_M$ for all $M$ then $\boundary G$ is
@@
 
-We begin the proof of \cref{thm:ddagimpliesLCd} by proving the following 
+We begin the proof of \cref{thm:ddagimpliesLCtwo} by proving the following 
 proposition, which extends the maps constructed in
@@
 
-\Cref{thm:ddagimpliesLCd} follows from this proposition:
-
-\ddagimpliesLCd*
+\Cref{thm:ddagimpliesLCtwo} follows from this proposition:
+
+\ddagimpliesLCtwo*
 
@@
 
+\section{Conclusion}\label{sec:conclusion}
+
+The results of Sections~\ref{sec:double_dagger}
+and~\ref{sec:local_simple_connectedness} together imply one direction of
+Theorem~\ref{thm:main_theorem}; we now complete the proof of this theorem.
+
+\begin{proof}[Proof of Theorem~\ref{thm:main_theorem}]
+  If $G$ is a one-ended hyperbolic group such that $\boundary G - \set\xi$ is
+  simply connected for any $\xi \in \boundary G$, then the condition $\S_M$ is
+  satisfied for any $M$ by Proposition~\ref{prop:sufficient_condition}. It
+  follows that $\boundary G$ is locally simply connected by
+  Theorem~\ref{thm:ddagimpliesLCtwo}.
+
+  For the converse, suppose that $\boundary G$ is connected and $\boundary$ 
+  is locally simply connected. Let $\xi$ be a point in $\boundary G$ and let
+  $\gamma\from S^1\to\boundary G - \set\xi$ be a continuous map.
+
+  The point $\xi$ is a conical limit point for the action of $G$ on $\boundary
+  G$, so there exist points $\zeta_-$ and $\zeta_+$ in $\boundary G$ and a
+  sequence $(g_n)_{n = 1}^\infty$ of elements of $G$ such that:
+  \begin{enumerate}
+    \item the sequence $g_n\cdot\xi$ converges to $\zeta_-$ as $n$ tends to
+      infinity, and
+    \item the sequence $(g_n)$, considered as continuous maps from $\boundary
+      G$ to $\boundary G$, converges uniformly on compact subsets of $\boundary
+      G - \set\xi$ to the constant map with image $\zeta_+$.
+  \end{enumerate}
+  See~\cite{bowditch99c} for further explanation of this property.
+
+  Let $U$ be a neighbourhood of $\zeta_+$ such that the closure of $U$ does not
+  contain $\zeta_-$ and let $V$ be a neighbourhood of $\zeta_+$ contained in
+  $U$ such that any map from the circle to $V$ is nullhomotopic in $U$. Then by
+  the properties of the sequence $(g_n)$ described above, there exists an
+  element $g_n$ such that $g_n\cdot\xi \notin U$ and $g_n\composed\gamma$ has
+  image in $V$. Then $g_n\composed\gamma$ admits a contracting homotopy with
+  image in $U$, and the image of this homotopy under $g_n^{-1}$ is a
+  contracting homotopy of $\gamma$ with image contaed in $\boundary G -
+  \set\xi$.
+\end{proof}
+
+If $G$ is a group such that $\boundary G - \set\xi$ is disconnected for some
+point $\xi$ in $\boundary G$, arguments due to Bowditch~\cite{bowditch98b} and
+Swarup~\cite{swarup96} build an action of $G$ on a tree-like space to show that
+$\boundary G$ is disconnected. It follows that $\boundary G$ is locally path
+connected if and only if either $G$ is one- or two-ended. No such argument is
+available in the higher dimensional case, but on the other hand no known
+example of a boundary of a hyperblic group contradicts the corresponding
+assertion. Therefore the following questions are natural.
+
+\begin{question} Is there a one-ended hyperbolic group $G$ such that $\boundary
+  G$ is simply connected but not locally simply connected? Conversely, if
+  $\boundary G$ is locally simply connected but not simply connected, does it
+  follow that $\boundary G$ is a circle and $G$ is virtually Fuchsian?
+\end{question}
+
+It is also natural to ask whether the theorem of this paper generalises to
+higher dimensions. The difficulty is in generalising the proof of
+Proposion~\ref{prop:sufficient_condition}: given a sequence of maps from $S^0$
+to $\boundary G$ we pass to a uniformly convergent subsequence, but this is not
+possible for higher dimensional spheres without controlling the modulus of
+continuity of the maps.
+
+\begin{question} Suppose that $\boundary G - \set\xi$ is $k$-connected for any
+  point $\xi \in \boundary G$. Does it follow that $\boundary G$ is
+  locally-$k$-connected?
+\end{question}
+
 \bibliography{references}

### 2020-04-01 paper.tex
Finished the introduction and proof-read sections 1,2

@@
 
-\todo{Proof-read all}
+\todo{Proof-read section 3 onwards}
 
@@
 
-\begin{enumerate}
-  \item Introduce boundaries. What are they, why are they important.
-  \item Kapovich's question. Not much flexibility, not very many restrictions
-    either.
-  \item Partial answers.
-\end{enumerate}
+If a group acts geometrically on a proper hyperbolic space then, following
+Gromov~\cite{gromov87}, we say that the group is hyperbolic, and quasi-isometry
+invariants of the space can be thought of as invariants of the group. One
+particularly powerful quasi-isometry invariant that can be used in
+this way is the Gromov boundary of the space. This is the set of geodesic rays
+in the space eminating from a fixed base point, where rays are defined to be
+equivalent if they remain a bounded distance apart. In this way one can define
+the boundary $\boundary G$ of a hyperbolic group $G$.
+
+The boundary of a hyperbolic group is useful as a quasi-isometry invariant of
+the group: if groups $G_1$ and $G_2$ are quasi-isometric then $\boundary G_1
+\isom \boundary G_2$. Furthermore, certain topological properties of the
+boundary translate directly into algebraic properties of the group. By a
+theorem of Stallings~\cite{stallings68}, $\boundary G$ is disconnected if and
+only if $G$ admits a splitting as an amalgamated product or HNN extension over
+a finite subgroup. A theorem of Bowditch further characterises splittings over
+virtually cyclic subgroups: if $\boundary G$ is connected then $G$ splits over
+a virtually cyclic subgroup if and only if $\boundary G$ can be separated by
+the removal of a pair of points. Sometimes the topology of $\boundary G$
+determines $G$ even more precisely: if $\boundary G$ is homeomorphic to a
+circle then the Convergence Group Theorem of Tukia, Casson, Jungreis and
+Gabai~\cite{tukia88,cassonjungreis94,gabai92} tells us that $G$ contains a
+surface group at finite index.
+
+In~\cite{gromov87}, Gromov showed that the boundary of a hyperbolic group is a
+compact metric space with finite topological dimension. Beyond these basic
+properties, and excepting the case when $G$ is the fundamental group of a
+negatively curved smooth manifold, in which case $\boundary G$ is a sphere,
+boundaries of hyperbolic groups tend to be wild, fractal-like objects.
+In~\cite{kapovichkleiner00}, Kapovich and Kleiner ask the following question.
+
+\begin{question}\cite[Question A]{kapovichkleiner00}
+  Which topological spaces are boundaries of hyperbolic groups?
+\end{question}
+
+On the one hand, finding concrete examples of spaces arising as boundaries has
+proved difficult, but on the other, relatively few restrictions on the topology
+of the boundary are known. One restriction of particular importance is a
+theorem of Bestvina and Mess~\cite{bestvinamess91}, which states that if
+$\boundary G$ is connected and is not disconnected by the removal of any single
+point then $\boundary G$ is locally path connected. Combined with a result of
+Bowditch~\cite{bowditch98b} and Swarup~\cite{swarup96}, this implies that
+$\boundary G$ is locally path connected whenever it is connected.
 
@@
 local complexity of the boundary of a hyperbolic group in terms of its global
-complexity.
+complexity in a similar way to the theorem of Bestvina and Mess described
+above.
 
@@
 
-In Section~\ref{sec:spheres} we use the Rips complex of a group $G$ to build a
-sequence of simplicial complexes $(K_n)_{n \geq 0}$ that give successively
-better approximations to the boundary $\boundary G$. These simplicial complexes
-are spheres in the Rips complex. There exist natural simplicial maps
-$p^n_m\from K_n\to K_m$ for $n - m$ large enough, and there exist natural
-continuous maps $p^\infty_n\from\boundary G \to K_n$ for all $n$.  The
-remainder of Section~\ref{sec:spheres} will be spent proving quantitative
-statements about these maps.
+The paper is structured as follows. In Section~\ref{sec:spheres} we use the
+Rips complex of the group $G$ to build a sequence $(K_n)_{n \geq 0}$ of
+simplicial complexes that give successively better approximations to the
+boundary $\boundary G$. These simplicial complexes are spheres in the Rips
+complex. There exist natural simplicial maps $p^n_m\from K_n\to K_m$ for $n -
+m$ large enough, and there exist natural continuous maps
+$p^\infty_n\from\boundary G \to K_n$ for all $n$.  The remainder of
+Section~\ref{sec:spheres} will be spent proving quantitative statements about
+these maps.
 
@@
 $\xi$. We then spend the remainder of Section~\ref{sec:horoball} describing
-projection maps $\boundary G - \set\xi \to H$.
+projection maps $\boundary G - \set\xi \to H$. This relates the topology of
+$\boundary G - \set\xi$ to that of $H$, and hence to the topology of large
+balls in $K_n$ for $n$ sufficiently large.
 
 In Section~\ref{sec:double_dagger} we begin by recalling the so-called
-double-dagger condition $\ddag$ of Bestvina and Mess. This condition is
+double-dagger condition $\ddag_M$ of Bestvina and Mess. This condition is
 guaranteed to hold if $\boundary G$ does not contain a cut point, and implies
 that $\boundary G$ is locally path connected. We then modify the condition to
-allow for easier generalisation, and introduce a new condition $\S$, which we
+allow for easier generalisation, and introduce a new condition $\S_M$, which we
 will see to be related the local simple connectedness of $\boundary G$. Using
@@
 Then, in Section~\ref{sec:local_simple_connectedness} we show that our new
-condition $\S$ implies the local simple connectedness of $\boundary G$. We
-begin by using $\S$ to construct a sequence of maps $(i^n_\infty)_n$ from the
+condition $\S_M$ implies the local simple connectedness of $\boundary G$. We
+begin by using $\S_M$ to construct a sequence of maps $(i^n_\infty)_n$ from the
 2-skeleton of $K_n$ to $\boundary G$. These maps can be thought of as
@@
 Let $G$ be a hyperbolic group and let $S$ be a symmetric generating set for
-$G$. Let $\dist(\cdot, \cdot)$ be the natural metric on the Cayley graph of $G$
-with respect to $S$; on $G$ this metric agrees with the word metric.
-
-Let $\delta \geq 0$ be such that the Cayley graph of $G$ with respect to $S$ is
-$\delta$-hyperbolic, meaning that all geodesic triangles in the Cayley graph of
-$G$ are $\delta$-thin. To reduce the growth of constants later on we in
-fact assume that all \emph{ideal} triangles (with vertices in $G \union
-\boundary G$) are $\delta$-hyperbolic; this can be guaranteed by multiplying
-$\delta$ by $4$.
-
-Fix an ordering on $S$. Let $S^\star$ be the free monoid on 
-$S$; order $S^\star$ by the lex-least ordering: this ordering is defined by 
-requiring that shorter words precede longer and that words of equal length are 
-ordered lexicographically. Let $D = 10^6\delta + 10^6$.
+$G$. Let $e$ be the identity element of $G$, which we use as a base point. Let
+$\dist(\cdot, \cdot)$ be the length metric on the Cayley graph of $G$ with
+respect to $S$ obtained by setting all edges to have length $1$; on $G$ this
+metric agrees with the word metric.
+
+Let $\delta \geq 0$ be large enough to ensure that the Cayley graph of $G$ with
+respect to $S$ is $\delta$-hyperbolic, meaning that all geodesic triangles in
+the Cayley graph of $G$ are $\delta$-slim. (This means that each edge of each
+triangle is contained in the $\delta$-neighbourhood of the union of the other
+two edges.) Let $\boundary G$ be the boundary of the group, which can be
+identified with the Gromov boundary of the Cayley graph of $G$. To reduce the
+growth of constants later on we in fact assume that all \emph{ideal} triangles
+(with vertices in $G \union \boundary G$) are $\delta$-hyperbolic; this can be
+guaranteed by multiplying $\delta$ by $4$.
+
+Given points $x$ and $y$ in $G \union \boundary G$ we will often denote by
+$[x,y]$ a geodesic from $x$ to $y$, thought of as a subset of the Cayley graph
+together with its boundary. Geodesics in hyperbolic spaces are not necessarily
+unique, so this notation will stand for a choice of geodesic, but the choice
+will not matter.
+
+Throughout this and subsequent sections we use~\cite{bridsonhaefliger99} as a
+reference for fundamental properties of hyperbolic spaces. The reader is
+referred to~\cite{benaklikapovich00} for a useful survey on boundaries of
+hyperbolic groups.
 
 \begin{definition}
-  We denote by $K$ the \emph{Rips complex} of $G$; this is the simplicial
-  complex with vertex set $G$ such that a finite set of elements of $G$ spans a
-  simplex if and only if that set has diameter at most $D$ with respect to the
-  word metric $d$.
+  Let $D = 10^6\delta + 10^6$.  We denote by $K$ the \emph{Rips complex} of
+  $G$; this is the simplicial complex with vertex set $G$ such that a finite
+  set of elements of $G$ spans a simplex if and only if that set has diameter
+  at most $D$ with respect to the word metric $d$.
 \end{definition}
@@
 \begin{remark}\label{rem:dist_vs_newdist}
-  The extended metric $\newdist$ is not a metric, but this will not cause a
-  problem.
-
-  Notice that $\newdist$ agrees with $\dist$ on $G$, and for any $x$ and $y$ in
-  $K$, if $x^\star$ and $y^\star$ are \emph{any} vertices of simplices
-  containing $x$ and $y$ respectively, then
+  The extended ``metric'' $\newdist$ is not a metric, since it only satisifes
+  the triangle inequality up to a bounded additive error, but this will not
+  cause a problem.
+
+  Notice that $\newdist$ agrees with $\dist$ on $G$, and also that the choice
+  of vertices $x^\star$ and $y\star$ in the definition does not matter very
+  much: for any $x$ and $y$ in $K$, if $x^\star$ and $y^\star$ are an
+  alternative choice of vertices of simplices containing $x$ and $y$
+  respectively, then
   \begin{equation*}
@@
 \begin{definition}
+  \todo{Extend to the boundary}
   Given points $x$, $y$ and $z$ in $K$, define the \emph{Gromov product
@@
 
-We now equip $K$ with a topology as follows.
+We now equip $K \union \boundary G$ with a topology as follows.
 
@@
 \begin{definition}
+  Fix an ordering on $S$. Let $S^\star$ be the free monoid on 
+  $S$; order $S^\star$ by the lex-least ordering: this ordering is defined by 
+  requiring that shorter words precede longer and that words of equal length are 
+  ordered lexicographically.
+
   For $n \geq m$ define a map $p^n_m \from S_n \to S_m$ as follows.
-  Given an element $g$ of $S_n$ let $w_g \in S^\star$ be the lexicographically
-  first representative of $g$; note that this word in $S^\star$ necessarily has
+  Given an element $g$ of $S_n$ let $w_g \in S^\star$ be the lex-least
+  representative of $g$; note that this word in $S^\star$ necessarily has
   length $n$.  Then define $p^n_m(g)$ to be the element of $G$ given by
@@
 \begin{proof}
-  Let $\set{g_1, \dotsc, g_k}$ span a simplex in $K_n$.  Then for $g_i$ and
-  $g_j$ in $\set{g_1, \dotsc, g_k}$, the distance from $p^n_m(g_i))$ to a
+  Let $\set{g_1, \dotsc, g_k}$ span a simplex in $K_n$.  Then for $i$ and
+  $j$ in $\set{1, \dotsc, k}$, the distance from $p^n_m(g_i)$ to any
   geodesic from $g_i$ to $g_j$ is at least $n - m - D$, which is greater than
@@
 
+\begin{remark}
   Note that $p^m_l \composed p^n_m = p^n_l$ whenever these maps are defined, and 
@@
   of simplicial complexes.
+\end{remark}
 
@@
 In order to define projections from $\boundary G$ into our system $(K_n)$, we
-first describe a sequence of open covers of $\boundary G$.
+first describe a sequence of covers of $\boundary G$.
 
@@
   For each $n$, fix a partition of unity subordinate to the covering
-  $\set{U_n(x)}_{x \in S_n}$ of $\boundary G$. This is gives a
+  $\set{U_n(x)}_{x \in S_n}$ of $\boundary G$. Equivalently, this is a
   continuous map from $\boundary G$ to the nerve of the covering. Denote by
@@
 
-  Then let $y_1 = \gamma_1(n)$ and $y_2 = \gamma_2(n+1)$. We have
-  $\dist(y_1, \gamma_2) \leq 2\delta$, so by the triangle inequality
-  $\dist(y_1, y_2) \leq 4\delta +1$. It follows that $\dist(x_1, x_2)
+  Then let $y_1 = \gamma_1(n)$ and $y_2 = \gamma_2(n+1)$. By considering the
+  degenerate triangle with edges $\gamma_1$ and $\gamma_2$,
+  $\dist(y_1, \gamma_2) \leq \delta$, so by the triangle inequality
+  $\dist(y_1, y_2) \leq 2\delta +1$. It follows that $\dist(x_1, x_2)
   \leq 6\delta+3$, and so the claimed inequality holds by
@@
   and the result follows. Otherwise $p_1$ is on $[\alpha_1(n_1),
-  \alpha_2(n_2)]$. Similarly either the claimed result holds, or there is a
-  point $p_2$ on $[\alpha_1(n_1), \alpha_2(n_2)]$ within a
-  distance $\delta$ of $\alpha_1(m_2)$.
+  \alpha_2(n_2)]$. Similarly either the claimed inequality holds, or there is a
+  point $p_2$ on $[\alpha_1(n_1), \alpha_2(n_2)]$ within a distance $\delta$ of
+  $\alpha_1(m_2)$.
 
@@
   $\alpha_2(m_2)$ and $\alpha_2(n_2)$, we see that $\dist(p_1, \alpha_2) \leq
-  2\delta$. Therefore $\dist(\alpha_1(m_1), \alpha_2) \leq 3\delta$, and so
+  2\delta$. Therefore $\dist(\alpha_1(m_1), \alpha_2) \leq 3\delta$, and so by
+  a repetition of the argument used earlier,
   \begin{equation*}
@@
            &+ \left(\dist(\alpha_2(m_2), \alpha_2(n_2)) - \dist(p_2, \alpha_2(m_2))\right) \\
-           &\mathllap{{}\leq{}} \delta+2\delta+\delta=4\delta 
+           &\mathllap{{}\leq{}} \delta+2\delta+\delta=4\delta.
   \end{align*}
@@
   \end{equation*}
-  and the result follows.
+  and the result follows since $D \geq 12\delta$.
 \end{proof}

### 2020-04-02 paper.tex
Proof read first lemma of section 3

@@
 
+We call an isometric embedding of an interval into the Cayley graph a
+\emph{geodesic}. If the interval is $(-\infty, \infty)$ we call the geodesic a
+\emph{bi-infinite geodesic}; if the interval is $[0, \infty)$ we call it a
+\emph{geodesic ray.} A bi-infinite geodesic has two ideal end points in
+$\boundary G$, while a geodesic ray has one end point in $G$ and one ideal end
+point in $\boundary G$.  Given points $x$ and $y$ in $G \union \boundary G$ we
+will often denote by $[x,y]$ a geodesic from $x$ to $y$, thought of as a subset
+of the Cayley graph together with its boundary. Geodesics in hyperbolic spaces
+are not necessarily unique, so this notation will stand for a choice of
+geodesic, but the choice will not matter.
+
 Let $\delta \geq 0$ be large enough to ensure that the Cayley graph of $G$ with
@@
 guaranteed by multiplying $\delta$ by $4$.
-
-Given points $x$ and $y$ in $G \union \boundary G$ we will often denote by
-$[x,y]$ a geodesic from $x$ to $y$, thought of as a subset of the Cayley graph
-together with its boundary. Geodesics in hyperbolic spaces are not necessarily
-unique, so this notation will stand for a choice of geodesic, but the choice
-will not matter.
 
@@
 
-\section{Horoballs in the Rips Complex}\label{sec:horoball}
-
-In Section~\ref{sec:double_dagger} we will make use of a limiting argument,
-which will relate the topology of the complement of a point in the boundary
-$\boundary G$ to a particular subcomplex of $K$, which we will think of as
-a horoball in $K$.  In this section we prove that this subcomplex possesses
-certain properties that we will apply later.
+\section{Horoballs in the Rips complex}\label{sec:horoball}
+
+In Section~\ref{sec:double_dagger} we will use a limiting argument, which will
+relate the topology of the complement of a point in the boundary $\boundary G$
+to a particular subcomplex of $K$, which we will think of as a horoball in $K$.
+In this section we prove that this subcomplex possesses the properties that we
+will apply later.
 
@@
   \item
-    The sequence $g_i = g_i\cdot 1$ of vertices of $K$ converges to a point
-    $\xi \in \boundary G$ as $i\to\infty$.
+    The sequence $(g_i)_{i=1}^\infty$ of group elements, considered also as a
+    sequence of vertices of $K$, converges to a point $\xi \in \boundary G$ as
+    $i\to\infty$.
 \end{enumerate}
@@
 
-Let $H$ be the union of the complexes $H_i \subset K$. We view $H$ as a
+Let $H$ be the union of the subcomplexes $H_i \subset K$. We view $H$ as a
 horosphere, the topology of which approximates that of $\boundary G - \set\xi$.
@@
 
-\subsection{Geodesics and and the horosphere}
+\subsection{Geodesics and the horosphere}
 
 \begin{lemma}\label{lem:geodesicsmeethorosphere}
-  Every bi-infinite geodesic with $\xi$ in its limit set meets $H$.
-\end{lemma}
-
-\begin{proof}
-  Let $\alpha$ be a bi-infinite geodesic with $\xi$ as a limit point. 
-  Let the distance $\dist(w,\alpha)$ be realised by a point $x \in \alpha$.
+  Every bi-infinite geodesic with one end point equal to $\xi$ meets $H$.
+\end{lemma}
+
+\begin{proof}
+  Let $\alpha$ be a bi-infinite geodesic with $\xi$ as an end point.  Let the
+  distance $\dist(v,\alpha)$ be realised by a point $x \in \alpha$.
 
@@
                           &= n_i - \dist(g_i, x) + \dist(x, y_i) - \delta\\
-                          &\geq \dist(x, y_i) - \dist(v,x) - \delta\\
+                          &\geq n_i - \dist(g_i, v) - \dist(x, v) + \dist(x,y_i) - \delta\\
+                          &= \dist(x,y_i) - \dist(x,v) - \delta\\
                           &\to \infty\text{ as $i \to \infty$}\tag{$\star$}
   \end{align*}
-  Therefore, for $i$ sufficiently large, there exists a point $p_i$ on $\alpha$
+  In particular, $n_i > \dist(g_i, z_i)$ for $i$ sufficiently large, so for
+  $i$ sufficiently large, there exists a point $p_i$ on $\alpha$
   such that $z_i$ lies between $\xi$ and $p_i$ on $\alpha$ and so that
@@
       It follows that $\dist(x,p_i) \leq \dist(g_i,p_i)-\dist(g_i,x)+2\delta
-      = 2\delta$.
+      \leq \dist(x, v) + 2\delta$.
     \item If $p_i$ is between $z_i$ and $x$ on $\alpha$ then by an identical 
@@
       \begin{equation*}
-        \dist(x,p_i)\leq\dist(g_i,x) - \dist(g_i,p_i) + 2\delta =2\delta.
+        \dist(x,p_i)\leq\dist(g_i,x) - \dist(g_i,p_i) + 2\delta \leq  \dist(x,v) + 2\delta.
       \end{equation*}
@@
 
-  Either way, $\dist(v, p_i) \leq \dist(v, x) + 2\delta$. In summary, we have
+  Either way, $\dist(v, p_i) \leq 2\dist(x, v) + 2\delta$. In summary, we have
   shown that for $i$ sufficiently large there is a point $p_i\in\alpha$ with
-  $\dist(g_i,p_i)=n_i$ and $\dist(p_i,f(\Vertices J))$ bounded by $\dist(x,w) +
-  2\delta$. Then $p_i \in H_i$ whenever $i$ is at least $\dist(x,w) + 2\delta$.
+  $\dist(g_i,p_i)=n_i$ and $\dist(v, p_i)$ bounded by $2\dist(x,w) +
+  2\delta$. Then $p_i \in H_i \intersection \alpha$ whenever $i$ is at least
+  $2\dist(x,w) + 2\delta$. 
 \end{proof}

### 2020-04-02 paper.tex
Removed redundancy in section 3.2

@@
 
-\begin{lemma}\label{lem:geodesicsmeethorosphere}
+\begin{lemma}\label{lem:nonempty_intersection}
   Every bi-infinite geodesic with one end point equal to $\xi$ meets $H$.
+  Furthermore, the intersection between the geodesic and $H$ is contained in a
+  ball with centre $v$ and radius depending only on $\delta$ and the distance
+  from the $v$ to the geodesic.
 \end{lemma}
@@
   shows that the distances $\dist([z_i, g_i], x)$ and $\dist([z_i, g_i], p_i)$
-  tend to infinity as $i\to\infty$.  We now divide into cases according to
-  which of $x$ and $p_i$ is closer to $z_i$.
+  tend to infinity as $i\to\infty$. Let $i_0$ be so that both distances are
+  greater than $\delta$ for $i\geq i_0$.
+
+  We now assume $i \geq i_0$ and divide into cases according to which of $x$
+  and $p_i$ is closer to $z_i$.
   \begin{enumerate}
@@
 
-  Either way, $\dist(v, p_i) \leq 2\dist(x, v) + 2\delta$. In summary, we have
-  shown that for $i$ sufficiently large there is a point $p_i\in\alpha$ with
-  $\dist(g_i,p_i)=n_i$ and $\dist(v, p_i)$ bounded by $2\dist(x,w) +
-  2\delta$. Then $p_i \in H_i \intersection \alpha$ whenever $i$ is at least
-  $2\dist(x,w) + 2\delta$. 
+  Either way, $\dist(v, p_i) \leq 2\dist(x, v) + 2\delta$ for $i \geq i_0$. In
+  summary, we have shown that for $i$ sufficiently large there is a point
+  $p_i\in\alpha$ with $\dist(g_i,p_i)=n_i$ and $\dist(v, p_i)$ bounded by
+  $2\dist(x,w) + 2\delta$. Then $p_i \in H_i \intersection \alpha$ whenever $i$
+  is at least $2\dist(x,w) + 2\delta$. Therefore the intersection is non-empty.
+
+  To see that it is bounded, let $p \in H \intersection \alpha$. Since $z_i \to
+  \xi$ as $i\to \infty$, $z_i$ is between $\xi$ and $p$ on $\alpha$ for $i$
+  sufficiently large. Fix $i \geq i_0$ so that this is true and also so that $p
+  \in H_i$, so $\dist(g_i, p) = n_i$. Then the point $p$ has the properties
+  assumed of $p_i$, so the argument above shows that $\dist(p, v) \leq
+  2\dist(x,v) + 2\delta$. Therefore the intersection $H \intersection \alpha$
+  is bounded.
 \end{proof}
@@
 \begin{proof}
-  Let $\alpha$ be any bi-infinite geodesic with $\alpha(-\infty)=\xi$ and 
-  $\alpha(\infty)\in C$. Let $x \in \alpha \intersection H$. Since $C$ is
-  compact, there exists a point $w \in \alpha$, between $\xi$ and $x$ on
-  $\alpha$, such for that any bi-infinite geodesic $\beta$ with
-  $\beta(-\infty)$ in $C$ and $\beta(\infty) = \alpha(\infty)$, $\beta$ does
-  not meet the $100\delta$-neighbourhood of the sub-ray of $\alpha$ between
-  $\xi$ and $w$: otherwise a limiting argument shows that $\xi$ is in $C$.
-
-  Since $g_i \to \xi$, the distance $\dist(w, [\xi, g_i]) \to \infty$ as
-  $i\to\infty$. The triangle with vertices $\xi$, $g_i$ and $x$ is
-  $\delta$-slim, so the geodesic path from $g_i$ to $x$ passes within a
-  distance $\delta$ of $w$ for $i$ large enough. Therefore, since $\dist(g_i,
-  x) = n_i$ for $i$ large enough, the following inequality holds for all $i$
-  large enough.
-  \begin{equation*}
-    0 \leq \dist(g_i, w) + \dist(w, x) - n_i \leq 2\delta.
-  \end{equation*}
-
-  Let $\alpha'$ be a bi-infinite geodesic with $\alpha'(-\infty) = \xi$ and
-  $\alpha'(\infty) \in C$ and let $x' \in \alpha' \intersection H$. The ideal
-  triangle with vertices $\xi$, $\alpha(\infty)$ and $\alpha'(\infty)$ is
-  $\delta$-slim, so the sub-ray of $\alpha$ between $\xi$ and $w$ is contained
-  in a $\delta$-neighbourhood of $\alpha'$.  Let $w' \in \alpha'$ be a point
-  with $\dist(w, w') \leq \delta$.
-
-  We split into cases according to the order of $\xi$, $w'$ and $x'$ on
-  $\alpha'$.
-  \begin{enumerate}
-    \item
-      First we suppose that $w'$ is between $x'$ and $\xi$ on $\alpha'$. Then as
-      in the argument above, for $i$ sufficiently large we have the following
-      inequality:
-      \begin{equation*}
-        0 \leq \dist(g_i, w') + \dist(w', x') - n_i \leq 2\delta.
-      \end{equation*}
-      And therefore,
-      \begin{equation*}
-        -2\delta \leq \dist(g_i, w) + \dist(w, x') - n_i \leq 4\delta.
-      \end{equation*}
-      Finally, putting these inequalities together,
-      \begin{equation*}
-        \dist(x, x') \leq 2\dist(w, x) + 4\delta,
-      \end{equation*}
-      and so we uniformly bound this distance in this case.
-    \item
-      Alternatively, $x'$ is between $w'$ and $\xi$ on $\alpha'$ and so (since
-      the triangle with vertices $\xi$, $w$ and $w'$ is $\delta$-slim) $x'$ is
-      within a distance $2\delta$ of the geodesic ray from $x$ to $\xi$. By
-      considering the triangle with vertices $\xi$, $g_i$ and $x$ for $i$ large
-      enough, a geodesic segment from $g_i$ to $x$ passes within a distance
-      $3\delta$ of $x'$. Therefore we have the following inequality for all $i$
-      sufficiently large:
-      \begin{equation*}
-        0 \leq \dist(g_i, x') + \dist(x', x) - \dist(g_i, x) \leq 6\delta.
-      \end{equation*}
-      Finally, for $i$ sufficiently large, $\dist(g_i, x') = \dist(g_i, x) = n_i$,
-      so
-      \begin{equation*}
-        \dist(x,x') \leq 6\delta.\qedhere
-      \end{equation*}
-  \end{enumerate}
-  Either way, $\dist(x, x')$ is bounded over all points $x'$ in the
-  intersections between $H$ and geodesics with one end point equal to $\xi$ and
-  the other in $C$.
+  By Lemma~\ref{lem:nonempty_intersection} it is sufficient to show that
+  $\dist(v, \alpha)$ is bounded as $\alpha$ ranges over all bi-infinite
+  geodesics with one end point equal to $\xi$ and the other in $C$.
+
+  Let $\beta$ be a geodesic ray from $v$ to $\xi$. Suppose that there is a
+  sequence $\zeta_i$ of points in $C$ with $\dist(v, [\xi, \zeta_i]) = m_i$
+  where $m_i \to \infty$ as $i\to \infty$. Let $\beta_i$ be a geodesic ray from
+  $v$ to $\zeta_i$. Let $p_i$ be a point on $\beta$ with $\dist(p_i, v) = m_i -
+  \delta - 1$, so $\dist(p_i, [\xi, \zeta_i]) > \delta$. Then by hyperbolicity
+  of the triangle with edges $\beta$, $\beta_i$ and $[\xi, \zeta_i]$ there is a
+  point $q_i \in \beta_i$ with $\dist(p_i, q_i) = \delta$. Then $\dist(v, q_i)
+  \geq \dist(v, p_i) - \delta$. Therefore,
+  \begin{align*}
+    \gromov{v}{\xi}{\zeta_i} &\geq \gromov{v}{p_i}{q_i} \\
+                             &\geq \dist(v, p_i) - \delta\\
+                             &\to \infty \text{ as $i\to\infty$},
+  \end{align*}
+  so $\zeta_i\to\xi$ as $i\to\infty$. But $C$ is a compact subset of $\boundary
+  G - \set\xi$, so we reach a contradiction.
 \end{proof}
@@
   C$ that does not meet $H$, contradicting
-  Lemma~\ref{lem:geodesicsmeethorosphere}.
+  Lemma~\ref{lem:nonempty_intersection}.
 \end{proof}

### 2020-04-02 paper.tex
Proof read new section 3.2
Proof read sections 3 & 4

@@
   Every bi-infinite geodesic with one end point equal to $\xi$ meets $H$.
+
   Furthermore, the intersection between the geodesic and $H$ is contained in a
@@
   \in H_i$, so $\dist(g_i, p) = n_i$. Then the point $p$ has the properties
-  assumed of $p_i$, so the argument above shows that $\dist(p, v) \leq
+  assumed of $p_i$ above, so the argument above shows that $\dist(p, v) \leq
   2\dist(x,v) + 2\delta$. Therefore the intersection $H \intersection \alpha$
@@
 
-\subsection{Projections to the horosphere}
+\subsection{Projections from the boundary to the horosphere}
 
@@
   H_i$ be the restriction of $g_i \composed p^\infty_{n_i}\composed g_i^{-1}$
-  to this set.
+  to $U_i$.
 \end{definition}
@@
     N_{2\delta+1}^{g_i\cdot S_{n_i}} \set{\eta(n_i)\suchthat\text{$\eta$ a geodesic ray with
-        $\eta(0) = g_i$ and $\eta(\infty) = \zeta$}} \subset H_i,
-  \end{equation*}
-  where $N_{2\delta+1}^{g_i\cdot S_{n_i}}$ denotes a $2\delta+1$-neighbourhood
-  in $g_i\cdot S_{n_i}$ taken with respect to the metric $\dist$.
-  Then $\zeta \in U_i$ and $q_i(\zeta)$ is contained in the simplex of $H_i$
-  spanned by this set of vertices.
+        $\eta(0) = g_i$ and $\eta(\infty) = \zeta$}}
+  \end{equation*}
+  is contained in $H_i$, where $N_{2\delta+1}^{g_i\cdot S_{n_i}}$ denotes a
+  $2\delta+1$-neighbourhood in $g_i\cdot S_{n_i}$ taken with respect to the
+  word metric $\dist$.  Then $\zeta \in U_i$ and $q_i(\zeta)$ is contained in
+  the simplex of $H_i$ spanned by this set of vertices.
 \end{lemma}
@@
   N_{i-4\delta-1}(v)$, which is equal to $H \intersection N_{i-4\delta-1}(v)$.
-  After passing to a subsequence, the rays $\alpha_i$ converge uniformly on
-  compact subsets to a bi-infinite geodesic from $\xi$ to some point $\zeta \in
-  C$ that does not meet $H$, contradicting
+  After passing to a subsequence and reparametrising, the rays $\alpha_i$
+  converge uniformly on compact subsets to a bi-infinite geodesic from $\xi$ to
+  some point $\zeta \in C$ that does not meet $H$, contradicting
   Lemma~\ref{lem:nonempty_intersection}.
@@
 \begin{proof}
-  Let $B\subset H$ be a bounded set containing all points where geodesics with
-  one limit point equal to $\xi$ and the other in $C$ meet $H$; this set exists
-  by \cref{lem:bounded_intersection}.
+  Let $B\subset H$ be the set of points of intersection between $H$ and
+  geodesics with one end point equal to $\xi$ and the other in $C$; this set is
+  bounded by Lemma~\ref{lem:bounded_intersection}.
 
@@
   $\alpha(\infty)\in C$ and let $x$ be a point of intersection between $\alpha$
-  and $B$. Since the triangle with vertices $x$, $g_i$ and $\xi$ is
-  $\delta$-slim, and $\dist(x, [\xi, g_i]) \to \infty$ as $i\to\infty$, for
+  and $H$, so $x \in B$.  Since the triangle with vertices $x$, $g_i$ and $\xi$
+  is $\delta$-slim, and $\dist(x, [\xi, g_i]) \to \infty$ as $i\to\infty$, for
   each $i$ there exists a point $y_i$ on $[g_i, x]$ with $\dist(y_i, \alpha)
@@
 
-  Let $V$ be the following set. It is easy to check that this is a
-  neighbourhood of $\zeta$.
+  Let $V$ be the following neighbourhood of $\zeta$.
   \begin{equation*}
     V = \set{\beta(\infty) \suchthat \text{$\beta$ a geodesic with
-            $\beta(-\infty) = \xi$ and $\dist(\beta, x) \leq 3\delta+1$}}
+            $\beta(-\infty) = \xi$ and $\dist(\beta, x) \leq 3\delta+1$}}.
   \end{equation*}
@@
 boundary. In~\cite{bestvinamess91}, Bestvina and Mess introduce the following
-condition that a hyperbolic group might satisfy. (Regarding the constants,
-note that with our convention that ideal triangles are $\delta$-hyperbolic,
-$C$ in the cited paper can be taken to be equal to $\delta$.)
+condition that a hyperbolic group might satisfy. (When comparing the constants
+appearing in our definition of the condition with that in the cited paper, note
+that with our convention that ideal triangles are $\delta$-hyperbolic, Bestvina
+and Mess's constant $C$ can be taken to be equal to $\delta$.)
 
@@
 
-\subsection{An modified condition}
-
-In this section we introduce a related condition. This condition is stronger
-than $\ddag_M$, but, using Bestvina and Mess's result, we show that it holds
-under the same assumption. This condition reinterprets the paths in $\ddag_M$
-as edge paths in the complexes $K_n$, with the additional assumption that
-these paths approximate paths that factor through the projection map
+\subsection{A modified condition}
+
+In this section we introduce a related condition. This condition appears
+stronger than $\ddag_M$, but, using Bestvina and Mess's result, we show that it
+holds under the same assumption. This condition reinterprets the paths in
+$\ddag_M$ as edge paths in the complexes $K_n$, with the additional assumption
+that these paths approximate paths that factor through the projection map
 $p^\infty_n$. This interpretation strengthens the link between
@@
 \begin{definition}
+  Let $I$ be the interval $[0,1]$, which we identify with a 1-simplex.
+
   We say that $G$ satisfies $\ddag'_M$ if there exist numbers $L$ and $n_0$
-  such that, for any $n \geq n_0$, any $\zeta_1$ and $\zeta_2$ in $\boundary
-  G$ such that $\newdist(p^\infty_n(\zeta_1), p^\infty_n(\zeta_2)) \leq M$,
-  and any vertices $x_1$ and $x_2$ of the minimal simplices of $K_n$
-  containing $p^\infty_n(\zeta_1)$ and $p^\infty_n(\zeta_2)$, there is a path
-  $\alpha\from I\to \boundary G$ from $\zeta_1$ to $\zeta_2$ in $\boundary G$
-  such that $p^\infty_n\composed\alpha$ admits a simplicial approximation
-  connecting $x_1$ to $x_2$ in $K_n$ after at most $L$ barycentric
-  subdivisions of $I$.
+  such that, for any $n \geq n_0$, any $\zeta_1$ and $\zeta_2$ in $\boundary G$
+  such that $\newdist(p^\infty_n(\zeta_1), p^\infty_n(\zeta_2)) \leq M$, and
+  any vertices $x_1$ and $x_2$ of simplices of $K_n$ containing
+  $p^\infty_n(\zeta_1)$ and $p^\infty_n(\zeta_2)$, there is a path $\alpha\from
+  I\to \boundary G$ from $\zeta_1$ to $\zeta_2$ in $\boundary G$ such that
+  $p^\infty_n\composed\alpha$ admits a simplicial approximation connecting
+  $x_1$ to $x_2$ in $K_n$ after at most $L$ barycentric subdivisions of $I$.
 \end{definition}
@@
   \geq i$, points $\zeta_1^i$ and $\zeta_2^i$ in $\boundary G$ and vertices
-  $x_1^i$ and $y_1^i$ of the minimal simplex of $K_{n_i}$ containing 
-  $p^\infty_{n_i}(\zeta^i_1)$ and $p^\infty_{n_i}(\zeta^i_2)$ such that there
-  is no path $\alpha$ from $\zeta_1^i$ to $\zeta_2^i$ in $\boundary G$ where
-  $p^\infty_{n_i}\composed\alpha$ admits a simplicial approximation after at
-  most $i$ barycentric subdivisions of the interval.
+  $x_1^i$ and $y_1^i$ of simplices of $K_{n_i}$ containing
+  $p^\infty_{n_i}(\zeta^i_1)$ and $p^\infty_{n_i}(\zeta^i_2)$ such that
+  $\newdist(p^\infty_{n_i}(\zeta^i_1), p^\infty_{n_i}(\zeta^i_2)) \leq M$ and
+  there is no path $\alpha$ from $\zeta_1^i$ to $\zeta_2^i$ in $\boundary G$
+  where $p^\infty_{n_i}\composed\alpha$ admits a simplicial approximation after
+  at most $i$ barycentric subdivisions of the interval.
 
@@
   $\zeta_1^i$ and $\zeta_2^i$ are contained in these neighbourhoods for $i \geq
-  i_0$. Let $\alpha_1^j$ be a path in the ball of radius $\epsilon$ centred at
-  $\zeta_j$ connecting $\zeta_j^i$ to $\zeta_j$.
+  i_0$. For $j=1$ and $j=2$ let $\alpha_1^j$ be a path in the ball of radius
+  $\epsilon$ centred at $\zeta_j$ connecting $\zeta_j^i$ to $\zeta_j$.
 
@@
   has image under $\alpha^i$ with diameter at most $\epsilon$. It follows that
-  the composition of $\alpha^i$ with $q_i$ is a path that admits a simplicial
-  approximation connecting $x_1$ to $x_2$ after boundedly many subdivisions of
-  the interval. For $i \geq i_0$ large enough this gives a contradiction.
+  the composition of $\alpha^i$ with $q_i$ is a path in $H$ that admits a
+  simplicial approximation connecting $x_1$ to $x_2$ after boundedly many
+  subdivisions of the interval. For $i \geq i_0$ large enough this gives a
+  contradiction.
 \end{proof}
@@
 
-  For an edge $e$ of $K_n$ connecting vertices $x_1$ and $x_2$,
+  For an edge $I$ of $K_n$ connecting vertices $x_1$ and $x_2$,
   $\dist(i^n_{n+1}(x_1), i^n_{n+1}(x_2))$ is at most $2(2\delta + 1) + D = D +
@@
   connecting $i^n_{n+1}(x_1)$ to $i^n_{n+1}(x_2)$ after $L$ subdivisions.
-  Define $i^n_{n+1}$ to be this simplicial map on $\sd^L e$.
+  Define $i^n_{n+1}$ to be this simplicial map on $\sd^L I$.
 
@@
 
-\subsection{A two-dimensional version}
+\subsection{Extending maps from the boundary of a 2-simplex}
 
@@
 \begin{definition}
-  Let $\Delta$ be the standard 2-simplex.  We say that $G$ satisfies $\S_M$ if
-  there exist $L$ and $n_0$ such that for any $n\geq n_0$ and any simplicial
-  map $f\from \sd^M\boundary\Delta \to K_n$ that is a simplicial approximation
-  to a map that factors through $p^\infty_n \from \boundary G \to K_n$, $f$
-  admits an extension to $\Delta$ that is affine on $\sd^L \Delta$. (We say
-  that a map between simplicial complexes is affine if its restriction to any
-  simplex of the domain is affine.)
+  Let $\Delta$ be the standard 2-simplex.
+
+  We say that $G$ satisfies $\S_M$ if there exist $L$ and $n_0$ such that for
+  any $n\geq n_0$ and any simplicial map $f\from \sd^M\boundary\Delta \to K_n$
+  that is a simplicial approximation to a map that factors through $p^\infty_n
+  \from \boundary G \to K_n$, $f$ admits an extension to $\Delta$ that is
+  affine on $\sd^L \Delta$. (We say that a map between simplicial complexes is
+  affine if its restriction to any simplex of the domain is affine.)
 \end{definition}
@@
   $L$ subdivision of a complex can be obtained from any degree $L$ relative
-  subdivision by further subdividing some simplices, so any map that is affine
-  on the relative subdivision is also affine on the full subdivision.
+  subdivision by further subdividing some simplices, so any map that is a
+  simplicial map on the relative subdivision is affine on the full subdivision.
 \end{proof}

### 2020-04-06 paper.tex
Minor changes up to lemma 5.3

@@
   There are constants $n_0$ and $L$ such that for each $n\geq n_0$ there is map
-  $i^n_{n+1}\from\Skel_2 K_n \to \Skel_2 K_{n+1}$ such that the
-  following conditions hold.
+  $i^n_{n+1}\from\Skel_2 K_n \to \Skel_2 K_{n+1}$ with the following properties.
   \begin{enumerate}
-    \item for each $n$, $i^n_{n+1}$ is an affine map on the subdivision
-      $\sd_L\Skel_2 K_n$,
-    \item for any vertex $x$ of $K_n$, $\dist(x, i^n_{n+1}(x)) \leq 2\delta+1$,
-      and
+    \item For each $n$, $i^n_{n+1}$ is an affine map on the subdivision
+      $\sd_L\Skel_2 K_n$.
+    \item For any vertex $x$ of $K_n$, $\dist(x, i^n_{n+1}(x)) \leq 2\delta+1$.
   \end{enumerate}
@@
   by that proposition, so there exists $M$ such that $i^n_{n+1}$ is a
-  simplicial map on $\sd^M\Skel_1 K_n$, and this map is a simplicial
+  simplicial map on $\sd^L\Skel_1 K_n$, and this map is a simplicial
   approximation to a map that factors through $p^\infty_{n+1} \from \boundary G
@@
 
-  Then $\S_M$ gives numbers $L$ and $n_0' \geq n_0$ such that for $n \geq
-  n_0'$, for any 2-simplex $\sigma$ of $K_n$, $i^n_{n+1}\restricted\boundary
-  \sigma$ admits an extension to $\sigma$ that is affine on $\sd^L\sigma$.
-  Gluing these extensions together extends $i^n_{n+1}$ to a map $\sd^2 K_n \to
-  \sd_2 K_{n+1}$ with the required properties.
+  Then $\S_L$ gives numbers $L'$ and $n_0' \geq n_0$ such that for $n \geq
+  n_0'$, for any 2-simplex $\sigma$ of $K_n$, $i^n_{n+1}\restricted{\boundary
+  \sigma}$ admits an extension to $\sigma$ that is affine on $\sd^{L'}\sigma$.
+  Gluing these extensions together extends $i^n_{n+1}$ to a map $\Skel_2 K_n \to
+  \Skel_2 K_{n+1}$ with the required properties.
 \end{proof}
@@
   With the notation of Proposition~\ref{prop:i_in_dimension_2}, for $n \geq m
-  \geq n_0$ let $i^n_m \from \Skel_2 K_m \to \Skel_2 K_n$ be the composition
+  \geq n_0$ let $i^m_n \from \Skel_2 K_m \to \Skel_2 K_n$ be the composition
   $i^{n-1}_n \composed \dotsb \composed i^m_{m+1} \from \Skel_2 K_m \to 
-  \Skel_2 K_n$.  This map is affine on a degree $L^{n-m}$ subdivision of 
-  $\Skel_2 K_m$.
+  \Skel_2 K_n$.  This map is affine on the degree $L^{n-m}$ barycentric
+  subdivision of $\Skel_2 K_m$.
 \end{definition}

### 2020-04-06 paper.tex
Proof read section 5.1

@@
   $i^{n-1}_n \composed \dotsb \composed i^m_{m+1} \from \Skel_2 K_m \to 
-  \Skel_2 K_n$.  This map is affine on the degree $L^{n-m}$ barycentric
+  \Skel_2 K_n$.  This map is affine on the degree $(n-m)L$ barycentric
   subdivision of $\Skel_2 K_m$.
@@
   number $R$ depending only on $B$ and $\delta$ such that the sequence $(x_n)$
-  is contained in an $R$-neighbourhood of a ray starting at $e$; let $(y_n)$ be
-  a sequence of points on this geodesic with $\dist(y_n, x_n) \leq R$. Then
-  $\gromov{e}{y_m}{y_n} = \min\{\dist(e, y_m), \dist(e, y_n)\}$, and the result
-  follows with $C = 5R/2$.
+  is contained in an $R$-neighbourhood of a geodesic ray starting at $e$; let
+  $(y_n)$ be a sequence of points on this geodesic with $\dist(y_n, x_n) \leq
+  R$. Then $\gromov{e}{y_m}{y_n} = \min\{\dist(e, y_m), \dist(e, y_n)\}$, and
+  the result follows with $C = 5R/2$.
 \end{proof}
@@
   respect to the visual metric $\vdistance$ is bounded above by $Ca^{-m}$.
+  \qed
 \end{corollary}
@@
   Fix $x \in \Skel_2 K_m$. For $n\geq 0$ let $U_n$ be the minimal subcomplex of
-  $\sd^{nk}\Skel_2 K_m$ containing a neighbourhood of $x$.
+  $\sd^{nk}\Skel_2 K_m$ containing a neighbourhood of $x$. Note that the
+  collection $(U_n)_{n \geq 0}$ is a neighbourhood basis for $x$ in $\Skel_2
+  K_m$.
 

### 2020-04-06 paper.tex
Finished proof read

@@
 
-\begin{proposition}
+\begin{proposition}\label{prop:sufficient_for_ddag_p}
   If $\boundary G - \set\xi$ is path connected then $G$ satisfies $\ddag'_M$
@@
 
+We complete our description of the maps $i^n_\infty$ with the following lemma,
+which can be thought of as saying that $i^n_\infty$ is an approximate section
+of the map $p^\infty_n$.
+
+\begin{lemma}\label{lem:convergestoidentity}
+  There is a constant $C$ such that the distance from $i^m_\infty \composed 
+  p^\infty_m$ to the identity map $\boundary G\to\boundary G$ is at most 
+  $Ca^{-m}$ for each $m \geq n_0$.
+\end{lemma}
+
+\begin{proof}
+  By \cref{lem:linearproduct} there is a constant $C$ such that  for $\xi \in
+  \boundary G$,
+  \begin{equation*}
+    \gromov{e}{i^m_n\composed p^\infty_m(\xi)}{p^\infty_m(\xi)} \geq m - C
+  \end{equation*} 
+  for each $n\geq m\geq n_0$.
+
+  Let $\alpha$ be a geodesic ray with $\alpha(0) = e$ and $\alpha(\infty) = 
+  \xi$. Then $\alpha(m)$ is a vertex of a simplex in $\Skel_2K_m$ containing 
+  $p^\infty_m(\xi)$, and $\gromov{e}{\alpha(m)}{\alpha(n)} = m$ for $n\geq m$.
+  It follows that there is a constant $\delta'$ depending only on $\delta$ such 
+  that
+  \begin{align*}
+    \mathrlap{\gromov{e}{\alpha(n)}{i^m_n\composed p^\infty_m(\xi)}}\quad\quad &\\
+          & \geq \min\{\gromov{e}{\alpha(n)}{\alpha(m)}, 
+            \gromov{e}{\alpha(m)}{p^\infty_m(\xi)}, 
+            \gromov{e}{p^\infty_m(\xi)}{i^m_n\composed p^\infty_m(\xi)}\} 
+            - 2\delta' \\
+          &\geq \min\{m, m - D/2, m - C\} - 2\delta' \\
+          &\geq m - C'
+  \end{align*}
+  for some constant $C'$.
+
+  Therefore $\gromov{e}{\xi}{i^m_\infty\composed p^\infty_m(\xi)} \geq m - C'$, 
+  from which the claim follows.
+\end{proof}
+
 \subsection{Homotopies in $\boundary G$}
@@
   Let $G$ satisfy $\ddag'_{C+D}$ with constants $L$ and $m_0 \geq n_0$.
-  Let $M$ be such that $3\cdot2^M \geq 2L+2$, so that $\sd^M\boundary\Delta$
-  has at least $2L+2$ edges.  By increasing $m_0$ we can also assume that $G$
+  Let $M$ be such that $3\cdot2^M \geq 2^L+2$, so that $\sd^M\boundary\Delta$
+  has at least $2^L+2$ edges.  By increasing $m_0$ we can also assume that $G$
   satisfies $\S_M$ with constants $L'$ and $m_0$.
@@
 
-  Using $\ddag'_{C+D}$ we can extend $\gamma_0\disjointunion\gamma_1$ to a simplicial map
-  \begin{equation*}
-    J\times\{0\} \union(\Vert J \times \sd^L [0,1]) \union J\times\{1\} \to K_n,
+  Using $\ddag'_{C+D}$ we can extend $\gamma_0\disjointunion\gamma_1$ to a
+  simplicial map
+  \begin{equation*}
+    J\times\{0\} \union(\Skel_0 J \times \sd^L [0,1]) \union J\times\{1\} \to K_n,
   \end{equation*}
@@
   complement of this subspace in $\boundary\Delta\times[0,1]$ is a $2$-cell
-  whose boundary is an edge path of length $2L+2$. Identifying this edge path
+  whose boundary is an edge path of length $2^L+2$. Identifying this edge path
   with a copy of $\sd^M\boundary\Delta$ with some edges collapsed to a point,
@@
 
-We now need two more lemmas.
-
-\begin{lemma}\label{lem:convergestoidentity}
-  There is a constant $C$ such that the distance from $i^m_\infty \composed 
-  p^\infty_m$ to the identity map $\boundary G\to\boundary G$ is at most 
-  $Ca^{-m}$ for each $m \geq n_0$.
-\end{lemma}
-
-\begin{proof}
-  By \cref{lem:linearproduct} there is a constant $C$ such that  for $\xi \in
-  \boundary G$,
-  \begin{equation*}
-    \gromov{e}{i^m_n\composed p^\infty_m(\xi)}{p^\infty_m(\xi)} \geq m - C
-  \end{equation*} 
-  for each $n\geq m\geq n_0$.
-
-  Let $\alpha$ be a geodesic ray with $\alpha(0) = e$ and $\alpha(\infty) = 
-  \xi$. Then $\alpha(m)$ is a vertex of a simplex in $\Skel_2K_m$ containing 
-  $p^\infty_m(\xi)$, and $\gromov{e}{\alpha(m)}{\alpha(n)} = m$ for $n\geq m$.
-  It follows that there is a constant $\delta'$ depending only on $\delta$ such 
-  that
-  \begin{align*}
-    \mathrlap{\gromov{e}{\alpha(n)}{i^m_n\composed p^\infty_m(\xi)}}\quad\quad &\\
-          & \geq \min\{\gromov{e}{\alpha(n)}{\alpha(m)}, 
-            \gromov{e}{\alpha(m)}{p^\infty_m(\xi)}, 
-            \gromov{e}{p^\infty_m(\xi)}{i^m_n\composed p^\infty_m(\xi)}\} 
-            - 2\delta' \\
-          &\geq \min\{m, m - D/2, m - C\} - 2\delta' \\
-          &\geq m - C'
-  \end{align*}
-  for some constant $C'$.
-
-  Therefore $\gromov{e}{\xi}{i^m_\infty\composed p^\infty_m(\xi)} \geq m - C'$, 
-  from which the claim follows.
-\end{proof}
+The following proposition extends the family of maps between which we can build
+homotopies.
+
+\begin{proposition}\label{prop:uniform_homotopies}
+  There exists numbers $m_0$ and $\nu$ with the following property. Let
+  $\gamma\from\boundary\Delta\to\boundary G$ be a continuous map. Let $n \geq
+  m_0$ and let $f$ a simplicial approximation to $p^\infty_n\composed\gamma$.
+  Then there is a homotopy $h$ from $\gamma$ to $i^n_\infty\composed f$ such
+  that for any $x \in \boundary\Delta$,
+  \begin{equation*}
+    \Diam(h(\{x\}\times [0,1])) \leq \nu a^{-n}.
+  \end{equation*}
+\end{proposition}
+
+To prove this proposition, we use the following lemma.
 
@@
   p^\infty_{n+1}(\xi))$ are bounded by $6\delta + 3 + 2D$. Let $y$ be a vertex
-  of a minimal simplex containing $p^\infty_n(\xi)$; then $\newdist(y,
-  p^\infty_n(\xi))$ is bounded by $D$.
+  of a minimal simplex containing $p^\infty_n(\xi)$.
 
@@
 
-\begin{proposition}\label{prop:uniform_homotopies}
-  There exists numbers $m_0$ and $\nu$ with the following property. Let
-  $\gamma\from\boundary\Delta\to\boundary G$ be a continuous map. Let $n \geq
-  m_0$ and let $f$ a simplicial approximation to $p^\infty_n\composed\gamma$.
-  Then there is a homotopy $h$ from $\gamma$ to $i^n_\infty\composed f$ such
-  that for any $x \in \boundary\Delta$,
-  \begin{equation*}
-    \Diam(h(\{x\}\times [0,1])) \leq \nu a^{-n}.
-  \end{equation*}
-\end{proposition}
-
-\begin{proof}
+\begin{proof}[Proof of Proposition~\ref{prop:uniform_homotopies}]
   Apply Proposition~\ref{prop:basic_homotopies} with $C$ as in
@@
   to a map $p^\infty_{n+m+1}\composed j_m$ for some map $j_m\from\Skel_1
-  K_{n+m}\to \boundary G$, and then $i^{n+m}_{n+m+1}\composed g_m$ is a
+  K_{n+m}\to \boundary G$, and then $i^{n+m}_{n+m+1}\composed f_m$ is a
   simplicial approximation to $p^\infty_{n+m+1}\composed j_m\composed f_m$.
@@
 
-  Let $x \in \boundary\Delta$ and let $\epsilon > 0$. There exists $M$ such
-  that for $m \geq M$ and $y \in \boundary \Delta$, $\rho(\gamma(y),
-  \gamma_m(y)) \leq \epsilon/3$. Increasing $M$ if necessary we may assume that
-  $\mu a^{-m-n} \leq \epsilon/3$.
-  Finally, let $U$ be a neighbourhood of $x$ such that $\rho(\gamma(x),
-  \gamma(y)) \leq \epsilon/3$ for $y \in U$. Now, for any $y \in U$ and 
-  $t \in (0, 2^{-M}]$,
+  Let $x \in \boundary\Delta$ and let $\epsilon > 0$. By
+  Lemma~\ref{lem:convergestoidentity} there exists $M$ such that for $m \geq M$
+  and $y \in \boundary \Delta$, $\rho(\gamma(y), \gamma_m(y)) \leq \epsilon/3$.
+  Increasing $M$ if necessary we may assume that $\mu a^{-M-n} \leq
+  \epsilon/3$.  Finally, let $U$ be a neighbourhood of $x$ such that
+  $\rho(\gamma(x), \gamma(y)) \leq \epsilon/3$ for $y \in U$. Now, for any $y
+  \in U$ and $t \in (0, 2^{-M}]$,
   \begin{equation*}
@@
 \begin{proof}[Proof of Theorem~\ref{thm:main_theorem}]
-  If $G$ is a one-ended hyperbolic group such that $\boundary G - \set\xi$ is
-  simply connected for any $\xi \in \boundary G$, then the condition $\S_M$ is
-  satisfied for any $M$ by Proposition~\ref{prop:sufficient_condition}. It
-  follows that $\boundary G$ is locally simply connected by
-  Theorem~\ref{thm:ddagimpliesLCtwo}.
-
-  For the converse, suppose that $\boundary G$ is connected and $\boundary$ 
-  is locally simply connected. Let $\xi$ be a point in $\boundary G$ and let
-  $\gamma\from S^1\to\boundary G - \set\xi$ be a continuous map.
+  If $G$ is one-ended then $\ddag'_M$ is satisfied for any $M$ by
+  Proposition~\ref{prop:sufficient_for_ddag_p}. Furthermore, if $\boundary G -
+  \set\xi$ is simply connected for any $\xi \in \boundary G$ then the condition
+  $\S_M$ is satisfied for any $M$ by
+  Proposition~\ref{prop:sufficient_condition}. It follows that $\boundary G$ is
+  locally simply connected by Theorem~\ref{thm:ddagimpliesLCtwo}.
+
+  For the converse, suppose that $\boundary G$ is connected and locally simply
+  connected. Let $\xi$ be a point in $\boundary G$ and let $\gamma\from
+  S^1\to\boundary G - \set\xi$ be a continuous map.
 
@@
   the properties of the sequence $(g_n)$ described above, there exists an
-  element $g_n$ such that $g_n\cdot\xi \notin U$ and $g_n\composed\gamma$ has
-  image in $V$. Then $g_n\composed\gamma$ admits a contracting homotopy with
-  image in $U$, and the image of this homotopy under $g_n^{-1}$ is a
-  contracting homotopy of $\gamma$ with image contaed in $\boundary G -
-  \set\xi$.
+  element $g_n$ of the sequence such that $g_n\cdot\xi \notin U$ and
+  $g_n\composed\gamma$ has image in $V$. Then $g_n\composed\gamma$ admits a
+  contracting homotopy with image in $U$, and the image of this homotopy under
+  $g_n^{-1}$ is a contracting homotopy of $\gamma$ with image contaed in
+  $\boundary G - \set\xi$.
 \end{proof}
@@
   $\boundary G$ is locally simply connected but not simply connected, does it
-  follow that $\boundary G$ is a circle and $G$ is virtually Fuchsian?
+  follow that $\boundary G$ is a circle, and so $G$ is virtually Fuchsian?
 \end{question}

### 2020-04-16 paper.tex
Added todos from comments

@@
 
-\todo{Proof-read section 3 onwards}
+\begin{abstract}
+  In this paper we prove a theorem describing the local topology of the
+  boundary of a hyperbolic group in terms of its global topology: the boundary
+  is locally simply connected if and only if the complement of any point in the
+  boundary is simply connected. This generalises a theorem of Bestvina and
+  Mess~\cite{bestvinamess91}.
+\end{abstract}
 
@@
 
-If a group acts geometrically on a proper hyperbolic space then, following
-Gromov~\cite{gromov87}, we say that the group is hyperbolic, and quasi-isometry
-invariants of the space can be thought of as invariants of the group. One
-particularly powerful quasi-isometry invariant that can be used in
-this way is the Gromov boundary of the space. This is the set of geodesic rays
-in the space eminating from a fixed base point, where rays are defined to be
-equivalent if they remain a bounded distance apart. In this way one can define
-the boundary $\boundary G$ of a hyperbolic group $G$.
+If a group acts geometrically on a proper hyperbolic metric space then,
+following Gromov~\cite{gromov87}, we say that the group is hyperbolic, and
+quasi-isometry invariants of the space can be thought of as invariants of the
+group. One particularly powerful quasi-isometry invariant that can be used in
+this way is the Gromov boundary of the space. This a topological space defined
+as the set of equivalence classes of geodesic rays in the space emanating from
+a fixed base point, where rays are defined to be equivalent if they remain a
+bounded distance apart. In this way one can define the boundary $\boundary G$
+of a hyperbolic group $G$.
 
@@
 properties, and excepting the case when $G$ is the fundamental group of a
-negatively curved smooth manifold, in which case $\boundary G$ is a sphere,
-boundaries of hyperbolic groups tend to be wild, fractal-like objects.
+negatively curved smooth closed manifold, in which case $\boundary G$ is a
+sphere, boundaries of hyperbolic groups tend to be wild, fractal-like objects.
 In~\cite{kapovichkleiner00}, Kapovich and Kleiner ask the following question.
+
+\todo{Survey of examples}
 
@@
 theorem of Bestvina and Mess~\cite{bestvinamess91}, which states that if
-$\boundary G$ is connected and is not disconnected by the removal of any single
-point then $\boundary G$ is locally path connected. Combined with a result of
-Bowditch~\cite{bowditch98b} and Swarup~\cite{swarup96}, this implies that
-$\boundary G$ is locally path connected whenever it is connected.
+$\boundary G$ is connected and cannot be disconnected by the removal of any
+single point then $\boundary G$ is locally path connected. Combined with a
+result of Bowditch~\cite{bowditch98b} and Swarup~\cite{swarup96}, this implies
+that $\boundary G$ is locally path connected whenever it is connected.
 
@@
 above.
+
+\todo{Example of space ruled out by theorem}
 
@@
 boundary $\boundary G$. These simplicial complexes are spheres in the Rips
-complex. There exist natural simplicial maps $p^n_m\from K_n\to K_m$ for $n -
-m$ large enough, and there exist natural continuous maps
-$p^\infty_n\from\boundary G \to K_n$ for all $n$.  The remainder of
-Section~\ref{sec:spheres} will be spent proving quantitative statements about
-these maps.
+complex. There exist natural simplicial maps $p^n_m\from K_n\to K_m$ for $n \gg
+m$, and there exist natural continuous maps $p^\infty_n\from\boundary G \to
+K_n$ for all $n$.  The remainder of Section~\ref{sec:spheres} will be spent
+proving quantitative statements about these maps.
 
@@
 the compactness results from Section~\ref{sec:horoball} we show that this
-condition is satisfied whenever we have that $\boundary G - \set\xi$ is simply
-connected for any $\xi$ in $\boundary G$.
-
+condition is satisfied if $\boundary G - \set\xi$ is simply connected for any
+$\xi$ in $\boundary G$.
+
+\todo{Maybe rephrase?}
 Then, in Section~\ref{sec:local_simple_connectedness} we show that our new
 condition $\S_M$ implies the local simple connectedness of $\boundary G$. We
-begin by using $\S_M$ to construct a sequence of maps $(i^n_\infty)_n$ from the
+begin by using $\S_M$ to construct a sequence of maps $(i^n_\infty)$ from the
 2-skeleton of $K_n$ to $\boundary G$. These maps can be thought of as
-approximate sections of $p^\infty_n$, in that $i^n_\infty\composed p^\infty_n$
-converges uniformly to the identity map $\boundary G \to \boundary G$ as $n$
-tends to $\infty$. By controlling the diameter of the image under $i^n_\infty$
-of a simplex in $K_n$ we are able to prove the local simple connectedness of
-$\boundary G$.
+approximate sections of $p^\infty_n$, in the following sense. For each $n$, let
+$r_n\from K_n \to \Skel_2 K_n$ be a (not necessarily continuous) map sending
+points to nearby points in the 2-skeleton. Then $i^n_\infty\composed r_n
+\composed p^\infty_n$ converges uniformly to the identity map $\boundary G \to
+\boundary G$ as $n$ tends to $\infty$. By controlling the diameter of the image
+under $i^n_\infty$ of a simplex in $K_n$ we are able to prove that $\boundary
+G$ is locally simply connected.
 
@@
 \begin{remark}\label{rem:dist_vs_newdist}
-  The extended ``metric'' $\newdist$ is not a metric, since it only satisifes
+  The extended ``metric'' $\newdist$ is not a metric, since it only satisfies
   the triangle inequality up to a bounded additive error, but this will not
@@
 \begin{definition}
-  \todo{Extend to the boundary}
-  Given points $x$, $y$ and $z$ in $K$, define the \emph{Gromov product
-  $\gromov{x}{y}{z}$ of $x$, $y$ and $z$} as follows.
-  \begin{equation*}
-    \gromov{x}{y}{z} = \frac{1}{2}\left(\newdist(x,y) + \newdist(x,z) -
-          \newdist(y,z)\right)
-  \end{equation*}
+  Let $x \in K$ and let $y$ and $z$ be points in $K \union \boundary G$. Let
+  $x^\star$ be a vertex of the minimal simplex of $K$ containing $x$. If $y$
+  (respectively $z$) is in $\boundary G$ let $y^\star = y$ (respectively
+  $z^\star = z$); otherwise let $y^\star$ (respectively $z^\star$) be a vertex
+  of the minimal simplex of $K$ containing $y$ (respectively $z$.)
+  Then define the \emph{Gromov product $\gromov{x}{y}{z}$ of $x$, $y$ and $z$}
+  as $\gromov{x}{y}{z} = \gromov{x^\star}{y^\star}{z^\star}$.
 \end{definition}
@@
   \begin{equation*}
-    \rho(\xi_1, \xi_2) \in \left[k_1 a^{-\gromov{e}{\xi_1}{\xi_2}}, k_2 a^{-\gromov{e}{\xi_1}{\xi_2}}\right]
+    \rho(\xi_1, \xi_2) \in \left[k_1 a^{-\gromov{e}{\xi_1}{\xi_2}}, k_2
+          a^{-\gromov{e}{\xi_1}{\xi_2}}\right]
   \end{equation*}
@@
     \item for each $n$, $i^n_{n+1}$ is a simplicial map on the subdivision
-      $\sd_L\Skel_1 K_n$,
+      $\sd^L\Skel_1 K_n$,
     \item for any vertex $x$ of $K_n$, $\dist(x, i^n_{n+1}(x)) \leq 2\delta+1$,
@@
   \end{enumerate}
+  (When $X$ is a simplicial complex, we denote by $\sd^n X$ the complex
+  obtained from $X$ by barycentrically subdividing $n$ times.)
 \end{proposition}
@@
     \item For each $n$, $i^n_{n+1}$ is an affine map on the subdivision
-      $\sd_L\Skel_2 K_n$.
+      $\sd^L\Skel_2 K_n$.
     \item For any vertex $x$ of $K_n$, $\dist(x, i^n_{n+1}(x)) \leq 2\delta+1$.
@@
 
+\todo{Doesn't quite make sense.}
 \begin{lemma}\label{lem:convergestoidentity}
@@
   contain $\zeta_-$ and let $V$ be a neighbourhood of $\zeta_+$ contained in
-  $U$ such that any map from the circle to $V$ is nullhomotopic in $U$. Then by
+  $U$ such that any map from the circle to $V$ is null-homotopic in $U$. Then by
   the properties of the sequence $(g_n)$ described above, there exists an
@@
   contracting homotopy with image in $U$, and the image of this homotopy under
-  $g_n^{-1}$ is a contracting homotopy of $\gamma$ with image contaed in
+  $g_n^{-1}$ is a contracting homotopy of $\gamma$ with image contained in
   $\boundary G - \set\xi$.
@@
 higher dimensions. The difficulty is in generalising the proof of
-Proposion~\ref{prop:sufficient_condition}: given a sequence of maps from $S^0$
+Proposition~\ref{prop:sufficient_condition}: given a sequence of maps from $S^0$
 to $\boundary G$ we pass to a uniformly convergent subsequence, but this is not

### 2020-04-23 paper.tex
Corrected some minor mistakes

@@
 
-\todo{Maybe rephrase?}
 Then, in Section~\ref{sec:local_simple_connectedness} we show that our new
@@
 
-\todo{Doesn't quite make sense.}
 \begin{lemma}\label{lem:convergestoidentity}
-  There is a constant $C$ such that the distance from $i^m_\infty \composed 
-  p^\infty_m$ to the identity map $\boundary G\to\boundary G$ is at most 
-  $Ca^{-m}$ for each $m \geq n_0$.
-\end{lemma}
-
-\begin{proof}
-  By \cref{lem:linearproduct} there is a constant $C$ such that  for $\xi \in
-  \boundary G$,
-  \begin{equation*}
-    \gromov{e}{i^m_n\composed p^\infty_m(\xi)}{p^\infty_m(\xi)} \geq m - C
-  \end{equation*} 
-  for each $n\geq m\geq n_0$.
-
+  There is a constant $C$ such that for any $m \geq n_0$, any point $\xi \in
+  \boundary G$, and point $x \in \Skel_2 K_n$ contained in a simplex
+  of $K_n$ containing $p^\infty_n(\xi)$, the visual distance from $\xi$ to
+  $i^\infty_n(x)$ is at most $Ca^{-m}$.
+\end{lemma}
+
+\begin{proof}
+  Let $m$, $\xi$ and $x$ be as in the statement of the lemma.
   Let $\alpha$ be a geodesic ray with $\alpha(0) = e$ and $\alpha(\infty) =
-  \xi$. Then $\alpha(m)$ is a vertex of a simplex in $\Skel_2K_m$ containing 
-  $p^\infty_m(\xi)$, and $\gromov{e}{\alpha(m)}{\alpha(n)} = m$ for $n\geq m$.
-  It follows that there is a constant $\delta'$ depending only on $\delta$ such 
-  that
+  \xi$; then $\alpha(m)$ is a vertex of a simplex of $K_n$ containing
+  $p^\infty_m(\xi)$. There is a path from $\alpha(m)$ to $x$ contained in the
+  union of two 2-simplices of $K_n$, so by Lemma~\ref{cor:visualdiameter} it is
+  sufficient to prove the lemma for $x = \alpha(m)$.
+
+  Let $C$ be the constant appearing in Lemma~\ref{lem:linearproduct}.
+  We have $\gromov{e}{\alpha(m)}{\alpha(n)} = m$ for $n\geq m$, and
+  by~\cite[Proposition III.H.1.22]{bridsonhaefliger99} there is a constant
+  $\delta'$ depending only on $\delta$ such that for $n\geq m$,
   \begin{align*}
-    \mathrlap{\gromov{e}{\alpha(n)}{i^m_n\composed p^\infty_m(\xi)}}\quad\quad &\\
+    \mathrlap{\gromov{e}{\alpha(n)}{i^m_n(\alpha(m))}}\quad\quad &\\
           & \geq \min\{\gromov{e}{\alpha(n)}{\alpha(m)}, 
-            \gromov{e}{\alpha(m)}{p^\infty_m(\xi)}, 
-            \gromov{e}{p^\infty_m(\xi)}{i^m_n\composed p^\infty_m(\xi)}\} 
-            - 2\delta' \\
-          &\geq \min\{m, m - D/2, m - C\} - 2\delta' \\
-          &\geq m - C'
+            \gromov{e}{\alpha(m)}{i^m_n(\alpha(m))}\} 
+            - \delta' \\
+          &\geq \min\{m, m - C\} - \delta' \\
+          &=  m - C - \delta'.
   \end{align*}
-  for some constant $C'$.
-
-  Therefore $\gromov{e}{\xi}{i^m_\infty\composed p^\infty_m(\xi)} \geq m - C'$, 
+  Therefore $\gromov{e}{\xi}{i^m_\infty(\alpha(m))} \geq m - C - \delta'$, 
   from which the claim follows.

### 2020-04-23 paper.tex
Added references

@@
 sphere, boundaries of hyperbolic groups tend to be wild, fractal-like objects.
+Concrete examples include the Menger curve~\cite{benakli92}, which is the
+generic case~\cite{champetier95}, Sierpinski compacta, which arise as
+boundaries of fundamental groups of compact hyperbolic manifolds with non-empty
+totally geodesic boundary, the universal Menger compacta of dimensions
+2~\cite{dranishnikov99} and 3~\cite{dymaraosajda07}, and Pontryagin
+surfaces~\cite{dranishnikov99}. See also~\cite{davisjanuszkiewicz91} for a
+flexible method for constructing interesting high-dimensional boundaries.
+
 In~\cite{kapovichkleiner00}, Kapovich and Kleiner ask the following question.
-
-\todo{Survey of examples}
 

### 2020-04-28 paper.tex
Removed todo. This will take more thought.
Henry's comments

@@
 
-\todo{Example of space ruled out by theorem}
-
 \begin{theorem}\label{thm:main_theorem}
   Let $G$ be a one-ended hyperbolic group. Then $\boundary G$ is locally simply
-  connected if and only if $\boundary G - \set\xi$ is simply connected for any
-  point $\xi \in \boundary G$.
+  connected if and only if, for every point $\xi \in \boundary G$,  $\boundary
+  G - \set\xi$ is simply connected.
 \end{theorem}
@@
 paper with some questions about strengthenings and generalisations.
+
+\subsection*{Acknowledgements}
+
+I am grateful to Henry Wilton for pointing out the proof of
+Proposition~\ref{prop:converse_theorem}, and for other helpful comments.  I am
+also grateful to John Mackay and Panos Papazoglou for helpful discussions on
+this topic.
 
@@
 example of a boundary of a hyperblic group contradicts the corresponding
-assertion. Therefore the following questions are natural.
-
-\begin{question} Is there a one-ended hyperbolic group $G$ such that $\boundary
-  G$ is simply connected but not locally simply connected? Conversely, if
-  $\boundary G$ is locally simply connected but not simply connected, does it
-  follow that $\boundary G$ is a circle, and so $G$ is virtually Fuchsian?
+assertion. Therefore the following question is natural.
+
+\begin{question} 
+  Is there a one-ended hyperbolic group $G$ such that $\boundary G$ is simply
+  connected but not locally simply connected? 
 \end{question}
+
+Note that the converse question has a positive answer if virtually Fuchsian
+groups (which have boundary homeomorphic to a circle) are excepted:
+
+\begin{proposition}\label{prop:converse_theorem}
+  If $G$ is a one-ended hyperbolic group such that $\boundary G$ is locally
+  simply connected then $\boundary G$ is either simply connected or
+  homeomorphic to a circle.
+\end{proposition}
+
+\begin{proof}
+  By Theorem~\ref{thm:main_theorem}, all point complements in $\boundary G$ are
+  simply connected. Let $p$ and $q$ be distinct points in $\boundary G$. If
+  $\boundary G - \set{p,q}$ is connected then $\boundary G$ is simply connected
+  by the Seifert--van Kampen theorem. It follows that either $\boundary G$ is
+  simply connected, or the complement of any two points in $\boundary G$ is
+  disconnected, in which case $\boundary G$ is a circle
+  by a classical theorem in point set topology~\cite[II.2.13]{wilder49}.
+\end{proof}
 

### 2020-06-22 paper.tex
minor changeds?

@@
 \begin{abstract}
-  In this paper we prove a theorem describing the local topology of the
+  In this article we prove a theorem describing the local topology of the
   boundary of a hyperbolic group in terms of its global topology: the boundary
@@
 
-The goal of this paper is to prove the following theorem, which restricts the
+The goal of this article is to prove the following theorem, which restricts the
 local complexity of the boundary of a hyperbolic group in terms of its global
@@
 
-The paper is structured as follows. In Section~\ref{sec:spheres} we use the
+The article is structured as follows. In Section~\ref{sec:spheres} we use the
 Rips complex of the group $G$ to build a sequence $(K_n)_{n \geq 0}$ of
@@
 sections together to prove Theorem~\ref{thm:main_theorem}, and conclude the
-paper with some questions about strengthenings and generalisations.
+article with some questions about strengthenings and generalisations.
 
@@
 condition that a hyperbolic group might satisfy. (When comparing the constants
-appearing in our definition of the condition with that in the cited paper, note
+appearing in our definition of the condition with that in the cited article, note
 that with our convention that ideal triangles are $\delta$-hyperbolic, Bestvina
@@
 
-It is also natural to ask whether the theorem of this paper generalises to
+It is also natural to ask whether the theorem of this article generalises to
 higher dimensions. The difficulty is in generalising the proof of

### 2020-10-01 paper.tex
Added a discussion of proposition 6.2 to the intro
In the process, prop 6.2 becomes prop 1.3

@@
 \end{theorem}
+
+It is natural to ask whether a similar result holds in which the assumption on
+the topology of point complements in $\boundary G$ is replaced by a similar
+assumption on the whole of the boundary. This question is discussed in
+Section~\ref{sec:conclusion}. Note however that one direction of this question
+can be proved as a corollary of Theorem~\ref{thm:main_theorem}, at least when
+circular boundaries (for which the implication does not hold) are excepted.
+
+\begin{proposition}\label{prop:converse_theorem}
+  If $G$ is a one-ended hyperbolic group such that $\boundary G$ is locally
+  simply connected then $\boundary G$ is either simply connected or
+  homeomorphic to a circle.
+\end{proposition}
 
@@
 Note that the converse question has a positive answer if virtually Fuchsian
-groups (which have boundary homeomorphic to a circle) are excepted:
-
-\begin{proposition}\label{prop:converse_theorem}
-  If $G$ is a one-ended hyperbolic group such that $\boundary G$ is locally
-  simply connected then $\boundary G$ is either simply connected or
-  homeomorphic to a circle.
-\end{proposition}
-
-\begin{proof}
+groups (which have boundary homeomorphic to a circle) are excepted. This is the
+content of Proposition~\ref{prop:converse_theorem}, which we now prove.
+
+\begin{proof}[Proof of Proposition~\ref{prop:converse_theorem}]
   By Theorem~\ref{thm:main_theorem}, all point complements in $\boundary G$ are

### 2020-10-01 paper.tex
Improved some phrasing

@@
 
-It is natural to ask whether a similar result holds in which the assumption on
+It is natural to ask whether a similar result holds in which the condition on
 the topology of point complements in $\boundary G$ is replaced by a similar
-assumption on the whole of the boundary. This question is discussed in
-Section~\ref{sec:conclusion}. Note however that one direction of this question
-can be proved as a corollary of Theorem~\ref{thm:main_theorem}, at least when
-circular boundaries (for which the implication does not hold) are excepted.
+condition on the whole of the boundary. This question is discussed in
+Section~\ref{sec:conclusion}. One direction of this question can be answered as
+a corollary of Theorem~\ref{thm:main_theorem}, as long as circular boundaries
+(for which the implication does not hold) are excepted.
 
